### 2020-03-16 paper/Template_2020_PdfLatex.tex
Initial Commit

% !TeX spellcheck = en_US 
\documentclass{ISMA_USD2020}
%\documentclass{isma2020_Spacing}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%

% The following packages are already loaded in the class definition

	% mfirstuc, inputenc, longtable, tabularx, amsmath, amssymb
	% siunitx, graphicx, epstopdf, pdfpages, bm, relsize,
	% epsfig, epstopdf, eurosym, floatrow, enumitem

% If other packages are required for your manuscript below, load them below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The "hyperref" package may be used in conjunction with PDFLatex %
% to add document information to the generated PDF file. Please,  %
% fill out the same title, author(s) and keywords as on the paper %
% submission form. Note, that the "hypperref" package should be   %
% loaded as the last.                                             %
%                                                                 %
% If you are not using PDFLatex, delete or comment the following  %
% lines. In that case, the conference secretary will add the      %
% document information to your PDF file.                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypersetup{pdftitle  = {Manuscript preparation instructions},
	pdfauthor = {S. Vandemaele, P. Sas},
	pdfkeywords = {ISMA2020, USD2020, template}}

%%%%%%%%%
% Title %
%%%%%%%%%

% Enter below the title of the paper. Use small captions, except for the first letter
\title{Manuscript preparation instructions }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author(s) and Affiliation(s) %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Enter below each author in order of appearance on the paper. 
% Use the format \author[Number of the corresponding affiliation]{Author name (Initial first name. Last name)}

\author[1,2]{S. Vandemaele}
\author[1,2]{P. Sas}
% Extra authors can be added by copying these lines.

% Enter below each affilliation in order of appearance on the paper. 
% Use the format \affil[Number of the affiliation, used in the author command above]{First line affiliation \NewlineAffil 
% 																					Second line affiliation (\NewAffil if required)}
% To ensure a good spacing on the paper, use the command \NewLineAffil at the end of the first line of the affiliation (=institution name)
% Use the command \NewAffil at the end of the affiliation description if multiple affiliations are added
% Extra affiliations can be added by copying these lines.

\affil[1]	{KU Leuven, Department of Mechanical Engineering,\NewLineAffil
			Celestijnenlaan 300, B-3001, Heverlee, Belgium \NewAffil}

\affil[2]	{Member of the ISMA2020 and USD2020 organisation team \NewLineAffil 
			e-mail: \textbf{info@isma-isaac.be} }

% Extra affiliations can be added by copying these lines.

\date{}

\begin{document}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

% Enter your abstract in the command below.

\abstract{This document contains the instructions for the preparation of your manuscript for the ISMA2020 and USD2020 conference in Leuven in September 2020. Template files for \LaTeXe and MS Word are available at the conference website (\textbf{http://www.isma-isaac.be}). For any questions about the manuscript preparation instructions, please contact Simon Vandemaele (\textbf{info@isma-isaac.be}).
A digital version of your manuscript should be submitted online through ConfTool \mbox{\textbf{before June 1, 2020}}.}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beginning of the paper %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

The manuscript will be used as camera-ready artwork and therefore, some basic rules must be followed to ensure quality and standardization of the conference proceedings:
\begin{itemize}
\item be accurate in your typing and thorough in your proof-reading. Your manuscript will be electronically reproduced without any proof-reading or correction,
\item limit the manuscript to \textbf{fifteen (15)} pages, including text, illustrations and references,
\item limit the size of the digital version of your manuscript to \textbf{five megabytes (5 Mb)}.
\end{itemize}
The digital version of your paper will be processed to appear on the on-line conference proceedings. This digital version of your manuscript should be in \textbf{Portable Document Format (PDF)}. Section \ref{s:pdf} discusses various strategies to obtain a PDF file of your manuscript.

\section{Layout of text}

\subsection{General}

The text should fit entirely into a rectangle of \mbox{\textbf{245mm x 166mm}}. Use the following margins on DIN A4-paper \mbox{(297mm x 210mm)}:
\begin{tabbing}
\hspace{4mm} \= $\bullet$ \hspace{1mm} \= top margin \hspace{10mm} \= 30mm,\\
\> $\bullet$ \> bottom margin \> 22mm,\\
\> $\bullet$ \> left margin  \> 22mm,\\
\> $\bullet$ \> right margin \> 22mm.
\end{tabbing}
Use a \textbf{1 column} format. Do \textbf{not} add \textbf{page numbers} nor any other header or footer to the pages.

Use the font Times or Times New Roman 11pt for normal text. The text should be justified. Use single line spacing. Insert a vertical space of 5pt between paragraphs.

Use Helvetica 14pt bold for the first heading, Helvetica 12pt bold for the second heading and Helvetica 11pt bold for the third heading. If Helvetica is not available the Arial font may be used.

Leave one blank line above and one beneath the headings. If a heading falls at the bottom of a page, transfer it to the top of the next page and leave blank space at the bottom.

\subsection{First page}

\subsubsection{Title of the paper}

The title should appear left justified at the top of the first page, in Helvetica 17pt bold. Only capitalize the first letter of the title.

Leave a space of 10mm (28pt) between the title and the authors. Use Times New Roman 11pt \textbf{bold} for the name(s) of the author(s). Type on the next lines (in Times New Roman 11pt) the affiliation of the authors. Use the format as specified in this document: \textless institution/corporation/university\textgreater ~[comma] \textless department/division\textgreater ~[comma] \textless optional lower divisions \textgreater ~[line break] \textless address information (city, state and country)\textgreater. Multiple affiliations should be separated by a blank line. If desired, add \textbf{a single} e-mail address.

\subsubsection{Abstract}

Include a short abstract (max. 10 lines). Use the word `Abstract' as heading in 14pt Helvetica bold, followed directly by the abstract itself. Leave 2 open lines before starting the text or first heading of the paper.

\subsection{Equations and units}

Equations should be centered and must be allowed sufficient space to ensure clarity. Equations must be numbered consecutively, with the numbers parenthesized at the end of the corresponding line: (1), (2) etc. Example:
\begin{equation}
\sin^2 \phi + \cos^2 \phi = 1 \label{e:circle}
\end{equation}

Use the International System of Units (SI) throughout the paper wherever possible. Acceptable alternates are to use SI units followed by other common units in parentheses, or vice versa, i.e. 25.4mm (1in), 1inch (25.4mm).

\subsection{Figures and tables}

Figures and tables must be numbered consecutively. Each figure and table should be centered, should not exceed the text width and should be accompanied by a small (1 or 2 lines), yet clear, caption. The correct place for a caption is at the bottom of a figure (see Figure~\ref{f:circle}), and at the top of a table (see Table~\ref{t:circle}). The most convenient place for figures is at the top of a page. Leave about 2 lines of space between the actual text and figure (including the caption).

\begin{figure}[t]
\begin{center}
\includegraphics[width=80mm]{circle_rgb}
\caption{$x = \cos \phi$ and $y = \sin \phi$ \label{f:circle}}
\end{center}
\end{figure}

\begin{table}[ht]
\centering
\begin{tabular}{c|cc}
$\phi$   & $x = \cos \phi$ & $y = \sin \phi$ \\
\hline
$0$      &    $1$          &    $0$          \\
$\pi/6$  &  $\sqrt{3}/2$   &    $1/2$        \\
$\pi/3$  &    $1/2$        &  $\sqrt{3}/2$   \\
$\pi/2$  &    $0$          &    $1$
\end{tabular}
\caption{Quarter of a circle \label{t:circle}}
\end{table}

Use only those illustrations pertinent to, and cited in the text. Tables and figures may be \textbf{in color}, but keep in mind that some people will print your manuscript in grayscale for off-line reading. Use preferably 2mm size of lettering and lines of 0.2mm thick on the figures.

\subsection{Acknowledgements and references}

Acknowledgements, if any, should be typed at the end of the text before the references.

References should be quoted in the text between square brackets (e.g. \cite{heylen1997modal}) and should be listed in order of appearance according to IEEE style, the default style of this document. Examples of how to reference books \cite{heylen1997modal}, journal papers \cite{sas1995active} and publications
in proceedings \cite{boonen2001modified} are shown at the end of these instructions.

\section{Generation of PDF file \label{s:pdf}}

\subsection{\LaTeX ~users}

Pdf\LaTeX{} can be used for the generation of the digital version of your manuscript. This
program can be obtained at e.g. CTAN (the Comprehensive \TeX{} Archive Network, \textbf{http://www.ctan.org}). Pdf\LaTeX{} directly generates a PDF file from a \LaTeX{} file. Furthermore, it allows the use of the `hyperref' package (\textbf{http://www.ctan.org/pkg/hyperref}), which is required to attach some document information to the PDF file (see the \LaTeX{} template file).

\subsection{MS Word users}

MS Word users can either directly generate PDF files or first print to a Postscript file, which will be converted to PDF in a later stage. If the Adobe Acrobat Distiller or the Adobe PDFWriter is installed, then export your Word document in PDF format. Recent versions of MS Word also allow to directly save in PDF format. Otherwise, first install a Postscript printer and use the option `Print to File' to generate a Postscript file. The Postscript file is converted to PDF as described in the next section. In both cases the conference secretary will attach the document information to the manuscript.

\subsection{Postscript to PDF conversion \label{s:ps2pdf}}

The commercially available program Adobe Acrobat Distiller is capable of converting Postscript files to PDF format. Alternative distiller programs, e.g. {\tt ps2pdf} and {\tt ghostview} (\textbf{http://www.cs.wisc.edu/$\sim$ghost/}), exist. Recall that the paper size must be A4 and therefore the online distiller of \textbf{http://www.ps2pdf.com} is not applicable, since it is only capable of exporting PDF files in US letter size. If you do not succeed in generating a proper digital version of your PDF file, please do not hesitate to contact Simon Vandemaele (\textbf{info@isma-isaac.be}).

\subsection{Fonts in PDF \label{s:pdf-fonts}}

In order to circumvent problems concerning the displaying and printing of certain font types (e.g. Asian fonts), it is recommended to use \textbf{only} the \textbf{Times New Roman} and the \textbf{Helvetica} font in the entire document. This includes figures (e.g. generated by {\sc Matlab}), table, equations, captions, \ldots.

%%%%%%%%%%%%%%%%%%%%
% Acknowledgements %
%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgements}

This PDF file is generated by pdf\LaTeX{} as delivered with the te\TeX{} distribution. The class file `isma2020.cls' and the packages `graphicx' and `hyperref' are explicitly called in the \LaTeX{} file.

%%%%%%%%%%%%%%
% References %
%%%%%%%%%%%%%%

% Include your references below, e.g. by appending a '.bib' file. 
% The style, IEEE, is already pre-defined in the class description.

\bibliography{References}

% If BibTeX is not used, you can enter each bibitem separately using the procedure below

	%\begin{thebibliography}{1}
	%	
	%	\bibitem{heylen}
	%	W. Heylen, S. Lammens, P. Sas,
	%	\textit{Modal Analysis Theory and Testing},
	%	Katholieke Universiteit Leuven, Departement Werktuigkunde, Leuven (1997).
	%	
	%	\bibitem{sas}
	%	P. Sas, C. Bao, F. Augusztinovicz, W. Desmet,
	%	\textit{Active control of sound transmission through a double panel partition},
	%	Journal of Sound and Vibration, Vol. 180, No. 4, Academic Press (1995), pp. 609-625.
	%	
	%	\bibitem{boonen}
	%	R. Boonen, P. Sas,
	%	\textit{Modified Smith Compensation for Feedback Active Noise Control in Ducts},
	%	in \mbox{R. Boone}, editor,
	%	\textit{Proceedings of The 2001 International Congress and Exhibition
	%		on Noise Control Engineering, The Hague, The Netherlands, 2001 August 27-30},
	%	The Hague (2001), pp. 619-624.
	%\end{thebibliography}

%%%%%%%%%%%%%%
% Appendices %
%%%%%%%%%%%%%%

% If none, remove the code below.

\newpage
\appendix

\section{Checklist}

\begin{itemize}
  \item file size:\\
    less than 5 Mb
  \item paper size:\\
    DIN A4-paper \mbox{(297mm x 210mm)}
  \item margins:\\
    top~30mm, bottom~22mm, left~22mm, right~22mm
  \item title:\\
    Helvetica 17pt, bold, left aligned, small captions, only the first letter capital \\
    Correct: \underline{M}anuscript \underline{p}reparation \underline{i}nstructions\\
    Wrong: Manuscript \underline{P}reparation \underline{I}nstructions\\
    Wrong: M\underline{ANUSCRIPT PREPARATION INSTRUCTIONS}
  \item author:\\
    Times New Roman 11pt, bold, left aligned\\
    Format
    \begin{itemize}
    	\item \textless initial(s) first name\textgreater\textless optional: initial(s) middle name\textgreater[space]\textless surname\textgreater
    	\item separate all authors in the list with a [comma].
    \end{itemize}
  \item affiliation:\\
    Times New Roman 11pt, regular, left aligned\\
    Format:\\
    \textless institution/corporation\textgreater[comma]\textless department/division/…\textgreater[comma]\textless optional lab/…\textgreater [enter]\\
    \textless optional address line\textgreater [enter]\\
    \textless optional single email address for the complete paper \textgreater.
  \item abstract\\
    The abstract should not exceed 10 lines, even if the reviewed abstract was longer.
  \item first headings:\\
    Helvetica 14pt, bold, left aligned
  \item second headings:\\
    Helvetica 12pt, bold, left aligned
  \item third headings:\\
    Helvetica 11pt, bold, left aligned
  \item plain text:\\
    Times New Roman 11pt, regular, justified, 5pt whitespace between paragraphs
  \item references:
   	\begin{itemize}
  		\item quotation with brackets [] and chronologically enumerated list with brackets
  		\item IEEE referencing style
	\end{itemize}
  \item equations
  	\begin{itemize}
  		\item font type
  		\item centered and numbered consecutively (1), (2)...
  	\end{itemize}
  \item figures and tables
	\begin{itemize}
		\item font type
		\item centered and numbered consecutively 
		\item clear and concise caption, below each figure and above each table
	\end{itemize}
  \item $\ldots$
\end{itemize}

\newpage

\section{Reference IEEE style}
According to the IEEE reference style, the following information needs to be specified (the name giving corresponds to the BibTeX field names):
\begin{itemize}
  \item book
  	\begin{itemize}
  		\item required: Author, Title, Publisher, Year
  		\item recommended: Address (publisher)
  		\item optional: Edition
  	\end{itemize}
  \item article (journal article)
  	\begin{itemize}
		\item required: Author, Title, Journal (preferred: full name, alternative: official abbreviation), Year
		\item recommended: Volume, Number, Pages
	\end{itemize}  
  \item inproceedings (conference proceedings)
  	\begin{itemize}
		\item required: Author, Title, Booktitle, Year
		\item recommended: Pages
		\item optional: Address
	\end{itemize}
\end{itemize}

\end{document}

### 2020-03-16 paper/paper.tex
Initial Commit

% Created 2020-03-16 lun. 10:50
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\date{}
\title{Vibration control of a rotating Stewart platform}
\begin{document}

\maketitle
\bibliographystyle{IEEEtran}

\abstract{
    Abstract text to be done
}

\section{Introduction}
\label{sec:org8c48899}
\label{sec:introduction}

\section{Theory}
\label{sec:org60f23e3}
\label{sec:theory}

\section{Conclusion}
\label{sec:orgd677659}
\label{sec:conclusion}

\section{Acknowledgment}
\label{sec:orgf333899}

\bibliography{ref}
\end{document}

### 2020-06-10 paper/paper.tex
Add figure to paper
Lot of works on simscape, IFF and DVF

@@
-% Created 2020-03-16 lun. 10:50
+% Created 2020-06-08 lun. 11:40
 % Intended LaTeX compiler: pdflatex
@@
 \title{Vibration control of a rotating Stewart platform}
+\hypersetup{
+ pdfauthor={},
+ pdftitle={Vibration control of a rotating Stewart platform},
+ pdfkeywords={},
+ pdfsubject={},
+ pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
+ pdflang={English}}
 \begin{document}
@@
 \maketitle
-\bibliographystyle{IEEEtran}
 
@@
 \section{Introduction}
-\label{sec:org8c48899}
+\label{sec:org335669b}
 \label{sec:introduction}
@@
 \section{Theory}
-\label{sec:org60f23e3}
+\label{sec:org8b756e7}
 \label{sec:theory}
 
+\subsection{Rotating Positioning Stage}
+\label{sec:orgbf4a596}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/rotating_xy_platform.pdf}
+\caption{\label{fig:rotating_xy_platform}Figure caption}
+\end{figure}
+
+\subsection{Equation of Motion}
+\label{sec:orgaa8880a}
+
+Let's express the kinetic energy \(T\) and the potential energy \(V\) of the mass \(m\):
+\begin{align}
+\label{eq:energy_inertial_frame}
+T & = \frac{1}{2} m \left( \dot{x}^2 + \dot{y}^2 \right) \\
+V & = \frac{1}{2} k \left( x^2 + y^2 \right)
+\end{align}
+
+The Lagrangian is the kinetic energy minus the potential energy.
+\begin{equation}
+\label{eq:lagrangian_inertial_frame}
+L = T-V = \frac{1}{2} m \left( \dot{x}^2 + \dot{y}^2 \right) - \frac{1}{2} k \left( x^2 + y^2 \right)
+\end{equation}
+
+\subsection{Integral Force Feedback}
+\label{sec:org754b644}
+
+\subsection{Direct Velocity Feedback}
+\label{sec:org9cbf82a}
+
 \section{Conclusion}
-\label{sec:orgd677659}
+\label{sec:org8d24de3}
 \label{sec:conclusion}
@@
 \section{Acknowledgment}
-\label{sec:orgf333899}
+\label{sec:orgb252937}
 

### 2020-06-22 paper/paper.tex
Update paper text

--- 2020-03-16 paper/paper.tex
@@
-% Created 2020-03-16 lun. 10:50
+% Created 2020-06-22 lun. 13:27
 % Intended LaTeX compiler: pdflatex
@@
 \affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
+\bibliographystyle{IEEEtran}
 \date{}
-\title{Vibration control of a rotating Stewart platform}
+\title{Active Damping of Rotating Positioning Platforms}
 \begin{document}
@@
 \section{Introduction}
-\label{sec:org8c48899}
+\label{sec:orgd20252d}
 \label{sec:introduction}
+\cite{dehaeze18_sampl_stabil_for_tomog_exper}
 
-\section{Theory}
-\label{sec:org60f23e3}
-\label{sec:theory}
+\section{System Under Study}
+\label{sec:orgacbe1ae}
+\subsection{Rotating Positioning Platform}
+\label{sec:org07e4fc8}
+Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.
+
+\begin{itemize}
+\item \(k\): Actuator's Stiffness [N/m]
+\item \(m\): Payload's mass [kg]
+\item \(\Omega = \dot{\theta}\): rotation speed [rad/s]
+\item \(F_u\), \(F_v\)
+\item \(d_u\), \(d_v\)
+\end{itemize}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/rotating_xy_platform.pdf}
+\caption{\label{fig:rotating_xy_platform}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.5\linewidth]{figs/cedrat_xy25xs.jpg}
+\caption{\label{fig:cedrat_xy25xs}Figure caption}
+\end{figure}
+
+\subsection{Equation of Motion}
+\label{sec:orgac1a52a}
+The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).
+
+Let's express the kinetic energy \(T\) and the potential energy \(V\) of the mass \(m\) (neglecting the rotational energy):
+
+Dissipation function \(R\)
+Kinetic energy \(T\)
+Potential energy \(V\)
+\begin{subequations}
+\label{eq:energy_inertial_frame}
+  \begin{align}
+    T & = \frac{1}{2} m \left( \left( \dot{u} - \Omega v \right)^2 + \left( \dot{v} + \Omega u \right)^2 \right) \\
+    R & = \frac{1}{2} c \left( \dot{u}^2 + \dot{v}^2 \right) \\
+    V & = \frac{1}{2} k \left( u^2 + v^2 \right)
+  \end{align}
+\end{subequations}
+
+The Lagrangian is the kinetic energy minus the potential energy:
+\begin{equation}
+\label{eq:lagrangian_inertial_frame}
+L = T - V
+\end{equation}
+
+From the Lagrange's equations of the second kind \eqref{eq:lagrange_second_kind}, the equation of motion \eqref{eq:eom_mixed} is obtained (\(q_1 = u\), \(q_2 = v\)).
+\begin{equation}
+  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
+\end{equation}
+
+\begin{equation}
+  \frac{d}{dt} \left( \frac{\partial T}{\partial \dot{q}_i} \right) - \frac{\partial T}{\partial q_i} + \frac{\partial R}{\partial \dot{q}_i} - \frac{\partial V}{\partial q_i} = Q_i
+\end{equation}
+
+with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(F_u\) and \(F_v\)).
+
+\begin{subequations}
+  \begin{align}
+    m \ddot{u} + c \dot{u} + ( k - m \Omega ) u &= F_u + 2 m \Omega \dot{v} \\
+    m \ddot{v} + c \dot{v} + ( k \underbrace{-\,m \Omega}_{\text{Centrif.}} ) v &= F_v \underbrace{-\,2 m \Omega \dot{u}}_{\text{Coriolis}}
+  \end{align}
+\end{subequations}
+
+\begin{subequations}
+  \begin{align}
+    u &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v \\
+    v &= \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v
+  \end{align}
+\end{subequations}
+
+\begin{equation}
+\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
+\bm{G}_d
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+Where \(\bm{G}_d\) is a \(2 \times 2\) transfer function matrix.
+
+\begin{equation}
+\bm{G}_d = \frac{1}{k} \frac{1}{G_{dp}}
+\begin{bmatrix}
+   G_{dz} & G_{dc} \\
+  -G_{dc} & G_{dz}
+\end{bmatrix}
+\end{equation}
+With:
+\begin{subequations}
+  \begin{align}
+    G_{dp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
+    G_{dz} &= \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
+    G_{dc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
+  \end{align}
+\end{subequations}
+
+\begin{itemize}
+\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Natural frequency of the mass-spring system in \(\si{\radian/\s}\)
+\item \(\xi\) damping ratio
+\end{itemize}
+
+\begin{equation}
+\label{eq:lagrange_second_kind}
+  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_j} \right) = \frac{\partial L}{\partial q_j}
+\end{equation}
+
+\begin{subequations}
+\label{eq:eom_mixed}
+  \begin{align}
+    m\ddot{x} + kx = F_u \cos{\theta} - F_v \sin{\theta}\\
+    m\ddot{y} + ky = F_u \sin{\theta} + F_v \cos{\theta}
+  \end{align}
+\end{subequations}
+
+Performing the change coordinates from \((x, y)\) to \((d_x, d_y, \theta)\):
+\begin{subequations}
+  \begin{align}
+    x & = d_u \cos{\theta} - d_v \sin{\theta}\\
+    y & = d_u \sin{\theta} + d_v \cos{\theta}
+  \end{align}
+\end{subequations}
+
+Gives
+\begin{subequations}
+\label{eq:oem_coupled}
+  \begin{align}
+    m \ddot{d_u} + (k - m\dot{\theta}^2) d_u &= F_u + 2 m\dot{d_v}\dot{\theta} + m d_v\ddot{\theta} \label{eq:du_coupled} \\
+    m \ddot{d_v} + (k \underbrace{-\ m\dot{\theta}^2}_{\text{Centrif.}}) d_v &= F_v \underbrace{-\ 2 m\dot{d_u}\dot{\theta}}_{\text{Coriolis}} \underbrace{-\ m d_u\ddot{\theta}}_{\text{Euler}} \label{eq:dv_coupled}
+  \end{align}
+\end{subequations}
+
+We obtain two differential equations that are coupled through:
+\begin{itemize}
+\item \textbf{Euler forces}: \(m d_v \ddot{\theta}\)
+\item \textbf{Coriolis forces}: \(2 m \dot{d_v} \dot{\theta}\)
+\end{itemize}
+
+Without the coupling terms, each equation is the equation of a one degree of freedom mass-spring system with mass \(m\) and stiffness \(k- m\dot{\theta}^2\).
+Thus, the term \(- m\dot{\theta}^2\) acts like a negative stiffness (due to \textbf{centrifugal forces}).
+
+\subsection{Constant Rotating Speed}
+\label{sec:org47aaeee}
+To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).
+
+\begin{equation}
+\label{eq:coupledplant}
+\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
+\frac{1}{(m s^2 + (k - m{\omega_0}^2))^2 + (2 m {\omega_0} s)^2}
+\begin{bmatrix}
+  ms^2 + (k-m{\omega_0}^2) & 2 m \omega_0 s \\
+  -2 m \omega_0 s          & ms^2 + (k-m{\omega_0}^2) \\
+\end{bmatrix}
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+\label{eq:coupled_plant}
+\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
+\frac{\frac{1}{k}}{\left( \frac{s^2}{{\omega_0}^2} + (1 - \frac{{\Omega}^2}{{\omega_0}^2}) \right)^2 + \left( 2 \frac{{\Omega} s}{{\omega_0}^2} \right)^2}
+\begin{bmatrix}
+  \frac{s^2}{{\omega_0}^2} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} & 2 \frac{\Omega s}{{\omega_0}^2} \\
+  -2 \frac{\Omega s}{{\omega_0}^2}          & \frac{s^2}{{\omega_0}^2} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
+\end{bmatrix}
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+When the rotation speed is null, the coupling terms are equal to zero and the diagonal terms corresponds to one degree of freedom mass spring system.
+\begin{equation}
+\label{eq:coupled_plant_no_rot}
+\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
+\frac{\frac{1}{k}}{\frac{s^2}{{\omega_0}^2} + 1}
+\begin{bmatrix}
+  1 & 0 \\
+  0 & 1
+\end{bmatrix}
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+When the rotation speed in not null, the resonance frequency is duplicated into two pairs of complex conjugate poles.
+As the rotation speed increases, one of the two resonant frequency goes to lower frequencies as the other one goes to higher frequencies (Figure \ref{fig:campbell_diagram}).
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/campbell_diagram.pdf}
+\caption{\label{fig:campbell_diagram}Campbell Diagram}
+\end{figure}
+
+The magnitude of the coupling terms are increasing with the rotation speed.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/plant_compare_rotating_speed.pdf}
+\caption{\label{fig:plant_compare_rotating_speed}Caption}
+\end{figure}
+
+\section{Integral Force Feedback}
+\label{sec:org78c2eab}
+\subsection{Control Schematic}
+\label{sec:org6a00238}
+
+\subsection{Equations}
+\label{sec:org5480f1b}
+
+\subsection{Plant Dynamics}
+\label{sec:orgbb0952e}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
+\caption{\label{fig:root_locus_pure_iff}Figure caption}
+\end{figure}
+
+\subsection{Physical Interpretation}
+\label{sec:orgdb25e2c}
+
+\section{Integral Force Feedback with Low Pass Filters}
+\label{sec:org2985d35}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
+\caption{\label{fig:loop_gain_modified_iff}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/root_locus_modified_iff_bis.pdf}
+\caption{\label{fig:root_locus_modified_iff}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
+\caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
+\end{figure}
+
+\section{Integral Force Feedback with Parallel Springs}
+\label{sec:orga4142a5}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/rotating_xy_platform_springs.pdf}
+\caption{\label{fig:rotating_xy_platform_springs}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
+\caption{\label{fig:plant_iff_kp}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
+\caption{\label{fig:root_locus_iff_kps}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/root_locus_iff_kp_bis.pdf}
+\caption{\label{fig:root_locus_iff_kp_bis}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/root_locus_opt_gain_iff_kp.pdf}
+\caption{\label{fig:root_locus_opt_gain_iff_kp}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
+\caption{\label{fig:plant_iff_compare_rotating_speed}Figure caption}
+\end{figure}
+
+\section{Direct Velocity Feedback}
+\label{sec:org6a1be4f}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/root_locus_dvf.pdf}
+\caption{\label{fig:root_locus_dvf}Figure caption}
+\end{figure}
+
+\section{Comparison of the Proposed Active Damping Techniques}
+\label{sec:orga9658c0}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_root_locus.pdf}
+\caption{\label{fig:comp_root_locus}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_compliance.pdf}
+\caption{\label{fig:comp_compliance}Figure caption}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
+\caption{\label{fig:comp_transmissibility}Figure caption}
+\end{figure}
 
 \section{Conclusion}
-\label{sec:orgd677659}
+\label{sec:orgcdf948f}
 \label{sec:conclusion}
 
-\section{Acknowledgment}
-\label{sec:orgf333899}
+\section*{Acknowledgment}
+\label{sec:org6c21e13}
 
-\bibliography{ref}
+\bibliography{ref.bib}
 \end{document}

### 2020-06-23 matlab/matlab/s1_system_description.m
Add tangled matlab scripts

@@ -1,0 +1,219 @@
+%% Clear Workspace and Close figures
+clear; close all; clc;
+
+%% Intialize Laplace variable
+s = zpk('s');
+
+% Numerical Values
+% Let's define initial values for the model.
+
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+% Campbell Diagram
+% The Campbell Diagram displays the evolution of the real and imaginary parts of the system as a function of the rotating speed.
+
+% It is shown in Figure [[fig:campbell_diagram]], and one can see that the system becomes unstable for $\Omega > \omega_0$ (the real part of one of the poles becomes positive).
+
+
+Ws = linspace(0, 2, 51); % Vector of considered rotation speed [rad/s]
+
+p_ws = zeros(4, length(Ws));
+
+for W_i = 1:length(Ws)
+    W = Ws(W_i);
+
+    pole_G = pole(1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2));
+    [~, i_sort] = sort(imag(pole_G));
+    p_ws(:, W_i) = pole_G(i_sort);
+end
+
+clear pole_G;
+
+figure;
+
+ax1 = subplot(1,2,1);
+hold on;
+for p_i = 1:size(p_ws, 1)
+    plot(Ws, real(p_ws(p_i, :)), 'k-')
+end
+plot(Ws, zeros(size(Ws)), 'k--')
+hold off;
+xlabel('Rotation Frequency [rad/s]'); ylabel('Real Part');
+
+ax2 = subplot(1,2,2);
+hold on;
+for p_i = 1:size(p_ws, 1)
+    plot(Ws,  imag(p_ws(p_i, :)), 'k-')
+    plot(Ws, -imag(p_ws(p_i, :)), 'k-')
+end
+hold off;
+xlabel('Rotation Frequency [rad/s]'); ylabel('Imaginary Part');
+
+% Simscape Model
+% Define the rotating speed for the Simscape Model.
+
[…]

### 2020-06-23 matlab/matlab/s2_iff_pure_int.m

@@ -1,0 +1,193 @@
+%% Clear Workspace and Close figures
+clear; close all; clc;
+
+%% Intialize Laplace variable
+s = zpk('s');
+
+% Plant Parameters
+% Let's define initial values for the model.
+
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+kp = 0; % [N/m]
+cp = 0; % [N/(m/s)]
+
+% Simscape Model
+% The rotation speed is set to $\Omega = 0.1 \omega_0$.
+
+W = 0.1*w0; % [rad/s]
+
+Kiff = tf(zeros(2));
+Kdvf = tf(zeros(2));
+
+open('rotating_frame.slx');
+
+
+
+% And the transfer function from $[F_u, F_v]$ to $[f_u, f_v]$ is identified using the Simscape model.
+
+%% Name of the Simulink File
+mdl = 'rotating_frame';
+
+%% Input/Output definition
+clear io; io_i = 1;
+io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
+io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
+
+Giff = linearize(mdl, io, 0);
+
+%% Input/Output definition
+Giff.InputName  = {'Fu', 'Fv'};
+Giff.OutputName = {'fu', 'fv'};
+
+% Comparison of the Analytical Model and the Simscape Model
+% The same transfer function from $[F_u, F_v]$ to $[f_u, f_v]$ is written down from the analytical model.
+
+Giff_th = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
+          [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
[…]

### 2020-06-23 matlab/matlab/s3_iff_hpf.m

@@ -1,0 +1,251 @@
+%% Clear Workspace and Close figures
+clear; close all; clc;
+
+%% Intialize Laplace variable
+s = zpk('s');
+
+% Plant Parameters
+% Let's define initial values for the model.
+
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+kp = 0; % [N/m]
+cp = 0; % [N/(m/s)]
+
+% Modified Integral Force Feedback Controller
+% Let's modify the initial Integral Force Feedback Controller ; instead of using pure integrators, pseudo integrators (i.e. low pass filters) are used:
+% \begin{equation}
+%   K_{\text{IFF}}(s) = g\frac{1}{\omega_i + s} \begin{bmatrix}
+%   1 & 0 \\
+%   0 & 1
+% \end{bmatrix}
+% \end{equation}
+% where $\omega_i$ characterize down to which frequency the signal is integrated.
+
+% Let's arbitrary choose the following control parameters:
+
+g = 2;
+wi = 0.1*w0;
+
+Kiff = (g/(wi+s))*eye(2);
+
+
+
+% And the following rotating speed.
+
+W = 0.1*w0;
+
+Giff = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
+        [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
+         (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2];
+
+
+
+% The obtained Loop Gain is shown in Figure [[fig:loop_gain_modified_iff]].
+
+freqs = logspace(-2, 1, 1000);
+
+figure;
+
+ax1 = subplot(2, 1, 1);
+hold on;
[…]

### 2020-06-23 matlab/matlab/s4_iff_kp.m

@@ -1,0 +1,389 @@
+%% Clear Workspace and Close figures
+clear; close all; clc;
+
+%% Intialize Laplace variable
+s = zpk('s');
+
+% Plant Parameters
+% Let's define initial values for the model.
+
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+kp = 0; % [N/m]
+cp = 0; % [N/(m/s)]
+
+% Comparison of the Analytical Model and the Simscape Model
+% The same transfer function from $[F_u, F_v]$ to $[f_u, f_v]$ is written down from the analytical model.
+
+W = 0.1*w0; % [rad/s]
+
+kp = 1.5*m*W^2;
+cp = 0;
+
+Kiff = tf(zeros(2));
+Kdvf = tf(zeros(2));
+
+open('rotating_frame.slx');
+
+%% Name of the Simulink File
+mdl = 'rotating_frame';
+
+%% Input/Output definition
+clear io; io_i = 1;
+io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
+io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
+
+Giff = linearize(mdl, io, 0);
+
+%% Input/Output definition
+Giff.InputName  = {'Fu', 'Fv'};
+Giff.OutputName = {'fu', 'fv'};
+
+w0p = sqrt((k + kp)/m);
+xip = c/(2*sqrt((k+kp)*m));
+
+Giff_th = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
+                   (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
[…]

### 2020-06-23 matlab/matlab/s5_dvf.m

@@ -1,0 +1,159 @@
+%% Clear Workspace and Close figures
+clear; close all; clc;
+
+%% Intialize Laplace variable
+s = zpk('s');
+
+% Plant Parameters
+% Let's define initial values for the model.
+
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+kp = 0; % [N/m]
+cp = 0; % [N/(m/s)]
+
+% Comparison of the Analytical Model and the Simscape Model
+% The rotating speed is set to $\Omega = 0.1 \omega_0$.
+
+W = 0.1*w0;
+
+Kiff = tf(zeros(2));
+Kdvf = tf(zeros(2));
+
+open('rotating_frame.slx');
+
+
+
+% And the transfer function from $[F_u, F_v]$ to $[v_u, v_v]$ is identified using the Simscape model.
+
+%% Name of the Simulink File
+mdl = 'rotating_frame';
+
+%% Input/Output definition
+clear io; io_i = 1;
+io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
+io(io_i) = linio([mdl, '/G'], 1, 'openoutput'); io_i = io_i + 1;
+
+Gdvf = linearize(mdl, io, 0);
+
+%% Input/Output definition
+Gdvf.InputName  = {'Fu', 'Fv'};
+Gdvf.OutputName = {'Vu', 'Vv'};
+
+
+
+% The same transfer function from $[F_u, F_v]$ to $[v_u, v_v]$ is written down from the analytical model.
+
+Gdvf_th = (s/k)/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
+          [(s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2), 2*W*s/(w0^2) ; ...
+           -2*W*s/(w0^2), (s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)];
+
+Gdvf_th.InputName  = {'Fu', 'Fv'};
+Gdvf_th.OutputName = {'vu', 'vv'};
+
+
+
[…]

### 2020-06-23 matlab/matlab/s6_act_damp_comparison.m

@@ -1,0 +1,364 @@
+%% Clear Workspace and Close figures
+clear; close all; clc;
+
+%% Intialize Laplace variable
+s = zpk('s');
+
+% Plant Parameters
+% Let's define initial values for the model.
+
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+kp = 0; % [N/m]
+cp = 0; % [N/(m/s)]
+
+
+
+% The rotating speed is set to $\Omega = 0.1 \omega_0$.
+
+W = 0.1*w0;
+
+% Root Locus
+% IFF with High Pass Filter
+
+wi = 0.1*w0; % [rad/s]
+
+Giff = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
+        [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
+         (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2];
+
+
+
+% IFF With parallel Stiffness
+
+kp = 5*m*W^2;
+k = k - kp;
+
+w0p = sqrt((k + kp)/m);
+xip = c/(2*sqrt((k+kp)*m));
+
+Giff_kp = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
+                   (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
[…]

### 2020-06-23 paper/paper.tex
Update paper bibliography

@@
-% Created 2020-06-22 lun. 13:27
+% Created 2020-06-22 lun. 17:38
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:orgd20252d}
+\label{sec:org67e0a4e}
 \label{sec:introduction}
@@
 \section{System Under Study}
-\label{sec:orgacbe1ae}
+\label{sec:org85bcde2}
 \subsection{Rotating Positioning Platform}
-\label{sec:org07e4fc8}
+\label{sec:org4959a5e}
 Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.
@@
 \centering
-\includegraphics[scale=1]{figs/rotating_xy_platform.pdf}
+\includegraphics[scale=1]{figs/system.pdf}
 \caption{\label{fig:rotating_xy_platform}Figure caption}
@@
 \subsection{Equation of Motion}
-\label{sec:orgac1a52a}
+\label{sec:orgdb109d9}
 The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).
@@
 \begin{subequations}
-\label{eq:energy_inertial_frame}
   \begin{align}
@@
 \begin{equation}
-\label{eq:lagrangian_inertial_frame}
 L = T - V
@@
 \end{equation}
-
-\begin{equation}
-  \frac{d}{dt} \left( \frac{\partial T}{\partial \dot{q}_i} \right) - \frac{\partial T}{\partial q_i} + \frac{\partial R}{\partial \dot{q}_i} - \frac{\partial V}{\partial q_i} = Q_i
-\end{equation}
-
-with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(F_u\) and \(F_v\)).
+with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).
 
@@
 \end{subequations}
+
+\begin{itemize}
+\item Coriolis Forces: coupling
+\item Centrifugal forces: negative stiffness
+\end{itemize}
+
+Without the coupling terms, each equation is the equation of a one degree of freedom mass-spring system with mass \(m\) and stiffness \(k- m\dot{\theta}^2\).
+Thus, the term \(- m\dot{\theta}^2\) acts like a negative stiffness (due to \textbf{centrifugal forces}).
+
+\subsection{Transfer Functions in the Laplace domain}
+\label{sec:orgfcd3def}
 
@@
 
-\begin{equation}
-\label{eq:lagrange_second_kind}
-  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_j} \right) = \frac{\partial L}{\partial q_j}
-\end{equation}
-
-\begin{subequations}
-\label{eq:eom_mixed}
-  \begin{align}
-    m\ddot{x} + kx = F_u \cos{\theta} - F_v \sin{\theta}\\
-    m\ddot{y} + ky = F_u \sin{\theta} + F_v \cos{\theta}
-  \end{align}
-\end{subequations}
-
-Performing the change coordinates from \((x, y)\) to \((d_x, d_y, \theta)\):
-\begin{subequations}
-  \begin{align}
-    x & = d_u \cos{\theta} - d_v \sin{\theta}\\
-    y & = d_u \sin{\theta} + d_v \cos{\theta}
-  \end{align}
-\end{subequations}
-
-Gives
-\begin{subequations}
-\label{eq:oem_coupled}
-  \begin{align}
-    m \ddot{d_u} + (k - m\dot{\theta}^2) d_u &= F_u + 2 m\dot{d_v}\dot{\theta} + m d_v\ddot{\theta} \label{eq:du_coupled} \\
-    m \ddot{d_v} + (k \underbrace{-\ m\dot{\theta}^2}_{\text{Centrif.}}) d_v &= F_v \underbrace{-\ 2 m\dot{d_u}\dot{\theta}}_{\text{Coriolis}} \underbrace{-\ m d_u\ddot{\theta}}_{\text{Euler}} \label{eq:dv_coupled}
-  \end{align}
-\end{subequations}
-
-We obtain two differential equations that are coupled through:
-\begin{itemize}
-\item \textbf{Euler forces}: \(m d_v \ddot{\theta}\)
-\item \textbf{Coriolis forces}: \(2 m \dot{d_v} \dot{\theta}\)
-\end{itemize}
-
-Without the coupling terms, each equation is the equation of a one degree of freedom mass-spring system with mass \(m\) and stiffness \(k- m\dot{\theta}^2\).
-Thus, the term \(- m\dot{\theta}^2\) acts like a negative stiffness (due to \textbf{centrifugal forces}).
-
 \subsection{Constant Rotating Speed}
-\label{sec:org47aaeee}
+\label{sec:org81c7074}
 To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).
@@
 \section{Integral Force Feedback}
-\label{sec:org78c2eab}
+\label{sec:orgc6c1b99}
 \subsection{Control Schematic}
-\label{sec:org6a00238}
+\label{sec:orgb93b297}
+
+Force Sensors are added in series with the actuators as shown in Figure \ref{fig:system_iff}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/system_iff.pdf}
+\caption{\label{fig:system_iff}System with Force Sensors in Series with the Actuators. Decentralized Integral Force Feedback is used}
+\end{figure}
 
 \subsection{Equations}
-\label{sec:org5480f1b}
+\label{sec:org4072ea4}
+The sensed forces are equal to:
+\begin{equation}
+\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
+\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
+\begin{bmatrix} d_u \\ d_v \end{bmatrix}
+\end{equation}
+
+Which then gives:
+\begin{equation}
+\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
+\bm{G}_{f}
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
+\frac{1}{G_{fp}}
+\begin{bmatrix}
+  G_{fz} & -G_{fc} \\
+  G_{fc} &  G_{fz}
+\end{bmatrix}
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{align}
+  G_{fp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
+  G_{fz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
+  G_{fc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)
+\end{align}
 
 \subsection{Plant Dynamics}
-\label{sec:orgbb0952e}
+\label{sec:org0250ac0}
 
@@
 \includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
-\caption{\label{fig:root_locus_pure_iff}Figure caption}
+\caption{\label{fig:root_locus_pure_iff}Root Locus}
 \end{figure}
@@
 \subsection{Physical Interpretation}
-\label{sec:orgdb25e2c}
+\label{sec:orgb2d79d2}
 
-\section{Integral Force Feedback with Low Pass Filters}
-\label{sec:org2985d35}
+At low frequency, the gain is very large and thus no force is transmitted between the payload and the rotating stage.
+This means that at low frequency, the system is decoupled (the force sensor removed) and thus the system is unstable.
+
+\section{Integral Force Feedback with High Pass Filters}
+\label{sec:orgabf7a6a}
+\subsection{Modification of the Control Low}
+\label{sec:org4766bd6}
+
+\subsection{Close Loop Analysis}
+\label{sec:org4c639fd}
 
@@
 
+\subsection{Optimal Cut-Off Frequency}
+\label{sec:orge829a45}
+
 \begin{figure}[htbp]
 \centering
-\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
+\includegraphics[scale=1]{figs/root_locus_wi_modified_iff_bis.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
+\caption{\label{fig:mod_iff_damping_wi}Figure caption}
+\end{figure}
+
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orga4142a5}
+\label{sec:orgd96ea25}
 
@@
 \section{Direct Velocity Feedback}
-\label{sec:org6a1be4f}
+\label{sec:org027d051}
 
@@
 \section{Comparison of the Proposed Active Damping Techniques}
-\label{sec:orga9658c0}
+\label{sec:org1eaa959}
 
@@
 \section{Conclusion}
-\label{sec:orgcdf948f}
+\label{sec:org1b2b4ae}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org6c21e13}
+\label{sec:org2ae16a5}
 

### 2020-06-23 paper/paper.tex
Update Figures, paper compiling fine

@@
-% Created 2020-06-22 lun. 17:38
+% Created 2020-06-23 mar. 19:34
 % Intended LaTeX compiler: pdflatex
@@
 \bibliographystyle{IEEEtran}
+\usepackage{tikz}
+\usetikzlibrary{shapes.misc}
 \date{}
 \title{Active Damping of Rotating Positioning Platforms}
+\hypersetup{
+ pdfauthor={},
+ pdftitle={Active Damping of Rotating Positioning Platforms},
+ pdfkeywords={},
+ pdfsubject={},
+ pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
+ pdflang={English}}
 \begin{document}
@@
 \section{Introduction}
-\label{sec:org67e0a4e}
+\label{sec:org977317c}
 \label{sec:introduction}
+Controller Poles are shown by black crosses (
+\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
+).
 \cite{dehaeze18_sampl_stabil_for_tomog_exper}
@@
 \section{System Under Study}
-\label{sec:org85bcde2}
+\label{sec:org042e800}
 \subsection{Rotating Positioning Platform}
-\label{sec:org4959a5e}
+\label{sec:org489e4b9}
 Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.
@@
 \subsection{Equation of Motion}
-\label{sec:orgdb109d9}
+\label{sec:orgb1836d5}
 The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).
@@
 
-From the Lagrange's equations of the second kind \eqref{eq:lagrange_second_kind}, the equation of motion \eqref{eq:eom_mixed} is obtained (\(q_1 = u\), \(q_2 = v\)).
+From the Lagrange's equations of the second kind, the equation of motion is obtained (\(q_1 = u\), \(q_2 = v\)).
 \begin{equation}
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:orgfcd3def}
+\label{sec:orgb1002ed}
 
@@
 \subsection{Constant Rotating Speed}
-\label{sec:org81c7074}
+\label{sec:orga4faf60}
 To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).
@@
 \section{Integral Force Feedback}
-\label{sec:orgc6c1b99}
+\label{sec:orgaf500b0}
 \subsection{Control Schematic}
-\label{sec:orgb93b297}
+\label{sec:orgbd9f859}
 
@@
 \subsection{Equations}
-\label{sec:org4072ea4}
+\label{sec:org48206d5}
 The sensed forces are equal to:
@@
 \subsection{Plant Dynamics}
-\label{sec:org0250ac0}
+\label{sec:orgec8431d}
 
@@
 \subsection{Physical Interpretation}
-\label{sec:orgb2d79d2}
+\label{sec:org159680e}
 
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:orgabf7a6a}
+\label{sec:org694707d}
 \subsection{Modification of the Control Low}
-\label{sec:org4766bd6}
+\label{sec:org931fb10}
 
 \subsection{Close Loop Analysis}
-\label{sec:org4c639fd}
+\label{sec:org9de0aa7}
 
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_modified_iff_bis.pdf}
+\includegraphics[scale=1]{figs/root_locus_modified_iff_ter.pdf}
 \caption{\label{fig:root_locus_modified_iff}Figure caption}
@@
 \subsection{Optimal Cut-Off Frequency}
-\label{sec:orge829a45}
+\label{sec:org9808de1}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orgd96ea25}
+\label{sec:orgd4915d5}
 
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_iff_kp_bis.pdf}
+\includegraphics[scale=1]{figs/root_locus_iff_kp_ter.pdf}
 \caption{\label{fig:root_locus_iff_kp_bis}Figure caption}
@@
 \section{Direct Velocity Feedback}
-\label{sec:org027d051}
+\label{sec:orgb0a5870}
 
@@
 \section{Comparison of the Proposed Active Damping Techniques}
-\label{sec:org1eaa959}
+\label{sec:org6097c1d}
 
@@
 \section{Conclusion}
-\label{sec:org1b2b4ae}
+\label{sec:org1624a6b}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org2ae16a5}
+\label{sec:org1b29790}
 

### 2020-06-24 paper/paper.tex
Add figure to show the opt gain on the root locus

@@
-% Created 2020-06-23 mar. 19:34
+% Created 2020-06-24 mer. 15:36
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{xcolor, import, hyperref}
+\usepackage{subcaption}
 \usepackage[USenglish, english]{babel}
@@
 \section{Introduction}
-\label{sec:org977317c}
+\label{sec:orgbec19fa}
 \label{sec:introduction}
@@
 ).
-\cite{dehaeze18_sampl_stabil_for_tomog_exper}
 
-\section{System Under Study}
-\label{sec:org042e800}
-\subsection{Rotating Positioning Platform}
-\label{sec:org489e4b9}
-Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.
+\section{Dynamics of Rotating Positioning Platforms}
+\label{sec:org81be86a}
+\subsection{Studied Rotating Positioning Platform}
+\label{sec:orgf8fad9b}
+Consider the rotating X-Y stage of Figure \ref{fig:system}.
 
@@
 \includegraphics[scale=1]{figs/system.pdf}
-\caption{\label{fig:rotating_xy_platform}Figure caption}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\linewidth]{figs/cedrat_xy25xs.jpg}
-\caption{\label{fig:cedrat_xy25xs}Figure caption}
+\caption{\label{fig:system}Figure caption}
 \end{figure}
@@
 \subsection{Equation of Motion}
-\label{sec:orgb1836d5}
+\label{sec:org926ba54}
 The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:orgb1002ed}
+\label{sec:org298e237}
 
@@
 \subsection{Constant Rotating Speed}
-\label{sec:orga4faf60}
+\label{sec:org8d2eda6}
 To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).
@@
 \begin{figure}[htbp]
+\begin{subfigure}[c]{0.4\linewidth}
+\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
+\caption{\label{fig:campbell_diagram_real} Real Part}
+\end{subfigure}
+\begin{subfigure}[c]{0.4\linewidth}
+\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
+\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
+\end{subfigure}
+\caption{\label{fig:campbell_diagram}Campbell Diagram}
 \centering
-\includegraphics[scale=1]{figs/campbell_diagram.pdf}
-\caption{\label{fig:campbell_diagram}Campbell Diagram}
 \end{figure}
@@
 \begin{figure}[htbp]
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
+\end{subfigure}
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(d_u/F_v\)}
+\end{subfigure}
+\caption{\label{fig:plant_compare_rotating_speed}Dynamics}
 \centering
-\includegraphics[scale=1]{figs/plant_compare_rotating_speed.pdf}
-\caption{\label{fig:plant_compare_rotating_speed}Caption}
 \end{figure}
@@
 \section{Integral Force Feedback}
-\label{sec:orgaf500b0}
+\label{sec:org2e8c85f}
 \subsection{Control Schematic}
-\label{sec:orgbd9f859}
+\label{sec:org50b6359}
 
@@
 \subsection{Equations}
-\label{sec:org48206d5}
+\label{sec:org99c13a7}
 The sensed forces are equal to:
@@
 \subsection{Plant Dynamics}
-\label{sec:orgec8431d}
+\label{sec:org1e476e3}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
+\caption{\label{fig:plant_iff_compare_rotating_speed}Figure caption}
+\end{figure}
+
+\subsection{Integral Force Feedback}
+\label{sec:orga5d8887}
 
@@
 
-\subsection{Physical Interpretation}
-\label{sec:org159680e}
-
 At low frequency, the gain is very large and thus no force is transmitted between the payload and the rotating stage.
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org694707d}
+\label{sec:org569b7db}
 \subsection{Modification of the Control Low}
-\label{sec:org931fb10}
+\label{sec:org4d0c1ca}
 
-\subsection{Close Loop Analysis}
-\label{sec:org9de0aa7}
+\subsection{Feedback Analysis}
+\label{sec:org1f34d25}
 
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_modified_iff_ter.pdf}
+\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
 \caption{\label{fig:root_locus_modified_iff}Figure caption}
@@
 \subsection{Optimal Cut-Off Frequency}
-\label{sec:org9808de1}
+\label{sec:org04a5aa4}
 
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_wi_modified_iff_bis.pdf}
+\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orgd4915d5}
+\label{sec:org03c54a4}
+\subsection{Stiffness in Parallel with the Force Sensor}
+\label{sec:orgc2d9221}
 
@@
 \centering
-\includegraphics[scale=1]{figs/rotating_xy_platform_springs.pdf}
-\caption{\label{fig:rotating_xy_platform_springs}Figure caption}
+\includegraphics[scale=1]{figs/system_parallel_springs.pdf}
+\caption{\label{fig:system_parallel_springs}Figure caption}
 \end{figure}
+
+\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
+\label{sec:org8097ba5}
 
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
-\caption{\label{fig:root_locus_iff_kps}Figure caption}
+\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
+\caption{\label{fig:root_locus_iff_kp}Figure caption}
 \end{figure}
+
+\subsection{Optimal Parallel Stiffness}
+\label{sec:org1f2e167}
 
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_iff_kp_ter.pdf}
-\caption{\label{fig:root_locus_iff_kp_bis}Figure caption}
+\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
+\caption{\label{fig:root_locus_iff_kps}Figure caption}
 \end{figure}
@@
 
+\section{Direct Velocity Feedback}
+\label{sec:orgda2e325}
+\subsection{Control Schematic}
+\label{sec:org0e84009}
+
 \begin{figure}[htbp]
 \centering
-\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
-\caption{\label{fig:plant_iff_compare_rotating_speed}Figure caption}
+\includegraphics[scale=1]{figs/system_dvf.pdf}
+\caption{\label{fig:system_dvf}Figure caption}
 \end{figure}
 
-\section{Direct Velocity Feedback}
-\label{sec:orgb0a5870}
+\subsection{Equations}
+\label{sec:org7cc244c}
+
+\subsection{Relative Direct Velocity Feedback}
+\label{sec:org668d842}
 
@@
 
-\section{Comparison of the Proposed Active Damping Techniques}
-\label{sec:org6097c1d}
+\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
+\label{sec:orgade0126}
+**
+
+**
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_compliance.pdf}
-\caption{\label{fig:comp_compliance}Figure caption}
-\end{figure}
+\subsection{Transmissibility and Compliance}
+\label{sec:org59b0db2}
 
 \begin{figure}[htbp]
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
+\caption{\label{fig:comp_compliance} Transmissibility}
+\end{subfigure}
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
+\caption{\label{fig:comp_transmissibility} Compliance}
+\end{subfigure}
+\caption{\label{fig:comp_active_damping}Comparison of the three proposed Active Damping Techniques}
 \centering
-\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
-\caption{\label{fig:comp_transmissibility}Figure caption}
 \end{figure}
@@
 \section{Conclusion}
-\label{sec:org1624a6b}
+\label{sec:org4b70853}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org1b29790}
+\label{sec:org7708a14}
 

### 2020-06-24 paper/paper.tex
Add captions

@@
-% Created 2020-06-24 mer. 15:36
+% Created 2020-06-24 mer. 16:28
 % Intended LaTeX compiler: pdflatex
@@
 \title{Active Damping of Rotating Positioning Platforms}
-\hypersetup{
- pdfauthor={},
- pdftitle={Active Damping of Rotating Positioning Platforms},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
- pdflang={English}}
 \begin{document}
@@
 \section{Introduction}
-\label{sec:orgbec19fa}
+\label{sec:org3cbd2ff}
 \label{sec:introduction}
@@
 ).
+This paper has been published
+The Matlab code that was use to obtain the results are available in \cite{dehaeze20_activ_dampin_rotat_posit_platf}.
 
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org81be86a}
+\label{sec:org3cf58d1}
 \subsection{Studied Rotating Positioning Platform}
-\label{sec:orgf8fad9b}
+\label{sec:orgf321431}
 Consider the rotating X-Y stage of Figure \ref{fig:system}.
@@
 \includegraphics[scale=1]{figs/system.pdf}
-\caption{\label{fig:system}Figure caption}
+\caption{\label{fig:system}Schematic of the studied System}
 \end{figure}
@@
 \subsection{Equation of Motion}
-\label{sec:org926ba54}
-The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).
+\label{sec:org9612ace}
+The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\) (describing the position of the mass in the rotating frame).
 
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org298e237}
+\label{sec:org1590670}
 
@@
 
-\subsection{Constant Rotating Speed}
-\label{sec:org8d2eda6}
-To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).
+\subsection{Constant Rotational Speed}
+\label{sec:orgd9375df}
+To simplify, let's consider a constant rotational speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).
 
@@
 \end{subfigure}
-\caption{\label{fig:campbell_diagram}Campbell Diagram}
+\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the poles as a function of the rotational speed \(\Omega\)}
 \centering
@@
 \end{subfigure}
-\caption{\label{fig:plant_compare_rotating_speed}Dynamics}
+\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\)}
 \centering
@@
 \section{Integral Force Feedback}
-\label{sec:org2e8c85f}
+\label{sec:org95f47e8}
 \subsection{Control Schematic}
-\label{sec:org50b6359}
+\label{sec:org8bb26ea}
 
@@
 \subsection{Equations}
-\label{sec:org99c13a7}
+\label{sec:orgbd9ebe0}
 The sensed forces are equal to:
@@
 \subsection{Plant Dynamics}
-\label{sec:org1e476e3}
+\label{sec:org392809f}
 
@@
 \includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
-\caption{\label{fig:plant_iff_compare_rotating_speed}Figure caption}
+\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of \(\bm{G}_f\) for several rotational speeds \(\Omega\)}
 \end{figure}
@@
 \subsection{Integral Force Feedback}
-\label{sec:orga5d8887}
+\label{sec:org049877c}
 
@@
 \includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
-\caption{\label{fig:root_locus_pure_iff}Root Locus}
+\caption{\label{fig:root_locus_pure_iff}Root Locus for the Decentralized Integral Force Feedback}
 \end{figure}
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org569b7db}
+\label{sec:org54452db}
 \subsection{Modification of the Control Low}
-\label{sec:org4d0c1ca}
+\label{sec:org325cdd4}
 
 \subsection{Feedback Analysis}
-\label{sec:org1f34d25}
+\label{sec:org5efee77}
 
@@
 \includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
-\caption{\label{fig:loop_gain_modified_iff}Figure caption}
+\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF}
 \end{figure}
@@
 \includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
-\caption{\label{fig:root_locus_modified_iff}Figure caption}
+\caption{\label{fig:root_locus_modified_iff}Root Locus for IFF with and without the HPF}
 \end{figure}
@@
 \subsection{Optimal Cut-Off Frequency}
-\label{sec:org04a5aa4}
+\label{sec:orgd5828e4}
 
@@
 \includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
-\caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
+\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\)}
 \end{figure}
@@
 \includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
-\caption{\label{fig:mod_iff_damping_wi}Figure caption}
+\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of the HPF cut-off frequency.
+Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
 \end{figure}
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org03c54a4}
+\label{sec:org22884d6}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:orgc2d9221}
+\label{sec:orgb871bfd}
 
@@
 \includegraphics[scale=1]{figs/system_parallel_springs.pdf}
-\caption{\label{fig:system_parallel_springs}Figure caption}
+\caption{\label{fig:system_parallel_springs}System with added springs \(k_p\) in parallel with the actuators}
 \end{figure}
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org8097ba5}
+\label{sec:org4d37cce}
 
@@
 \includegraphics[scale=1]{figs/plant_iff_kp.pdf}
-\caption{\label{fig:plant_iff_kp}Figure caption}
+\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
 \end{figure}
@@
 \includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
-\caption{\label{fig:root_locus_iff_kp}Figure caption}
+\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
 \end{figure}
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org1f2e167}
+\label{sec:orgd19b212}
 
@@
 \includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
-\caption{\label{fig:root_locus_iff_kps}Figure caption}
+\caption{\label{fig:root_locus_iff_kps}Root Locus for IFF for several parallel spring stiffnesses \(k_p\)}
 \end{figure}
@@
 \includegraphics[scale=1]{figs/root_locus_opt_gain_iff_kp.pdf}
-\caption{\label{fig:root_locus_opt_gain_iff_kp}Figure caption}
+\caption{\label{fig:root_locus_opt_gain_iff_kp}Root Locus for IFF with \(k_p = 5 m \Omega^2\). The poles of the system using the gain that yields the maximum damping ratio are shown by black crosses}
 \end{figure}
@@
 \section{Direct Velocity Feedback}
-\label{sec:orgda2e325}
+\label{sec:org6904969}
 \subsection{Control Schematic}
-\label{sec:org0e84009}
+\label{sec:org103e18b}
 
@@
 \includegraphics[scale=1]{figs/system_dvf.pdf}
-\caption{\label{fig:system_dvf}Figure caption}
+\caption{\label{fig:system_dvf}System with relative velocity sensors and with decentralized controllers \(K_V\)}
 \end{figure}
@@
 \subsection{Equations}
-\label{sec:org7cc244c}
+\label{sec:org793c22d}
 
 \subsection{Relative Direct Velocity Feedback}
-\label{sec:org668d842}
+\label{sec:orgc28d518}
 
@@
 \includegraphics[scale=1]{figs/root_locus_dvf.pdf}
-\caption{\label{fig:root_locus_dvf}Figure caption}
+\caption{\label{fig:root_locus_dvf}Root Locus for Decentralized Direct Velocity Feedback for several rotational speeds \(\Omega\)}
 \end{figure}
@@
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:orgade0126}
-**
+\label{sec:org6af1fdb}
+\subsection{Physical Comparison}
+\label{sec:orgdff3aa2}
 
-**
+\subsection{Attainable Damping}
+\label{sec:org22c8f42}
 
@@
 \includegraphics[scale=1]{figs/comp_root_locus.pdf}
-\caption{\label{fig:comp_root_locus}Figure caption}
+\caption{\label{fig:comp_root_locus}Root Locus for the three proposed decentralized active damping techniques: IFF with HFP, IFF with parallel springs, and relative DVF}
 \end{figure}
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org59b0db2}
+\label{sec:org3e2cf56}
 
@@
 \section{Conclusion}
-\label{sec:org4b70853}
+\label{sec:orge292803}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org7708a14}
+\label{sec:orgaf681fb}
 

### 2020-06-25 paper/paper.tex
Start to rewrite all the equations

@@
-% Created 2020-06-24 mer. 16:28
+% Created 2020-06-25 jeu. 10:07
 % Intended LaTeX compiler: pdflatex
@@
 \date{}
-\title{Active Damping of Rotating Positioning Platforms}
+\title{Decentralized Active Damping of Rotating Positioning Platforms}
+\hypersetup{
+ pdfauthor={},
+ pdftitle={Decentralized Active Damping of Rotating Positioning Platforms},
+ pdfkeywords={},
+ pdfsubject={},
+ pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
+ pdflang={English}}
 \begin{document}
@@
 \section{Introduction}
-\label{sec:org3cbd2ff}
+\label{sec:org5780a8f}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org3cf58d1}
+\label{sec:orga8db619}
 \subsection{Studied Rotating Positioning Platform}
-\label{sec:orgf321431}
+\label{sec:org70ddefe}
 Consider the rotating X-Y stage of Figure \ref{fig:system}.
@@
 
-\subsection{Equation of Motion}
-\label{sec:org9612ace}
-The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\) (describing the position of the mass in the rotating frame).
+\subsection{Equations of Motion}
+\label{sec:org647b64d}
+The system has two degrees of freedom and is thus fully described by the generalized coordinates \([q_1\ q_2] = [d_u\ d_v]\) (describing the position of the mass in the rotating frame).
 
-Let's express the kinetic energy \(T\) and the potential energy \(V\) of the mass \(m\) (neglecting the rotational energy):
-
-Dissipation function \(R\)
-Kinetic energy \(T\)
-Potential energy \(V\)
+Let's express the kinetic energy \(T\), the potential energy \(V\) of the mass \(m\) (neglecting the rotational energy) as well as the deceptive function \(R\):
 \begin{subequations}
+\label{eq:energy_functions_lagrange}
   \begin{align}
-    T & = \frac{1}{2} m \left( \left( \dot{u} - \Omega v \right)^2 + \left( \dot{v} + \Omega u \right)^2 \right) \\
-    R & = \frac{1}{2} c \left( \dot{u}^2 + \dot{v}^2 \right) \\
-    V & = \frac{1}{2} k \left( u^2 + v^2 \right)
+    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right) \\
+    V & = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right) \\
+    R & = \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right)
   \end{align}
@@
 
-The Lagrangian is the kinetic energy minus the potential energy:
+The equations of motion are derived from the Lagrangian equation:
 \begin{equation}
-L = T - V
-\end{equation}
-
-From the Lagrange's equations of the second kind, the equation of motion is obtained (\(q_1 = u\), \(q_2 = v\)).
-\begin{equation}
+\label{eq:lagrangian_equations}
   \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
 \end{equation}
-with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).
+with \(L = T - V\) is the Lagrangian and \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).
 
 \begin{subequations}
+\label{eq:eom_coupled}
   \begin{align}
-    m \ddot{u} + c \dot{u} + ( k - m \Omega ) u &= F_u + 2 m \Omega \dot{v} \\
-    m \ddot{v} + c \dot{v} + ( k \underbrace{-\,m \Omega}_{\text{Centrif.}} ) v &= F_v \underbrace{-\,2 m \Omega \dot{u}}_{\text{Coriolis}}
+    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
+    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
   \end{align}
@@
 
+The Gyroscopic effects can be seen from the two following terms:
 \begin{itemize}
@@
 
-Without the coupling terms, each equation is the equation of a one degree of freedom mass-spring system with mass \(m\) and stiffness \(k- m\dot{\theta}^2\).
-Thus, the term \(- m\dot{\theta}^2\) acts like a negative stiffness (due to \textbf{centrifugal forces}).
+\subsection{Transfer Functions in the Laplace domain}
+\label{sec:org55c9228}
 
-\subsection{Transfer Functions in the Laplace domain}
-\label{sec:org1590670}
-
+Using the Laplace transformation on the equations of motion \eqref{eq:eom_coupled}, the transfer functions from \([F_u,\ F_v]\) to \([d_u,\ d_v]\) are obtained:
 \begin{subequations}
+\label{eq:oem_laplace_domain}
   \begin{align}
-    u &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v \\
-    v &= \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v
+    d_u &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v \\
+    d_v &= \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v
   \end{align}
@@
 
+Without rotation \(\Omega = 0\) and the system corresponds to two uncoupled one degree of freedom mass-spring-damper systems:
+\begin{subequations}
+\label{eq:oem_no_rotation}
+  \begin{align}
+    d_u &= \frac{1}{m s^2 + cs + k} F_u \\
+    d_v &= \frac{1}{m s^2 + cs + k} F_v
+  \end{align}
+\end{subequations}
+
+\subsection{Change of Variables / Parameters for the study}
+\label{sec:orgb7d090c}
+
+In order this study is more independent on the system parameters, the following change of variable is performed:
+\begin{itemize}
+\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Natural frequency of the mass-spring system in \(\si{\radian/\s}\)
+\item \(\xi = \frac{c}{2 \sqrt{k m}}\): Damping ratio
+\end{itemize}
+
 \begin{equation}
-\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
-\bm{G}_d
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\label{eq:tf_d}
+  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
 \end{equation}
@@
 
-\begin{itemize}
-\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Natural frequency of the mass-spring system in \(\si{\radian/\s}\)
-\item \(\xi\) damping ratio
-\end{itemize}
+\(G_{dp}\) describes to poles of the system, \(G_{dz}\) the zeros of the diagonal terms and \(G_{dc}\) the coupling.
 
-\subsection{Constant Rotational Speed}
-\label{sec:orgd9375df}
-To simplify, let's consider a constant rotational speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).
+\subsection{System Dynamics and Campbell Diagram}
+\label{sec:org24f5f5f}
+The bode plot of \(\bm{G}_d\) is shown in Figure \ref{fig:plant_compare_rotating_speed}.
 
-\begin{equation}
-\label{eq:coupledplant}
-\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
-\frac{1}{(m s^2 + (k - m{\omega_0}^2))^2 + (2 m {\omega_0} s)^2}
-\begin{bmatrix}
-  ms^2 + (k-m{\omega_0}^2) & 2 m \omega_0 s \\
-  -2 m \omega_0 s          & ms^2 + (k-m{\omega_0}^2) \\
-\end{bmatrix}
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
+\begin{figure}[htbp]
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
+\end{subfigure}
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(d_u/F_v\)}
+\end{subfigure}
+\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\)}
+\centering
+\end{figure}
 
-\begin{equation}
-\label{eq:coupled_plant}
-\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
-\frac{\frac{1}{k}}{\left( \frac{s^2}{{\omega_0}^2} + (1 - \frac{{\Omega}^2}{{\omega_0}^2}) \right)^2 + \left( 2 \frac{{\Omega} s}{{\omega_0}^2} \right)^2}
-\begin{bmatrix}
-  \frac{s^2}{{\omega_0}^2} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} & 2 \frac{\Omega s}{{\omega_0}^2} \\
-  -2 \frac{\Omega s}{{\omega_0}^2}          & \frac{s^2}{{\omega_0}^2} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
-\end{bmatrix}
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
+When the rotation speed in non-null, the resonance frequency is split into two pairs of complex conjugate poles.
+As the rotation speed increases, one of the two resonant frequency goes to lower frequencies as the other one goes to higher frequencies.
 
-When the rotation speed is null, the coupling terms are equal to zero and the diagonal terms corresponds to one degree of freedom mass spring system.
-\begin{equation}
-\label{eq:coupled_plant_no_rot}
-\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
-\frac{\frac{1}{k}}{\frac{s^2}{{\omega_0}^2} + 1}
-\begin{bmatrix}
-  1 & 0 \\
-  0 & 1
-\end{bmatrix}
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
+When the rotational speed \(\Omega\) reaches \(\omega_0\), the real part of one pair of complex conjugate becomes position meaning is system is unstable.
 
-When the rotation speed in not null, the resonance frequency is duplicated into two pairs of complex conjugate poles.
-As the rotation speed increases, one of the two resonant frequency goes to lower frequencies as the other one goes to higher frequencies (Figure \ref{fig:campbell_diagram}).
+The stiffness of the X-Y stage is too small to hold to rotating payload hence the instability.
+
+Stiff positioning platforms should be used if high rotational speeds or heavy payloads are used.
 
@@
 
-The magnitude of the coupling terms are increasing with the rotation speed.
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
-\end{subfigure}
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(d_u/F_v\)}
-\end{subfigure}
-\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\)}
-\centering
-\end{figure}
-
-\section{Integral Force Feedback}
-\label{sec:org95f47e8}
+\section{Decentralized Integral Force Feedback}
+\label{sec:orgd957fd6}
 \subsection{Control Schematic}
-\label{sec:org8bb26ea}
+\label{sec:orgc01d8cf}
 
@@
 \subsection{Equations}
-\label{sec:orgbd9ebe0}
-The sensed forces are equal to:
+\label{sec:orge5896ec}
+The forces measured by the force sensors are equal to:
 \begin{equation}
+\label{eq:measured_force}
   \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
@@
 
-Which then gives:
+Reinjecting \eqref{eq:tf_d} into \eqref{eq:measured_force} yields:
 \begin{equation}
-\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
-\bm{G}_{f}
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\label{eq:tf_f}
+\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
 \end{equation}
@@
 \begin{equation}
-\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
+\bm{G}_f =
 \frac{1}{G_{fp}}
@@
 \end{bmatrix}
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
 \end{equation}
@@
 
+\begin{equation}
+\bm{G}_f =
+\frac{1}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
+\begin{bmatrix}
+  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 & -G_{fc} \\
+  G_{fc} &  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2
+\end{bmatrix}
+\end{equation}
+
 \subsection{Plant Dynamics}
-\label{sec:org392809f}
+\label{sec:org0a22a10}
 
@@
 
-\subsection{Integral Force Feedback}
-\label{sec:org049877c}
+\subsection{Problems with Integral Force Feedback}
+\label{sec:orgd432439}
 
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org54452db}
+\label{sec:org2e1883a}
 \subsection{Modification of the Control Low}
-\label{sec:org325cdd4}
+\label{sec:org218110f}
+\begin{equation}
+  \bm{K}_{F}(s) = \frac{1}{s} \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = \frac{1}{s + \omega_i}
+\end{equation}
 
 \subsection{Feedback Analysis}
-\label{sec:org5efee77}
+\label{sec:org03090fc}
 
@@
 \subsection{Optimal Cut-Off Frequency}
-\label{sec:orgd5828e4}
+\label{sec:org6ba4e55}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org22884d6}
+\label{sec:org90ec20f}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:orgb871bfd}
+\label{sec:org60d6640}
 
@@
 
+\begin{equation}
+\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
+\bm{G}_k
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
+\frac{1}{G_{kp}}
+\begin{bmatrix}
+   G_{kz} & -G_{kc} \\
+   G_{kc} &  G_{kz}
+\end{bmatrix}
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+With:
+\begin{align}
+  G_{kp} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
+  G_{kz} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
+  G_{kc} &= \left( 2 \xi^\prime \frac{s}{\omega_0^\prime} + \frac{k}{k + k_p} \right) \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)
+\end{align}
+
+where:
+\begin{itemize}
+\item \(\omega_0^\prime = \frac{k + k_p}{m}\)
+\item \(\xi^\prime = \frac{c}{2 \sqrt{(k + k_p) m}}\)
+\end{itemize}
+
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org4d37cce}
+\label{sec:org3ec34fe}
+
+\begin{equation}
+  \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} > 0
+\end{equation}
+Which is equivalent to
+\begin{equation}
+  k_p > m \Omega^2
+\end{equation}
 
@@
 \includegraphics[scale=1]{figs/plant_iff_kp.pdf}
-\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
+\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\)}
 \end{figure}
@@
 \includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
-\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
+\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\)}
 \end{figure}
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:orgd19b212}
+\label{sec:org9c47159}
 
@@
 \section{Direct Velocity Feedback}
-\label{sec:org6904969}
+\label{sec:org5cb3076}
 \subsection{Control Schematic}
-\label{sec:org103e18b}
+\label{sec:orgaaa522f}
 
@@
 \subsection{Equations}
-\label{sec:org793c22d}
+\label{sec:orge0a4555}
+
+\begin{equation}
+\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
+\bm{G}_v
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
+\frac{s}{k} \frac{1}{G_{vp}}
+\begin{bmatrix}
+   G_{vz} & G_{vc} \\
+  -G_{vc} & G_{vz}
+\end{bmatrix}
+\begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+With:
+\begin{align}
+  G_{vp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
+  G_{vz} &= \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
+  G_{vc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
+\end{align}
 
 \subsection{Relative Direct Velocity Feedback}
-\label{sec:orgc28d518}
+\label{sec:org5401110}
 
@@
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:org6af1fdb}
+\label{sec:org4cbf163}
 \subsection{Physical Comparison}
-\label{sec:orgdff3aa2}
+\label{sec:org5eba275}
 
 \subsection{Attainable Damping}
-\label{sec:org22c8f42}
+\label{sec:org44635e0}
 
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org3e2cf56}
+\label{sec:org58e9594}
 
@@
 \section{Conclusion}
-\label{sec:orge292803}
+\label{sec:org292b448}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orgaf681fb}
+\label{sec:orgff7af07}
 

### 2020-06-25 paper/paper.tex
Add equations

@@
-% Created 2020-06-25 jeu. 10:07
+% Created 2020-06-25 jeu. 17:24
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org5780a8f}
+\label{sec:org7ff5c70}
 \label{sec:introduction}
@@
 ).
+Due to gyroscopic effects, the guaranteed robustness properties of Integral Force Feedback do not hold.
+Either the control architecture can be slightly modfied or mechanical changes in the system can be performed.
 This paper has been published
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:orga8db619}
+\label{sec:org029ca48}
 \subsection{Studied Rotating Positioning Platform}
-\label{sec:org70ddefe}
+\label{sec:org7eec6c5}
 Consider the rotating X-Y stage of Figure \ref{fig:system}.
@@
 \subsection{Equations of Motion}
-\label{sec:org647b64d}
+\label{sec:orgca181a2}
 The system has two degrees of freedom and is thus fully described by the generalized coordinates \([q_1\ q_2] = [d_u\ d_v]\) (describing the position of the mass in the rotating frame).
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org55c9228}
+\label{sec:orge7e184a}
 
@@
 \subsection{Change of Variables / Parameters for the study}
-\label{sec:orgb7d090c}
+\label{sec:org3cdb1ab}
 
@@
 
+\begin{itemize}
+\item \(k = \SI{1}{N/m}\), \(m = \SI{1}{kg}\), \(c = \SI{0.05}{\newton\per\meter\second}\)
+\item \(\omega_0 = \SI{1}{\radian\per\second}\), \(\xi = 0.025\)
+\end{itemize}
+
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:org24f5f5f}
+\label{sec:org42dee20}
 The bode plot of \(\bm{G}_d\) is shown in Figure \ref{fig:plant_compare_rotating_speed}.
@@
 \end{figure}
+
+The poles are the roots of \(G_{dp}\).
+Two pairs of complex conjugate poles (supposing small damping \(\xi \approx 0\)):
+\begin{subequations}
+  \begin{align}
+    p_1 &= \pm j (\omega_0 - \Omega) \\
+    p_2 &= \pm j (\omega_0 + \Omega)
+  \end{align}
+\end{subequations}
 
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgd957fd6}
-\subsection{Control Schematic}
-\label{sec:orgc01d8cf}
+\label{sec:orgda38ad7}
+\subsection{System Schematic and Control Architecture}
+\label{sec:orgf08eb9d}
 
@@
 
-\subsection{Equations}
-\label{sec:orge5896ec}
+\subsection{Plant Dynamics}
+\label{sec:orgf2f22c2}
 The forces measured by the force sensors are equal to:
@@
 
-Reinjecting \eqref{eq:tf_d} into \eqref{eq:measured_force} yields:
+Re-injecting \eqref{eq:tf_d} into \eqref{eq:measured_force} yields:
 \begin{equation}
@@
 \end{equation}
+Where \(\bm{G}_f\) is a \(2 \times 2\) transfer function matrix.
 
@@
 \end{equation}
-
+with:
 \begin{align}
@@
 
+The zeros of the diagonal terms are the roots of \(G_{fz}\) (supposing small damping):
+\begin{subequations}
+  \begin{align}
+    z_1 &= \pm j \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} + \frac{\Omega^2}{{\omega_0}^2} + \frac{1}{2} } \\
+    z_2 &= \pm   \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} - \frac{\Omega^2}{{\omega_0}^2} - \frac{1}{2} }
+  \end{align}
+\end{subequations}
+
+The frequency of the two complex conjugate zeros \(z_1\) is between the frequency of the two pairs of complex conjugate poles \(p_1\) and \(p_2\).
+This is the expected behavior of a collocated pair of actuator and sensor.
+
+However, the two real zeros \(z_2\) induces an increase of +2 of the slope without change of phase (Figure \ref{fig:plant_iff_compare_rotating_speed}).
+This represents non-minimum phase behavior.
+
+The low frequency gain, for \(\Omega < \omega_0\), is no longer zero:
 \begin{equation}
-\bm{G}_f =
-\frac{1}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\begin{bmatrix}
-  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 & -G_{fc} \\
-  G_{fc} &  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2
+\label{low_freq_gain_iff_plan}
+  \bm{G}_{f0} = \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
+  \frac{- \Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
+  0  & \frac{- \Omega^2}{{\omega_0}^2 - \Omega^2}
 \end{bmatrix}
@@
 
-\subsection{Plant Dynamics}
-\label{sec:org0a22a10}
+It increase with the rotational speed \(\Omega\).
 
@@
 
-\subsection{Problems with Integral Force Feedback}
-\label{sec:orgd432439}
+\subsection{Decentralized Integral Force Feedback}
+\label{sec:orge1a14b4}
+
+\begin{equation}
+  \bm{K}_F(s) = g \cdot \frac{1}{s}
+\end{equation}
+
+Also, as one zero has a positive real part, the \textbf{IFF control is no more unconditionally stable}.
+This is due to the fact that the zeros of the plant are the poles of the closed loop system with an infinite gain.
+Thus, for some finite IFF gain, one pole will have a positive real part and the system will be unstable.
 
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org2e1883a}
+\label{sec:org7f551f8}
 \subsection{Modification of the Control Low}
-\label{sec:org218110f}
+\label{sec:org4c39c6d}
 \begin{equation}
-  \bm{K}_{F}(s) = \frac{1}{s} \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = \frac{1}{s + \omega_i}
+  \bm{K}_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
 \end{equation}
@@
 \subsection{Feedback Analysis}
-\label{sec:org03090fc}
-
+\label{sec:org2673698}
 \begin{figure}[htbp]
@@
 \end{figure}
+
+\begin{equation}
+  g_\text{max} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right) \label{eq:iff_gmax}
+\end{equation}
 
@@
 \subsection{Optimal Cut-Off Frequency}
-\label{sec:org6ba4e55}
+\label{sec:org7d8a789}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org90ec20f}
+\label{sec:org9bc19d0}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org60d6640}
-
+\label{sec:orgdfd59fa}
 \begin{figure}[htbp]
@@
 \includegraphics[scale=1]{figs/system_parallel_springs.pdf}
-\caption{\label{fig:system_parallel_springs}System with added springs \(k_p\) in parallel with the actuators}
+\caption{\label{fig:system_parallel_springs}System with added springs in parallel with the actuators}
 \end{figure}
+
+\subsection{Plant Dynamics}
+\label{sec:org70fc8fa}
+
+We define an adimensional parameter \(\alpha\), \(0 \le \alpha < 1\), that describes the proportion of the stiffness in parallel with the actuator and force sensor:
+\begin{subequations}
+  \begin{align}
+    k_p &= \alpha k \\
+    k_a &= (1 - \alpha) k
+  \end{align}
+\end{subequations}
+
+The overall stiffness \(k\) stays constant:
+\begin{equation}
+  k = k_a + k_p
+\end{equation}
 
@@
 With:
+\begin{subequations}
   \begin{align}
-  G_{kp} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
-  G_{kz} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
-  G_{kc} &= \left( 2 \xi^\prime \frac{s}{\omega_0^\prime} + \frac{k}{k + k_p} \right) \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)
+    G_{kp} &= \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{\omega_0} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
+    G_{kz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{\omega_0} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
+    G_{kc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)
   \end{align}
-
-where:
-\begin{itemize}
-\item \(\omega_0^\prime = \frac{k + k_p}{m}\)
-\item \(\xi^\prime = \frac{c}{2 \sqrt{(k + k_p) m}}\)
-\end{itemize}
+\end{subequations}
 
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org3ec34fe}
-
+\label{sec:orge20adc9}
 \begin{equation}
-  \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} > 0
-\end{equation}
-Which is equivalent to
-\begin{equation}
-  k_p > m \Omega^2
+  \begin{align}
+    \alpha > \frac{\Omega^2}{{\omega_0}^2} \\
+    \Leftrightarrow k_p > m \Omega^2
+  \end{align}
 \end{equation}
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org9c47159}
-
+\label{sec:orgb14b5c2}
 \begin{figure}[htbp]
+\begin{subfigure}[c]{0.49\linewidth}
+\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
+\caption{\label{fig:root_locus_iff_kps} Three values of \(k_p\)}
+\end{subfigure}
+\begin{subfigure}[c]{0.49\linewidth}
+\includegraphics[width=\linewidth]{figs/root_locus_opt_gain_iff_kp.pdf}
+\caption{\label{fig:root_locus_opt_gain_iff_kp} \(k_p = 5 m \Omega^2\), optimal damping is shown}
+\end{subfigure}
+\caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness is used}
 \centering
-\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
-\caption{\label{fig:root_locus_iff_kps}Root Locus for IFF for several parallel spring stiffnesses \(k_p\)}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/root_locus_opt_gain_iff_kp.pdf}
-\caption{\label{fig:root_locus_opt_gain_iff_kp}Root Locus for IFF with \(k_p = 5 m \Omega^2\). The poles of the system using the gain that yields the maximum damping ratio are shown by black crosses}
 \end{figure}
@@
 \section{Direct Velocity Feedback}
-\label{sec:org5cb3076}
-\subsection{Control Schematic}
-\label{sec:orgaaa522f}
-
+\label{sec:org7628683}
+\subsection{System Schematic and Control Architecture}
+\label{sec:org6953bc7}
 \begin{figure}[htbp]
@@
 \subsection{Equations}
-\label{sec:orge0a4555}
+\label{sec:orgfab42cd}
 
@@
 \begin{bmatrix} v_u \\ v_v \end{bmatrix} =
-\frac{s}{k} \frac{1}{G_{vp}}
+\frac{1}{k} \frac{1}{G_{vp}}
 \begin{bmatrix}
@@
 With:
+\begin{subequations}
   \begin{align}
     G_{vp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
-  G_{vz} &= \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
+    G_{vz} &= s \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) \\
     G_{vc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
   \end{align}
+\end{subequations}
 
 \subsection{Relative Direct Velocity Feedback}
-\label{sec:org5401110}
+\label{sec:org5cf0d6b}
 
@@
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:org4cbf163}
+\label{sec:orga2b60a8}
 \subsection{Physical Comparison}
-\label{sec:org5eba275}
+\label{sec:orgb69316c}
 
 \subsection{Attainable Damping}
-\label{sec:org44635e0}
+\label{sec:org5c23e13}
 
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org58e9594}
+\label{sec:org723fb63}
 
@@
 \section{Conclusion}
-\label{sec:org292b448}
+\label{sec:orgd52b568}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orgff7af07}
+\label{sec:orge4d73e9}
 

### 2020-06-26 paper/paper.tex
Clarify some equations (location of poles/zeros)

@@
-% Created 2020-06-25 jeu. 17:24
+% Created 2020-06-26 ven. 17:28
 % Intended LaTeX compiler: pdflatex
@@
 \date{}
-\title{Decentralized Active Damping of Rotating Positioning Platforms}
+\title{Active Damping of Rotating Positioning Platforms using Force Feedback}
 \hypersetup{
  pdfauthor={},
- pdftitle={Decentralized Active Damping of Rotating Positioning Platforms},
+ pdftitle={Active Damping of Rotating Positioning Platforms using Force Feedback},
  pdfkeywords={},
@@
 \section{Introduction}
-\label{sec:org7ff5c70}
+\label{sec:org4effc95}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org029ca48}
-\subsection{Studied Rotating Positioning Platform}
-\label{sec:org7eec6c5}
-Consider the rotating X-Y stage of Figure \ref{fig:system}.
+\label{sec:org5eef93b}
+\subsection{Model of a Rotating Positioning Platform}
+\label{sec:org905e0e5}
+To study how the rotation of positioning platforms does affect the use of force feedback, a simple model is developed.
 
+It represents an X-Y positioning stage on top of a Rotating Stage and is schematically represented in Figure \ref{fig:system}.
+
+Two frames of reference are used:
 \begin{itemize}
-\item \(k\): Actuator's Stiffness [N/m]
-\item \(m\): Payload's mass [kg]
-\item \(\Omega = \dot{\theta}\): rotation speed [rad/s]
-\item \(F_u\), \(F_v\)
-\item \(d_u\), \(d_v\)
+\item \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\) is an inertial frame
+\item \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\) is a frame fixed on the Rotating Stage with its origin align with the rotation axis
 \end{itemize}
+
+The rotating stage is supposed to be ideal, meaning it is infinitely rigid and induces a rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
+
+The parallel X-Y positioning stage consists of two orthogonal actuators represented by the three following elements in parallel:
+\begin{itemize}
+\item A spring with a stiffness \(k\) in \(\si{\newton\per\meter}\)
+\item A dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\)
+\item An ideal force source \(F_u, F_v\) in \(\si{\newton}\)
+\end{itemize}
+
+The X-Y stage is supporting a payload with a payload with a mass \(m\) in \(\si{\kilo\gram}\).
+The position of the payload is represented by \((d_u, d_v)\) expressed in the rotating frame \((\vec{i}_u, \vec{i}_v)\).
 
@@
 \subsection{Equations of Motion}
-\label{sec:orgca181a2}
-The system has two degrees of freedom and is thus fully described by the generalized coordinates \([q_1\ q_2] = [d_u\ d_v]\) (describing the position of the mass in the rotating frame).
-
-Let's express the kinetic energy \(T\), the potential energy \(V\) of the mass \(m\) (neglecting the rotational energy) as well as the deceptive function \(R\):
+\label{sec:org08efe1c}
+To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
+\begin{equation}
+\label{eq:lagrangian_equations}
+  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
+\end{equation}
+with \(L = T - V\) is the Lagrangian, \(D\) is the dissipation function, and \(Q_i\) is the generalized force associated with the generalized variable \([q_1\ q_2] = [d_u\ d_v]\):
 \begin{subequations}
@@
     V & = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right) \\
-    R & = \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right)
+    D & = \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right) \\
+    Q_1 &= F_u, \quad Q_2 = F_v
   \end{align}
@@
 
-The equations of motion are derived from the Lagrangian equation:
-\begin{equation}
-\label{eq:lagrangian_equations}
-  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
-\end{equation}
-with \(L = T - V\) is the Lagrangian and \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).
-
+Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} gives the two coupled differential equations:
 \begin{subequations}
@@
 
-The Gyroscopic effects can be seen from the two following terms:
+The rotation of the XY positioning platform induces two Gyroscopic effects:
 \begin{itemize}
-\item Coriolis Forces: coupling
-\item Centrifugal forces: negative stiffness
+\item Coriolis Forces: that adds coupling between the two orthogonal controlled directions
+\item Centrifugal forces: that can been seen as negative stiffness
 \end{itemize}
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:orge7e184a}
+\label{sec:org6daa125}
+To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the transfer functions from \([F_u,\ F_v]\) to \([d_u,\ d_v]\) are obtained:
+\begin{equation}
+\label{eq:Gd_mimo_tf}
+  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
 
-Using the Laplace transformation on the equations of motion \eqref{eq:eom_coupled}, the transfer functions from \([F_u,\ F_v]\) to \([d_u,\ d_v]\) are obtained:
-\begin{subequations}
-\label{eq:oem_laplace_domain}
-  \begin{align}
-    d_u &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v \\
-    d_v &= \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v
-  \end{align}
-\end{subequations}
+with \(\bm{G}_d\) a \(2 \times 2\) transfer function matrix
+\begin{equation}
+\label{eq:Gd_m_k_c}
+  \bm{G}_{d} =
+  \begin{bmatrix}
+    \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
+    \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}
+  \end{bmatrix}
+\end{equation}
 
-Without rotation \(\Omega = 0\) and the system corresponds to two uncoupled one degree of freedom mass-spring-damper systems:
+One can verify that without rotation (\(\Omega = 0\)) the system becomes equivalent as to two uncoupled one degree of freedom mass-spring-damper systems:
 \begin{subequations}
@@
 \subsection{Change of Variables / Parameters for the study}
-\label{sec:org3cdb1ab}
+\label{sec:orgda057f2}
 
-In order this study is more independent on the system parameters, the following change of variable is performed:
+In order to make this study less dependent on the system parameters, the following change of variable is performed:
 \begin{itemize}
@@
 
+The transfer function matrix \eqref{eq:Gd_m_k_c} becomes equal to
 \begin{equation}
-\label{eq:tf_d}
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
-Where \(\bm{G}_d\) is a \(2 \times 2\) transfer function matrix.
-
-\begin{equation}
-\bm{G}_d = \frac{1}{k} \frac{1}{G_{dp}}
+\label{eq:Gd_w0_xi_k}
+\bm{G}_{d} =
+  \frac{1}{k}
   \begin{bmatrix}
-   G_{dz} & G_{dc} \\
-  -G_{dc} & G_{dz}
+    \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
+    \frac{- 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
   \end{bmatrix}
 \end{equation}
-With:
+
+During the rest of this study, the following parameters are used for numerical analysis
+\begin{itemize}
+\item \(\omega_0 = \SI{1}{\radian\per\second}\), \(\xi = 0.025 = \SI{2.5}{\percent}\)
+\item \(k = \SI{1}{N/m}\), \(m = \SI{1}{kg}\), \(c = \SI{0.05}{\newton\per\meter\second}\)
+\end{itemize}
+
+\subsection{System Dynamics and Campbell Diagram}
+\label{sec:org9c94a4d}
+The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
+\begin{equation}
+  \left( \frac{p^2}{{\omega_0}^2} + 2 \xi \frac{p}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{p}{\omega_0} \right)^2 = 0
+\end{equation}
+
+Supposing small damping (\(\xi \ll 1\)), two pairs of complex conjugate poles are obtained:
 \begin{subequations}
+\label{eq:pole_values}
   \begin{align}
-    G_{dp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
-    G_{dz} &= \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
-    G_{dc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
+    p_{+} &= - \xi \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \pm j \left( \omega_0 + \Omega \right) \\
+    p_{-} &= - \xi \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right) \pm j \left( \omega_0 - \Omega \right)
   \end{align}
@@
 
-\(G_{dp}\) describes to poles of the system, \(G_{dz}\) the zeros of the diagonal terms and \(G_{dc}\) the coupling.
+When the rotation speed in non-null, the resonance frequency is split into two pairs of complex conjugate poles.
+As the rotation speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) to lower frequencies.
 
+When the rotational speed \(\Omega\) reaches \(\omega_0\), the real part \(p_{-}\) is positive meaning the system becomes unstable.
+The stiffness of the X-Y stage is too low to hold to rotating payload hence the instability.
+Stiff positioning platforms should be used if high rotational speeds or heavy payloads are used.
+
+This is graphically represented with the Campbell Diagram in Figure \ref{fig:campbell_diagram}.
+
+\begin{figure}[htbp]
+\begin{subfigure}[c]{0.4\linewidth}
+\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
+\caption{\label{fig:campbell_diagram_real} Real Part}
+\end{subfigure}
+\begin{subfigure}[c]{0.4\linewidth}
+\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
+\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
+\end{subfigure}
+\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
+\centering
+\end{figure}
+
+Looking at the transfer function matrix \(\bm{G}_d\) \eqref{eq:Gd_w0_xi_k}, one can see it has two distinct terms that can be studied separately:
 \begin{itemize}
-\item \(k = \SI{1}{N/m}\), \(m = \SI{1}{kg}\), \(c = \SI{0.05}{\newton\per\meter\second}\)
-\item \(\omega_0 = \SI{1}{\radian\per\second}\), \(\xi = 0.025\)
+\item the direct (diagonal) terms
+\item the coupling (off-diagonal) terms
 \end{itemize}
 
-\subsection{System Dynamics and Campbell Diagram}
-\label{sec:org42dee20}
-The bode plot of \(\bm{G}_d\) is shown in Figure \ref{fig:plant_compare_rotating_speed}.
+The bode plot of the direct and coupling terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speed \(\Omega\).
+
+Without rotation, the dynamics of the direct terms is equivalent to the dynamics of a one degree of freedom mass spring damper system and the coupling terms are null.
+As the rotational speed increases, the pair of complex conjugate poles is separated into two pairs of complex conjugate poles, one going to lower frequencies and the other to higher frequencies.
+When the
 
@@
 \end{subfigure}
-\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\)}
+\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
 \centering
@@
 
-The poles are the roots of \(G_{dp}\).
-Two pairs of complex conjugate poles (supposing small damping \(\xi \approx 0\)):
-\begin{subequations}
-  \begin{align}
-    p_1 &= \pm j (\omega_0 - \Omega) \\
-    p_2 &= \pm j (\omega_0 + \Omega)
-  \end{align}
-\end{subequations}
-
-When the rotation speed in non-null, the resonance frequency is split into two pairs of complex conjugate poles.
-As the rotation speed increases, one of the two resonant frequency goes to lower frequencies as the other one goes to higher frequencies.
-
-When the rotational speed \(\Omega\) reaches \(\omega_0\), the real part of one pair of complex conjugate becomes position meaning is system is unstable.
-
-The stiffness of the X-Y stage is too small to hold to rotating payload hence the instability.
-
-Stiff positioning platforms should be used if high rotational speeds or heavy payloads are used.
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.4\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
-\caption{\label{fig:campbell_diagram_real} Real Part}
-\end{subfigure}
-\begin{subfigure}[c]{0.4\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
-\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
-\end{subfigure}
-\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the poles as a function of the rotational speed \(\Omega\)}
-\centering
-\end{figure}
+In the rest of this study, \(\Omega < \omega_0\)
 
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgda38ad7}
+\label{sec:org729cd5f}
 \subsection{System Schematic and Control Architecture}
-\label{sec:orgf08eb9d}
-
+\label{sec:org87ee3ad}
 Force Sensors are added in series with the actuators as shown in Figure \ref{fig:system_iff}.
@@
 \subsection{Plant Dynamics}
-\label{sec:orgf2f22c2}
+\label{sec:orge10a341}
 The forces measured by the force sensors are equal to:
@@
 
-Re-injecting \eqref{eq:tf_d} into \eqref{eq:measured_force} yields:
+Re-injecting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields:
 \begin{equation}
-\label{eq:tf_f}
+\label{eq:Gf_mimo_tf}
   \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
 \end{equation}
-Where \(\bm{G}_f\) is a \(2 \times 2\) transfer function matrix.
-
+with \(\bm{G}_f\) a \(2 \times 2\) transfer function matrix
 \begin{equation}
-\bm{G}_f =
-\frac{1}{G_{fp}}
-\begin{bmatrix}
-  G_{fz} & -G_{fc} \\
-  G_{fc} &  G_{fz}
+\label{eq:Gf}
+  \bm{G}_{f} = \begin{bmatrix}
+  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
+  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
 \end{bmatrix}
 \end{equation}
-with:
-\begin{align}
-  G_{fp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
-  G_{fz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
-  G_{fc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)
-\end{align}
 
-The zeros of the diagonal terms are the roots of \(G_{fz}\) (supposing small damping):
+The zeros of the diagonal terms of \(\bm{G}_f\) are equal to (neglecting the damping)
 \begin{subequations}
   \begin{align}
-    z_1 &= \pm j \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} + \frac{\Omega^2}{{\omega_0}^2} + \frac{1}{2} } \\
-    z_2 &= \pm   \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} - \frac{\Omega^2}{{\omega_0}^2} - \frac{1}{2} }
+    z_c &= \pm j \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} + \frac{\Omega^2}{{\omega_0}^2} + \frac{1}{2} } \label{eq:iff_zero_cc} \\
+    z_r &= \pm   \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} - \frac{\Omega^2}{{\omega_0}^2} - \frac{1}{2} } \label{eq:iff_zero_real}
   \end{align}
@@
 
-The frequency of the two complex conjugate zeros \(z_1\) is between the frequency of the two pairs of complex conjugate poles \(p_1\) and \(p_2\).
+The frequency of the two complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} is between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
 This is the expected behavior of a collocated pair of actuator and sensor.
 
-However, the two real zeros \(z_2\) induces an increase of +2 of the slope without change of phase (Figure \ref{fig:plant_iff_compare_rotating_speed}).
+However, the two real zeros \(z_c\) induces an increase of +2 of the slope without change of phase (Figure \ref{fig:plant_iff_compare_rotating_speed}).
 This represents non-minimum phase behavior.
@@
 
-It increase with the rotational speed \(\Omega\).
+It increases with the rotational speed \(\Omega\).
 
@@
 \subsection{Decentralized Integral Force Feedback}
-\label{sec:orge1a14b4}
+\label{sec:org1d15108}
 
 \begin{equation}
-  \bm{K}_F(s) = g \cdot \frac{1}{s}
+  K_F(s) = g \cdot \frac{1}{s}
 \end{equation}
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org7f551f8}
+\label{sec:org95ed1b6}
 \subsection{Modification of the Control Low}
-\label{sec:org4c39c6d}
+\label{sec:orgfadc2c2}
 \begin{equation}
-  \bm{K}_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
+  K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
 \end{equation}
@@
 \subsection{Feedback Analysis}
-\label{sec:org2673698}
+\label{sec:org6ef2134}
 \begin{figure}[htbp]
@@
 \subsection{Optimal Cut-Off Frequency}
-\label{sec:org7d8a789}
+\label{sec:org23e0758}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org9bc19d0}
+\label{sec:org6947a77}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:orgdfd59fa}
+\label{sec:org9a80ee7}
 \begin{figure}[htbp]
@@
 \subsection{Plant Dynamics}
-\label{sec:org70fc8fa}
+\label{sec:org14f5b78}
 
@@
 \begin{equation}
+\label{eq:Gk_mimo_tf}
 \begin{bmatrix} f_u \\ f_v \end{bmatrix} =
@@
 \begin{equation}
-\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
-\frac{1}{G_{kp}}
+\label{eq:Gk}
+\bm{G}_k =
 \begin{bmatrix}
-   G_{kz} & -G_{kc} \\
-   G_{kc} &  G_{kz}
+  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
+  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
 \end{bmatrix}
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
 \end{equation}
-With:
-\begin{subequations}
-  \begin{align}
-    G_{kp} &= \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{\omega_0} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
-    G_{kz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{\omega_0} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
-    G_{kc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)
-  \end{align}
-\end{subequations}
 
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:orge20adc9}
+\label{sec:org4b26266}
 \begin{equation}
-  \begin{align}
+  \begin{aligned}
     \alpha > \frac{\Omega^2}{{\omega_0}^2} \\
     \Leftrightarrow k_p > m \Omega^2
-  \end{align}
+  \end{aligned}
 \end{equation}
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:orgb14b5c2}
+\label{sec:orgfd42bdb}
 \begin{figure}[htbp]
@@
 
-\section{Direct Velocity Feedback}
-\label{sec:org7628683}
-\subsection{System Schematic and Control Architecture}
-\label{sec:org6953bc7}
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/system_dvf.pdf}
-\caption{\label{fig:system_dvf}System with relative velocity sensors and with decentralized controllers \(K_V\)}
-\end{figure}
-
-\subsection{Equations}
-\label{sec:orgfab42cd}
-
-\begin{equation}
-\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
-\bm{G}_v
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
-\frac{1}{k} \frac{1}{G_{vp}}
-\begin{bmatrix}
-   G_{vz} & G_{vc} \\
-  -G_{vc} & G_{vz}
-\end{bmatrix}
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
-With:
-\begin{subequations}
-  \begin{align}
-    G_{vp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
-    G_{vz} &= s \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) \\
-    G_{vc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
-  \end{align}
-\end{subequations}
-
-\subsection{Relative Direct Velocity Feedback}
-\label{sec:org5cf0d6b}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/root_locus_dvf.pdf}
-\caption{\label{fig:root_locus_dvf}Root Locus for Decentralized Direct Velocity Feedback for several rotational speeds \(\Omega\)}
-\end{figure}
-
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:orga2b60a8}
+\label{sec:org67dd4e8}
 \subsection{Physical Comparison}
-\label{sec:orgb69316c}
+\label{sec:orgf742b29}
 
 \subsection{Attainable Damping}
-\label{sec:org5c23e13}
+\label{sec:orgdb615c3}
 
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org723fb63}
+\label{sec:org59532ce}
 
@@
 \section{Conclusion}
-\label{sec:orgd52b568}
+\label{sec:orgde4f24d}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orge4d73e9}
+\label{sec:org3284e1c}
 

### 2020-06-29 paper/paper.tex
Removed DVF from the study (replace with passive)

@@
-% Created 2020-06-26 ven. 17:28
+% Created 2020-06-29 lun. 10:22
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org4effc95}
+\label{sec:org8a431d3}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org5eef93b}
+\label{sec:org6c19606}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:org905e0e5}
+\label{sec:orga59b20f}
 To study how the rotation of positioning platforms does affect the use of force feedback, a simple model is developed.
@@
 \subsection{Equations of Motion}
-\label{sec:org08efe1c}
+\label{sec:orgad9d82d}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org6daa125}
+\label{sec:orgb80a7b8}
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the transfer functions from \([F_u,\ F_v]\) to \([d_u,\ d_v]\) are obtained:
@@
 \end{equation}
-
 with \(\bm{G}_d\) a \(2 \times 2\) transfer function matrix
@@
 \subsection{Change of Variables / Parameters for the study}
-\label{sec:orgda057f2}
+\label{sec:org97136f3}
 
@@
 \begin{itemize}
-\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Natural frequency of the mass-spring system in \(\si{\radian/\s}\)
+\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Undamped natural frequency of the mass-spring system in \(\si{\radian/\s}\)
 \item \(\xi = \frac{c}{2 \sqrt{k m}}\): Damping ratio
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:org9c94a4d}
+\label{sec:orgf368845}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
   \begin{align}
-    p_{+} &= - \xi \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \pm j \left( \omega_0 + \Omega \right) \\
-    p_{-} &= - \xi \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right) \pm j \left( \omega_0 - \Omega \right)
+    p_{+} &= - \xi \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \pm j \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \\
+    p_{-} &= - \xi \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right) \pm j \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right)
   \end{align}
@@
 
-When the rotation speed in non-null, the resonance frequency is split into two pairs of complex conjugate poles.
+The real part and complex part of these two pairs of complex conjugate poles are represented in Figure \ref{fig:campbell_diagram} as a function of the rotational speed \(\Omega\).
+
 As the rotation speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) to lower frequencies.
-
-When the rotational speed \(\Omega\) reaches \(\omega_0\), the real part \(p_{-}\) is positive meaning the system becomes unstable.
-The stiffness of the X-Y stage is too low to hold to rotating payload hence the instability.
-Stiff positioning platforms should be used if high rotational speeds or heavy payloads are used.
-
-This is graphically represented with the Campbell Diagram in Figure \ref{fig:campbell_diagram}.
+When the rotational speed \(\Omega\) reaches \(\omega_0\), the real part \(p_{-}\) becomes positive rendering the system unstable.
+Physically, the negative stiffness term induced by centrifugal forces exceeds the spring stiffness.
+Thus, stiff positioning platforms should be used when working at high rotational speeds.
 
@@
 \begin{itemize}
-\item the direct (diagonal) terms
-\item the coupling (off-diagonal) terms
+\item the direct (diagonal) terms (Figure \ref{fig:plant_compare_rotating_speed_direct})
+\item the coupling (off-diagonal) terms (Figure \ref{fig:plant_compare_rotating_speed_coupling})
 \end{itemize}
@@
 
-In the rest of this study, \(\Omega < \omega_0\)
+In the rest of this study, rotational speeds smaller than the undamped natural frequency of the system are used (\(\Omega < \omega_0\)).
 
 \section{Decentralized Integral Force Feedback}
-\label{sec:org729cd5f}
-\subsection{System Schematic and Control Architecture}
-\label{sec:org87ee3ad}
-Force Sensors are added in series with the actuators as shown in Figure \ref{fig:system_iff}.
+\label{sec:orge7b2b3c}
+\subsection{Force Sensors and Control Architecture}
+\label{sec:org2b4254d}
+In order to apply Decentralized Integral Force Feedback to the system, force sensors are added in series of the two actuators (Figure \ref{fig:system_iff}).
 
@@
 \subsection{Plant Dynamics}
-\label{sec:orge10a341}
+\label{sec:org59a4f35}
 The forces measured by the force sensors are equal to:
@@
 \subsection{Decentralized Integral Force Feedback}
-\label{sec:org1d15108}
+\label{sec:orgf040b7e}
 
@@
 
-Also, as one zero has a positive real part, the \textbf{IFF control is no more unconditionally stable}.
+Also, as one zero has a positive real part, the IFF control is no more unconditionally stable.
 This is due to the fact that the zeros of the plant are the poles of the closed loop system with an infinite gain.
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org95ed1b6}
+\label{sec:org5533f47}
 \subsection{Modification of the Control Low}
-\label{sec:orgfadc2c2}
+\label{sec:orge3f4cc0}
 \begin{equation}
@@
 \subsection{Feedback Analysis}
-\label{sec:org6ef2134}
+\label{sec:orgd0fed6b}
 \begin{figure}[htbp]
@@
 \includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
-\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF}
+\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF, \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
-\caption{\label{fig:root_locus_modified_iff}Root Locus for IFF with and without the HPF}
+\caption{\label{fig:root_locus_modified_iff}Root Locus for IFF with and without the HPF, \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \subsection{Optimal Cut-Off Frequency}
-\label{sec:org23e0758}
+\label{sec:org4740973}
 
@@
 \includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
-\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\)}
+\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org6947a77}
+\label{sec:org1b53815}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org9a80ee7}
+\label{sec:org3a8c426}
 \begin{figure}[htbp]
@@
 \subsection{Plant Dynamics}
-\label{sec:org14f5b78}
+\label{sec:orgf26a6f4}
 
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org4b26266}
+\label{sec:org6a55282}
 \begin{equation}
@@
 \includegraphics[scale=1]{figs/plant_iff_kp.pdf}
-\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\)}
+\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
-\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\)}
+\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:orgfd42bdb}
+\label{sec:org358dd73}
 \begin{figure}[htbp]
@@
 \end{subfigure}
-\caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness is used}
+\caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness is used, \(\Omega = 0.1 \omega_0\)}
 \centering
@@
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:org67dd4e8}
+\label{sec:org3cc6699}
 \subsection{Physical Comparison}
-\label{sec:orgf742b29}
+\label{sec:orgc34b986}
 
 \subsection{Attainable Damping}
-\label{sec:orgdb615c3}
+\label{sec:org993a1d7}
 
@@
 \includegraphics[scale=1]{figs/comp_root_locus.pdf}
-\caption{\label{fig:comp_root_locus}Root Locus for the three proposed decentralized active damping techniques: IFF with HFP, IFF with parallel springs, and relative DVF}
+\caption{\label{fig:comp_root_locus}Root Locus for the three proposed decentralized active damping techniques: IFF with HFP, IFF with parallel springs, and relative DVF, \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org59532ce}
+\label{sec:org0674052}
 
@@
 \end{subfigure}
-\caption{\label{fig:comp_active_damping}Comparison of the three proposed Active Damping Techniques}
+\caption{\label{fig:comp_active_damping}Comparison of the two proposed Active Damping Techniques, \(\Omega = 0.1 \omega_0\)}
 \centering
@@
 \section{Conclusion}
-\label{sec:orgde4f24d}
+\label{sec:orgba18ca5}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org3284e1c}
+\label{sec:org4c68ce2}
 

### 2020-07-01 paper/paper.tex
Worked on sections 2 and 3

@@
-% Created 2020-06-29 lun. 10:22
+% Created 2020-07-01 mer. 10:02
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{tikz}
-\usetikzlibrary{shapes.misc}
+\usetikzlibrary{shapes.misc,arrows,arrows.meta}
 \date{}
@@
 \section{Introduction}
-\label{sec:org8a431d3}
+\label{sec:org38db2d2}
 \label{sec:introduction}
-Controller Poles are shown by black crosses (
-\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
-).
 Due to gyroscopic effects, the guaranteed robustness properties of Integral Force Feedback do not hold.
-Either the control architecture can be slightly modfied or mechanical changes in the system can be performed.
+Either the control architecture can be slightly modified or mechanical changes in the system can be performed.
 This paper has been published
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org6c19606}
+\label{sec:orgd0419a7}
+\label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:orga59b20f}
-To study how the rotation of positioning platforms does affect the use of force feedback, a simple model is developed.
+\label{sec:org4c3a41a}
+In order to study how the rotation of a positioning platforms does affect the use of force feedback, a simple model of an X-Y positioning stage on top of a rotating stage is developed.
 
-It represents an X-Y positioning stage on top of a Rotating Stage and is schematically represented in Figure \ref{fig:system}.
+The model is schematically represented in Figure \ref{fig:system} and forms the simplest system where gyroscopic forces can be studied.
 
-Two frames of reference are used:
+The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
+
+The parallel X-Y positioning stage consists of two orthogonal actuators represented by three elements in parallel:
 \begin{itemize}
-\item \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\) is an inertial frame
-\item \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\) is a frame fixed on the Rotating Stage with its origin align with the rotation axis
+\item a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\)
+\item a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\)
+\item an ideal force source \(F_u, F_v\)
 \end{itemize}
 
-The rotating stage is supposed to be ideal, meaning it is infinitely rigid and induces a rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
+A payload with a mass \(m\) in \(\si{\kilo\gram}\) is mounted on the rotating X-Y stage.
 
-The parallel X-Y positioning stage consists of two orthogonal actuators represented by the three following elements in parallel:
+Two reference frames are used:
 \begin{itemize}
-\item A spring with a stiffness \(k\) in \(\si{\newton\per\meter}\)
-\item A dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\)
-\item An ideal force source \(F_u, F_v\) in \(\si{\newton}\)
+\item an inertial frame \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\)
+\item a uniform rotating frame \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\) rigidly fixed on top of the rotating stage. \(\vec{i}_w\) is aligned with the rotation axis
 \end{itemize}
 
-The X-Y stage is supporting a payload with a payload with a mass \(m\) in \(\si{\kilo\gram}\).
-The position of the payload is represented by \((d_u, d_v)\) expressed in the rotating frame \((\vec{i}_u, \vec{i}_v)\).
+The position of the payload is represented by \((d_u, d_v)\) expressed in the rotating frame.
 
@@
 \subsection{Equations of Motion}
-\label{sec:orgad9d82d}
+\label{sec:orga2d4956}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \end{equation}
-with \(L = T - V\) is the Lagrangian, \(D\) is the dissipation function, and \(Q_i\) is the generalized force associated with the generalized variable \([q_1\ q_2] = [d_u\ d_v]\):
+with \(L = T - V\) the Lagrangian, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
+
+The constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is here disregarded as it is imposed by the rotating stage.
 \begin{subequations}
@@
   \begin{align}
-    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
-    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
+    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega^2 ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
+    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega^2}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
   \end{align}
@@
 
-The rotation of the XY positioning platform induces two Gyroscopic effects:
+The constant rotation of the system induces two Gyroscopic effects:
 \begin{itemize}
-\item Coriolis Forces: that adds coupling between the two orthogonal controlled directions
-\item Centrifugal forces: that can been seen as negative stiffness
+\item Centrifugal forces: that can been seen as added negative stiffness along \(\vec{i}_u\) and \(\vec{i}_v\)
+\item Coriolis Forces: that couples the motion in the two orthogonal directions
 \end{itemize}
 
+One can verify that without rotation (\(\Omega = 0\)) the system becomes equivalent as to two uncoupled one degree of freedom mass-spring-damper systems:
+\begin{subequations}
+\label{eq:oem_no_rotation}
+  \begin{align}
+    m \ddot{d}_u + c \dot{d}_u + k d_u &= F_u \\
+    m \ddot{d}_v + c \dot{d}_v + k d_v &= F_v
+  \end{align}
+\end{subequations}
+
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:orgb80a7b8}
-To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the transfer functions from \([F_u,\ F_v]\) to \([d_u,\ d_v]\) are obtained:
+\label{sec:org16be790}
+To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the transfer function matrix from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained:
 \begin{equation}
@@
 
-One can verify that without rotation (\(\Omega = 0\)) the system becomes equivalent as to two uncoupled one degree of freedom mass-spring-damper systems:
-\begin{subequations}
-\label{eq:oem_no_rotation}
-  \begin{align}
-    d_u &= \frac{1}{m s^2 + cs + k} F_u \\
-    d_v &= \frac{1}{m s^2 + cs + k} F_v
-  \end{align}
-\end{subequations}
-
-\subsection{Change of Variables / Parameters for the study}
-\label{sec:org97136f3}
-
-In order to make this study less dependent on the system parameters, the following change of variable is performed:
+To simply the analysis, the following change of variable is performed:
 \begin{itemize}
@@
 
-During the rest of this study, the following parameters are used for numerical analysis
-\begin{itemize}
-\item \(\omega_0 = \SI{1}{\radian\per\second}\), \(\xi = 0.025 = \SI{2.5}{\percent}\)
-\item \(k = \SI{1}{N/m}\), \(m = \SI{1}{kg}\), \(c = \SI{0.05}{\newton\per\meter\second}\)
-\end{itemize}
+For all the numerical analysis in this study, \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
+
+Even tough no system with such parameters will be encountered in practice, conclusions will be drawn relative to these parameters such that they can be generalized to any other parameter.
 
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:orgf368845}
+\label{sec:org0ed334c}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 The real part and complex part of these two pairs of complex conjugate poles are represented in Figure \ref{fig:campbell_diagram} as a function of the rotational speed \(\Omega\).
+As the rotational speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) to lower frequencies.
+The system becomes unstable for \(\Omega > \omega_0\) as the real part of \(p_{-}\) is positive.
+Physically, the negative stiffness term \(-m\Omega^2\) induced by centrifugal forces exceeds the spring stiffness \(k\).
 
-As the rotation speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) to lower frequencies.
-When the rotational speed \(\Omega\) reaches \(\omega_0\), the real part \(p_{-}\) becomes positive rendering the system unstable.
-Physically, the negative stiffness term induced by centrifugal forces exceeds the spring stiffness.
-Thus, stiff positioning platforms should be used when working at high rotational speeds.
+In the rest of this study, rotational speeds smaller than the undamped natural frequency of the system are used (\(\Omega < \omega_0\)).
 
@@
 
-Looking at the transfer function matrix \(\bm{G}_d\) \eqref{eq:Gd_w0_xi_k}, one can see it has two distinct terms that can be studied separately:
-\begin{itemize}
-\item the direct (diagonal) terms (Figure \ref{fig:plant_compare_rotating_speed_direct})
-\item the coupling (off-diagonal) terms (Figure \ref{fig:plant_compare_rotating_speed_coupling})
-\end{itemize}
+Looking at the transfer function matrix \(\bm{G}_d\) in Eq. \eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and the two off-diagonal (coupling) terms are opposite.
+The bode plot of these two distinct terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
 
-The bode plot of the direct and coupling terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speed \(\Omega\).
-
-Without rotation, the dynamics of the direct terms is equivalent to the dynamics of a one degree of freedom mass spring damper system and the coupling terms are null.
-As the rotational speed increases, the pair of complex conjugate poles is separated into two pairs of complex conjugate poles, one going to lower frequencies and the other to higher frequencies.
-When the
+It is confirmed that the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
+For \(\Omega > \omega_0\), the low frequency complex conjugate poles \(p_{-}\) becomes unstable.
 
@@
 \includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(d_u/F_v\)}
+\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
 \end{subfigure}
@@
 
-In the rest of this study, rotational speeds smaller than the undamped natural frequency of the system are used (\(\Omega < \omega_0\)).
+\section{Decentralized Integral Force Feedback}
+\label{sec:org284335d}
+\label{sec:iff}
+\subsection{Force Sensors and Control Architecture}
+\label{sec:org5b8858f}
+In order to apply Decentralized Integral Force Feedback to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
+Two identical controllers \(K_F\) are added to feedback each of the sensed forces to its collocated actuator.
+The control diagram is shown in Figure \ref{fig:control_diagram_iff}.
 
-\section{Decentralized Integral Force Feedback}
-\label{sec:orge7b2b3c}
-\subsection{Force Sensors and Control Architecture}
-\label{sec:org2b4254d}
-In order to apply Decentralized Integral Force Feedback to the system, force sensors are added in series of the two actuators (Figure \ref{fig:system_iff}).
-
-\begin{figure}[htbp]
-\centering
+\begin{minipage}[t]{0.55\linewidth}
+\begin{center}
 \includegraphics[scale=1]{figs/system_iff.pdf}
-\caption{\label{fig:system_iff}System with Force Sensors in Series with the Actuators. Decentralized Integral Force Feedback is used}
-\end{figure}
+\captionof{figure}{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
+\end{center}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.40\linewidth}
+\begin{center}
+\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
+\captionof{figure}{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
+\end{center}
+\end{minipage}
 
 \subsection{Plant Dynamics}
-\label{sec:org59a4f35}
+\label{sec:orge8dea8f}
 The forces measured by the force sensors are equal to:
@@
 
-The zeros of the diagonal terms of \(\bm{G}_f\) are equal to (neglecting the damping)
+The zeros of the diagonal terms are equal to (neglecting the damping for simplicity)
 \begin{subequations}
@@
 
-However, the two real zeros \(z_c\) induces an increase of +2 of the slope without change of phase (Figure \ref{fig:plant_iff_compare_rotating_speed}).
-This represents non-minimum phase behavior.
+However for non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms which represent a non-minimum phase behavior.
+This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the magnitude experiences an increase of its slope without any change of phase.
 
-The low frequency gain, for \(\Omega < \omega_0\), is no longer zero:
+The low frequency gain of \(\bm{G}_f\) is no longer zero, and increases with the rotational speed \(\Omega\)
 \begin{equation}
 \label{low_freq_gain_iff_plan}
-  \bm{G}_{f0} = \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
+  \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
   \frac{- \Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
@@
 
-It increases with the rotational speed \(\Omega\).
+This low frequency gain can be explained as follows: a constant force induces a small displacement of the mass, which then increases the centrifugal forces measured by the force sensors.
 
@@
 \includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
-\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of \(\bm{G}_f\) for several rotational speeds \(\Omega\)}
+\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the diagonal terms of \(\bm{G}_f\) for several rotational speeds \(\Omega\)}
 \end{figure}
 
-\subsection{Decentralized Integral Force Feedback}
-\label{sec:orgf040b7e}
+\subsection{Decentralized Integral Force Feedback with Pure Integrators}
+\label{sec:org8280bcd}
+The two IFF controllers \(K_F\) are pure integrators
+\begin{equation}
+  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_F(s) = g \cdot \frac{1}{s}
+\end{equation}
+where \(g\) is a scalar value representing the gain of the controller.
 
-\begin{equation}
-  K_F(s) = g \cdot \frac{1}{s}
-\end{equation}
-
-Also, as one zero has a positive real part, the IFF control is no more unconditionally stable.
-This is due to the fact that the zeros of the plant are the poles of the closed loop system with an infinite gain.
-Thus, for some finite IFF gain, one pole will have a positive real part and the system will be unstable.
+In order to see how the controller affects the poles of the closed loop system, the Root Locus is constructed as follows.
+The poles of the closed-loop system are drawn in the complex plane as the gain \(g\) varies from \(0\) to \(\infty\) for the two controllers simultaneously.
+The closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
+The direction of increasing gains is shown by the arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
 
@@
 
-At low frequency, the gain is very large and thus no force is transmitted between the payload and the rotating stage.
-This means that at low frequency, the system is decoupled (the force sensor removed) and thus the system is unstable.
+Whereas collocated IFF is known for its guaranteed stability, which is the case here for \(\Omega = 0\), this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
+This can be seen in the Root Locus (Figure \ref{fig:root_locus_pure_iff}) where the pole corresponding to the controller is bounded to the right half plane implying closed-loop system instability.
+
+Two system modifications are proposed in the next sections to deal with this stability problem.
+Either the control law can be change (Section \ref{sec:iff_hpf}) or the mechanical system slightly modified (Section \ref{sec:iff_kp}).
 
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org5533f47}
+\label{sec:org6cc7c03}
+\label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:orge3f4cc0}
+\label{sec:org9575a34}
 \begin{equation}
+\label{eq:IFF_LHF}
   K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
@@
 \subsection{Feedback Analysis}
-\label{sec:orgd0fed6b}
+\label{sec:orgbc7c7f2}
 \begin{figure}[htbp]
@@
 \includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
-\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF, \(\Omega = 0.1 \omega_0\)}
+\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF with \(\omega_i = 0.1 \omega_0\), \(g = 2\) and \(\Omega = 0.1 \omega_0\)}
 \end{figure}
 
+As shown in Figure \ref{fig:root_locus_modified_iff}, the poles of the closed loop system are stable for \(g < g_\text{max}\)
 \begin{equation}
-  g_\text{max} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right) \label{eq:iff_gmax}
+  g_{\text{max}} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right)
 \end{equation}
@@
 
-\subsection{Optimal Cut-Off Frequency}
-\label{sec:org4740973}
+\subsection{Optimal Control Parameters}
+\label{sec:org6e31c47}
+
+Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}, the gain \(g\) and the frequency of the pole \(\omega_i\).
+
+Root Locus plots for several \(\omega_i\) are shown in Figure \ref{fig:root_locus_wi_modified_iff}.
 
@@
 \end{figure}
+
+The optimal values of \(\omega_i\) and \(g\) may be considered as the values for which the closed-loop poles are equally damped.
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org1b53815}
+\label{sec:org8681b34}
+\label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org3a8c426}
+\label{sec:org0dff3a7}
+Stiffness can be added in parallel to the force sensor to counteract the negative stiffness due to centrifugal forces.
+If the added stiffness is higher than the maximum negative stiffness, then the poles of the IFF damped system will stay in the (stable) right half-plane.
+
 \begin{figure}[htbp]
@@
 \includegraphics[scale=1]{figs/system_parallel_springs.pdf}
-\caption{\label{fig:system_parallel_springs}System with added springs in parallel with the actuators}
+\label{fig:system_parallel_springs}
 \end{figure}
 
+The forces measured by the force sensors are equal to:
+\begin{equation}
+\label{eq:measured_force_kp}
+  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
+  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k_a)
+  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
+\end{equation}
+
+This could represent a system where
+
 \subsection{Plant Dynamics}
-\label{sec:orgf26a6f4}
+\label{sec:orgc00a18e}
 
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org6a55282}
+\label{sec:orgdbd366f}
 \begin{equation}
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org358dd73}
+\label{sec:org8a2fab9}
 \begin{figure}[htbp]
@@
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:org3cc6699}
+\label{sec:orgf0c901c}
+\label{sec:comparison}
 \subsection{Physical Comparison}
-\label{sec:orgc34b986}
+\label{sec:orgb81fedd}
 
 \subsection{Attainable Damping}
-\label{sec:org993a1d7}
+\label{sec:org9975e71}
 
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org0674052}
-
+\label{sec:org0a87dc5}
 \begin{figure}[htbp]
@@
 \section{Conclusion}
-\label{sec:orgba18ca5}
+\label{sec:orgcf2c965}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org4c68ce2}
+\label{sec:orga6bcde3}
 

### 2020-07-01 paper/paper.tex
Shrinked two figures to make them subfigures

@@
-% Created 2020-07-01 mer. 10:02
+% Created 2020-07-01 mer. 10:48
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org38db2d2}
+\label{sec:org6a18e43}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:orgd0419a7}
+\label{sec:orgd72985f}
 \label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:org4c3a41a}
+\label{sec:org617200e}
 In order to study how the rotation of a positioning platforms does affect the use of force feedback, a simple model of an X-Y positioning stage on top of a rotating stage is developed.
@@
 \subsection{Equations of Motion}
-\label{sec:orga2d4956}
+\label{sec:orgb84906d}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org16be790}
+\label{sec:orgda6662b}
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the transfer function matrix from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained:
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:org0ed334c}
+\label{sec:org006f494}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org284335d}
+\label{sec:org586ab0c}
 \label{sec:iff}
 \subsection{Force Sensors and Control Architecture}
-\label{sec:org5b8858f}
+\label{sec:org56ae682}
 In order to apply Decentralized Integral Force Feedback to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
@@
 \subsection{Plant Dynamics}
-\label{sec:orge8dea8f}
+\label{sec:org6b43274}
 The forces measured by the force sensors are equal to:
@@
 \subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:org8280bcd}
+\label{sec:orgaedf7bc}
 The two IFF controllers \(K_F\) are pure integrators
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org6cc7c03}
+\label{sec:org34f8977}
 \label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:org9575a34}
+\label{sec:org809db54}
+In order to limit the low frequency loop gain, an high pass filter (HPF) can be added to the controller.
+The controller becomes
 \begin{equation}
 \label{eq:IFF_LHF}
-  K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
+  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
 \end{equation}
+This is equivalent as to slightly shifting to pole to the left along the real axis.
+This modification of the IFF controller is typically done to avoid saturation associated with the pure integrator \cite{preumont91_activ}.
 
 \subsection{Feedback Analysis}
-\label{sec:orgbc7c7f2}
+\label{sec:orga2d434f}
+\begin{minipage}[c]{0.45\linewidth}
+\begin{center}
+\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
+\captionof{figure}{\label{fig:loop_gain_modified_iff}Bode Plot of the loop gain for IFF with and without the HPF with, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
+\end{center}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{0.5\linewidth}
+\begin{center}
+\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
+\captionof{figure}{\label{fig:root_locus_modified_iff}Root Locus for IFF with and without the HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
+\end{center}
+\end{minipage}
+
 \begin{figure}[htbp]
@@
 \includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
-\caption{\label{fig:root_locus_modified_iff}Root Locus for IFF with and without the HPF, \(\Omega = 0.1 \omega_0\)}
+\label{fig:root_locus_modified_iff}
 \end{figure}
@@
 \subsection{Optimal Control Parameters}
-\label{sec:org6e31c47}
+\label{sec:org7cc60ca}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org8681b34}
+\label{sec:org8ffeef1}
 \label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org0dff3a7}
+\label{sec:org831f255}
 Stiffness can be added in parallel to the force sensor to counteract the negative stiffness due to centrifugal forces.
@@
 \subsection{Plant Dynamics}
-\label{sec:orgc00a18e}
+\label{sec:org98721cc}
 
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:orgdbd366f}
+\label{sec:org0b03ba2}
 \begin{equation}
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org8a2fab9}
+\label{sec:org0aa60d8}
 \begin{figure}[htbp]
@@
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:orgf0c901c}
+\label{sec:orgde2e2f0}
 \label{sec:comparison}
 \subsection{Physical Comparison}
-\label{sec:orgb81fedd}
+\label{sec:org661a4d0}
 
 \subsection{Attainable Damping}
-\label{sec:org9975e71}
+\label{sec:orgb54beda}
 
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org0a87dc5}
+\label{sec:org63e90d2}
 \begin{figure}[htbp]
@@
 \section{Conclusion}
-\label{sec:orgcf2c965}
+\label{sec:org646f615}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orga6bcde3}
+\label{sec:org7bb2645}
 

### 2020-07-01 paper/paper.tex
Add XY-Stage picture

--- 2020-07-01 paper/paper.tex
@@
-% Created 2020-07-01 mer. 10:02
+% Created 2020-07-01 mer. 14:20
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org38db2d2}
+\label{sec:org5531002}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:orgd0419a7}
+\label{sec:org35aebb5}
 \label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:org4c3a41a}
+\label{sec:org61dc9aa}
 In order to study how the rotation of a positioning platforms does affect the use of force feedback, a simple model of an X-Y positioning stage on top of a rotating stage is developed.
@@
 \subsection{Equations of Motion}
-\label{sec:orga2d4956}
+\label{sec:orgdd30881}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org16be790}
+\label{sec:org12fe22b}
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the transfer function matrix from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained:
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:org0ed334c}
+\label{sec:org5558523}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org284335d}
+\label{sec:orga42580e}
 \label{sec:iff}
 \subsection{Force Sensors and Control Architecture}
-\label{sec:org5b8858f}
+\label{sec:orgdd7381f}
 In order to apply Decentralized Integral Force Feedback to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
@@
 \subsection{Plant Dynamics}
-\label{sec:orge8dea8f}
+\label{sec:org7bc5629}
 The forces measured by the force sensors are equal to:
@@
 \subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:org8280bcd}
+\label{sec:orgbe4061b}
 The two IFF controllers \(K_F\) are pure integrators
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:org6cc7c03}
+\label{sec:orgd914f89}
 \label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:org9575a34}
+\label{sec:org9cbf657}
+In order to limit the low frequency controller gain, an high pass filter (HPF) can be added to the controller which becomes
 \begin{equation}
 \label{eq:IFF_LHF}
-  K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
+  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
 \end{equation}
 
+This is equivalent as to slightly shifting to controller pole to the left along the real axis.
+This modification of the IFF controller is typically done to avoid saturation associated with the pure integrator \cite{preumont91_activ}.
+This is however not the case in this study as it will become in the next section.
+
 \subsection{Feedback Analysis}
-\label{sec:orgbc7c7f2}
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
-\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF with \(\omega_i = 0.1 \omega_0\), \(g = 2\) and \(\Omega = 0.1 \omega_0\)}
-\end{figure}
+\label{sec:org5571d5f}
+The loop gains for an individual decentralized controller \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
+The effect of the added HPF is a limitation of the low frequency gain.
 
-As shown in Figure \ref{fig:root_locus_modified_iff}, the poles of the closed loop system are stable for \(g < g_\text{max}\)
+The Root Loci for the decentralized IFF with and without the HPF are displayed in Figure \ref{fig:root_locus_modified_iff}.
+With the added HPF, the poles of the closed loop system are shown to be stable up to some value of the gain \(g_\text{max}\)
 \begin{equation}
+\label{eq:gmax_iff_hpf}
   g_{\text{max}} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right)
 \end{equation}
+This gain also corresponds as to when the low frequency loop gain reaches one.
 
-\begin{figure}[htbp]
-\centering
+\begin{minipage}[b]{0.45\linewidth}
+\begin{center}
+\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
+\captionof{figure}{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
+\end{center}
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.5\linewidth}
+\begin{center}
 \includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
-\caption{\label{fig:root_locus_modified_iff}Root Locus for IFF with and without the HPF, \(\Omega = 0.1 \omega_0\)}
-\end{figure}
+\captionof{figure}{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
+\end{center}
+\end{minipage}
 
 \subsection{Optimal Control Parameters}
-\label{sec:org6e31c47}
+\label{sec:org5313add}
 
-Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}, the gain \(g\) and the frequency of the pole \(\omega_i\).
+Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}: the gain \(g\) and the location of the pole \(\omega_i\).
+The optimal values of \(\omega_i\) and \(g\) are considered as the values for which the damping of all the closed-loop poles are simultaneously maximized.
 
-Root Locus plots for several \(\omega_i\) are shown in Figure \ref{fig:root_locus_wi_modified_iff}.
+The Root Loci for several \(\omega_i\) are shown in Figure \ref{fig:root_locus_wi_modified_iff}.
+It is shown that even tough small \(\omega_i\) seems to allow more damping to be added to the system resonances, the control gain \(g\) may be limited to small values due to Eq.
+\eqref{eq:gmax_iff_hpf}.
 
@@
 
-The optimal values of \(\omega_i\) and \(g\) may be considered as the values for which the closed-loop poles are equally damped.
-
 \begin{figure}[htbp]
@@
 \includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
-\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of the HPF cut-off frequency.
+\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of the ratio \(\omega_i/\omega_0\).
 Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org8681b34}
+\label{sec:org9bf4afa}
 \label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org0dff3a7}
-Stiffness can be added in parallel to the force sensor to counteract the negative stiffness due to centrifugal forces.
-If the added stiffness is higher than the maximum negative stiffness, then the poles of the IFF damped system will stay in the (stable) right half-plane.
+\label{sec:org7253a28}
+As was shown in the previous sections, the instability when using Decentralized IFF for rotating positioning platforms is due to Gyroscopic effects, more precisely to the negative stiffnesses induced by centrifugal forces.
+The idea in this section is to include additional springs in parallel with the force sensors to counteract the negative stiffness due to centrifugal forces.
+Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
 
-\begin{figure}[htbp]
-\centering
+\begin{minipage}[t]{0.55\linewidth}
+\begin{center}
 \includegraphics[scale=1]{figs/system_parallel_springs.pdf}
-\label{fig:system_parallel_springs}
-\end{figure}
+\captionof{figure}{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
+\end{center}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.40\linewidth}
+\begin{center}
+\includegraphics[width=\linewidth]{figs/cedrat_xy25xs.png}
+\captionof{figure}{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat-Technology)}
+\end{center}
+\end{minipage}
 
@@
 
-\subsection{Plant Dynamics}
-\label{sec:orgc00a18e}
+\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
+\label{sec:orgf4cd5ba}
 
@@
 
-\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:orgdbd366f}
 \begin{equation}
@@
 \end{equation}
+
+If the added stiffness is higher than the maximum negative stiffness, then the poles of the IFF damped system will stay in the (stable) right half-plane.
 
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org8a2fab9}
+\label{sec:orgeadc68d}
 \begin{figure}[htbp]
@@
 \section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:orgf0c901c}
+\label{sec:org21311c2}
 \label{sec:comparison}
 \subsection{Physical Comparison}
-\label{sec:orgb81fedd}
+\label{sec:orgff9353a}
 
 \subsection{Attainable Damping}
-\label{sec:org9975e71}
+\label{sec:org43e21e8}
 
@@
 \subsection{Transmissibility and Compliance}
-\label{sec:org0a87dc5}
+\label{sec:org4cd8990}
 \begin{figure}[htbp]
@@
 \section{Conclusion}
-\label{sec:orgcf2c965}
+\label{sec:org2c33141}
 \label{sec:conclusion}
 
+MIMO approach to study the coupling effects?
+
 \section*{Acknowledgment}
-\label{sec:orga6bcde3}
+\label{sec:org33821c1}
 

### 2020-07-01 paper/paper.tex
Finish first pass on all sections

@@
-% Created 2020-07-01 mer. 14:20
+% Created 2020-07-01 mer. 16:58
 % Intended LaTeX compiler: pdflatex
@@
 \title{Active Damping of Rotating Positioning Platforms using Force Feedback}
-\hypersetup{
- pdfauthor={},
- pdftitle={Active Damping of Rotating Positioning Platforms using Force Feedback},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
- pdflang={English}}
 \begin{document}
@@
 \section{Introduction}
-\label{sec:org5531002}
+\label{sec:org5846940}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org35aebb5}
+\label{sec:orge0b9fb2}
 \label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:org61dc9aa}
+\label{sec:org906209e}
 In order to study how the rotation of a positioning platforms does affect the use of force feedback, a simple model of an X-Y positioning stage on top of a rotating stage is developed.
-
 The model is schematically represented in Figure \ref{fig:system} and forms the simplest system where gyroscopic forces can be studied.
@@
 \subsection{Equations of Motion}
-\label{sec:orgdd30881}
+\label{sec:org8561102}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org12fe22b}
-To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the transfer function matrix from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained:
-\begin{equation}
-\label{eq:Gd_mimo_tf}
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
-with \(\bm{G}_d\) a \(2 \times 2\) transfer function matrix
-\begin{equation}
-\label{eq:Gd_m_k_c}
-  \bm{G}_{d} =
+\label{sec:org2ee1be9}
+To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
+\begin{align}
+  \begin{bmatrix} d_u \\ d_v \end{bmatrix} &= \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gd_mimo_tf} \\
+  \bm{G}_{d} &=
   \begin{bmatrix}
@@
     \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}
-  \end{bmatrix}
-\end{equation}
+  \end{bmatrix} \label{eq:Gd_m_k_c}
+\end{align}
 
@@
 For all the numerical analysis in this study, \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
-
 Even tough no system with such parameters will be encountered in practice, conclusions will be drawn relative to these parameters such that they can be generalized to any other parameter.
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:org5558523}
+\label{sec:orga228a88}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 The bode plot of these two distinct terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
-
 It is confirmed that the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orga42580e}
+\label{sec:orgd6c59cc}
 \label{sec:iff}
 \subsection{Force Sensors and Control Architecture}
-\label{sec:orgdd7381f}
+\label{sec:orgcc446a6}
 In order to apply Decentralized Integral Force Feedback to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
@@
 \subsection{Plant Dynamics}
-\label{sec:org7bc5629}
+\label{sec:org8c9a16a}
 The forces measured by the force sensors are equal to:
@@
 This low frequency gain can be explained as follows: a constant force induces a small displacement of the mass, which then increases the centrifugal forces measured by the force sensors.
-
 \begin{figure}[htbp]
@@
 \subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:orgbe4061b}
+\label{sec:org99fa3c9}
 The two IFF controllers \(K_F\) are pure integrators
 \begin{equation}
+\label{eq:Kf_pure_int}
   \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_F(s) = g \cdot \frac{1}{s}
@@
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:orgd914f89}
+\label{sec:orgcdcaab1}
 \label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:org9cbf657}
+\label{sec:org9d35c60}
 In order to limit the low frequency controller gain, an high pass filter (HPF) can be added to the controller which becomes
@@
 \subsection{Feedback Analysis}
-\label{sec:org5571d5f}
+\label{sec:org54e6be5}
 The loop gains for an individual decentralized controller \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
@@
 \subsection{Optimal Control Parameters}
-\label{sec:org5313add}
+\label{sec:org9dc1d7f}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org9bf4afa}
+\label{sec:orgfb6b0e8}
 \label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org7253a28}
+\label{sec:org4af80eb}
+
 As was shown in the previous sections, the instability when using Decentralized IFF for rotating positioning platforms is due to Gyroscopic effects, more precisely to the negative stiffnesses induced by centrifugal forces.
-The idea in this section is to include additional springs in parallel with the force sensors to counteract the negative stiffness due to centrifugal forces.
+The idea in this section is to include additional springs in parallel with the force sensors to counteract this negative stiffness.
 Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
+
+Such system could consist of additional springs, or it could also be
+This could represent a system where \ref{fig:cedrat_xy25xs}.
+The use of such amplified piezoelectric actuator for IFF is discussed in  \cite{souleille18_concep_activ_mount_space_applic}.
 
@@
 \includegraphics[width=\linewidth]{figs/cedrat_xy25xs.png}
-\captionof{figure}{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat-Technology)}
+\captionof{figure}{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
 \end{center}
@@
 
-The forces measured by the force sensors are equal to:
+\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
+\label{sec:org47b3420}
+The forces measured by the sensors are equal to
 \begin{equation}
@@
 
-This could represent a system where
-
-\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:orgf4cd5ba}
-
-We define an adimensional parameter \(\alpha\), \(0 \le \alpha < 1\), that describes the proportion of the stiffness in parallel with the actuator and force sensor:
+A scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
 \begin{subequations}
@@
 \end{subequations}
+Note that the overall stiffness \(k = k_a + k_p\) is kept constant.
 
-The overall stiffness \(k\) stays constant:
-\begin{equation}
-  k = k_a + k_p
-\end{equation}
-
+The equations of motion are derived and transformed in the Laplace domain
 \begin{equation}
@@
 \end{equation}
-
+with \(\bm{G}_k\) a \(2 \times 2\) transfer function matrix
 \begin{equation}
@@
 
+Comparing \(\bm{G}_k\) \eqref{eq:Gk} with \(\bm{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
+
+The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros for
 \begin{equation}
   \begin{aligned}
-    \alpha > \frac{\Omega^2}{{\omega_0}^2} \\
-    \Leftrightarrow k_p > m \Omega^2
+    \alpha &> \frac{\Omega^2}{{\omega_0}^2} \\
+    \Leftrightarrow k_p &> m \Omega^2
   \end{aligned}
@@
 
-If the added stiffness is higher than the maximum negative stiffness, then the poles of the IFF damped system will stay in the (stable) right half-plane.
-
+Thus, if the added parallel stiffness \(k_p\) is higher than the negative stiffness induced by centrifugal forces \(m \Omega^2\), the direct dynamics from actuator to force sensor will show minimum phase behavior.
+This is confirmed by the Bode plot in Figure \ref{fig:plant_iff_kp}.
 \begin{figure}[htbp]
@@
 \end{figure}
+
+Figure \ref{fig:root_locus_iff_kp} shows Root Loci plots for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\) when \(K_F\) is a pure integrator \eqref{eq:Kf_pure_int}.
+It is shown that if the added stiffness is higher than the maximum negative stiffness, the poles of the closed-loop system stay in the (stable) right half-plane, and hence the unconditional stability of IFF is recovered.
 
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:orgeadc68d}
+\label{sec:orgbfbcf95}
+Figure \ref{fig:root_locus_iff_kps} shows Root Loci plots for several parallel stiffnesses \(k_p > m \Omega^2\).
+It is shown that large parallel stiffness \(k_p\) reduces the attainable damping.
+This can be explained by the fact that as the parallel stiffnesses increases, the transmission zeros are closer to the poles.
+As explained in \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the attainable damping is generally proportional to the distance between the poles and zeros.
+The frequency of the transmission zeros of the system are increasing with the fraction used as parallel stiffness \(k_p\).
+
+For any \(k_p > m \Omega^2\), the control gain \(g\) can be tuned such that the maximum simultaneous damping is added to the resonances of the system as shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\).
+
 \begin{figure}[htbp]
@@
 \includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
-\caption{\label{fig:root_locus_iff_kps} Three values of \(k_p\)}
+\caption{\label{fig:root_locus_iff_kps} Comparison of three parallel stiffnesses \(k_p\)}
 \end{subfigure}
@@
 \includegraphics[width=\linewidth]{figs/root_locus_opt_gain_iff_kp.pdf}
-\caption{\label{fig:root_locus_opt_gain_iff_kp} \(k_p = 5 m \Omega^2\), optimal damping is shown}
+\caption{\label{fig:root_locus_opt_gain_iff_kp} \(k_p = 5 m \Omega^2\), optimal damping \(\xi_\text{opt}\) is shown}
 \end{subfigure}
-\caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness is used, \(\Omega = 0.1 \omega_0\)}
+\caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness \(k_p\) is added, \(\Omega = 0.1 \omega_0\)}
 \centering
@@
 
-\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
-\label{sec:org21311c2}
+\section{Comparison of the Proposed Modification to Decentralized Integral Force Feedback for Rotating Positioning Stages}
+\label{sec:org25de90d}
 \label{sec:comparison}
-\subsection{Physical Comparison}
-\label{sec:orgff9353a}
+The two proposed modification to the decentralized IFF for rotating positioning stages are now compared.
+Two modification to the decentralized IFF for rotating positioning stages have been proposed.
 
-\subsection{Attainable Damping}
-\label{sec:org43e21e8}
+The first modification concerns the controller.
+It consists of adding an high pass filter to \(K_F\) \eqref{eq:IFF_LHF}.
+This allows the system to be stable for gains up to \(g_\text{max}\) \eqref{eq:gmax_iff_hpf}.
+
+The second proposed modification concerns the mechanical system.
+If springs are added in parallel to the actuators and force sensors with a stiffness \(k_p > m \Omega^2\), decentralized IFF can be applied with unconditional stability.
+
+These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
+For the following comparisons, the high pass cut-off frequency is set to \(\omega_i = 0.1 \omega_0\) and the parallel stiffness is \(k_p = 5 m \Omega^2\).
+\subsection{Comparison of the Attainable Damping}
+\label{sec:orgd307a58}
+Figure \ref{fig:comp_root_locus} shows to Root Locus plots for the two proposed IFF techniques.
+The maximum added damping is very similar for both techniques and are reached for \(g_\text{opt} \approx 2\) in both cases.
 
@@
 \includegraphics[scale=1]{figs/comp_root_locus.pdf}
-\caption{\label{fig:comp_root_locus}Root Locus for the three proposed decentralized active damping techniques: IFF with HFP, IFF with parallel springs, and relative DVF, \(\Omega = 0.1 \omega_0\)}
+\caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
 \end{figure}
 
-\subsection{Transmissibility and Compliance}
-\label{sec:org4cd8990}
+\subsection{Comparison Transmissibility and Compliance}
+\label{sec:orgb48201a}
+The two proposed techniques are now compared in terms of closed-loop compliance and transmissibility.
+
+The compliance is defined as the transfer function from external forces applied to the payload to the displacement of the payload in an inertial frame.
+The transmissibility is the dynamics from the displacement of the rotating stage to the displacement of the payload.
+It is used to characterize how much vibration of the rotating stage is transmitted to the payload.
+
+The two techniques are also compared with passive damping (Figure \ref{fig:system}) with \(c\) tuned to critically damp the resonance when \(\Omega = 0\)
+\begin{equation}
+  c_\text{crit} = 2 \sqrt{k m}
+\end{equation}
+
+Very similar results are obtained for both techniques as shown in Figures \ref{fig:comp_compliance} and \ref{fig:comp_transmissibility}.
+It is also confirmed that these techniques can significantly damp the system's resonances.
+
+Compared to passive damping, the two techniques degrades the compliance at low frequency (Figure \ref{fig:comp_compliance}).
+They however do not degrades the transmissibility as high frequency as its the case with passive damping (Figure \ref{fig:comp_transmissibility})
+
 \begin{figure}[htbp]
@@
 \includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
-\caption{\label{fig:comp_compliance} Transmissibility}
+\caption{\label{fig:comp_compliance} Compliance}
 \end{subfigure}
@@
 \includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
-\caption{\label{fig:comp_transmissibility} Compliance}
+\caption{\label{fig:comp_transmissibility} Transmissibility}
 \end{subfigure}
@@
 \section{Conclusion}
-\label{sec:org2c33141}
+\label{sec:orgf8ee171}
 \label{sec:conclusion}
 
-MIMO approach to study the coupling effects?
-
 \section*{Acknowledgment}
-\label{sec:org33821c1}
+\label{sec:org66fd2b5}
+This research benefited from a FRIA grant from the French Community of Belgium.
 

### 2020-07-01 paper/paper.tex
Rework section 3

@@
-% Created 2020-07-01 mer. 16:58
+% Created 2020-07-01 mer. 18:51
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org5846940}
+\label{sec:orgde2fe58}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:orge0b9fb2}
+\label{sec:org3a70473}
 \label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:org906209e}
-In order to study how the rotation of a positioning platforms does affect the use of force feedback, a simple model of an X-Y positioning stage on top of a rotating stage is developed.
+\label{sec:org76d65cf}
+In order to study how the rotation of a positioning platforms does affect the use of integral force feedback, a model of an XY positioning stage on top of a rotating stage is developed.
 The model is schematically represented in Figure \ref{fig:system} and forms the simplest system where gyroscopic forces can be studied.
@@
 
-The parallel X-Y positioning stage consists of two orthogonal actuators represented by three elements in parallel:
-\begin{itemize}
-\item a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\)
-\item a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\)
-\item an ideal force source \(F_u, F_v\)
-\end{itemize}
+The parallel XY positioning stage consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
+A payload with a mass \(m\) in \(\si{\kilo\gram}\) is mounted on the (rotating) XY stage.
 
-A payload with a mass \(m\) in \(\si{\kilo\gram}\) is mounted on the rotating X-Y stage.
-
-Two reference frames are used:
-\begin{itemize}
-\item an inertial frame \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\)
-\item a uniform rotating frame \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\) rigidly fixed on top of the rotating stage. \(\vec{i}_w\) is aligned with the rotation axis
-\end{itemize}
-
-The position of the payload is represented by \((d_u, d_v)\) expressed in the rotating frame.
+Two reference frames are used: an inertial frame \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\) and a uniform rotating frame \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\) rigidly fixed on top of the rotating stage with \(\vec{i}_w\) aligned with the rotation axis.
+The position of the payload is represented by \((d_u, d_v, 0)\) expressed in the rotating frame.
 
@@
 \subsection{Equations of Motion}
-\label{sec:org8561102}
+\label{sec:org118fe28}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 
-The constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is here disregarded as it is imposed by the rotating stage.
+The constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is here disregarded as it is imposed by the ideal rotating stage.
 \begin{subequations}
@@
 
-Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} gives the two coupled differential equations:
+Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} gives two coupled differential equations
 \begin{subequations}
@@
 
-The constant rotation of the system induces two Gyroscopic effects:
+The uniform rotation of the system induces two Gyroscopic effects as shown in Eq. \eqref{eq:eom_coupled}:
 \begin{itemize}
-\item Centrifugal forces: that can been seen as added negative stiffness along \(\vec{i}_u\) and \(\vec{i}_v\)
+\item Centrifugal forces: that can been seen as added negative stiffness \(- m \Omega^2\) along \(\vec{i}_u\) and \(\vec{i}_v\)
 \item Coriolis Forces: that couples the motion in the two orthogonal directions
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org2ee1be9}
+\label{sec:org25fe13e}
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
@@
 
-To simply the analysis, the following change of variable is performed:
-\begin{itemize}
-\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Undamped natural frequency of the mass-spring system in \(\si{\radian/\s}\)
-\item \(\xi = \frac{c}{2 \sqrt{k m}}\): Damping ratio
-\end{itemize}
+To simplify the analysis, the undamped natural frequency \(\omega_0\) and the damping ratio \(\xi\) are used
+\begin{subequations}
+  \begin{align}
+    \omega_0 &= \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second} \\
+    \xi &= \frac{c}{2 \sqrt{k m}}
+  \end{align}
+\end{subequations}
 
-The transfer function matrix \eqref{eq:Gd_m_k_c} becomes equal to
+The transfer function matrix \(\bm{G}_d\) \eqref{eq:Gd_m_k_c} becomes equal to
 \begin{equation}
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:orga228a88}
+\label{sec:org20292fd}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 
-In the rest of this study, rotational speeds smaller than the undamped natural frequency of the system are used (\(\Omega < \omega_0\)).
+In the rest of this study, rotational speeds smaller than the undamped natural frequency of the system are assumed (\(\Omega < \omega_0\)).
 
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgd6c59cc}
+\label{sec:orgfbbc9cb}
 \label{sec:iff}
 \subsection{Force Sensors and Control Architecture}
-\label{sec:orgcc446a6}
-In order to apply Decentralized Integral Force Feedback to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
-Two identical controllers \(K_F\) are added to feedback each of the sensed forces to its collocated actuator.
-The control diagram is shown in Figure \ref{fig:control_diagram_iff}.
+\label{sec:org3fd01aa}
+In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
+As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
+The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.
 
@@
 \subsection{Plant Dynamics}
-\label{sec:org8c9a16a}
-The forces measured by the force sensors are equal to:
+\label{sec:orgf93dde0}
+The forces measured by the two force sensors are equal to
 \begin{equation}
@@
 
-Re-injecting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields:
+Re-injecting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
 \begin{equation}
@@
 
-The zeros of the diagonal terms are equal to (neglecting the damping for simplicity)
+The zeros of the diagonal terms of \(\bm{G}_f\) are equal to (neglecting the damping for simplicity)
 \begin{subequations}
@@
 
-The frequency of the two complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} is between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
-This is the expected behavior of a collocated pair of actuator and sensor.
+It can be easily shown that the frequency of the two complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
 
-However for non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms which represent a non-minimum phase behavior.
+For non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms inducing a non-minimum phase behavior.
 This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the magnitude experiences an increase of its slope without any change of phase.
 
-The low frequency gain of \(\bm{G}_f\) is no longer zero, and increases with the rotational speed \(\Omega\)
+Similarly, the low frequency gain of \(\bm{G}_f\) is no longer zero and increases with the rotational speed \(\Omega\)
 \begin{equation}
@@
   \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
-  \frac{- \Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
-  0  & \frac{- \Omega^2}{{\omega_0}^2 - \Omega^2}
+  \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
+  0  & \frac{\Omega^2}{{\omega_0}^2 - \Omega^2}
 \end{bmatrix}
@@
 
-This low frequency gain can be explained as follows: a constant force induces a small displacement of the mass, which then increases the centrifugal forces measured by the force sensors.
+This low frequency gain can be explained as follows: a constant force \(F_u\) induces a small displacement of the mass \(d_u = \frac{F_u}{k - m\Omega^2}\), which increases the centrifugal force \(m\Omega^2d_u = \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} F_u\) which is measured by the force sensors.
+
 \begin{figure}[htbp]
@@
 \subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:org99fa3c9}
-The two IFF controllers \(K_F\) are pure integrators
+\label{sec:orgfde6b0e}
+The two IFF controllers \(K_F\) consist of a pure integrator
 \begin{equation}
@@
 \end{equation}
-where \(g\) is a scalar value representing the gain of the controller.
+where \(g\) is a scalar representing the gain of the controller.
 
-In order to see how the controller affects the poles of the closed loop system, the Root Locus is constructed as follows.
-The poles of the closed-loop system are drawn in the complex plane as the gain \(g\) varies from \(0\) to \(\infty\) for the two controllers simultaneously.
-The closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
-The direction of increasing gains is shown by the arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
+In order to see how the IFF affects the poles of the closed loop system, a Root Locus (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the gain \(g\) varies from \(0\) to \(\infty\) for the two controllers simultaneously.
+As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
+The direction of increasing gain is indicated by arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
 
@@
 \includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
-\caption{\label{fig:root_locus_pure_iff}Root Locus for the Decentralized Integral Force Feedback}
+\caption{\label{fig:root_locus_pure_iff}Root Locus for the Decentralized Integral Force Feedback for several rotating speeds \(\Omega\)}
 \end{figure}
 
-Whereas collocated IFF is known for its guaranteed stability, which is the case here for \(\Omega = 0\), this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
+Whereas collocated IFF is usually associated with unconditional stability \cite{preumont91_activ}, this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
 This can be seen in the Root Locus (Figure \ref{fig:root_locus_pure_iff}) where the pole corresponding to the controller is bounded to the right half plane implying closed-loop system instability.
 
-Two system modifications are proposed in the next sections to deal with this stability problem.
-Either the control law can be change (Section \ref{sec:iff_hpf}) or the mechanical system slightly modified (Section \ref{sec:iff_kp}).
+In order to apply Decentralized IFF on rotating positioning stages, two solutions are proposed to deal with this instability problem.
+The first one consists of slightly modifying the control law (Section \ref{sec:iff_hpf}) while the second one consists of adding springs in parallel with the force sensors (Section \ref{sec:iff_kp}).
 
 \section{Integral Force Feedback with High Pass Filters}
-\label{sec:orgcdcaab1}
+\label{sec:org58cf10c}
 \label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:org9d35c60}
+\label{sec:org24c412f}
 In order to limit the low frequency controller gain, an high pass filter (HPF) can be added to the controller which becomes
@@
 \subsection{Feedback Analysis}
-\label{sec:org54e6be5}
+\label{sec:org6529021}
 The loop gains for an individual decentralized controller \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
@@
 \subsection{Optimal Control Parameters}
-\label{sec:org9dc1d7f}
+\label{sec:org8e0597b}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orgfb6b0e8}
+\label{sec:orga467957}
 \label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org4af80eb}
+\label{sec:org298d71d}
 
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org47b3420}
+\label{sec:org31339f0}
 The forces measured by the sensors are equal to
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:orgbfbcf95}
+\label{sec:org3826010}
 Figure \ref{fig:root_locus_iff_kps} shows Root Loci plots for several parallel stiffnesses \(k_p > m \Omega^2\).
@@
 \section{Comparison of the Proposed Modification to Decentralized Integral Force Feedback for Rotating Positioning Stages}
-\label{sec:org25de90d}
+\label{sec:orga5dc79a}
 \label{sec:comparison}
@@
 \subsection{Comparison of the Attainable Damping}
-\label{sec:orgd307a58}
+\label{sec:org6e1b03e}
 Figure \ref{fig:comp_root_locus} shows to Root Locus plots for the two proposed IFF techniques.
@@
 \subsection{Comparison Transmissibility and Compliance}
-\label{sec:orgb48201a}
+\label{sec:orga92e362}
 The two proposed techniques are now compared in terms of closed-loop compliance and transmissibility.
@@
 \section{Conclusion}
-\label{sec:orgf8ee171}
+\label{sec:org617679b}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org66fd2b5}
+\label{sec:orgc1771f7}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-02 paper/paper.tex
Finish reworking section 3

@@
-% Created 2020-07-01 mer. 18:51
+% Created 2020-07-02 jeu. 09:22
 % Intended LaTeX compiler: pdflatex
@@
 \title{Active Damping of Rotating Positioning Platforms using Force Feedback}
+\hypersetup{
+ pdfauthor={},
+ pdftitle={Active Damping of Rotating Positioning Platforms using Force Feedback},
+ pdfkeywords={},
+ pdfsubject={},
+ pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
+ pdflang={English}}
 \begin{document}
@@
 \section{Introduction}
-\label{sec:orgde2fe58}
+\label{sec:org7e0661e}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org3a70473}
+\label{sec:org526efa7}
 \label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:org76d65cf}
+\label{sec:orgf882853}
 In order to study how the rotation of a positioning platforms does affect the use of integral force feedback, a model of an XY positioning stage on top of a rotating stage is developed.
+
 The model is schematically represented in Figure \ref{fig:system} and forms the simplest system where gyroscopic forces can be studied.
@@
 \subsection{Equations of Motion}
-\label{sec:org118fe28}
+\label{sec:org54d120d}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org25fe13e}
+\label{sec:org13cedeb}
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
@@
 For all the numerical analysis in this study, \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
+
 Even tough no system with such parameters will be encountered in practice, conclusions will be drawn relative to these parameters such that they can be generalized to any other parameter.
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:org20292fd}
+\label{sec:org859b848}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 The bode plot of these two distinct terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
+
 It is confirmed that the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgfbbc9cb}
+\label{sec:org8e753fb}
 \label{sec:iff}
 \subsection{Force Sensors and Control Architecture}
-\label{sec:org3fd01aa}
+\label{sec:org536426c}
 In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
@@
 \subsection{Plant Dynamics}
-\label{sec:orgf93dde0}
+\label{sec:orgffd14ec}
 The forces measured by the two force sensors are equal to
@@
 
-This low frequency gain can be explained as follows: a constant force \(F_u\) induces a small displacement of the mass \(d_u = \frac{F_u}{k - m\Omega^2}\), which increases the centrifugal force \(m\Omega^2d_u = \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} F_u\) which is measured by the force sensors.
+This low frequency gain can be explained as follows: a constant force \(F_u\) induces a small displacement of the mass \(d_u = \frac{F_u}{k - m\Omega^2}\), which increases the centrifugal force \(m\Omega^2d_u = \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} F_u\) which is then measured by the force sensors.
 
@@
 \subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:orgfde6b0e}
+\label{sec:org07bf4ec}
 The two IFF controllers \(K_F\) consist of a pure integrator
@@
 
+Physically, this can be explained by realizing that below some frequency, the loop gain being very large, the decentralized IFF effectively decouples the payload from the XY stage.
+Moreover, the payload experiences centrifugal forces, which can be modeled by negative stiffnesses pulling it away from the rotation axis rendering the system unstable, hence the poles in the right half plane.
+
 In order to apply Decentralized IFF on rotating positioning stages, two solutions are proposed to deal with this instability problem.
@@
 
-\section{Integral Force Feedback with High Pass Filters}
-\label{sec:org58cf10c}
+\section{Integral Force Feedback with High Pass Filter}
+\label{sec:org122be2f}
 \label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:org24c412f}
+\label{sec:orgcbcee98}
 In order to limit the low frequency controller gain, an high pass filter (HPF) can be added to the controller which becomes
@@
 \subsection{Feedback Analysis}
-\label{sec:org6529021}
+\label{sec:orgfee3532}
 The loop gains for an individual decentralized controller \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
@@
 \subsection{Optimal Control Parameters}
-\label{sec:org8e0597b}
+\label{sec:org0971873}
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orga467957}
+\label{sec:orgef66bd9}
 \label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org298d71d}
+\label{sec:org561caf7}
 
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org31339f0}
+\label{sec:org64ab164}
 The forces measured by the sensors are equal to
@@
 This is confirmed by the Bode plot in Figure \ref{fig:plant_iff_kp}.
+
 \begin{figure}[htbp]
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org3826010}
+\label{sec:org8d24b66}
 Figure \ref{fig:root_locus_iff_kps} shows Root Loci plots for several parallel stiffnesses \(k_p > m \Omega^2\).
@@
 \section{Comparison of the Proposed Modification to Decentralized Integral Force Feedback for Rotating Positioning Stages}
-\label{sec:orga5dc79a}
+\label{sec:orgc33a2c0}
 \label{sec:comparison}
@@
 \subsection{Comparison of the Attainable Damping}
-\label{sec:org6e1b03e}
+\label{sec:org7077499}
 Figure \ref{fig:comp_root_locus} shows to Root Locus plots for the two proposed IFF techniques.
@@
 \subsection{Comparison Transmissibility and Compliance}
-\label{sec:orga92e362}
+\label{sec:org4ef5531}
 The two proposed techniques are now compared in terms of closed-loop compliance and transmissibility.
@@
 \section{Conclusion}
-\label{sec:org617679b}
+\label{sec:org340aa08}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orgc1771f7}
+\label{sec:orge888fc9}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-02 paper/paper.tex
Reworked sections 5 and 6

@@
-% Created 2020-07-02 jeu. 09:22
+% Created 2020-07-02 jeu. 16:30
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org7e0661e}
+\label{sec:org7ce36f4}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org526efa7}
+\label{sec:org1767f3e}
 \label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:orgf882853}
+\label{sec:org3d795b1}
 In order to study how the rotation of a positioning platforms does affect the use of integral force feedback, a model of an XY positioning stage on top of a rotating stage is developed.
@@
 \subsection{Equations of Motion}
-\label{sec:org54d120d}
+\label{sec:orgeda87e3}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org13cedeb}
+\label{sec:org133b2f9}
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:org859b848}
+\label{sec:orgd6473a3}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org8e753fb}
+\label{sec:org9704fad}
 \label{sec:iff}
 \subsection{Force Sensors and Control Architecture}
-\label{sec:org536426c}
+\label{sec:orgf2a5a4d}
 In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
@@
 \subsection{Plant Dynamics}
-\label{sec:orgffd14ec}
+\label{sec:org5e54ed9}
 The forces measured by the two force sensors are equal to
@@
 \subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:org07bf4ec}
+\label{sec:org8461ad2}
+\label{sec:iff_pure_int}
 The two IFF controllers \(K_F\) consist of a pure integrator
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:org122be2f}
+\label{sec:orgcd3018b}
 \label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:orgcbcee98}
-In order to limit the low frequency controller gain, an high pass filter (HPF) can be added to the controller which becomes
+\label{sec:org256e76b}
+As was just explained, the instability when using IFF with pure integrators comes from the low frequency gain.
+
+In order to limit the low frequency controller gain, an high pass filter (HPF) can be added to the controller
 \begin{equation}
@@
 This is equivalent as to slightly shifting to controller pole to the left along the real axis.
+
 This modification of the IFF controller is typically done to avoid saturation associated with the pure integrator \cite{preumont91_activ}.
-This is however not the case in this study as it will become in the next section.
+This is however not the case in this study as it will become clear in the next section.
 
 \subsection{Feedback Analysis}
-\label{sec:orgfee3532}
-The loop gains for an individual decentralized controller \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
-The effect of the added HPF is a limitation of the low frequency gain.
+\label{sec:org6765624}
+The loop gains for the decentralized controllers \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
+The effect of the added HPF clearly limits the low frequency gain.
 
@@
 \end{equation}
-This gain also corresponds as to when the low frequency loop gain reaches one.
+It is interesting to note that this gain \(g_{\text{max}}\) also corresponds as to when the low frequency loop gain (Figure \ref{fig:loop_gain_modified_iff}) reaches one.
 
@@
 \subsection{Optimal Control Parameters}
-\label{sec:org0971873}
+\label{sec:org122256a}
+Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
+The optimal values of \(\omega_i\) and \(g\) are here considered as the values for which the damping of all the closed-loop poles are simultaneously maximized.
 
-Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}: the gain \(g\) and the location of the pole \(\omega_i\).
-The optimal values of \(\omega_i\) and \(g\) are considered as the values for which the damping of all the closed-loop poles are simultaneously maximized.
-
-The Root Loci for several \(\omega_i\) are shown in Figure \ref{fig:root_locus_wi_modified_iff}.
+In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Loci for several \(\omega_i\) are displayed in Figure \ref{fig:root_locus_wi_modified_iff}.
 It is shown that even tough small \(\omega_i\) seems to allow more damping to be added to the system resonances, the control gain \(g\) may be limited to small values due to Eq.
@@
 
+In order to study this trade off, the attainable damping ratio \(\xi_{\text{cl}}\) is computed as a function of the ratio \(\omega_i/\omega_0\).
+The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also display and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi})r.
+
+Three regions can be observed:
+\begin{itemize}
+\item \(\frac{\omega_i}{\omega_0} < 0.02\): the added damping is limited by the maximum allowed control gain \(g_{\text{max}}\)
+\item \(0.02 < \frac{\omega_i}{\omega_0} < 0.2\): good amount of damping can be added for \(g \approx 2\)
+\item \(0.2 < \frac{\omega_i}{\omega_0}\): the added damping becomes small due to the shape of the Root Locus (Figure \ref{fig:root_locus_wi_modified_iff})
+\end{itemize}
+
 \begin{figure}[htbp]
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orgef66bd9}
+\label{sec:orgb9e95b0}
 \label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org561caf7}
-
-As was shown in the previous sections, the instability when using Decentralized IFF for rotating positioning platforms is due to Gyroscopic effects, more precisely to the negative stiffnesses induced by centrifugal forces.
-The idea in this section is to include additional springs in parallel with the force sensors to counteract this negative stiffness.
+\label{sec:org3fd6edd}
+As was explained in section \ref{sec:iff_pure_int}, the instability when using decentralized IFF for rotating positioning platforms is due to Gyroscopic effects and more precisely to the negative stiffnesses induced by centrifugal forces.
+In this section additional springs in parallel with the force sensors are added to counteract this negative stiffness.
 Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
 
-Such system could consist of additional springs, or it could also be
-This could represent a system where \ref{fig:cedrat_xy25xs}.
-The use of such amplified piezoelectric actuator for IFF is discussed in  \cite{souleille18_concep_activ_mount_space_applic}.
+Amplified piezoelectric stack actuators can also be used for such purpose where a part of the piezoelectric stack is used as an actuator while the rest is used as a force sensor \cite{souleille18_concep_activ_mount_space_applic}.
+The parallel stiffness \(k_p\) then corresponds to the amplification structure.
+An example of such system is shown in Figure \ref{fig:cedrat_xy25xs}.
 
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org64ab164}
+\label{sec:org6d160ef}
 The forces measured by the sensors are equal to
@@
 
-A scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
+In order to keep the overall stiffness \(k = k_a + k_p\) constant, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
 \begin{subequations}
@@
 \end{subequations}
-Note that the overall stiffness \(k = k_a + k_p\) is kept constant.
 
@@
 Comparing \(\bm{G}_k\) \eqref{eq:Gk} with \(\bm{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
-
-The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros for
+The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros is Eq. \ref{eq:kp_cond_cc_zeros} is verified.
 \begin{equation}
+\label{eq:kp_cond_cc_zeros}
   \begin{aligned}
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
-\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{figure}
-
 Figure \ref{fig:root_locus_iff_kp} shows Root Loci plots for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\) when \(K_F\) is a pure integrator \eqref{eq:Kf_pure_int}.
@@
 
-\begin{figure}[htbp]
-\centering
+\begin{minipage}[b]{0.42\linewidth}
+\begin{center}
+\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
+\captionof{figure}{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\end{center}
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.52\linewidth}
+\begin{center}
 \includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
-\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{figure}
+\captionof{figure}{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\end{center}
+\end{minipage}
 
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org8d24b66}
-Figure \ref{fig:root_locus_iff_kps} shows Root Loci plots for several parallel stiffnesses \(k_p > m \Omega^2\).
-It is shown that large parallel stiffness \(k_p\) reduces the attainable damping.
-This can be explained by the fact that as the parallel stiffnesses increases, the transmission zeros are closer to the poles.
-As explained in \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the attainable damping is generally proportional to the distance between the poles and zeros.
-The frequency of the transmission zeros of the system are increasing with the fraction used as parallel stiffness \(k_p\).
+\label{sec:org1c9ca29}
+Even though the parallel stiffness \(k_p\) has no impact on the open-loop poles (as the overall stiffness \(k\) stays constant), it has a large impact on the transmission zeros.
+Moreover, as the attainable damping is generally proportional to the distance between poles and zeros \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the parallel stiffness \(k_p\) is foreseen to have a large impact on the attainable damping.
 
-For any \(k_p > m \Omega^2\), the control gain \(g\) can be tuned such that the maximum simultaneous damping is added to the resonances of the system as shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\).
+To study this effect, Root Locus plots for several parallel stiffnesses \(k_p > m \Omega^2\) are shown in Figure \ref{fig:root_locus_iff_kps}.
+The frequencies of the transmission zeros of the system are increasing with the parallel stiffness \(k_p\) and the associated attainable damping is reduced.
+Therefore the parallel stiffness \(k_p\) should not be taken too high while being larger than \(m \Omega^2\) for stability reasons.
+
+For any \(k_p > m \Omega^2\), the control gain \(g\) can be tuned such that the maximum simultaneous damping \(\xi_\text{opt}\) is added to the resonances of the system.
+An example is shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\) where \(\xi_{\text{opt}} \approx 0.83\) is obtained for a control gain \(g_\text{opt} \approx 2 \omega_0\).
 
@@
 \section{Comparison of the Proposed Modification to Decentralized Integral Force Feedback for Rotating Positioning Stages}
-\label{sec:orgc33a2c0}
+\label{sec:org3dedf99}
 \label{sec:comparison}
-The two proposed modification to the decentralized IFF for rotating positioning stages are now compared.
-Two modification to the decentralized IFF for rotating positioning stages have been proposed.
+Two modifications to the decentralized IFF for rotating positioning stages have been proposed.
 
-The first modification concerns the controller.
-It consists of adding an high pass filter to \(K_F\) \eqref{eq:IFF_LHF}.
-This allows the system to be stable for gains up to \(g_\text{max}\) \eqref{eq:gmax_iff_hpf}.
+The first modification concerns the controller and consists of adding an high pass filter to \(K_F\) \eqref{eq:IFF_LHF}.
+The system was shown to be stable for gains up to \(g_\text{max}\) \eqref{eq:gmax_iff_hpf}.
 
 The second proposed modification concerns the mechanical system.
-If springs are added in parallel to the actuators and force sensors with a stiffness \(k_p > m \Omega^2\), decentralized IFF can be applied with unconditional stability.
+It was shown that if springs with a stiffness \(k_p > m \Omega^2\) are added in parallel to the actuators and force sensors, decentralized IFF can be applied with unconditional stability.
 
 These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
-For the following comparisons, the high pass cut-off frequency is set to \(\omega_i = 0.1 \omega_0\) and the parallel stiffness is \(k_p = 5 m \Omega^2\).
+For the following comparisons, the cut-off frequency for the high pass filters is set to \(\omega_i = 0.1 \omega_0\) and the parallel springs have a stiffness \(k_p = 5 m \Omega^2\).
 \subsection{Comparison of the Attainable Damping}
-\label{sec:org7077499}
+\label{sec:org173dfab}
 Figure \ref{fig:comp_root_locus} shows to Root Locus plots for the two proposed IFF techniques.
-The maximum added damping is very similar for both techniques and are reached for \(g_\text{opt} \approx 2\) in both cases.
+While the two pairs of complex conjugate open-loop poles are identical for both techniques, the transmission zeros are not.
+This means that their closed-loop behavior will differ when large control gains are used.
+
+It is interesting to note that the maximum added damping is very similar for both techniques and are reached for the same value of the gain in both cases \(g_\text{opt} \approx 2 \omega_0\).
 
@@
 \subsection{Comparison Transmissibility and Compliance}
-\label{sec:org4ef5531}
+\label{sec:org411478b}
 The two proposed techniques are now compared in terms of closed-loop compliance and transmissibility.
@@
 
-The two techniques are also compared with passive damping (Figure \ref{fig:system}) with \(c\) tuned to critically damp the resonance when \(\Omega = 0\)
+The two techniques are also compared with passive damping (Figure \ref{fig:system}) where \(c = c_\text{crit}\) is tuned to critically damp the resonance when the rotating speed is null
 \begin{equation}
@@
 
-Very similar results are obtained for both techniques as shown in Figures \ref{fig:comp_compliance} and \ref{fig:comp_transmissibility}.
-It is also confirmed that these techniques can significantly damp the system's resonances.
+Very similar results are obtained for the two proposed decentralized IFF modifications in terms of compliance (Figure \ref{fig:comp_compliance}) and transmissibility (Figure \ref{fig:comp_transmissibility}).
+It is also confirmed that these two techniques can significantly damp the system's resonances.
 
 Compared to passive damping, the two techniques degrades the compliance at low frequency (Figure \ref{fig:comp_compliance}).
-They however do not degrades the transmissibility as high frequency as its the case with passive damping (Figure \ref{fig:comp_transmissibility})
+They however do not degrades the transmissibility as high frequency as its the case with passive damping (Figure \ref{fig:comp_transmissibility}).
 
@@
 \section{Conclusion}
-\label{sec:org340aa08}
+\label{sec:orgf8a3da6}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orge888fc9}
+\label{sec:orgee9adb1}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-03 paper/paper.tex
Removed subsections

@@
-% Created 2020-07-02 jeu. 16:30
+% Created 2020-07-02 jeu. 11:48
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org7ce36f4}
+\label{sec:org2b4a2e8}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org1767f3e}
+\label{sec:org96ff785}
 \label{sec:dynamics}
 \subsection{Model of a Rotating Positioning Platform}
-\label{sec:org3d795b1}
+\label{sec:orgcceb66c}
 In order to study how the rotation of a positioning platforms does affect the use of integral force feedback, a model of an XY positioning stage on top of a rotating stage is developed.
@@
 \subsection{Equations of Motion}
-\label{sec:orgeda87e3}
+\label{sec:org69c2427}
 To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
@@
 \subsection{Transfer Functions in the Laplace domain}
-\label{sec:org133b2f9}
+\label{sec:orgb638120}
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
@@
 \subsection{System Dynamics and Campbell Diagram}
-\label{sec:orgd6473a3}
+\label{sec:orge52a4e9}
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org9704fad}
+\label{sec:org96f0657}
 \label{sec:iff}
 \subsection{Force Sensors and Control Architecture}
-\label{sec:orgf2a5a4d}
+\label{sec:org5b40356}
 In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
@@
 \subsection{Plant Dynamics}
-\label{sec:org5e54ed9}
+\label{sec:org1a3334e}
 The forces measured by the two force sensors are equal to
@@
 \subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:org8461ad2}
+\label{sec:org62e8d62}
 \label{sec:iff_pure_int}
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgcd3018b}
+\label{sec:org0394efe}
 \label{sec:iff_hpf}
 \subsection{Modification of the Control Low}
-\label{sec:org256e76b}
+\label{sec:orgd5972ba}
 As was just explained, the instability when using IFF with pure integrators comes from the low frequency gain.
@@
 \subsection{Feedback Analysis}
-\label{sec:org6765624}
+\label{sec:org51db5d4}
 The loop gains for the decentralized controllers \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
@@
 \subsection{Optimal Control Parameters}
-\label{sec:org122256a}
+\label{sec:org77a266b}
 Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orgb9e95b0}
+\label{sec:orgfe69ffb}
 \label{sec:iff_kp}
 \subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org3fd6edd}
+\label{sec:org02dc3a4}
 As was explained in section \ref{sec:iff_pure_int}, the instability when using decentralized IFF for rotating positioning platforms is due to Gyroscopic effects and more precisely to the negative stiffnesses induced by centrifugal forces.
@@
 \subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org6d160ef}
+\label{sec:orgb29f2a0}
 The forces measured by the sensors are equal to
@@
 \subsection{Optimal Parallel Stiffness}
-\label{sec:org1c9ca29}
-Even though the parallel stiffness \(k_p\) has no impact on the open-loop poles (as the overall stiffness \(k\) stays constant), it has a large impact on the transmission zeros.
-Moreover, as the attainable damping is generally proportional to the distance between poles and zeros \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the parallel stiffness \(k_p\) is foreseen to have a large impact on the attainable damping.
+\label{sec:orgbcc4bb0}
+The parallel stiffness \(k_p\)
 
-To study this effect, Root Locus plots for several parallel stiffnesses \(k_p > m \Omega^2\) are shown in Figure \ref{fig:root_locus_iff_kps}.
-The frequencies of the transmission zeros of the system are increasing with the parallel stiffness \(k_p\) and the associated attainable damping is reduced.
-Therefore the parallel stiffness \(k_p\) should not be taken too high while being larger than \(m \Omega^2\) for stability reasons.
+Figure \ref{fig:root_locus_iff_kps} shows Root Loci plots for several parallel stiffnesses \(k_p > m \Omega^2\).
+It is shown that large parallel stiffness \(k_p\) reduces the attainable damping.
+This can be explained by the fact that as the parallel stiffnesses increases, the transmission zeros gets closer to the poles.
+As explained in \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the attainable damping is generally proportional to the distance between the poles and zeros.
+The frequency of the transmission zeros of the system are increasing with the fraction used as parallel stiffness \(k_p\).
 
-For any \(k_p > m \Omega^2\), the control gain \(g\) can be tuned such that the maximum simultaneous damping \(\xi_\text{opt}\) is added to the resonances of the system.
-An example is shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\) where \(\xi_{\text{opt}} \approx 0.83\) is obtained for a control gain \(g_\text{opt} \approx 2 \omega_0\).
+For any \(k_p > m \Omega^2\), the control gain \(g\) can be tuned such that the maximum simultaneous damping is added to the resonances of the system as shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\).
+
+\(g_{\text{opt}} \approx 2\)
+\(\xi_{\text{opt}} \approx 0.83\)
 
@@
 \section{Comparison of the Proposed Modification to Decentralized Integral Force Feedback for Rotating Positioning Stages}
-\label{sec:org3dedf99}
+\label{sec:org1e5f410}
 \label{sec:comparison}
-Two modifications to the decentralized IFF for rotating positioning stages have been proposed.
+Two modification to the decentralized IFF for rotating positioning stages have been proposed.
 
-The first modification concerns the controller and consists of adding an high pass filter to \(K_F\) \eqref{eq:IFF_LHF}.
-The system was shown to be stable for gains up to \(g_\text{max}\) \eqref{eq:gmax_iff_hpf}.
+The first modification concerns the controller.
+It consists of adding an high pass filter to \(K_F\) \eqref{eq:IFF_LHF}.
+This allows the system to be stable for gains up to \(g_\text{max}\) \eqref{eq:gmax_iff_hpf}.
 
 The second proposed modification concerns the mechanical system.
-It was shown that if springs with a stiffness \(k_p > m \Omega^2\) are added in parallel to the actuators and force sensors, decentralized IFF can be applied with unconditional stability.
+If springs are added in parallel to the actuators and force sensors with a stiffness \(k_p > m \Omega^2\), decentralized IFF can be applied with unconditional stability.
 
 These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
-For the following comparisons, the cut-off frequency for the high pass filters is set to \(\omega_i = 0.1 \omega_0\) and the parallel springs have a stiffness \(k_p = 5 m \Omega^2\).
+For the following comparisons, the high pass cut-off frequency is set to \(\omega_i = 0.1 \omega_0\) and the parallel stiffness is \(k_p = 5 m \Omega^2\).
 \subsection{Comparison of the Attainable Damping}
-\label{sec:org173dfab}
+\label{sec:org29462c9}
 Figure \ref{fig:comp_root_locus} shows to Root Locus plots for the two proposed IFF techniques.
-While the two pairs of complex conjugate open-loop poles are identical for both techniques, the transmission zeros are not.
-This means that their closed-loop behavior will differ when large control gains are used.
-
-It is interesting to note that the maximum added damping is very similar for both techniques and are reached for the same value of the gain in both cases \(g_\text{opt} \approx 2 \omega_0\).
+The maximum added damping is very similar for both techniques and are reached for \(g_\text{opt} \approx 2\) in both cases.
 
@@
 \subsection{Comparison Transmissibility and Compliance}
-\label{sec:org411478b}
+\label{sec:orgbff6e4e}
 The two proposed techniques are now compared in terms of closed-loop compliance and transmissibility.
@@
 
-The two techniques are also compared with passive damping (Figure \ref{fig:system}) where \(c = c_\text{crit}\) is tuned to critically damp the resonance when the rotating speed is null
+The two techniques are also compared with passive damping (Figure \ref{fig:system}) with \(c\) tuned to critically damp the resonance when \(\Omega = 0\)
 \begin{equation}
@@
 
-Very similar results are obtained for the two proposed decentralized IFF modifications in terms of compliance (Figure \ref{fig:comp_compliance}) and transmissibility (Figure \ref{fig:comp_transmissibility}).
-It is also confirmed that these two techniques can significantly damp the system's resonances.
+Very similar results are obtained for both techniques as shown in Figures \ref{fig:comp_compliance} and \ref{fig:comp_transmissibility}.
+It is also confirmed that these techniques can significantly damp the system's resonances.
 
 Compared to passive damping, the two techniques degrades the compliance at low frequency (Figure \ref{fig:comp_compliance}).
-They however do not degrades the transmissibility as high frequency as its the case with passive damping (Figure \ref{fig:comp_transmissibility}).
+They however do not degrades the transmissibility as high frequency as its the case with passive damping (Figure \ref{fig:comp_transmissibility})
 
@@
 \section{Conclusion}
-\label{sec:orgf8a3da6}
+\label{sec:orgb954137}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orgee9adb1}
+\label{sec:orge7698ad}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-06 matlab/src/computeSimultaneousDamping.m
Add analysis about DC compliance gain

@@ -1,0 +1,10 @@
+% Compute Damping
+
+function [xi_min] = computeSimultaneousDamping(g, G, K)
+    [w, xi] = damp(minreal(feedback(G, g*K)));
+    xi_min = 1/min(xi);
+
+    if xi_min < 0
+      xi_min = 1e8;
+    end
+end

### 2020-07-07 paper/paper.tex
Modify figure sizes

--- 2020-07-02 paper/paper.tex
@@
-% Created 2020-07-02 jeu. 16:30
+% Created 2020-07-07 mar. 18:24
 % Intended LaTeX compiler: pdflatex
@@
 \date{}
-\title{Active Damping of Rotating Positioning Platforms using Force Feedback}
+\title{Active Damping of Rotating Platforms using Integral Force Feedback}
 \hypersetup{
  pdfauthor={},
- pdftitle={Active Damping of Rotating Positioning Platforms using Force Feedback},
+ pdftitle={Active Damping of Rotating Platforms using Integral Force Feedback},
  pdfkeywords={},
@@
 \abstract{
-    Abstract text to be done
+This paper investigates the use of Integral Force Feedback (IFF) for the active damping of rotating mechanical systems.
+Guaranteed stability, typical benefit of IFF, is lost as soon as the system is rotating due to gyroscopic effects.
+To overcome this issue, two modifications of the classical IFF control are proposed.
+The first consists of slightly modifying the control law while the second consists of adding springs in parallel with the force sensors.
+Conditions for stability and optimal parameters are derived.
+The results reveal that, despite their different implementations, both modified IFF control have almost identical damping authority on suspension modes.
 }
@@
 \section{Introduction}
-\label{sec:org7ce36f4}
+\label{sec:org72e892d}
 \label{sec:introduction}
-Due to gyroscopic effects, the guaranteed robustness properties of Integral Force Feedback do not hold.
-Either the control architecture can be slightly modified or mechanical changes in the system can be performed.
-This paper has been published
-The Matlab code that was use to obtain the results are available in \cite{dehaeze20_activ_dampin_rotat_posit_platf}.
+There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
+A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
+In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.
+
+In \cite{preumont92_activ_dampin_by_local_force}, the Integral Force Feedback (IFF) control scheme has been proposed, where a force sensor, a force actuator and an integral controller are used to directly augment the damping of a mechanical system.
+When the force sensor is collocated with the actuator, the open-loop transfer function has alternating poles and zeros which facilitate to guarantee the stability of the closed loop system \cite{preumont02_force_feedb_versus_accel_feedb}.
+
+However, when the platform is rotating, the system dynamics is altered and IFF cannot be applied as is.
+The purpose of this paper is to study how the IFF strategy can be adapted to deal with these Gyroscopic effects.
+
+The paper is structured as follows.
+Section \ref{sec:dynamics} presents a simple model of a rotating suspended platform that will be used throughout this study.
+Section \ref{sec:iff} explains how the unconditional stability of IFF is lost due to Gyroscopic effects induced by the rotation.
+Section \ref{sec:iff_hpf} suggests a simple modification of the control law such that damping can be added to the suspension modes in a robust way.
+Section \ref{sec:iff_kp} proposes to add springs in parallel with the force sensors to regain the unconditional stability of IFF.
+Section \ref{sec:comparison} compares both proposed modifications to the classical IFF in terms of damping authority and closed-loop system behavior.
 
 \section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org1767f3e}
+\label{sec:org967f3ca}
 \label{sec:dynamics}
-\subsection{Model of a Rotating Positioning Platform}
-\label{sec:org3d795b1}
-In order to study how the rotation of a positioning platforms does affect the use of integral force feedback, a model of an XY positioning stage on top of a rotating stage is developed.
+In order to study how the rotation of a positioning platforms does affect the use of integral force feedback, a model of an XY positioning stage on top of a rotating stage is used.
+Figure \ref{fig:system} represents the model schematically.
+This model is the simplest in which gyroscopic forces can be studied.
 
-The model is schematically represented in Figure \ref{fig:system} and forms the simplest system where gyroscopic forces can be studied.
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/system.pdf}
+\caption{\label{fig:system}Schematic of the studied System}
+\end{figure}
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/system.pdf}
-\caption{\label{fig:system}Schematic of the studied System}
-\end{figure}
-
-\subsection{Equations of Motion}
-\label{sec:orgeda87e3}
-To obtain of equation of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
+\par
+To obtain the equations of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
 \begin{equation}
@@
 \end{equation}
-with \(L = T - V\) the Lagrangian, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
+with \(L = T - V\) the Lagrangian, \(T\) the kinetic coenergy, \(V\) the potential energy, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
+The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) is disregarded as the motion is considered to be imposed by the rotation stage.
+\begin{equation}
+\label{eq:energy_functions_lagrange}
+  \begin{aligned}
+    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \quad V = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right),\\
+    D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
+  \end{aligned}
+\end{equation}
 
-The constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is here disregarded as it is imposed by the ideal rotating stage.
-\begin{subequations}
-\label{eq:energy_functions_lagrange}
-  \begin{align}
-    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right) \\
-    V & = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right) \\
-    D & = \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right) \\
-    Q_1 &= F_u, \quad Q_2 = F_v
-  \end{align}
-\end{subequations}
-
-Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} gives two coupled differential equations
+Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} for both generalized coordinates gives two coupled differential equations
 \begin{subequations}
@@
 
-\subsection{Transfer Functions in the Laplace domain}
-\label{sec:org133b2f9}
+\par
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
@@
 To simplify the analysis, the undamped natural frequency \(\omega_0\) and the damping ratio \(\xi\) are used
-\begin{subequations}
-  \begin{align}
-    \omega_0 &= \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second} \\
-    \xi &= \frac{c}{2 \sqrt{k m}}
-  \end{align}
-\end{subequations}
+\begin{equation}
+  \omega_0 = \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second}, \quad \xi = \frac{c}{2 \sqrt{k m}}
+\end{equation}
 
@@
 
-For all the numerical analysis in this study, \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
+For all further numerical analysis in this study, we consider \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
+Even though no system with such parameters will be encountered in practice, conclusions can be drawn relative to these parameters such that they can be generalized to any other set of parameters.
 
-Even tough no system with such parameters will be encountered in practice, conclusions will be drawn relative to these parameters such that they can be generalized to any other parameter.
-
-\subsection{System Dynamics and Campbell Diagram}
-\label{sec:orgd6473a3}
+\par
 The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
@@
 \end{subfigure}
+\hfill
 \begin{subfigure}[c]{0.4\linewidth}
@@
 \end{subfigure}
+\hfill
 \caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
@@
 The bode plot of these two distinct terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
-
-It is confirmed that the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
-For \(\Omega > \omega_0\), the low frequency complex conjugate poles \(p_{-}\) becomes unstable.
+These plots confirm the expected behavior: the frequency of the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
+For \(\Omega > \omega_0\), the low frequency pair of complex conjugate poles \(p_{-}\) becomes unstable.
 
@@
 \end{subfigure}
+\hfill
 \begin{subfigure}[c]{0.45\linewidth}
@@
 \end{subfigure}
+\hfill
 \caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org9704fad}
+\label{sec:org69e5bf1}
 \label{sec:iff}
-\subsection{Force Sensors and Control Architecture}
-\label{sec:orgf2a5a4d}
 In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
@@
 
-\begin{minipage}[t]{0.55\linewidth}
+\begin{minipage}[t]{0.50\linewidth}
 \begin{center}
-\includegraphics[scale=1]{figs/system_iff.pdf}
+\includegraphics[width=\linewidth]{figs/system_iff.pdf}
 \captionof{figure}{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
@@
 \hfill
-\begin{minipage}[t]{0.40\linewidth}
+\begin{minipage}[t]{0.45\linewidth}
 \begin{center}
-\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
+\includegraphics[width=\linewidth]{figs/control_diagram_iff.pdf}
 \captionof{figure}{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
@@
 
-\subsection{Plant Dynamics}
-\label{sec:org5e54ed9}
-The forces measured by the two force sensors are equal to
+\par
+The forces \(\begin{bmatrix}f_u, f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_iff} are equal to
 \begin{equation}
@@
 
-Re-injecting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
+Inserting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
 \begin{equation}
@@
 
-It can be easily shown that the frequency of the two complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
+It can be easily shown that the frequency of the two complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} always lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
 
@@
 \includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
-\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the diagonal terms of \(\bm{G}_f\) for several rotational speeds \(\Omega\)}
+\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
 \end{figure}
 
-\subsection{Decentralized Integral Force Feedback with Pure Integrators}
-\label{sec:org8461ad2}
+\par
 \label{sec:iff_pure_int}
@@
 \includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
-\caption{\label{fig:root_locus_pure_iff}Root Locus for the Decentralized Integral Force Feedback for several rotating speeds \(\Omega\)}
+\caption{\label{fig:root_locus_pure_iff}Root Locus for the decentralized IFF: evolution of the closed-loop poles with increasing gains. This is done for several rotating speeds \(\Omega\)}
 \end{figure}
@@
 Whereas collocated IFF is usually associated with unconditional stability \cite{preumont91_activ}, this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
-This can be seen in the Root Locus (Figure \ref{fig:root_locus_pure_iff}) where the pole corresponding to the controller is bounded to the right half plane implying closed-loop system instability.
+This can be seen in the Root Locus (Figure \ref{fig:root_locus_pure_iff}) where the pole corresponding to the controller is bound to the right half plane implying closed-loop system instability.
 
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgcd3018b}
+\label{sec:orgaa5d9a8}
 \label{sec:iff_hpf}
-\subsection{Modification of the Control Low}
-\label{sec:org256e76b}
-As was just explained, the instability when using IFF with pure integrators comes from the low frequency gain.
+As was explained in the previous section, the instability when using IFF with pure integrators comes from high controller gain at low frequency.
 
@@
 
-This is equivalent as to slightly shifting to controller pole to the left along the real axis.
+This is equivalent to slightly shifting the controller pole to the left along the real axis.
 
@@
 
-\subsection{Feedback Analysis}
-\label{sec:org6765624}
+\par
 The loop gains for the decentralized controllers \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
-The effect of the added HPF clearly limits the low frequency gain.
+The effect of the added HPF limits the low frequency gain as expected.
 
@@
 \end{equation}
-It is interesting to note that this gain \(g_{\text{max}}\) also corresponds as to when the low frequency loop gain (Figure \ref{fig:loop_gain_modified_iff}) reaches one.
+It is interesting to note that \(g_{\text{max}}\) also corresponds to the gain where the low frequency loop gain (Figure \ref{fig:loop_gain_modified_iff}) reaches one.
 
@@
 
-\subsection{Optimal Control Parameters}
-\label{sec:org122256a}
+\par
 Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
@@
 In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Loci for several \(\omega_i\) are displayed in Figure \ref{fig:root_locus_wi_modified_iff}.
-It is shown that even tough small \(\omega_i\) seems to allow more damping to be added to the system resonances, the control gain \(g\) may be limited to small values due to Eq.
+It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the system resonances, the control gain \(g\) may be limited to small values due to Eq.
 \eqref{eq:gmax_iff_hpf}.
@@
 
-In order to study this trade off, the attainable damping ratio \(\xi_{\text{cl}}\) is computed as a function of the ratio \(\omega_i/\omega_0\).
-The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also display and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi})r.
+In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of the ratio \(\omega_i/\omega_0\).
+The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also display and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi}).
 
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orgb9e95b0}
+\label{sec:orge64ac7f}
 \label{sec:iff_kp}
-\subsection{Stiffness in Parallel with the Force Sensor}
-\label{sec:org3fd6edd}
-As was explained in section \ref{sec:iff_pure_int}, the instability when using decentralized IFF for rotating positioning platforms is due to Gyroscopic effects and more precisely to the negative stiffnesses induced by centrifugal forces.
+As was explained in section \ref{sec:iff_pure_int}, the instability when using decentralized IFF for rotating positioning platforms is due to Gyroscopic effects and, more precisely, due to the negative stiffness induced by centrifugal forces.
 In this section additional springs in parallel with the force sensors are added to counteract this negative stiffness.
@@
 
-\begin{minipage}[t]{0.55\linewidth}
+\begin{minipage}[t]{0.48\linewidth}
 \begin{center}
-\includegraphics[scale=1]{figs/system_parallel_springs.pdf}
+\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
 \captionof{figure}{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
@@
 \hfill
-\begin{minipage}[t]{0.40\linewidth}
+\begin{minipage}[t]{0.48\linewidth}
 \begin{center}
@@
 
-\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
-\label{sec:org6d160ef}
-The forces measured by the sensors are equal to
+\par
+The forces \(\begin{bmatrix}f_u, f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_parallel_springs} are equal to
 \begin{equation}
@@
 In order to keep the overall stiffness \(k = k_a + k_p\) constant, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
-\begin{subequations}
-  \begin{align}
-    k_p &= \alpha k \\
-    k_a &= (1 - \alpha) k
-  \end{align}
-\end{subequations}
+\begin{equation}
+  k_p = \alpha k, \quad k_a = (1 - \alpha) k
+\end{equation}
 
@@
 Comparing \(\bm{G}_k\) \eqref{eq:Gk} with \(\bm{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
-The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros is Eq. \ref{eq:kp_cond_cc_zeros} is verified.
+The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros if the following condition hold
 \begin{equation}
 \label{eq:kp_cond_cc_zeros}
-  \begin{aligned}
-    \alpha &> \frac{\Omega^2}{{\omega_0}^2} \\
-    \Leftrightarrow k_p &> m \Omega^2
-  \end{aligned}
+  \alpha > \frac{\Omega^2}{{\omega_0}^2} \quad \Leftrightarrow \quad k_p > m \Omega^2
 \end{equation}
@@
 
-\subsection{Optimal Parallel Stiffness}
-\label{sec:org1c9ca29}
+\par
 Even though the parallel stiffness \(k_p\) has no impact on the open-loop poles (as the overall stiffness \(k\) stays constant), it has a large impact on the transmission zeros.
@@
 The frequencies of the transmission zeros of the system are increasing with the parallel stiffness \(k_p\) and the associated attainable damping is reduced.
-Therefore the parallel stiffness \(k_p\) should not be taken too high while being larger than \(m \Omega^2\) for stability reasons.
+Therefore, even though the parallel stiffness \(k_p\) should be larger than \(m \Omega^2\) for stability reasons, it should not be taken too high as this would limit the attainable bandwidth.
 
 For any \(k_p > m \Omega^2\), the control gain \(g\) can be tuned such that the maximum simultaneous damping \(\xi_\text{opt}\) is added to the resonances of the system.
-An example is shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\) where \(\xi_{\text{opt}} \approx 0.83\) is obtained for a control gain \(g_\text{opt} \approx 2 \omega_0\).
+An example is shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\) where the damping \(\xi_{\text{opt}} \approx 0.83\) is obtained for a control gain \(g_\text{opt} \approx 2 \omega_0\).
 
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.49\linewidth}
+\begin{subfigure}[c]{0.45\linewidth}
 \includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
@@
 \end{subfigure}
-\begin{subfigure}[c]{0.49\linewidth}
+\hfill
+\begin{subfigure}[c]{0.45\linewidth}
 \includegraphics[width=\linewidth]{figs/root_locus_opt_gain_iff_kp.pdf}
@@
 \end{subfigure}
+\hfill
 \caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness \(k_p\) is added, \(\Omega = 0.1 \omega_0\)}
@@
 
-\section{Comparison of the Proposed Modification to Decentralized Integral Force Feedback for Rotating Positioning Stages}
-\label{sec:org3dedf99}
+\section{Comparison and Discussion}
+\label{sec:org118e3e9}
 \label{sec:comparison}
@@
 For the following comparisons, the cut-off frequency for the high pass filters is set to \(\omega_i = 0.1 \omega_0\) and the parallel springs have a stiffness \(k_p = 5 m \Omega^2\).
-\subsection{Comparison of the Attainable Damping}
-\label{sec:org173dfab}
-Figure \ref{fig:comp_root_locus} shows to Root Locus plots for the two proposed IFF techniques.
+
+\par
+Figure \ref{fig:comp_root_locus} shows two Root Locus plots for the two proposed IFF techniques.
 While the two pairs of complex conjugate open-loop poles are identical for both techniques, the transmission zeros are not.
@@
 
-It is interesting to note that the maximum added damping is very similar for both techniques and are reached for the same value of the gain in both cases \(g_\text{opt} \approx 2 \omega_0\).
+It is interesting to note that the maximum added damping is very similar for both techniques and is reached for the same control gain in both cases \(g_\text{opt} \approx 2 \omega_0\).
 
@@
 
-\subsection{Comparison Transmissibility and Compliance}
-\label{sec:org411478b}
+\par
 The two proposed techniques are now compared in terms of closed-loop compliance and transmissibility.
@@
 The compliance is defined as the transfer function from external forces applied to the payload to the displacement of the payload in an inertial frame.
-The transmissibility is the dynamics from the displacement of the rotating stage to the displacement of the payload.
+The transmissibility describes the dynamic behaviour between the displacement of the rotating stage and the displacement of the payload.
 It is used to characterize how much vibration of the rotating stage is transmitted to the payload.
 
-The two techniques are also compared with passive damping (Figure \ref{fig:system}) where \(c = c_\text{crit}\) is tuned to critically damp the resonance when the rotating speed is null
+The two techniques are also compared with passive damping (Figure \ref{fig:system}) where \(c = c_\text{crit}\) is tuned to critically damp the resonance when the rotating speed is null.
+
 \begin{equation}
@@
 
-Compared to passive damping, the two techniques degrades the compliance at low frequency (Figure \ref{fig:comp_compliance}).
-They however do not degrades the transmissibility as high frequency as its the case with passive damping (Figure \ref{fig:comp_transmissibility}).
+Compared to passive damping, the two techniques degrade the compliance at low frequency (Figure \ref{fig:comp_compliance}).
+They however do not degrade the transmissibility at high frequency as it is the case with passive damping (Figure \ref{fig:comp_transmissibility}).
 
@@
 \end{subfigure}
+\hfill
 \caption{\label{fig:comp_active_damping}Comparison of the two proposed Active Damping Techniques, \(\Omega = 0.1 \omega_0\)}
@@
 \section{Conclusion}
-\label{sec:orgf8a3da6}
+\label{sec:org419f838}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orgee9adb1}
+\label{sec:org19e4dbd}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-08 matlab/matlab/s4_iff_kp.m
Update Matlab code

@@ -1,389 +1,79 @@
-%% Clear Workspace and Close figures
-clear; close all; clc;
+% Attainable Damping as a function of $k_p$
 
-%% Intialize Laplace variable
-s = zpk('s');
+tic;
+alphas = logspace(-2, 0, 10);
+gains = linspace(0.5, 2.5, 100);
 
-% Plant Parameters
-% Let's define initial values for the model.
+opt_zeta = zeros(1, length(alphas)); % Optimal simultaneous damping
+opt_gain = zeros(1, length(alphas)); % Corresponding optimal gain
 
-k = 1;    % Actuator Stiffness [N/m]
-c = 0.05; % Actuator Damping [N/(m/s)]
-m = 1;    % Payload mass [kg]
-
-xi = c/(2*sqrt(k*m));
-w0 = sqrt(k/m); % [rad/s]
-
-kp = 0; % [N/m]
-cp = 0; % [N/(m/s)]
-
-% Comparison of the Analytical Model and the Simscape Model
-% The same transfer function from $[F_u, F_v]$ to $[f_u, f_v]$ is written down from the analytical model.
-
-W = 0.1*w0; % [rad/s]
-
-kp = 1.5*m*W^2;
-cp = 0;
-
-Kiff = tf(zeros(2));
-Kdvf = tf(zeros(2));
-
-open('rotating_frame.slx');
-
-%% Name of the Simulink File
-mdl = 'rotating_frame';
-
-%% Input/Output definition
-clear io; io_i = 1;
-io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
-io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
-
-Giff = linearize(mdl, io, 0);
-
-%% Input/Output definition
-Giff.InputName  = {'Fu', 'Fv'};
-Giff.OutputName = {'fu', 'fv'};
-
-w0p = sqrt((k + kp)/m);
-xip = c/(2*sqrt((k+kp)*m));
-
-Giff_th = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
[…]

### 2020-07-08 paper/paper.tex
Review, Section 6

@@
-% Created 2020-07-07 mar. 18:24
+% Created 2020-07-08 mer. 18:02
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org72e892d}
+\label{sec:org639dbba}
 \label{sec:introduction}
@@
 
-However, when the platform is rotating, the system dynamics is altered and IFF cannot be applied as is.
+However, when the platform is rotating, gyroscopic effects alter the system dynamics and IFF cannot be applied as is.
 The purpose of this paper is to study how the IFF strategy can be adapted to deal with these Gyroscopic effects.
@@
 
-\section{Dynamics of Rotating Positioning Platforms}
-\label{sec:org967f3ca}
+\section{Dynamics of Rotating Platforms}
+\label{sec:orgea844f7}
 \label{sec:dynamics}
-In order to study how the rotation of a positioning platforms does affect the use of integral force feedback, a model of an XY positioning stage on top of a rotating stage is used.
-Figure \ref{fig:system} represents the model schematically.
-This model is the simplest in which gyroscopic forces can be studied.
+In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
+Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.
 
@@
 
-The parallel XY positioning stage consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
-A payload with a mass \(m\) in \(\si{\kilo\gram}\) is mounted on the (rotating) XY stage.
+The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
+A payload with a mass \(m\) in \(\si{\kilo\gram}\), representing the sensitive equipment, is mounted on the (rotating) suspended platform.
 
@@
 
-The transfer function matrix \(\bm{G}_d\) \eqref{eq:Gd_m_k_c} becomes equal to
+The transfer function matrix \(\bm{G}_d\) becomes equal to
 \begin{equation}
@@
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.4\linewidth}
+\begin{subfigure}[c]{0.45\linewidth}
 \includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
@@
 \hfill
-\begin{subfigure}[c]{0.4\linewidth}
+\begin{subfigure}[c]{0.45\linewidth}
 \includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org69e5bf1}
+\label{sec:org7bfaed6}
 \label{sec:iff}
@@
 \par
-The forces \(\begin{bmatrix}f_u, f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_iff} are equal to
+The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_iff} are equal to
 \begin{equation}
@@
 Inserting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
-\begin{equation}
-\label{eq:Gf_mimo_tf}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
-with \(\bm{G}_f\) a \(2 \times 2\) transfer function matrix
-\begin{equation}
-\label{eq:Gf}
-  \bm{G}_{f} = \begin{bmatrix}
+\begin{align}
+  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} &= \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gf_mimo_tf} \\
+  \bm{G}_{f} &= \begin{bmatrix}
   \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
   \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix}
-\end{equation}
+\end{bmatrix} \label{eq:Gf}
+\end{align}
 
@@
 
-It can be easily shown that the frequency of the two complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} always lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
+The frequency of the pair of complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} always lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
 
 For non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms inducing a non-minimum phase behavior.
-This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the magnitude experiences an increase of its slope without any change of phase.
+This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(\SI{180}{\degree}\).
 
-Similarly, the low frequency gain of \(\bm{G}_f\) is no longer zero and increases with the rotational speed \(\Omega\)
+The low frequency gain of \(\bm{G}_f\) increases with the rotational speed \(\Omega\)
 \begin{equation}
-\label{low_freq_gain_iff_plan}
+\label{eq:low_freq_gain_iff_plan}
   \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
@@
 
-This low frequency gain can be explained as follows: a constant force \(F_u\) induces a small displacement of the mass \(d_u = \frac{F_u}{k - m\Omega^2}\), which increases the centrifugal force \(m\Omega^2d_u = \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} F_u\) which is then measured by the force sensors.
+This can be explained as follows: a constant force \(F_u\) induces a small displacement of the mass \(d_u = \frac{F_u}{k - m\Omega^2}\), which increases the centrifugal force \(m\Omega^2d_u = \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} F_u\) which is then measured by the force sensors.
 
@@
 
-In order to see how the IFF affects the poles of the closed loop system, a Root Locus (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the gain \(g\) varies from \(0\) to \(\infty\) for the two controllers simultaneously.
+In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers simultaneously.
 As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
@@
 \includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
-\caption{\label{fig:root_locus_pure_iff}Root Locus for the decentralized IFF: evolution of the closed-loop poles with increasing gains. This is done for several rotating speeds \(\Omega\)}
+\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
 \end{figure}
@@
 Whereas collocated IFF is usually associated with unconditional stability \cite{preumont91_activ}, this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
-This can be seen in the Root Locus (Figure \ref{fig:root_locus_pure_iff}) where the pole corresponding to the controller is bound to the right half plane implying closed-loop system instability.
+This can be seen in the Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) where the poles corresponding to the controller are bound to the right half plane implying closed-loop system instability.
 
-Physically, this can be explained by realizing that below some frequency, the loop gain being very large, the decentralized IFF effectively decouples the payload from the XY stage.
-Moreover, the payload experiences centrifugal forces, which can be modeled by negative stiffnesses pulling it away from the rotation axis rendering the system unstable, hence the poles in the right half plane.
+Physically, this can be explain like so: at low frequency, the loop gain is very large due to the pure integrators in \(K_F\).
+The control system is thus canceling the spring forces which makes the suspended platform no able to hold the payload against centrifugal forces, hence the instability.
 
-In order to apply Decentralized IFF on rotating positioning stages, two solutions are proposed to deal with this instability problem.
+In order to apply Decentralized IFF on rotating platforms, two solutions are proposed to deal with this instability problem.
 The first one consists of slightly modifying the control law (Section \ref{sec:iff_hpf}) while the second one consists of adding springs in parallel with the force sensors (Section \ref{sec:iff_kp}).
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgaa5d9a8}
+\label{sec:org380bd8d}
 \label{sec:iff_hpf}
-As was explained in the previous section, the instability when using IFF with pure integrators comes from high controller gain at low frequency.
+As was explained in the previous section, the instability comes in part from the high gain at low frequency caused by the pure integrators.
 
-In order to limit the low frequency controller gain, an high pass filter (HPF) can be added to the controller
+In order to limit this low frequency controller gain, an high pass filter (HPF) can be added to the controller
 \begin{equation}
@@
 \par
-The loop gains for the decentralized controllers \(K_F(s)\) with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
+The loop gains, \(K_F(s)\) times the direct dynamics \(f_u/F_u\), with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
 The effect of the added HPF limits the low frequency gain as expected.
@@
 \par
-Two parameters can be tuned for the controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
+Two parameters can be tuned for the modified controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
 The optimal values of \(\omega_i\) and \(g\) are here considered as the values for which the damping of all the closed-loop poles are simultaneously maximized.
@@
 In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Loci for several \(\omega_i\) are displayed in Figure \ref{fig:root_locus_wi_modified_iff}.
-It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the system resonances, the control gain \(g\) may be limited to small values due to Eq.
+It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the suspension modes, the control gain \(g\) may be limited to small values due to Eq.
 \eqref{eq:gmax_iff_hpf}.
@@
 
-In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of the ratio \(\omega_i/\omega_0\).
-The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also display and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi}).
-
-Three regions can be observed:
-\begin{itemize}
-\item \(\frac{\omega_i}{\omega_0} < 0.02\): the added damping is limited by the maximum allowed control gain \(g_{\text{max}}\)
-\item \(0.02 < \frac{\omega_i}{\omega_0} < 0.2\): good amount of damping can be added for \(g \approx 2\)
-\item \(0.2 < \frac{\omega_i}{\omega_0}\): the added damping becomes small due to the shape of the Root Locus (Figure \ref{fig:root_locus_wi_modified_iff})
-\end{itemize}
+In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of the \(\omega_i/\omega_0\).
+The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also displayed and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi}).
 
@@
 \includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
-\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of the ratio \(\omega_i/\omega_0\).
+\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
 Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
@@
 
+Three regions can be observed:
+\begin{itemize}
+\item \(\omega_i/\omega_0 < 0.02\): the added damping is limited by the maximum allowed control gain \(g_{\text{max}}\)
+\item \(0.02 < \omega_i/\omega_0 < 0.2\): the attainable damping ratio is maximized and is reached for \(g \approx 2\)
+\item \(0.2 < \omega_i/\omega_0\): the added damping decreases as the \(\omega_i/\omega_0\) increases
+\end{itemize}
+
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orge64ac7f}
+\label{sec:org93348b6}
 \label{sec:iff_kp}
-As was explained in section \ref{sec:iff_pure_int}, the instability when using decentralized IFF for rotating positioning platforms is due to Gyroscopic effects and, more precisely, due to the negative stiffness induced by centrifugal forces.
-In this section additional springs in parallel with the force sensors are added to counteract this negative stiffness.
+In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
 Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
@@
 
-In order to keep the overall stiffness \(k = k_a + k_p\) constant, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
+In order to keep the overall stiffness \(k = k_a + k_p\) constant, thus not modifying the open-loop poles as \(k_p\) is changed, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
 \begin{equation}
@@
 The equations of motion are derived and transformed in the Laplace domain
-\begin{equation}
-\label{eq:Gk_mimo_tf}
-\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
+\begin{align}
+\begin{bmatrix} f_u \\ f_v \end{bmatrix} &=
 \bm{G}_k
-\begin{bmatrix} F_u \\ F_v \end{bmatrix}
-\end{equation}
-with \(\bm{G}_k\) a \(2 \times 2\) transfer function matrix
-\begin{equation}
-\label{eq:Gk}
-\bm{G}_k =
+\begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gk_mimo_tf} \\
+\bm{G}_k &=
 \begin{bmatrix}
@@
   \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix}
-\end{equation}
+\end{bmatrix} \label{eq:Gk}
+\end{align}
 
@@
 Thus, if the added parallel stiffness \(k_p\) is higher than the negative stiffness induced by centrifugal forces \(m \Omega^2\), the direct dynamics from actuator to force sensor will show minimum phase behavior.
-This is confirmed by the Bode plot in Figure \ref{fig:plant_iff_kp}.
+This is confirmed by the Bode plot of the direct dynamics in Figure \ref{fig:plant_iff_kp}.
 
@@
 
-\begin{minipage}[b]{0.42\linewidth}
+\begin{minipage}[b]{0.43\linewidth}
 \begin{center}
@@
 \hfill
-\begin{minipage}[b]{0.52\linewidth}
+\begin{minipage}[b]{0.53\linewidth}
 \begin{center}
@@
 
-For any \(k_p > m \Omega^2\), the control gain \(g\) can be tuned such that the maximum simultaneous damping \(\xi_\text{opt}\) is added to the resonances of the system.
-An example is shown in Figure \ref{fig:root_locus_opt_gain_iff_kp} for \(k_p = 5 m \Omega^2\) where the damping \(\xi_{\text{opt}} \approx 0.83\) is obtained for a control gain \(g_\text{opt} \approx 2 \omega_0\).
+This is confirmed in Figure \ref{fig:mod_iff_damping_kp} where the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) and the associated control gain \(g_\text{opt}\) are computed as a function of \(\alpha\).
 
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
+\begin{minipage}[t]{0.48\linewidth}
+\begin{center}
 \includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
-\caption{\label{fig:root_locus_iff_kps} Comparison of three parallel stiffnesses \(k_p\)}
-\end{subfigure}
+\captionof{figure}{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
+\end{center}
+\end{minipage}
 \hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/root_locus_opt_gain_iff_kp.pdf}
-\caption{\label{fig:root_locus_opt_gain_iff_kp} \(k_p = 5 m \Omega^2\), optimal damping \(\xi_\text{opt}\) is shown}
-\end{subfigure}
-\hfill
-\caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness \(k_p\) is added, \(\Omega = 0.1 \omega_0\)}
-\centering
-\end{figure}
+\begin{minipage}[t]{0.48\linewidth}
+\begin{center}
+\includegraphics[width=\linewidth]{figs/mod_iff_damping_kp.pdf}
+\captionof{figure}{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
+\end{center}
+\end{minipage}
 
 \section{Comparison and Discussion}
-\label{sec:org118e3e9}
+\label{sec:org5f56e74}
 \label{sec:comparison}
-Two modifications to the decentralized IFF for rotating positioning stages have been proposed.
+Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
+These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
 
-The first modification concerns the controller and consists of adding an high pass filter to \(K_F\) \eqref{eq:IFF_LHF}.
-The system was shown to be stable for gains up to \(g_\text{max}\) \eqref{eq:gmax_iff_hpf}.
-
-The second proposed modification concerns the mechanical system.
-It was shown that if springs with a stiffness \(k_p > m \Omega^2\) are added in parallel to the actuators and force sensors, decentralized IFF can be applied with unconditional stability.
-
-These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
-For the following comparisons, the cut-off frequency for the high pass filters is set to \(\omega_i = 0.1 \omega_0\) and the parallel springs have a stiffness \(k_p = 5 m \Omega^2\).
+For the following comparisons, the cut-off frequency for the HPF is set to \(\omega_i = 0.1 \omega_0\) and the stiffness of the parallel springs is set to \(k_p = 5 m \Omega^2\).
 
 \par
-Figure \ref{fig:comp_root_locus} shows two Root Locus plots for the two proposed IFF techniques.
+Figure \ref{fig:comp_root_locus} shows the Root Loci for the two proposed IFF modifications.
 While the two pairs of complex conjugate open-loop poles are identical for both techniques, the transmission zeros are not.
-This means that their closed-loop behavior will differ when large control gains are used.
+This means that the closed-loop behavior of both systems will differ when large control gains are used.
 
-It is interesting to note that the maximum added damping is very similar for both techniques and is reached for the same control gain in both cases \(g_\text{opt} \approx 2 \omega_0\).
+One can observe that the closed loop poles of the system with added springs (in red) are bounded to the left half plane implying unconditional stability.
+This is not the case for the system where the controller is augmented with an HPF (in blue).
+
+It is interesting to note that the maximum added damping is very similar for both techniques and is reached for the same control gain \(g_\text{opt} \approx 2 \omega_0\).
 
@@
 \par
-The two proposed techniques are now compared in terms of closed-loop compliance and transmissibility.
+The two proposed techniques are now compared in terms of closed-loop transmissibility and compliance.
 
-The compliance is defined as the transfer function from external forces applied to the payload to the displacement of the payload in an inertial frame.
-The transmissibility describes the dynamic behaviour between the displacement of the rotating stage and the displacement of the payload.
-It is used to characterize how much vibration of the rotating stage is transmitted to the payload.
+The transmissibility is defined as the transfer function from the displacement of the rotating stage to the displacement of the payload.
+It is used to characterize how much vibration is transmitted through the suspended platform to the payload.
 
-The two techniques are also compared with passive damping (Figure \ref{fig:system}) where \(c = c_\text{crit}\) is tuned to critically damp the resonance when the rotating speed is null.
+The compliance describes the displacement response of the payload to external forces applied to it.
+This is a useful metric when disturbances are directly applied to the payload.
 
+The two techniques are also compared with passive damping (Figure \ref{fig:system}) where the damping coefficient \(c\) is tuned to critically damp the resonance when the rotating speed is null.
 \begin{equation}
@@
 
-Very similar results are obtained for the two proposed decentralized IFF modifications in terms of compliance (Figure \ref{fig:comp_compliance}) and transmissibility (Figure \ref{fig:comp_transmissibility}).
+Very similar results are obtained for the two proposed IFF modifications in terms of transmissibility (Figure \ref{fig:comp_transmissibility}) and compliance (Figure \ref{fig:comp_compliance}).
 It is also confirmed that these two techniques can significantly damp the system's resonances.
 
-Compared to passive damping, the two techniques degrade the compliance at low frequency (Figure \ref{fig:comp_compliance}).
-They however do not degrade the transmissibility at high frequency as it is the case with passive damping (Figure \ref{fig:comp_transmissibility}).
-
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
+\begin{subfigure}[c]{0.49\linewidth}
+\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
+\caption{\label{fig:comp_transmissibility} Transmissibility}
+\end{subfigure}
+\hfill
+\begin{subfigure}[c]{0.49\linewidth}
 \includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
 \caption{\label{fig:comp_compliance} Compliance}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
-\caption{\label{fig:comp_transmissibility} Transmissibility}
 \end{subfigure}
@@
 
+On can see in Figure \ref{fig:comp_transmissibility} that the problem of the degradation of the transmissibility at high frequency when using passive damping techniques is overcome by the use of IFF.
+
+The addition of the HPF or the use of the parallel stiffness permit to limit the degradation of the compliance as compared with classical IFF (Figure \ref{fig:comp_compliance}).
+
 \section{Conclusion}
-\label{sec:org419f838}
+\label{sec:org6ee721e}
 \label{sec:conclusion}
 
+Due to gyroscopic effects, decentralized IFF with pure integrators was shown not to be stable when applied to rotating platforms.
+Two modifications of the classical IFF control have been proposed to overcome this issue.
+
+The first modification concerns the controller and consists of adding an high pass filter to the pure integrators.
+This is equivalent as to moving the controller pole to the left along the real axis.
+This renders the closed loop system stable up to some value of the controller gain \(g_\text{max}\).
+
+The second proposed modification concerns the mechanical system.
+Additional springs are added in parallel with the actuators and force sensors.
+It was shown that if the stiffness \(k_p\) of the addition springs is larger than the negative stiffness \(m \Omega^2\) induced by centrifugal forces, the classical decentralized IFF regains its unconditional stability property.
+
+While having very different implementations, both proposed modifications are very similar when it comes to the attainable damping and the obtained closed loop system behavior.
+
+Future work will focus on the experimental validation of the proposed active damping techniques.
+
 \section*{Acknowledgment}
-\label{sec:org19e4dbd}
+\label{sec:orgd2f72ff}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-08 paper/paper.tex
Add source code reference

@@
-% Created 2020-07-08 mer. 18:02
+% Created 2020-07-08 mer. 18:07
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org639dbba}
+\label{sec:orgc580a8f}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Platforms}
-\label{sec:orgea844f7}
+\label{sec:orgf7cef1f}
 \label{sec:dynamics}
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org7bfaed6}
+\label{sec:orgcb8c9c7}
 \label{sec:iff}
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:org380bd8d}
+\label{sec:org0b913ec}
 \label{sec:iff_hpf}
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org93348b6}
+\label{sec:org082b3c2}
 \label{sec:iff_kp}
@@
 \section{Comparison and Discussion}
-\label{sec:org5f56e74}
+\label{sec:org1f46ad4}
 \label{sec:comparison}
@@
 \section{Conclusion}
-\label{sec:org6ee721e}
+\label{sec:org071db57}
 \label{sec:conclusion}
@@
 
+The Matlab code that was used for this study is available under a MIT License and archived in Zenodo \cite{dehaeze20_activ_dampin_rotat_posit_platf}.
+
 \section*{Acknowledgment}
-\label{sec:orgd2f72ff}
+\label{sec:orgd8daf24}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-09 paper/paper.tex
Last Review

@@
-% Created 2020-07-08 mer. 18:07
+% Created 2020-07-09 jeu. 09:06
 % Intended LaTeX compiler: pdflatex
@@
 Guaranteed stability, typical benefit of IFF, is lost as soon as the system is rotating due to gyroscopic effects.
-To overcome this issue, two modifications of the classical IFF control are proposed.
+To overcome this issue, two modifications of the classical IFF control scheme are proposed.
 The first consists of slightly modifying the control law while the second consists of adding springs in parallel with the force sensors.
 Conditions for stability and optimal parameters are derived.
-The results reveal that, despite their different implementations, both modified IFF control have almost identical damping authority on suspension modes.
+The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on suspension modes.
 }
@@
 \section{Introduction}
-\label{sec:orgc580a8f}
+\label{sec:orgf2d9f1e}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Platforms}
-\label{sec:orgf7cef1f}
+\label{sec:orgf97884c}
 \label{sec:dynamics}
@@
 with \(L = T - V\) the Lagrangian, \(T\) the kinetic coenergy, \(V\) the potential energy, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
-The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) is disregarded as the motion is considered to be imposed by the rotation stage.
+The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is disregarded as the motion is considered to be imposed by the rotation stage.
 \begin{equation}
@@
 
-The uniform rotation of the system induces two Gyroscopic effects as shown in Eq. \eqref{eq:eom_coupled}:
+The uniform rotation of the system induces two Gyroscopic effects as shown in \eqref{eq:eom_coupled}:
 \begin{itemize}
@@
 \end{itemize}
-
-One can verify that without rotation (\(\Omega = 0\)) the system becomes equivalent as to two uncoupled one degree of freedom mass-spring-damper systems:
-\begin{subequations}
-\label{eq:oem_no_rotation}
-  \begin{align}
-    m \ddot{d}_u + c \dot{d}_u + k d_u &= F_u \\
-    m \ddot{d}_v + c \dot{d}_v + k d_v &= F_v
-  \end{align}
-\end{subequations}
 
@@
 Looking at the transfer function matrix \(\bm{G}_d\) in Eq. \eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and the two off-diagonal (coupling) terms are opposite.
-The bode plot of these two distinct terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
+The bode plot of these two terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
 These plots confirm the expected behavior: the frequency of the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgcb8c9c7}
+\label{sec:orgf541d3f}
 \label{sec:iff}
@@
 
-In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers simultaneously.
+In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers \(K_F\) simultaneously.
 As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
@@
 
-In order to apply Decentralized IFF on rotating platforms, two solutions are proposed to deal with this instability problem.
+In order to apply decentralized IFF on rotating platforms, two solutions are proposed to deal with this instability problem.
 The first one consists of slightly modifying the control law (Section \ref{sec:iff_hpf}) while the second one consists of adding springs in parallel with the force sensors (Section \ref{sec:iff_kp}).
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:org0b913ec}
+\label{sec:orgf53673d}
 \label{sec:iff_hpf}
@@
 \label{eq:IFF_LHF}
-  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
+  K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
 \end{equation}
@@
 In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Loci for several \(\omega_i\) are displayed in Figure \ref{fig:root_locus_wi_modified_iff}.
-It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the suspension modes, the control gain \(g\) may be limited to small values due to Eq.
-\eqref{eq:gmax_iff_hpf}.
+It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the suspension modes, the control gain \(g\) may be limited to small values due to \eqref{eq:gmax_iff_hpf}.
 
@@
 
-In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of the \(\omega_i/\omega_0\).
+In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of \(\omega_i/\omega_0\).
 The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also displayed and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi}).
@@
 \item \(0.02 < \omega_i/\omega_0 < 0.2\): the attainable damping ratio is maximized and is reached for \(g \approx 2\)
-\item \(0.2 < \omega_i/\omega_0\): the added damping decreases as the \(\omega_i/\omega_0\) increases
+\item \(0.2 < \omega_i/\omega_0\): the added damping decreases as \(\omega_i/\omega_0\) increases
 \end{itemize}
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org082b3c2}
+\label{sec:org4c124af}
 \label{sec:iff_kp}
@@
 \par
-The forces \(\begin{bmatrix}f_u, f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_parallel_springs} are equal to
+The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_parallel_springs} are equal to
 \begin{equation}
@@
 \section{Comparison and Discussion}
-\label{sec:org1f46ad4}
+\label{sec:org537f1b3}
 \label{sec:comparison}
@@
 Very similar results are obtained for the two proposed IFF modifications in terms of transmissibility (Figure \ref{fig:comp_transmissibility}) and compliance (Figure \ref{fig:comp_compliance}).
-It is also confirmed that these two techniques can significantly damp the system's resonances.
+It is also confirmed that these two techniques can significantly damp the suspension modes.
 
@@
 \section{Conclusion}
-\label{sec:org071db57}
+\label{sec:orga805aaa}
 \label{sec:conclusion}
 
-Due to gyroscopic effects, decentralized IFF with pure integrators was shown not to be stable when applied to rotating platforms.
+Due to gyroscopic effects, decentralized IFF with pure integrators was shown to be unstable when applied to rotating platforms.
 Two modifications of the classical IFF control have been proposed to overcome this issue.
@@
 Additional springs are added in parallel with the actuators and force sensors.
-It was shown that if the stiffness \(k_p\) of the addition springs is larger than the negative stiffness \(m \Omega^2\) induced by centrifugal forces, the classical decentralized IFF regains its unconditional stability property.
+It was shown that if the stiffness \(k_p\) of the additional springs is larger than the negative stiffness \(m \Omega^2\) induced by centrifugal forces, the classical decentralized IFF regains its unconditional stability property.
 
@@
 \section*{Acknowledgment}
-\label{sec:orgd8daf24}
+\label{sec:orge39bf3f}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-07-09 matlab/matlab/s1_system_description.m
Update Matlab code

@@ -43,24 +43,25 @@ for p_i = 1:size(p_ws, 1)
 end
 plot(Ws, zeros(size(Ws)), 'k--')
 hold off;
-xlabel('Rotation Frequency [rad/s]'); ylabel('Real Part');
+xlabel('Rotational Speed [rad/s]'); ylabel('Real Part');
 
 ax2 = subplot(1,2,2);
 hold on;
 for p_i = 1:size(p_ws, 1)
-    plot(Ws,  imag(p_ws(p_i, :)), 'k-')
-    plot(Ws, -imag(p_ws(p_i, :)), 'k-')
+    plot(Ws, imag(p_ws(p_i, :)), 'k-')
 end
 hold off;
-xlabel('Rotation Frequency [rad/s]'); ylabel('Imaginary Part');
+xlabel('Rotational Speed [rad/s]'); ylabel('Imaginary Part');
 
 % Simscape Model
-% Define the rotating speed for the Simscape Model.
+% In order to validate all the equations of motion, a Simscape model of the same system has been developed.
+% The dynamics of the system can be identified from the Simscape model and compare with the analytical model.
+
+% The rotating speed for the Simscape Model is defined.
 
 W = 0.1; % Rotation Speed [rad/s]
 
 Kiff = tf(zeros(2));
-Kdvf = tf(zeros(2));
 
 kp = 0; % Parallel Stiffness [N/m]
 cp = 0; % Parallel Damping [N/(m/s)]
@@ -206,7 +207,7 @@ title('$d_u/F_v$, $d_v/F_u$');
 ax4 = subplot(2, 2, 4);
 hold on;
 for W_i = 1:length(Ws)
-    plot(freqs, 180/pi*angle(squeeze(freqresp(Gs{W_i}(1,1), freqs))))
+    plot(freqs, 180/pi*angle(squeeze(freqresp(Gs{W_i}(2,1), freqs))))
 end
 set(gca, 'XScale', 'log'); set(gca, 'YScale', 'lin');
 xlabel('Frequency [rad/s]'); ylabel('Phase [deg]');

### 2020-07-09 matlab/matlab/s2_iff_pure_int.m

@@ -17,13 +17,12 @@ w0 = sqrt(k/m); % [rad/s]
 kp = 0; % [N/m]
 cp = 0; % [N/(m/s)]
 
-% Simscape Model
+% Comparison of the Analytical Model and the Simscape Model
 % The rotation speed is set to $\Omega = 0.1 \omega_0$.
 
 W = 0.1*w0; % [rad/s]
 
 Kiff = tf(zeros(2));
-Kdvf = tf(zeros(2));
 
 open('rotating_frame.slx');
 
@@ -45,7 +44,8 @@ Giff = linearize(mdl, io, 0);
 Giff.InputName  = {'Fu', 'Fv'};
 Giff.OutputName = {'fu', 'fv'};
 
-% Comparison of the Analytical Model and the Simscape Model
+
+
 % The same transfer function from $[F_u, F_v]$ to $[f_u, f_v]$ is written down from the analytical model.
 
 Giff_th = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
@@ -55,7 +55,6 @@ Giff_th = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2)
 
 
 % The two are compared in Figure [[fig:plant_iff_comp_simscape_analytical]] and found to perfectly match.
-
 
 freqs = logspace(-1, 1, 1000);
 

### 2020-07-09 matlab/matlab/s3_iff_hpf.m

@@ -206,41 +206,36 @@ xlabel('Real Part'); ylabel('Imaginary Part');
 
 % While it seems that small $\omega_i$ do allow more damping to be added to the system (Figure [[fig:root_locus_wi_modified_iff]]), the control gains may be limited to small values due to eqref:eq:iff_gmax thus reducing the attainable damping.
 
-
 % There must be an optimum for $\omega_i$.
 % To find the optimum, the gain that maximize the simultaneous damping of the mode is identified for a wide range of $\omega_i$ (Figure [[fig:mod_iff_damping_wi]]).
 
-wis = logspace(-2, 1, 31)*w0; % [rad/s]
 
-opt_zeta = zeros(1, length(wis)); % Optimal simultaneous damping
+wis = logspace(-2, 1, 100)*w0; % [rad/s]
+
+opt_xi = zeros(1, length(wis)); % Optimal simultaneous damping
 opt_gain = zeros(1, length(wis)); % Corresponding optimal gain
 
 for wi_i = 1:length(wis)
     wi = wis(wi_i);
-    gains = linspace(0, (w0^2/W^2 - 1)*wi, 100);
+    Kiff = 1/(s + wi)*eye(2);
 
-    for g = gains
-        Kiff = (g/(wi+s))*eye(2);
+    fun = @(g)computeSimultaneousDamping(g, Giff, Kiff);
 
-        [w, zeta] = damp(minreal(feedback(Giff, Kiff)));
-
-        if min(zeta) > opt_zeta(wi_i) && all(zeta > 0)
-            opt_zeta(wi_i) = min(zeta);
-            opt_gain(wi_i) = g;
-        end
-    end
+    [g_opt, xi_opt] = fminsearch(fun, 0.5*wi*((w0/W)^2 - 1));
+    opt_xi(wi_i) = 1/xi_opt;
+    opt_gain(wi_i) = g_opt;
 end
 
 figure;
 yyaxis left
-plot(wis, opt_zeta, '-o', 'DisplayName', '$\xi_{cl}$');
+plot(wis, opt_xi, '-', 'DisplayName', '$\xi_{cl}$');
 set(gca, 'YScale', 'lin');
 ylim([0,1]);
 ylabel('Attainable Damping Ratio $\xi$');
 
 yyaxis right
 hold on;
-plot(wis, opt_gain, '-x', 'DisplayName', '$g_{opt}$');
[…]

### 2020-07-09 matlab/matlab/s4_iff_kp.m

@@ -1,61 +1,339 @@
-% Attainable Damping as a function of $k_p$
+%% Clear Workspace and Close figures
+clear; close all; clc;
 
-tic;
-alphas = logspace(-2, 0, 10);
-gains = linspace(0.5, 2.5, 100);
+%% Intialize Laplace variable
+s = zpk('s');
 
-opt_zeta = zeros(1, length(alphas)); % Optimal simultaneous damping
-opt_gain = zeros(1, length(alphas)); % Corresponding optimal gain
+% Plant Parameters
+% Let's define initial values for the model.
 
-for alpha_i = 1:length(alphas)
-    kp = alphas(alpha_i);
-    k = 1 - alphas(alpha_i);
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+kp = 0; % [N/m]
+cp = 0; % [N/(m/s)]
+
+% Comparison of the Analytical Model and the Simscape Model
+% The same transfer function from $[F_u, F_v]$ to $[f_u, f_v]$ is written down from the analytical model.
+
+W = 0.1*w0; % [rad/s]
+
+kp = 1.5*m*W^2;
+cp = 0;
+
+Kiff = tf(zeros(2));
+
+open('rotating_frame.slx');
+
+%% Name of the Simulink File
+mdl = 'rotating_frame';
+
+%% Input/Output definition
+clear io; io_i = 1;
+io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
+io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
+
+Giff = linearize(mdl, io, 0);
+
+%% Input/Output definition
+Giff.InputName  = {'Fu', 'Fv'};
+Giff.OutputName = {'fu', 'fv'};
+
+w0p = sqrt((k + kp)/m);
+xip = c/(2*sqrt((k+kp)*m));
+
[…]

### 2020-07-09 matlab/matlab/s5_act_damp_comparison.m

@@ -1,0 +1,227 @@
+%% Clear Workspace and Close figures
+clear; close all; clc;
+
+%% Intialize Laplace variable
+s = zpk('s');
+
+% Plant Parameters
+% Let's define initial values for the model.
+
+k = 1;    % Actuator Stiffness [N/m]
+c = 0.05; % Actuator Damping [N/(m/s)]
+m = 1;    % Payload mass [kg]
+
+xi = c/(2*sqrt(k*m));
+w0 = sqrt(k/m); % [rad/s]
+
+kp = 0; % [N/m]
+cp = 0; % [N/(m/s)]
+
+
+
+% The rotating speed is set to $\Omega = 0.1 \omega_0$.
+
+W = 0.1*w0;
+
+% Root Locus
+% IFF with High Pass Filter
+
+wi = 0.1*w0; % [rad/s]
+
+Giff = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
+        [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
+         (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2];
+
+
+
+% IFF With parallel Stiffness
+
+kp = 5*m*W^2;
+k = k - kp;
+
+w0p = sqrt((k + kp)/m);
+xip = c/(2*sqrt((k+kp)*m));
+
+Giff_kp = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
+                   (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
[…]

### 2020-07-09 matlab/matlab/s5_dvf.m

@@ -1,159 +1,0 @@
-%% Clear Workspace and Close figures
-clear; close all; clc;
-
-%% Intialize Laplace variable
-s = zpk('s');
-
-% Plant Parameters
-% Let's define initial values for the model.
-
-k = 1;    % Actuator Stiffness [N/m]
-c = 0.05; % Actuator Damping [N/(m/s)]
-m = 1;    % Payload mass [kg]
-
-xi = c/(2*sqrt(k*m));
-w0 = sqrt(k/m); % [rad/s]
-
-kp = 0; % [N/m]
-cp = 0; % [N/(m/s)]
-
-% Comparison of the Analytical Model and the Simscape Model
-% The rotating speed is set to $\Omega = 0.1 \omega_0$.
-
-W = 0.1*w0;
-
-Kiff = tf(zeros(2));
-Kdvf = tf(zeros(2));
-
-open('rotating_frame.slx');
-
-
-
-% And the transfer function from $[F_u, F_v]$ to $[v_u, v_v]$ is identified using the Simscape model.
-
-%% Name of the Simulink File
-mdl = 'rotating_frame';
-
-%% Input/Output definition
-clear io; io_i = 1;
-io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
-io(io_i) = linio([mdl, '/G'], 1, 'openoutput'); io_i = io_i + 1;
-
-Gdvf = linearize(mdl, io, 0);
-
-%% Input/Output definition
-Gdvf.InputName  = {'Fu', 'Fv'};
-Gdvf.OutputName = {'Vu', 'Vv'};
-
-
-
-% The same transfer function from $[F_u, F_v]$ to $[v_u, v_v]$ is written down from the analytical model.
-
-Gdvf_th = (s/k)/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
-          [(s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2), 2*W*s/(w0^2) ; ...
-           -2*W*s/(w0^2), (s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)];
-
-Gdvf_th.InputName  = {'Fu', 'Fv'};
-Gdvf_th.OutputName = {'vu', 'vv'};
-
-
-
[…]

### 2020-07-09 matlab/matlab/s6_act_damp_comparison.m

@@ -1,364 +1,0 @@
-%% Clear Workspace and Close figures
-clear; close all; clc;
-
-%% Intialize Laplace variable
-s = zpk('s');
-
-% Plant Parameters
-% Let's define initial values for the model.
-
-k = 1;    % Actuator Stiffness [N/m]
-c = 0.05; % Actuator Damping [N/(m/s)]
-m = 1;    % Payload mass [kg]
-
-xi = c/(2*sqrt(k*m));
-w0 = sqrt(k/m); % [rad/s]
-
-kp = 0; % [N/m]
-cp = 0; % [N/(m/s)]
-
-
-
-% The rotating speed is set to $\Omega = 0.1 \omega_0$.
-
-W = 0.1*w0;
-
-% Root Locus
-% IFF with High Pass Filter
-
-wi = 0.1*w0; % [rad/s]
-
-Giff = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
-        [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
-         (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2];
-
-
-
-% IFF With parallel Stiffness
-
-kp = 5*m*W^2;
-k = k - kp;
-
-w0p = sqrt((k + kp)/m);
-xip = c/(2*sqrt((k+kp)*m));
-
-Giff_kp = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
-                   (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
[…]

### 2020-07-09 matlab/src/computeSimultaneousDamping.m

@@ -1,4 +1,4 @@
-% Compute Damping
+% =computeSimultaneousDamping=
 
 function [xi_min] = computeSimultaneousDamping(g, G, K)
     [w, xi] = damp(minreal(feedback(G, g*K)));

### 2020-07-09 matlab/matlab/s1_system_description.m
Tangle matlab files and add links

@@ -79,7 +79,7 @@ mdl = 'rotating_frame';
 %% Input/Output definition
 clear io; io_i = 1;
 io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
-io(io_i) = linio([mdl, '/G'], 3, 'openoutput'); io_i = io_i + 1;
+io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
 
 G = linearize(mdl, io, 0);
 

### 2020-07-09 matlab/matlab/s2_iff_pure_int.m

@@ -36,7 +36,7 @@ mdl = 'rotating_frame';
 %% Input/Output definition
 clear io; io_i = 1;
 io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
-io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
+io(io_i) = linio([mdl, '/G'], 1, 'openoutput'); io_i = io_i + 1;
 
 Giff = linearize(mdl, io, 0);
 

### 2020-07-09 matlab/matlab/s4_iff_kp.m

@@ -35,7 +35,7 @@ mdl = 'rotating_frame';
 %% Input/Output definition
 clear io; io_i = 1;
 io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
-io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
+io(io_i) = linio([mdl, '/G'], 1, 'openoutput'); io_i = io_i + 1;
 
 Giff = linearize(mdl, io, 0);
 

### 2020-07-29 talk/talk.tex
Add first version of the talk

% Created 2020-07-29 mer. 15:27
% Intended LaTeX compiler: pdflatex
\documentclass[t, minted]{clean-beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{tikz}
\usetikzlibrary{decorations.text}
\author[shortname]{Thomas Dehaeze \inst{1,3} \and Christophe Collette \inst{1,2}}
\institute[shortinst]{\inst{1} Precision Mechatronics Laboratory, University of Liege, Belgium \and %
\inst{2} BEAMS Department, Free University of Brussels, Belgium \and %
\inst{3} European Synchrotron Radiation Facility, Grenoble, France}
\titlegraphic{\includegraphics[height=1.5cm]{figs/logo_pml.png} \hspace{5em} %
\includegraphics[height=1.5cm]{figs/logo_esrf.png} \hspace{5em} %
\includegraphics[height=1.5cm]{figs/logo_isma.png}}
\beamertemplatenavigationsymbolsempty
\addtobeamertemplate{navigation symbols}{}{%
\usebeamerfont{footline}%
\usebeamercolor[fg]{footline}%
\hspace{1em}%
\insertframenumber/\inserttotalframenumber
}
\setbeamertemplate{itemize items}[circle]
\usefonttheme[onlymath]{serif}
\AtBeginSection[]{
\begin{frame}<beamer>{Outline}
\tableofcontents[currentsection, hideothersubsections, sectionstyle=show/shaded]
\end{frame}
}
\usetheme{default}
\date{}
\title{Active Damping of Rotating Platforms using Integral Force Feedback}
\subtitle{ISMA-USD 2020, September 7-9, 2020}
\hypersetup{
 pdfauthor={},
 pdftitle={Active Damping of Rotating Platforms using Integral Force Feedback},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{frame}{Outline}
\tableofcontents
\end{frame}

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:orge7d05a8}
\begin{frame}[label={sec:orgb466daa}]{Model of a Rotating Positioning Platform}
\begin{columns}
\begin{column}{0.55\columnwidth}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/system.pdf}
\caption{Schematic of the studied System}
\end{figure}
\end{column}

\begin{column}{0.45\columnwidth}
Simplest model to study the \textbf{gyroscopic effects} on Decentralized IFF

\vspace{1em}

Assumptions:
\begin{itemize}
\item Perfect Rotating Stage
\item \(\dot{\theta}(t) = \Omega = \text{cst}\)
\item Small displacements
\item Position of the mass described by \([d_u\ d_v]\)
\end{itemize}

\vspace{1em}

Two frames:
\begin{itemize}
\item Inertial frame \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\)
\item Uniform rotating frame \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\)
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}[label={sec:orgc029b67}]{Equations of Motion - Lagrangian Formalism}
\vspace{-1em}
\begin{equation*}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation*}
with \(L = T - V\) the Lagrangian, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable.
\begin{align*}
  T &= \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \quad V = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right) \\
  D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
\end{align*}
\vspace{-1em}
\begin{align*}
  m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega^2 ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
  m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega^2}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
\end{align*}
\begin{cbox}[]{blue}{}
\begin{center}
Centrifugal forces \(\Longleftrightarrow\) Negative Stiffness

Coriolis Forces \(\Longleftrightarrow\) Coupling
\end{center}
\end{cbox}
\end{frame}

\begin{frame}[label={sec:org9fc6840}]{Transfer Function Matrix the Laplace domain}
\vspace{-1em}
\begin{equation*}
  {\scriptsize \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}}
\end{equation*}
\begin{equation*}
  {\scriptsize \bm{G}_{d} =
               \frac{1}{k}
               \begin{bmatrix}
                 \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
                 \frac{- 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
               \end{bmatrix}}
\end{equation*}

\begin{figure}[htbp]
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\hfill
\caption{Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
\centering
\end{figure}
\end{frame}

\begin{frame}[label={sec:orge87dc7b}]{Bode Plots of the System's Dynamics}
\begin{figure}[htbp]
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
\end{subfigure}
\hfill
\caption{Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
\centering
\end{figure}

For all the numerical analysis, \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
\end{frame}

\section{Problem with the Decentralized Integral Force Feedback}
\label{sec:org59c3dbc}
\begin{frame}[label={sec:org6faf2d3}]{Force Sensors and Control Architecture}
\vspace{-1em}
\begin{columns}
\begin{column}{0.6\columnwidth}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/system_iff.pdf}
\caption{System with added Force Sensor in series with the actuators}
\end{figure}
\end{column}

\begin{column}{0.4\columnwidth}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/control_diagram_iff.pdf}
\caption{Control Diagram for decentralized IFF}
\end{figure}

\begin{equation*}
  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}
\end{equation*}

\begin{equation*}
  K_F(s) = g \cdot \frac{1}{s}
\end{equation*}
\end{column}
\end{columns}
\end{frame}

\begin{frame}[label={sec:org387ca99}]{Plant Dynamics}
\vspace{-1em}

\begin{equation*}
  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation*}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
\caption{Bode plot of the diagonal terms of \(\bm{G}_f\) for several rotational speeds \(\Omega\)}
\end{figure}
\end{frame}

\begin{frame}[label={sec:orgb8d521c}]{Decentralized IFF with Pure Integrators}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.7\linewidth]{figs/root_locus_pure_iff.pdf}
\caption{Root Locus for Decentralized IFF for several rotating speeds \(\Omega\)}
\end{figure}

\vspace{-1em}

\begin{cbox}[]{blue}{}
\centering For \(\Omega > 0\), the closed loop system is unstable
\end{cbox}
\end{frame}

\section{Modification of the control law: Add High-Pass Filter}
\label{sec:orgc733c30}
\begin{frame}[label={sec:orga459f5e}]{Modification of the Control Low}
\vspace{-1em}

\begin{equation*}
  K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
\end{equation*}

\begin{minipage}[b]{0.45\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/loop_gain_modified_iff.pdf}
\captionof{figure}{Loop Gain}
\end{center}
\end{minipage}
\hfill
\begin{minipage}[b]{0.5\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/root_locus_modified_iff.pdf}
\captionof{figure}{Root Locus}
\end{center}
\end{minipage}

\vspace{-1em}

\begin{align*}
\text{Added HPF} &\Longleftrightarrow \text{limit the low frequency gain} \\
                 &\Longleftrightarrow \text{shift the pole to the left along the real axis} \\
                 &\Longrightarrow \text{stable system for small values of the gain}
\end{align*}
\end{frame}

\begin{frame}[label={sec:org4390eac}]{Effect of \(\omega_i\) on the attainable damping}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_wi_modified_iff.pdf}
\caption{Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

\vspace{-2em}

\begin{columns}
\begin{column}{0.3\columnwidth}
\begin{equation*}
  g_{\text{max}} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right)
\end{equation*}
\end{column}

\begin{column}{0.7\columnwidth}
\begin{cbox}[]{blue}{}
small \(\omega_i\) \(\Longrightarrow\) increase maximum damping

small \(\omega_i\) \(\Longrightarrow\) reduces maximum gain \(g_\text{max}\)
\end{cbox}
\end{column}
\end{columns}
\end{frame}

\begin{frame}[label={sec:org84c72de}]{Optimal Control Parameters}
\vspace{1em}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/mod_iff_damping_wi.pdf}
\caption{Attainable damping ratio \(\xi_\text{cl}\) as a function of the ratio \(\omega_i/\omega_0\). Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
\end{figure}
\end{frame}

\section{Modification of the Mechanical System: Parallel Stiffness}
\label{sec:orgfa77c9b}
\begin{frame}[label={sec:org4d07a64}]{Stiffness in Parallel with the Force Sensor}
\vspace{-1em}
\begin{columns}
\begin{column}{0.6\columnwidth}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
\caption{Studied system with additional springs in parallel with the actuators and force sensors}
\end{figure}
\end{column}

\begin{column}{0.4\columnwidth}
\begin{cbox}[Intuitive Idea]{blue}{}
\(k_p\) is used to counteract the negative stiffness \(-m\Omega^2\) when high control gains are used.
\end{cbox}

\vspace{-2em}

\begin{align*}
  k_p &= \alpha k \\
  k_a &= (1 - \alpha) k
\end{align*}
with \(0 < \alpha < 1\).

\vspace{1em}

The overall stiffness \(k = k_a + k_p = \text{cst}\) \(\Longrightarrow\) the open-loop poles remains unchanged
\end{column}
\end{columns}
\end{frame}

\begin{frame}[label={sec:org223db59}]{Effect of the Parallel Stiffness on the Plant Dynamics}
\begin{minipage}[b]{0.42\linewidth}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/plant_iff_kp.pdf}
\caption{Bode Plot of \(f_u/F_u\) for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}
\end{minipage}
\hfill
\begin{minipage}[b]{0.55\linewidth}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
\caption{Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}
\end{minipage}

\begin{cbox}[]{blue}{}
If \(k_p > m \Omega^2\), the poles of the closed-loop system stay in the (stable) right half-plane, and hence the \textbf{unconditional stability of IFF is recovered}.
\end{cbox}
\end{frame}

\begin{frame}[label={sec:org8be51fd}]{Optimal Parallel Stiffness}
\begin{figure}[htbp]
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
\caption{\label{fig:root_locus_iff_kps} Comparison of three parallel stiffnesses \(k_p\)}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/root_locus_opt_gain_iff_kp.pdf}
\caption{\label{fig:root_locus_opt_gain_iff_kp} \(k_p = 5 m \Omega^2\), optimal damping \(\xi_\text{opt}\) is shown}
\end{subfigure}
\hfill
\caption{Root Locus for IFF when parallel stiffness \(k_p\) is added, \(\Omega = 0.1 \omega_0\)}
\centering
\end{figure}

\begin{cbox}[]{blue}{}
\centering
Large parallel stiffness \(k_p\) reduces the attainable damping.
\end{cbox}
\end{frame}

\section{Comparison of the two Proposed Modifications}
\label{sec:orge227508}
\begin{frame}[label={sec:org783f2c4}]{Comparison of the Attainable Damping}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.7\linewidth]{figs/comp_root_locus.pdf}
\caption{Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
\end{figure}
\end{frame}

\begin{frame}[label={sec:orgdd42828}]{Comparison Transmissibility and Compliance}
\begin{figure}[htbp]
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
\caption{\label{fig:comp_compliance} Compliance}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
\caption{\label{fig:comp_transmissibility} Transmissibility}
\end{subfigure}
\hfill
\caption{Comparison of the two proposed Active Damping Techniques, \(\Omega = 0.1 \omega_0\)}
\centering
\end{figure}
\end{frame}

\begin{frame}[label={sec:org5db221d}]{Conclusion \& Further work}
The two proposed techniques gives almost identical results but are very different when it comes to their implementations

\vspace{2em}

The best technique depends on the application

\vspace{2em}

\begin{wrapfigure}{r}{0.45\textwidth}
\vspace{-1em}
\begin{center}
\includegraphics[width=\linewidth]{figs/apa_schematic.pdf}
\end{center}
\end{wrapfigure}

Amplified Piezoelectric Actuators are a nice way to have an actuator, a force sensors and a parallel stiffness in a compact manner

\vspace{2em}

Will be tested on the nano-hexapod
\end{frame}
\end{document}

### 2020-10-08 talk/talk.tex
Last talk update

@@
-% Created 2020-07-29 mer. 15:27
+% Created 2020-08-24 lun. 18:19
 % Intended LaTeX compiler: pdflatex
@@
  pdfsubject={},
- pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
+ pdfcreator={Emacs 27.1.50 (Org mode 9.4)}, 
  pdflang={English}}
@@
 
-\section{Dynamics of Rotating Positioning Platforms}
-\label{sec:orge7d05a8}
-\begin{frame}[label={sec:orgb466daa}]{Model of a Rotating Positioning Platform}
-\begin{columns}
-\begin{column}{0.55\columnwidth}
+\section{Dynamics of Rotating Platforms}
+\label{sec:orge3e010f}
+\begin{frame}[label={sec:orgac66c89}]{Model of a Rotating Positioning Platform}
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=\linewidth]{figs/system.pdf}
+\includegraphics[width=0.7\linewidth]{figs/system.pdf}
 \caption{Schematic of the studied System}
 \end{figure}
-\end{column}
+\end{frame}
 
-\begin{column}{0.45\columnwidth}
-Simplest model to study the \textbf{gyroscopic effects} on Decentralized IFF
+\begin{frame}[label={sec:org614e76f}]{Equations of Motion - Lagrangian Formalism}
+Lagrangian equations:
+\begin{equation*}
+  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
+\end{equation*}
 
@@
 
-Assumptions:
-\begin{itemize}
-\item Perfect Rotating Stage
-\item \(\dot{\theta}(t) = \Omega = \text{cst}\)
-\item Small displacements
-\item Position of the mass described by \([d_u\ d_v]\)
-\end{itemize}
-
-\vspace{1em}
-
-Two frames:
-\begin{itemize}
-\item Inertial frame \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\)
-\item Uniform rotating frame \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\)
-\end{itemize}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}[label={sec:orgc029b67}]{Equations of Motion - Lagrangian Formalism}
-\vspace{-1em}
-\begin{equation*}
-  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
-\end{equation*}
-with \(L = T - V\) the Lagrangian, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable.
-\begin{align*}
-  T &= \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \quad V = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right) \\
-  D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
-\end{align*}
-\vspace{-1em}
+Equations of motion:
 \begin{align*}
@@
 \end{align*}
+
+\vspace{1em}
+
 \begin{cbox}[]{blue}{}
@@
 
-\begin{frame}[label={sec:org9fc6840}]{Transfer Function Matrix the Laplace domain}
-\vspace{-1em}
-\begin{equation*}
-  {\scriptsize \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}}
-\end{equation*}
-\begin{equation*}
-  {\scriptsize \bm{G}_{d} =
-               \frac{1}{k}
-               \begin{bmatrix}
-                 \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-                 \frac{- 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-               \end{bmatrix}}
-\end{equation*}
+\begin{frame}[label={sec:org0a25ba1}]{Transfer Function Matrix the Laplace domain}
+\vspace{2em}
 
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.4\linewidth}
+\begin{subfigure}[c]{0.49\linewidth}
 \includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
@@
 \hfill
-\begin{subfigure}[c]{0.4\linewidth}
+\begin{subfigure}[c]{0.49\linewidth}
 \includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
@@
 
-\begin{frame}[label={sec:orge87dc7b}]{Bode Plots of the System's Dynamics}
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
-\end{subfigure}
-\hfill
-\caption{Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
-\centering
-\end{figure}
-
-For all the numerical analysis, \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
-\end{frame}
-
-\section{Problem with the Decentralized Integral Force Feedback}
-\label{sec:org59c3dbc}
-\begin{frame}[label={sec:org6faf2d3}]{Force Sensors and Control Architecture}
-\vspace{-1em}
-\begin{columns}
-\begin{column}{0.6\columnwidth}
+\section{Decentralized Integral Force Feedback}
+\label{sec:org8107aa6}
+\begin{frame}[label={sec:org818bd83}]{Force Sensors and Decentralized IFF Control Architecture}
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=\linewidth]{figs/system_iff.pdf}
-\caption{System with added Force Sensor in series with the actuators}
-\end{figure}
-\end{column}
-
-\begin{column}{0.4\columnwidth}
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=\linewidth]{figs/control_diagram_iff.pdf}
-\caption{Control Diagram for decentralized IFF}
-\end{figure}
-
-\begin{equation*}
-  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}
-\end{equation*}
-
-\begin{equation*}
-  K_F(s) = g \cdot \frac{1}{s}
-\end{equation*}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}[label={sec:org387ca99}]{Plant Dynamics}
-\vspace{-1em}
-
-\begin{equation*}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
-  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
-\end{equation*}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.9\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
-\caption{Bode plot of the diagonal terms of \(\bm{G}_f\) for several rotational speeds \(\Omega\)}
+\includegraphics[width=0.7\linewidth]{figs/system_iff.pdf}
+\caption{System with added Force Sensor in series with the actuators, \(K_F(s) = g \cdot \frac{1}{s}\)}
 \end{figure}
@@
 
-\begin{frame}[label={sec:orgb8d521c}]{Decentralized IFF with Pure Integrators}
+\begin{frame}[label={sec:org159eb7e}]{IFF Plant Dynamics}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
+\caption{Bode plot of the dynamics from force actuator to force sensor for several rotational speeds \(\Omega\)}
+\end{figure}
+\end{frame}
+
+\begin{frame}[label={sec:orge6035da}]{Decentralized IFF with Pure Integrators}
 \begin{figure}[htbp]
@@
 
-\section{Modification of the control law: Add High-Pass Filter}
-\label{sec:orgc733c30}
-\begin{frame}[label={sec:orga459f5e}]{Modification of the Control Low}
-\vspace{-1em}
-
+\section{Integral Force Feedback with High Pass Filter}
+\label{sec:org789619d}
+\begin{frame}[label={sec:org2020343}]{Modification of the Control Law}
 \begin{equation*}
@@
 \end{equation*}
+
+\vspace{1em}
 
@@
 \end{minipage}
-
-\vspace{-1em}
-
-\begin{align*}
-\text{Added HPF} &\Longleftrightarrow \text{limit the low frequency gain} \\
-                 &\Longleftrightarrow \text{shift the pole to the left along the real axis} \\
-                 &\Longrightarrow \text{stable system for small values of the gain}
-\end{align*}
 \end{frame}
 
-\begin{frame}[label={sec:org4390eac}]{Effect of \(\omega_i\) on the attainable damping}
+\begin{frame}[label={sec:org38b9bd2}]{Effect of \(\omega_i\) on the attainable damping}
 \begin{figure}[htbp]
@@
 
-\begin{frame}[label={sec:org84c72de}]{Optimal Control Parameters}
+\begin{frame}[label={sec:orga2c2166}]{Optimal Control Parameters}
 \vspace{1em}
@@
 
-\section{Modification of the Mechanical System: Parallel Stiffness}
-\label{sec:orgfa77c9b}
-\begin{frame}[label={sec:org4d07a64}]{Stiffness in Parallel with the Force Sensor}
-\vspace{-1em}
-\begin{columns}
-\begin{column}{0.6\columnwidth}
+\section{Integral Force Feedback with Parallel Springs}
+\label{sec:org7a61560}
+\begin{frame}[label={sec:orga6be4f6}]{Stiffness in Parallel with the Force Sensor}
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
-\caption{Studied system with additional springs in parallel with the actuators and force sensors}
+\includegraphics[width=0.65\linewidth]{figs/system_parallel_springs.pdf}
+\caption{System with additional springs in parallel with the actuators and force sensors}
 \end{figure}
-\end{column}
-
-\begin{column}{0.4\columnwidth}
-\begin{cbox}[Intuitive Idea]{blue}{}
-\(k_p\) is used to counteract the negative stiffness \(-m\Omega^2\) when high control gains are used.
-\end{cbox}
-
-\vspace{-2em}
-
-\begin{align*}
-  k_p &= \alpha k \\
-  k_a &= (1 - \alpha) k
-\end{align*}
-with \(0 < \alpha < 1\).
-
-\vspace{1em}
-
-The overall stiffness \(k = k_a + k_p = \text{cst}\) \(\Longrightarrow\) the open-loop poles remains unchanged
-\end{column}
-\end{columns}
 \end{frame}
 
-\begin{frame}[label={sec:org223db59}]{Effect of the Parallel Stiffness on the Plant Dynamics}
+\begin{frame}[label={sec:org497c282}]{Effect of the Parallel Stiffness on the Plant Dynamics}
 \begin{minipage}[b]{0.42\linewidth}
@@
 \includegraphics[width=\linewidth]{figs/plant_iff_kp.pdf}
-\caption{Bode Plot of \(f_u/F_u\) for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\caption{Bode Plot of \(f_u/F_u\)}
 \end{figure}
@@
 \includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
-\caption{Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\caption{Root Locus for IFF}
 \end{figure}
 \end{minipage}
+
+\vspace{1em}
 
@@
 
-\begin{frame}[label={sec:org8be51fd}]{Optimal Parallel Stiffness}
+\begin{frame}[label={sec:orgd7eccc9}]{Optimal Parallel Stiffness}
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
-\caption{\label{fig:root_locus_iff_kps} Comparison of three parallel stiffnesses \(k_p\)}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/root_locus_opt_gain_iff_kp.pdf}
-\caption{\label{fig:root_locus_opt_gain_iff_kp} \(k_p = 5 m \Omega^2\), optimal damping \(\xi_\text{opt}\) is shown}
-\end{subfigure}
-\hfill
-\caption{Root Locus for IFF when parallel stiffness \(k_p\) is added, \(\Omega = 0.1 \omega_0\)}
 \centering
+\includegraphics[width=0.60\linewidth]{figs/root_locus_iff_kps.pdf}
+\caption{Root Locus for three parallel stiffnesses \(k_p\)}
 \end{figure}
@@
 
-\section{Comparison of the two Proposed Modifications}
-\label{sec:orge227508}
-\begin{frame}[label={sec:org783f2c4}]{Comparison of the Attainable Damping}
+\section{Comparison and Discussion}
+\label{sec:org79d4359}
+\begin{frame}[label={sec:org7dda174}]{Comparison of the Attainable Damping}
 \begin{figure}[htbp]
@@
 
-\begin{frame}[label={sec:orgdd42828}]{Comparison Transmissibility and Compliance}
+\begin{frame}[label={sec:org9effb95}]{Comparison Transmissibility and Compliance}
 \begin{figure}[htbp]
@@
 
-\begin{frame}[label={sec:org5db221d}]{Conclusion \& Further work}
-The two proposed techniques gives almost identical results but are very different when it comes to their implementations
+\begin{frame}[label={sec:org46c3efd}]{}
+\vspace{8em}
+\begin{center}
+\Huge Thank you!
+\end{center}
+\vspace{8em}
 
-\vspace{2em}
-
-The best technique depends on the application
-
-\vspace{2em}
-
-\begin{wrapfigure}{r}{0.45\textwidth}
-\vspace{-1em}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/apa_schematic.pdf}
-\end{center}
-\end{wrapfigure}
-
-Amplified Piezoelectric Actuators are a nice way to have an actuator, a force sensors and a parallel stiffness in a compact manner
-
-\vspace{2em}
-
-Will be tested on the nano-hexapod
+Contact: \href{mailto:dehaeze.thomas@gmail.com}{dehaeze.thomas@gmail.com}
+\vspace{1em}
+\small \url{https://tdehaeze.github.io/dehaeze20\_contr\_stewa\_platf/}
 \end{frame}

### 2020-10-26 journal/_region_.tex
Add Journal folder for extended publication

--- 2020-07-09 paper/paper.tex
@@
-% Created 2020-07-09 jeu. 09:06
+\message{ !name(paper.tex)}% Created 2020-10-20 mar. 17:19
 % Intended LaTeX compiler: pdflatex
-\documentclass{ISMA_USD2020}
+\documentclass[Afour,sageh,times]{sagej}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{siunitx}
+\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
 \usepackage{amsmath,amssymb,amsfonts, cases}
@@
 \usepackage[USenglish, english]{babel}
-\setcounter{footnote}{1}
-\input{config.tex}
-\author[1,3] {T. Dehaeze}
-\author[1,2] {C. Collette}
-\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
-\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
-\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
-\bibliographystyle{IEEEtran}
 \usepackage{tikz}
 \usetikzlibrary{shapes.misc,arrows,arrows.meta}
+\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\def\volumeyear{2016}
+\author{Dehaeze Thomas\affilnum{1} and Collette Christophe\affilnum{2}}
+\affiliation{\affilnum{1}Precision Mechatronics Laboratory, University of Liege, Belgium\\
+\affilnum{2}BEAMS Department, Free University of Brussels, Belgium\\
+\affilnum{3}European Synchrotron Radiation Facility, Grenoble, France}
+\email{dehaeze.thomas@gmail.com}
+\bibliographystyle{SageH}
 \date{}
 \title{Active Damping of Rotating Platforms using Integral Force Feedback}
-\hypersetup{
- pdfauthor={},
- pdftitle={Active Damping of Rotating Platforms using Integral Force Feedback},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
- pdflang={English}}
+\input{abstract.tex}
 \begin{document}
 
-\maketitle
+\message{ !name(paper.tex) !offset(-4) }
+\input{abstract.tex}
+\message{ !name(paper.tex) !offset(511) }
 
-\abstract{
-This paper investigates the use of Integral Force Feedback (IFF) for the active damping of rotating mechanical systems.
-Guaranteed stability, typical benefit of IFF, is lost as soon as the system is rotating due to gyroscopic effects.
-To overcome this issue, two modifications of the classical IFF control scheme are proposed.
-The first consists of slightly modifying the control law while the second consists of adding springs in parallel with the force sensors.
-Conditions for stability and optimal parameters are derived.
-The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on suspension modes.
-}
-
-\section{Introduction}
-\label{sec:orgf2d9f1e}
-\label{sec:introduction}
-There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
-A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
-In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.
-
-In \cite{preumont92_activ_dampin_by_local_force}, the Integral Force Feedback (IFF) control scheme has been proposed, where a force sensor, a force actuator and an integral controller are used to directly augment the damping of a mechanical system.
-When the force sensor is collocated with the actuator, the open-loop transfer function has alternating poles and zeros which facilitate to guarantee the stability of the closed loop system \cite{preumont02_force_feedb_versus_accel_feedb}.
-
-However, when the platform is rotating, gyroscopic effects alter the system dynamics and IFF cannot be applied as is.
-The purpose of this paper is to study how the IFF strategy can be adapted to deal with these Gyroscopic effects.
-
-The paper is structured as follows.
-Section \ref{sec:dynamics} presents a simple model of a rotating suspended platform that will be used throughout this study.
-Section \ref{sec:iff} explains how the unconditional stability of IFF is lost due to Gyroscopic effects induced by the rotation.
-Section \ref{sec:iff_hpf} suggests a simple modification of the control law such that damping can be added to the suspension modes in a robust way.
-Section \ref{sec:iff_kp} proposes to add springs in parallel with the force sensors to regain the unconditional stability of IFF.
-Section \ref{sec:comparison} compares both proposed modifications to the classical IFF in terms of damping authority and closed-loop system behavior.
-
-\section{Dynamics of Rotating Platforms}
-\label{sec:orgf97884c}
-\label{sec:dynamics}
-In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
-Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/system.pdf}
-\caption{\label{fig:system}Schematic of the studied System}
-\end{figure}
-
-The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
-
-The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
-A payload with a mass \(m\) in \(\si{\kilo\gram}\), representing the sensitive equipment, is mounted on the (rotating) suspended platform.
-
-Two reference frames are used: an inertial frame \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\) and a uniform rotating frame \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\) rigidly fixed on top of the rotating stage with \(\vec{i}_w\) aligned with the rotation axis.
-The position of the payload is represented by \((d_u, d_v, 0)\) expressed in the rotating frame.
-
-\par
-To obtain the equations of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
-\begin{equation}
-\label{eq:lagrangian_equations}
-  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
-\end{equation}
-with \(L = T - V\) the Lagrangian, \(T\) the kinetic coenergy, \(V\) the potential energy, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
-The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is disregarded as the motion is considered to be imposed by the rotation stage.
-\begin{equation}
-\label{eq:energy_functions_lagrange}
-  \begin{aligned}
-    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \quad V = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right),\\
-    D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
-  \end{aligned}
-\end{equation}
-
-Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} for both generalized coordinates gives two coupled differential equations
-\begin{subequations}
-\label{eq:eom_coupled}
-  \begin{align}
-    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega^2 ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
-    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega^2}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
-  \end{align}
-\end{subequations}
-
-The uniform rotation of the system induces two Gyroscopic effects as shown in \eqref{eq:eom_coupled}:
-\begin{itemize}
-\item Centrifugal forces: that can been seen as added negative stiffness \(- m \Omega^2\) along \(\vec{i}_u\) and \(\vec{i}_v\)
-\item Coriolis Forces: that couples the motion in the two orthogonal directions
-\end{itemize}
-
-\par
-To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
-\begin{align}
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix} &= \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gd_mimo_tf} \\
-  \bm{G}_{d} &=
-  \begin{bmatrix}
-    \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
-    \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}
-  \end{bmatrix} \label{eq:Gd_m_k_c}
-\end{align}
-
-To simplify the analysis, the undamped natural frequency \(\omega_0\) and the damping ratio \(\xi\) are used
-\begin{equation}
-  \omega_0 = \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second}, \quad \xi = \frac{c}{2 \sqrt{k m}}
-\end{equation}
-
-The transfer function matrix \(\bm{G}_d\) becomes equal to
-\begin{equation}
-\label{eq:Gd_w0_xi_k}
-\bm{G}_{d} =
-  \frac{1}{k}
-  \begin{bmatrix}
-    \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-    \frac{- 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-  \end{bmatrix}
-\end{equation}
-
-For all further numerical analysis in this study, we consider \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
-Even though no system with such parameters will be encountered in practice, conclusions can be drawn relative to these parameters such that they can be generalized to any other set of parameters.
-
-\par
-The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
-\begin{equation}
-  \left( \frac{p^2}{{\omega_0}^2} + 2 \xi \frac{p}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{p}{\omega_0} \right)^2 = 0
-\end{equation}
-
-Supposing small damping (\(\xi \ll 1\)), two pairs of complex conjugate poles are obtained:
-\begin{subequations}
-\label{eq:pole_values}
-  \begin{align}
-    p_{+} &= - \xi \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \pm j \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \\
-    p_{-} &= - \xi \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right) \pm j \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right)
-  \end{align}
-\end{subequations}
-
-The real part and complex part of these two pairs of complex conjugate poles are represented in Figure \ref{fig:campbell_diagram} as a function of the rotational speed \(\Omega\).
-As the rotational speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) to lower frequencies.
-The system becomes unstable for \(\Omega > \omega_0\) as the real part of \(p_{-}\) is positive.
-Physically, the negative stiffness term \(-m\Omega^2\) induced by centrifugal forces exceeds the spring stiffness \(k\).
-
-In the rest of this study, rotational speeds smaller than the undamped natural frequency of the system are assumed (\(\Omega < \omega_0\)).
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
-\caption{\label{fig:campbell_diagram_real} Real Part}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
-\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
-\end{subfigure}
-\hfill
-\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
-\centering
-\end{figure}
-
-Looking at the transfer function matrix \(\bm{G}_d\) in Eq. \eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and the two off-diagonal (coupling) terms are opposite.
-The bode plot of these two terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
-These plots confirm the expected behavior: the frequency of the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
-For \(\Omega > \omega_0\), the low frequency pair of complex conjugate poles \(p_{-}\) becomes unstable.
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
-\end{subfigure}
-\hfill
-\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
-\centering
-\end{figure}
-
-\section{Decentralized Integral Force Feedback}
-\label{sec:orgf541d3f}
-\label{sec:iff}
-In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
-As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
-The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.
-
-\begin{minipage}[t]{0.50\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/system_iff.pdf}
-\captionof{figure}{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.45\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/control_diagram_iff.pdf}
-\captionof{figure}{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
-\end{center}
-\end{minipage}
-
-\par
-The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_iff} are equal to
-\begin{equation}
-\label{eq:measured_force}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
-  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
-\end{equation}
-
-Inserting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
-\begin{align}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} &= \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gf_mimo_tf} \\
-  \bm{G}_{f} &= \begin{bmatrix}
-  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix} \label{eq:Gf}
-\end{align}
-
-The zeros of the diagonal terms of \(\bm{G}_f\) are equal to (neglecting the damping for simplicity)
-\begin{subequations}
-  \begin{align}
-    z_c &= \pm j \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} + \frac{\Omega^2}{{\omega_0}^2} + \frac{1}{2} } \label{eq:iff_zero_cc} \\
-    z_r &= \pm   \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} - \frac{\Omega^2}{{\omega_0}^2} - \frac{1}{2} } \label{eq:iff_zero_real}
-  \end{align}
-\end{subequations}
-
-The frequency of the pair of complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} always lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
-
-For non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms inducing a non-minimum phase behavior.
-This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(\SI{180}{\degree}\).
-
-The low frequency gain of \(\bm{G}_f\) increases with the rotational speed \(\Omega\)
-\begin{equation}
-\label{eq:low_freq_gain_iff_plan}
-  \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
-  \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
-  0  & \frac{\Omega^2}{{\omega_0}^2 - \Omega^2}
-\end{bmatrix}
-\end{equation}
-
-This can be explained as follows: a constant force \(F_u\) induces a small displacement of the mass \(d_u = \frac{F_u}{k - m\Omega^2}\), which increases the centrifugal force \(m\Omega^2d_u = \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} F_u\) which is then measured by the force sensors.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
-\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
-\end{figure}
-
-\par
-\label{sec:iff_pure_int}
-The two IFF controllers \(K_F\) consist of a pure integrator
-\begin{equation}
-\label{eq:Kf_pure_int}
-  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_F(s) = g \cdot \frac{1}{s}
-\end{equation}
-where \(g\) is a scalar representing the gain of the controller.
-
-In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers \(K_F\) simultaneously.
-As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
-The direction of increasing gain is indicated by arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
-\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
-\end{figure}
-
-Whereas collocated IFF is usually associated with unconditional stability \cite{preumont91_activ}, this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
-This can be seen in the Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) where the poles corresponding to the controller are bound to the right half plane implying closed-loop system instability.
-
-Physically, this can be explain like so: at low frequency, the loop gain is very large due to the pure integrators in \(K_F\).
-The control system is thus canceling the spring forces which makes the suspended platform no able to hold the payload against centrifugal forces, hence the instability.
-
-In order to apply decentralized IFF on rotating platforms, two solutions are proposed to deal with this instability problem.
-The first one consists of slightly modifying the control law (Section \ref{sec:iff_hpf}) while the second one consists of adding springs in parallel with the force sensors (Section \ref{sec:iff_kp}).
-
-\section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgf53673d}
-\label{sec:iff_hpf}
-As was explained in the previous section, the instability comes in part from the high gain at low frequency caused by the pure integrators.
-
-In order to limit this low frequency controller gain, an high pass filter (HPF) can be added to the controller
-\begin{equation}
-\label{eq:IFF_LHF}
-  K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
-\end{equation}
-
-This is equivalent to slightly shifting the controller pole to the left along the real axis.
-
-This modification of the IFF controller is typically done to avoid saturation associated with the pure integrator \cite{preumont91_activ}.
-This is however not the case in this study as it will become clear in the next section.
-
-\par
-The loop gains, \(K_F(s)\) times the direct dynamics \(f_u/F_u\), with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
-The effect of the added HPF limits the low frequency gain as expected.
-
-The Root Loci for the decentralized IFF with and without the HPF are displayed in Figure \ref{fig:root_locus_modified_iff}.
-With the added HPF, the poles of the closed loop system are shown to be stable up to some value of the gain \(g_\text{max}\)
-\begin{equation}
-\label{eq:gmax_iff_hpf}
-  g_{\text{max}} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right)
-\end{equation}
-It is interesting to note that \(g_{\text{max}}\) also corresponds to the gain where the low frequency loop gain (Figure \ref{fig:loop_gain_modified_iff}) reaches one.
-
-\begin{minipage}[b]{0.45\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
-\captionof{figure}{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.5\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
-\captionof{figure}{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-
-\par
-Two parameters can be tuned for the modified controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
-The optimal values of \(\omega_i\) and \(g\) are here considered as the values for which the damping of all the closed-loop poles are simultaneously maximized.
-
-In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Loci for several \(\omega_i\) are displayed in Figure \ref{fig:root_locus_wi_modified_iff}.
-It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the suspension modes, the control gain \(g\) may be limited to small values due to \eqref{eq:gmax_iff_hpf}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
-\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
-\end{figure}
-
-In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of \(\omega_i/\omega_0\).
-The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also displayed and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi}).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
-\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
-Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
-\end{figure}
-
-Three regions can be observed:
-\begin{itemize}
-\item \(\omega_i/\omega_0 < 0.02\): the added damping is limited by the maximum allowed control gain \(g_{\text{max}}\)
-\item \(0.02 < \omega_i/\omega_0 < 0.2\): the attainable damping ratio is maximized and is reached for \(g \approx 2\)
-\item \(0.2 < \omega_i/\omega_0\): the added damping decreases as \(\omega_i/\omega_0\) increases
-\end{itemize}
-
-\section{Integral Force Feedback with Parallel Springs}
-\label{sec:org4c124af}
-\label{sec:iff_kp}
-In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
-Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
-
-Amplified piezoelectric stack actuators can also be used for such purpose where a part of the piezoelectric stack is used as an actuator while the rest is used as a force sensor \cite{souleille18_concep_activ_mount_space_applic}.
-The parallel stiffness \(k_p\) then corresponds to the amplification structure.
-An example of such system is shown in Figure \ref{fig:cedrat_xy25xs}.
-
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
-\captionof{figure}{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/cedrat_xy25xs.png}
-\captionof{figure}{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
-\end{center}
-\end{minipage}
-
-\par
-The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_parallel_springs} are equal to
-\begin{equation}
-\label{eq:measured_force_kp}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
-  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k_a)
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
-\end{equation}
-
-In order to keep the overall stiffness \(k = k_a + k_p\) constant, thus not modifying the open-loop poles as \(k_p\) is changed, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
-\begin{equation}
-  k_p = \alpha k, \quad k_a = (1 - \alpha) k
-\end{equation}
-
-The equations of motion are derived and transformed in the Laplace domain
-\begin{align}
-\begin{bmatrix} f_u \\ f_v \end{bmatrix} &=
-\bm{G}_k
-\begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gk_mimo_tf} \\
-\bm{G}_k &=
-\begin{bmatrix}
-  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix} \label{eq:Gk}
-\end{align}
-
-Comparing \(\bm{G}_k\) \eqref{eq:Gk} with \(\bm{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
-The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros if the following condition hold
-\begin{equation}
-\label{eq:kp_cond_cc_zeros}
-  \alpha > \frac{\Omega^2}{{\omega_0}^2} \quad \Leftrightarrow \quad k_p > m \Omega^2
-\end{equation}
-
-Thus, if the added parallel stiffness \(k_p\) is higher than the negative stiffness induced by centrifugal forces \(m \Omega^2\), the direct dynamics from actuator to force sensor will show minimum phase behavior.
-This is confirmed by the Bode plot of the direct dynamics in Figure \ref{fig:plant_iff_kp}.
-
-Figure \ref{fig:root_locus_iff_kp} shows Root Loci plots for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\) when \(K_F\) is a pure integrator \eqref{eq:Kf_pure_int}.
-It is shown that if the added stiffness is higher than the maximum negative stiffness, the poles of the closed-loop system stay in the (stable) right half-plane, and hence the unconditional stability of IFF is recovered.
-
-\begin{minipage}[b]{0.43\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
-\captionof{figure}{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.53\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
-\captionof{figure}{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-
-\par
-Even though the parallel stiffness \(k_p\) has no impact on the open-loop poles (as the overall stiffness \(k\) stays constant), it has a large impact on the transmission zeros.
-Moreover, as the attainable damping is generally proportional to the distance between poles and zeros \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the parallel stiffness \(k_p\) is foreseen to have a large impact on the attainable damping.
-
-To study this effect, Root Locus plots for several parallel stiffnesses \(k_p > m \Omega^2\) are shown in Figure \ref{fig:root_locus_iff_kps}.
-The frequencies of the transmission zeros of the system are increasing with the parallel stiffness \(k_p\) and the associated attainable damping is reduced.
-Therefore, even though the parallel stiffness \(k_p\) should be larger than \(m \Omega^2\) for stability reasons, it should not be taken too high as this would limit the attainable bandwidth.
-
-This is confirmed in Figure \ref{fig:mod_iff_damping_kp} where the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) and the associated control gain \(g_\text{opt}\) are computed as a function of \(\alpha\).
-
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
-\captionof{figure}{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/mod_iff_damping_kp.pdf}
-\captionof{figure}{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
-\end{center}
-\end{minipage}
-
-\section{Comparison and Discussion}
-\label{sec:org537f1b3}
-\label{sec:comparison}
-Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
-These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
-
-For the following comparisons, the cut-off frequency for the HPF is set to \(\omega_i = 0.1 \omega_0\) and the stiffness of the parallel springs is set to \(k_p = 5 m \Omega^2\).
-
-\par
-Figure \ref{fig:comp_root_locus} shows the Root Loci for the two proposed IFF modifications.
-While the two pairs of complex conjugate open-loop poles are identical for both techniques, the transmission zeros are not.
-This means that the closed-loop behavior of both systems will differ when large control gains are used.
-
-One can observe that the closed loop poles of the system with added springs (in red) are bounded to the left half plane implying unconditional stability.
-This is not the case for the system where the controller is augmented with an HPF (in blue).
-
-It is interesting to note that the maximum added damping is very similar for both techniques and is reached for the same control gain \(g_\text{opt} \approx 2 \omega_0\).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_root_locus.pdf}
-\caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
-\end{figure}
-
-\par
-The two proposed techniques are now compared in terms of closed-loop transmissibility and compliance.
-
-The transmissibility is defined as the transfer function from the displacement of the rotating stage to the displacement of the payload.
-It is used to characterize how much vibration is transmitted through the suspended platform to the payload.
-
-The compliance describes the displacement response of the payload to external forces applied to it.
-This is a useful metric when disturbances are directly applied to the payload.
-
-The two techniques are also compared with passive damping (Figure \ref{fig:system}) where the damping coefficient \(c\) is tuned to critically damp the resonance when the rotating speed is null.
-\begin{equation}
-  c_\text{crit} = 2 \sqrt{k m}
-\end{equation}
-
-Very similar results are obtained for the two proposed IFF modifications in terms of transmissibility (Figure \ref{fig:comp_transmissibility}) and compliance (Figure \ref{fig:comp_compliance}).
-It is also confirmed that these two techniques can significantly damp the suspension modes.
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
-\caption{\label{fig:comp_transmissibility} Transmissibility}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
-\caption{\label{fig:comp_compliance} Compliance}
-\end{subfigure}
-\hfill
-\caption{\label{fig:comp_active_damping}Comparison of the two proposed Active Damping Techniques, \(\Omega = 0.1 \omega_0\)}
-\centering
-\end{figure}
-
-On can see in Figure \ref{fig:comp_transmissibility} that the problem of the degradation of the transmissibility at high frequency when using passive damping techniques is overcome by the use of IFF.
-
-The addition of the HPF or the use of the parallel stiffness permit to limit the degradation of the compliance as compared with classical IFF (Figure \ref{fig:comp_compliance}).
-
-\section{Conclusion}
-\label{sec:orga805aaa}
-\label{sec:conclusion}
-
-Due to gyroscopic effects, decentralized IFF with pure integrators was shown to be unstable when applied to rotating platforms.
-Two modifications of the classical IFF control have been proposed to overcome this issue.
-
-The first modification concerns the controller and consists of adding an high pass filter to the pure integrators.
-This is equivalent as to moving the controller pole to the left along the real axis.
-This renders the closed loop system stable up to some value of the controller gain \(g_\text{max}\).
-
-The second proposed modification concerns the mechanical system.
-Additional springs are added in parallel with the actuators and force sensors.
-It was shown that if the stiffness \(k_p\) of the additional springs is larger than the negative stiffness \(m \Omega^2\) induced by centrifugal forces, the classical decentralized IFF regains its unconditional stability property.
-
-While having very different implementations, both proposed modifications are very similar when it comes to the attainable damping and the obtained closed loop system behavior.
-
-Future work will focus on the experimental validation of the proposed active damping techniques.
-
-The Matlab code that was used for this study is available under a MIT License and archived in Zenodo \cite{dehaeze20_activ_dampin_rotat_posit_platf}.
-
-\section*{Acknowledgment}
-\label{sec:orge39bf3f}
-This research benefited from a FRIA grant from the French Community of Belgium.
-
-\bibliography{ref.bib}
 \end{document}

### 2020-10-26 journal/abstract.tex
Add Journal folder for extended publication

--- 2020-07-09 paper/paper.tex
@@
-% Created 2020-07-09 jeu. 09:06
-% Intended LaTeX compiler: pdflatex
-\documentclass{ISMA_USD2020}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{grffile}
-\usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{capt-of}
-\usepackage{hyperref}
-\usepackage[most]{tcolorbox}
-\usepackage{bm}
-\usepackage{booktabs}
-\usepackage{tabularx}
-\usepackage{array}
-\usepackage{siunitx}
-\usepackage{amsmath,amssymb,amsfonts, cases}
-\usepackage{algorithmic, graphicx, textcomp}
-\usepackage{xcolor, import, hyperref}
-\usepackage{subcaption}
-\usepackage[USenglish, english]{babel}
-\setcounter{footnote}{1}
-\input{config.tex}
-\author[1,3] {T. Dehaeze}
-\author[1,2] {C. Collette}
-\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
-\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
-\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
-\bibliographystyle{IEEEtran}
-\usepackage{tikz}
-\usetikzlibrary{shapes.misc,arrows,arrows.meta}
-\date{}
-\title{Active Damping of Rotating Platforms using Integral Force Feedback}
-\hypersetup{
- pdfauthor={},
- pdftitle={Active Damping of Rotating Platforms using Integral Force Feedback},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
- pdflang={English}}
-\begin{document}
-
-\maketitle
-
-\abstract{
+\begin{abstract}
 This paper investigates the use of Integral Force Feedback (IFF) for the active damping of rotating mechanical systems.
@@
 The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on suspension modes.
-}
-
-\section{Introduction}
-\label{sec:orgf2d9f1e}
-\label{sec:introduction}
-There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
-A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
-In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.
-
-In \cite{preumont92_activ_dampin_by_local_force}, the Integral Force Feedback (IFF) control scheme has been proposed, where a force sensor, a force actuator and an integral controller are used to directly augment the damping of a mechanical system.
-When the force sensor is collocated with the actuator, the open-loop transfer function has alternating poles and zeros which facilitate to guarantee the stability of the closed loop system \cite{preumont02_force_feedb_versus_accel_feedb}.
-
-However, when the platform is rotating, gyroscopic effects alter the system dynamics and IFF cannot be applied as is.
-The purpose of this paper is to study how the IFF strategy can be adapted to deal with these Gyroscopic effects.
-
-The paper is structured as follows.
-Section \ref{sec:dynamics} presents a simple model of a rotating suspended platform that will be used throughout this study.
-Section \ref{sec:iff} explains how the unconditional stability of IFF is lost due to Gyroscopic effects induced by the rotation.
-Section \ref{sec:iff_hpf} suggests a simple modification of the control law such that damping can be added to the suspension modes in a robust way.
-Section \ref{sec:iff_kp} proposes to add springs in parallel with the force sensors to regain the unconditional stability of IFF.
-Section \ref{sec:comparison} compares both proposed modifications to the classical IFF in terms of damping authority and closed-loop system behavior.
-
-\section{Dynamics of Rotating Platforms}
-\label{sec:orgf97884c}
-\label{sec:dynamics}
-In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
-Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/system.pdf}
-\caption{\label{fig:system}Schematic of the studied System}
-\end{figure}
-
-The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
-
-The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
-A payload with a mass \(m\) in \(\si{\kilo\gram}\), representing the sensitive equipment, is mounted on the (rotating) suspended platform.
-
-Two reference frames are used: an inertial frame \((\vec{i}_x, \vec{i}_y, \vec{i}_z)\) and a uniform rotating frame \((\vec{i}_u, \vec{i}_v, \vec{i}_w)\) rigidly fixed on top of the rotating stage with \(\vec{i}_w\) aligned with the rotation axis.
-The position of the payload is represented by \((d_u, d_v, 0)\) expressed in the rotating frame.
-
-\par
-To obtain the equations of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
-\begin{equation}
-\label{eq:lagrangian_equations}
-  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
-\end{equation}
-with \(L = T - V\) the Lagrangian, \(T\) the kinetic coenergy, \(V\) the potential energy, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
-The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is disregarded as the motion is considered to be imposed by the rotation stage.
-\begin{equation}
-\label{eq:energy_functions_lagrange}
-  \begin{aligned}
-    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \quad V = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right),\\
-    D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
-  \end{aligned}
-\end{equation}
-
-Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} for both generalized coordinates gives two coupled differential equations
-\begin{subequations}
-\label{eq:eom_coupled}
-  \begin{align}
-    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega^2 ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
-    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega^2}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
-  \end{align}
-\end{subequations}
-
-The uniform rotation of the system induces two Gyroscopic effects as shown in \eqref{eq:eom_coupled}:
-\begin{itemize}
-\item Centrifugal forces: that can been seen as added negative stiffness \(- m \Omega^2\) along \(\vec{i}_u\) and \(\vec{i}_v\)
-\item Coriolis Forces: that couples the motion in the two orthogonal directions
-\end{itemize}
-
-\par
-To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
-\begin{align}
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix} &= \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gd_mimo_tf} \\
-  \bm{G}_{d} &=
-  \begin{bmatrix}
-    \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
-    \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}
-  \end{bmatrix} \label{eq:Gd_m_k_c}
-\end{align}
-
-To simplify the analysis, the undamped natural frequency \(\omega_0\) and the damping ratio \(\xi\) are used
-\begin{equation}
-  \omega_0 = \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second}, \quad \xi = \frac{c}{2 \sqrt{k m}}
-\end{equation}
-
-The transfer function matrix \(\bm{G}_d\) becomes equal to
-\begin{equation}
-\label{eq:Gd_w0_xi_k}
-\bm{G}_{d} =
-  \frac{1}{k}
-  \begin{bmatrix}
-    \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-    \frac{- 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-  \end{bmatrix}
-\end{equation}
-
-For all further numerical analysis in this study, we consider \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
-Even though no system with such parameters will be encountered in practice, conclusions can be drawn relative to these parameters such that they can be generalized to any other set of parameters.
-
-\par
-The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
-\begin{equation}
-  \left( \frac{p^2}{{\omega_0}^2} + 2 \xi \frac{p}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{p}{\omega_0} \right)^2 = 0
-\end{equation}
-
-Supposing small damping (\(\xi \ll 1\)), two pairs of complex conjugate poles are obtained:
-\begin{subequations}
-\label{eq:pole_values}
-  \begin{align}
-    p_{+} &= - \xi \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \pm j \omega_0 \left( 1 + \frac{\Omega}{\omega_0} \right) \\
-    p_{-} &= - \xi \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right) \pm j \omega_0 \left( 1 - \frac{\Omega}{\omega_0} \right)
-  \end{align}
-\end{subequations}
-
-The real part and complex part of these two pairs of complex conjugate poles are represented in Figure \ref{fig:campbell_diagram} as a function of the rotational speed \(\Omega\).
-As the rotational speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) to lower frequencies.
-The system becomes unstable for \(\Omega > \omega_0\) as the real part of \(p_{-}\) is positive.
-Physically, the negative stiffness term \(-m\Omega^2\) induced by centrifugal forces exceeds the spring stiffness \(k\).
-
-In the rest of this study, rotational speeds smaller than the undamped natural frequency of the system are assumed (\(\Omega < \omega_0\)).
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
-\caption{\label{fig:campbell_diagram_real} Real Part}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
-\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
-\end{subfigure}
-\hfill
-\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
-\centering
-\end{figure}
-
-Looking at the transfer function matrix \(\bm{G}_d\) in Eq. \eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and the two off-diagonal (coupling) terms are opposite.
-The bode plot of these two terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
-These plots confirm the expected behavior: the frequency of the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
-For \(\Omega > \omega_0\), the low frequency pair of complex conjugate poles \(p_{-}\) becomes unstable.
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
-\end{subfigure}
-\hfill
-\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
-\centering
-\end{figure}
-
-\section{Decentralized Integral Force Feedback}
-\label{sec:orgf541d3f}
-\label{sec:iff}
-In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
-As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
-The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.
-
-\begin{minipage}[t]{0.50\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/system_iff.pdf}
-\captionof{figure}{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.45\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/control_diagram_iff.pdf}
-\captionof{figure}{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
-\end{center}
-\end{minipage}
-
-\par
-The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_iff} are equal to
-\begin{equation}
-\label{eq:measured_force}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
-  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
-\end{equation}
-
-Inserting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
-\begin{align}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} &= \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gf_mimo_tf} \\
-  \bm{G}_{f} &= \begin{bmatrix}
-  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix} \label{eq:Gf}
-\end{align}
-
-The zeros of the diagonal terms of \(\bm{G}_f\) are equal to (neglecting the damping for simplicity)
-\begin{subequations}
-  \begin{align}
-    z_c &= \pm j \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} + \frac{\Omega^2}{{\omega_0}^2} + \frac{1}{2} } \label{eq:iff_zero_cc} \\
-    z_r &= \pm   \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} - \frac{\Omega^2}{{\omega_0}^2} - \frac{1}{2} } \label{eq:iff_zero_real}
-  \end{align}
-\end{subequations}
-
-The frequency of the pair of complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} always lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
-
-For non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms inducing a non-minimum phase behavior.
-This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(\SI{180}{\degree}\).
-
-The low frequency gain of \(\bm{G}_f\) increases with the rotational speed \(\Omega\)
-\begin{equation}
-\label{eq:low_freq_gain_iff_plan}
-  \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
-  \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
-  0  & \frac{\Omega^2}{{\omega_0}^2 - \Omega^2}
-\end{bmatrix}
-\end{equation}
-
-This can be explained as follows: a constant force \(F_u\) induces a small displacement of the mass \(d_u = \frac{F_u}{k - m\Omega^2}\), which increases the centrifugal force \(m\Omega^2d_u = \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} F_u\) which is then measured by the force sensors.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
-\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
-\end{figure}
-
-\par
-\label{sec:iff_pure_int}
-The two IFF controllers \(K_F\) consist of a pure integrator
-\begin{equation}
-\label{eq:Kf_pure_int}
-  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_F(s) = g \cdot \frac{1}{s}
-\end{equation}
-where \(g\) is a scalar representing the gain of the controller.
-
-In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers \(K_F\) simultaneously.
-As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
-The direction of increasing gain is indicated by arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
-\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
-\end{figure}
-
-Whereas collocated IFF is usually associated with unconditional stability \cite{preumont91_activ}, this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
-This can be seen in the Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) where the poles corresponding to the controller are bound to the right half plane implying closed-loop system instability.
-
-Physically, this can be explain like so: at low frequency, the loop gain is very large due to the pure integrators in \(K_F\).
-The control system is thus canceling the spring forces which makes the suspended platform no able to hold the payload against centrifugal forces, hence the instability.
-
-In order to apply decentralized IFF on rotating platforms, two solutions are proposed to deal with this instability problem.
-The first one consists of slightly modifying the control law (Section \ref{sec:iff_hpf}) while the second one consists of adding springs in parallel with the force sensors (Section \ref{sec:iff_kp}).
-
-\section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgf53673d}
-\label{sec:iff_hpf}
-As was explained in the previous section, the instability comes in part from the high gain at low frequency caused by the pure integrators.
-
-In order to limit this low frequency controller gain, an high pass filter (HPF) can be added to the controller
-\begin{equation}
-\label{eq:IFF_LHF}
-  K_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
-\end{equation}
-
-This is equivalent to slightly shifting the controller pole to the left along the real axis.
-
-This modification of the IFF controller is typically done to avoid saturation associated with the pure integrator \cite{preumont91_activ}.
-This is however not the case in this study as it will become clear in the next section.
-
-\par
-The loop gains, \(K_F(s)\) times the direct dynamics \(f_u/F_u\), with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
-The effect of the added HPF limits the low frequency gain as expected.
-
-The Root Loci for the decentralized IFF with and without the HPF are displayed in Figure \ref{fig:root_locus_modified_iff}.
-With the added HPF, the poles of the closed loop system are shown to be stable up to some value of the gain \(g_\text{max}\)
-\begin{equation}
-\label{eq:gmax_iff_hpf}
-  g_{\text{max}} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right)
-\end{equation}
-It is interesting to note that \(g_{\text{max}}\) also corresponds to the gain where the low frequency loop gain (Figure \ref{fig:loop_gain_modified_iff}) reaches one.
-
-\begin{minipage}[b]{0.45\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
-\captionof{figure}{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.5\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
-\captionof{figure}{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-
-\par
-Two parameters can be tuned for the modified controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
-The optimal values of \(\omega_i\) and \(g\) are here considered as the values for which the damping of all the closed-loop poles are simultaneously maximized.
-
-In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Loci for several \(\omega_i\) are displayed in Figure \ref{fig:root_locus_wi_modified_iff}.
-It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the suspension modes, the control gain \(g\) may be limited to small values due to \eqref{eq:gmax_iff_hpf}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
-\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
-\end{figure}
-
-In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of \(\omega_i/\omega_0\).
-The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also displayed and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi}).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
-\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
-Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
-\end{figure}
-
-Three regions can be observed:
-\begin{itemize}
-\item \(\omega_i/\omega_0 < 0.02\): the added damping is limited by the maximum allowed control gain \(g_{\text{max}}\)
-\item \(0.02 < \omega_i/\omega_0 < 0.2\): the attainable damping ratio is maximized and is reached for \(g \approx 2\)
-\item \(0.2 < \omega_i/\omega_0\): the added damping decreases as \(\omega_i/\omega_0\) increases
-\end{itemize}
-
-\section{Integral Force Feedback with Parallel Springs}
-\label{sec:org4c124af}
-\label{sec:iff_kp}
-In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
-Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
-
-Amplified piezoelectric stack actuators can also be used for such purpose where a part of the piezoelectric stack is used as an actuator while the rest is used as a force sensor \cite{souleille18_concep_activ_mount_space_applic}.
-The parallel stiffness \(k_p\) then corresponds to the amplification structure.
-An example of such system is shown in Figure \ref{fig:cedrat_xy25xs}.
-
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
-\captionof{figure}{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/cedrat_xy25xs.png}
-\captionof{figure}{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
-\end{center}
-\end{minipage}
-
-\par
-The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_parallel_springs} are equal to
-\begin{equation}
-\label{eq:measured_force_kp}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
-  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k_a)
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
-\end{equation}
-
-In order to keep the overall stiffness \(k = k_a + k_p\) constant, thus not modifying the open-loop poles as \(k_p\) is changed, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
-\begin{equation}
-  k_p = \alpha k, \quad k_a = (1 - \alpha) k
-\end{equation}
-
-The equations of motion are derived and transformed in the Laplace domain
-\begin{align}
-\begin{bmatrix} f_u \\ f_v \end{bmatrix} &=
-\bm{G}_k
-\begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gk_mimo_tf} \\
-\bm{G}_k &=
-\begin{bmatrix}
-  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix} \label{eq:Gk}
-\end{align}
-
-Comparing \(\bm{G}_k\) \eqref{eq:Gk} with \(\bm{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
-The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros if the following condition hold
-\begin{equation}
-\label{eq:kp_cond_cc_zeros}
-  \alpha > \frac{\Omega^2}{{\omega_0}^2} \quad \Leftrightarrow \quad k_p > m \Omega^2
-\end{equation}
-
-Thus, if the added parallel stiffness \(k_p\) is higher than the negative stiffness induced by centrifugal forces \(m \Omega^2\), the direct dynamics from actuator to force sensor will show minimum phase behavior.
-This is confirmed by the Bode plot of the direct dynamics in Figure \ref{fig:plant_iff_kp}.
-
-Figure \ref{fig:root_locus_iff_kp} shows Root Loci plots for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\) when \(K_F\) is a pure integrator \eqref{eq:Kf_pure_int}.
-It is shown that if the added stiffness is higher than the maximum negative stiffness, the poles of the closed-loop system stay in the (stable) right half-plane, and hence the unconditional stability of IFF is recovered.
-
-\begin{minipage}[b]{0.43\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
-\captionof{figure}{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.53\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
-\captionof{figure}{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-
-\par
-Even though the parallel stiffness \(k_p\) has no impact on the open-loop poles (as the overall stiffness \(k\) stays constant), it has a large impact on the transmission zeros.
-Moreover, as the attainable damping is generally proportional to the distance between poles and zeros \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the parallel stiffness \(k_p\) is foreseen to have a large impact on the attainable damping.
-
-To study this effect, Root Locus plots for several parallel stiffnesses \(k_p > m \Omega^2\) are shown in Figure \ref{fig:root_locus_iff_kps}.
-The frequencies of the transmission zeros of the system are increasing with the parallel stiffness \(k_p\) and the associated attainable damping is reduced.
-Therefore, even though the parallel stiffness \(k_p\) should be larger than \(m \Omega^2\) for stability reasons, it should not be taken too high as this would limit the attainable bandwidth.
-
-This is confirmed in Figure \ref{fig:mod_iff_damping_kp} where the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) and the associated control gain \(g_\text{opt}\) are computed as a function of \(\alpha\).
-
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
-\captionof{figure}{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/mod_iff_damping_kp.pdf}
-\captionof{figure}{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
-\end{center}
-\end{minipage}
-
-\section{Comparison and Discussion}
-\label{sec:org537f1b3}
-\label{sec:comparison}
-Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
-These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
-
-For the following comparisons, the cut-off frequency for the HPF is set to \(\omega_i = 0.1 \omega_0\) and the stiffness of the parallel springs is set to \(k_p = 5 m \Omega^2\).
-
-\par
-Figure \ref{fig:comp_root_locus} shows the Root Loci for the two proposed IFF modifications.
-While the two pairs of complex conjugate open-loop poles are identical for both techniques, the transmission zeros are not.
-This means that the closed-loop behavior of both systems will differ when large control gains are used.
-
-One can observe that the closed loop poles of the system with added springs (in red) are bounded to the left half plane implying unconditional stability.
-This is not the case for the system where the controller is augmented with an HPF (in blue).
-
-It is interesting to note that the maximum added damping is very similar for both techniques and is reached for the same control gain \(g_\text{opt} \approx 2 \omega_0\).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_root_locus.pdf}
-\caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
-\end{figure}
-
-\par
-The two proposed techniques are now compared in terms of closed-loop transmissibility and compliance.
-
-The transmissibility is defined as the transfer function from the displacement of the rotating stage to the displacement of the payload.
-It is used to characterize how much vibration is transmitted through the suspended platform to the payload.
-
-The compliance describes the displacement response of the payload to external forces applied to it.
-This is a useful metric when disturbances are directly applied to the payload.
-
-The two techniques are also compared with passive damping (Figure \ref{fig:system}) where the damping coefficient \(c\) is tuned to critically damp the resonance when the rotating speed is null.
-\begin{equation}
-  c_\text{crit} = 2 \sqrt{k m}
-\end{equation}
-
-Very similar results are obtained for the two proposed IFF modifications in terms of transmissibility (Figure \ref{fig:comp_transmissibility}) and compliance (Figure \ref{fig:comp_compliance}).
-It is also confirmed that these two techniques can significantly damp the suspension modes.
-
-\begin{figure}[htbp]
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
-\caption{\label{fig:comp_transmissibility} Transmissibility}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
-\caption{\label{fig:comp_compliance} Compliance}
-\end{subfigure}
-\hfill
-\caption{\label{fig:comp_active_damping}Comparison of the two proposed Active Damping Techniques, \(\Omega = 0.1 \omega_0\)}
-\centering
-\end{figure}
-
-On can see in Figure \ref{fig:comp_transmissibility} that the problem of the degradation of the transmissibility at high frequency when using passive damping techniques is overcome by the use of IFF.
-
-The addition of the HPF or the use of the parallel stiffness permit to limit the degradation of the compliance as compared with classical IFF (Figure \ref{fig:comp_compliance}).
-
-\section{Conclusion}
-\label{sec:orga805aaa}
-\label{sec:conclusion}
-
-Due to gyroscopic effects, decentralized IFF with pure integrators was shown to be unstable when applied to rotating platforms.
-Two modifications of the classical IFF control have been proposed to overcome this issue.
-
-The first modification concerns the controller and consists of adding an high pass filter to the pure integrators.
-This is equivalent as to moving the controller pole to the left along the real axis.
-This renders the closed loop system stable up to some value of the controller gain \(g_\text{max}\).
-
-The second proposed modification concerns the mechanical system.
-Additional springs are added in parallel with the actuators and force sensors.
-It was shown that if the stiffness \(k_p\) of the additional springs is larger than the negative stiffness \(m \Omega^2\) induced by centrifugal forces, the classical decentralized IFF regains its unconditional stability property.
-
-While having very different implementations, both proposed modifications are very similar when it comes to the attainable damping and the obtained closed loop system behavior.
-
-Future work will focus on the experimental validation of the proposed active damping techniques.
-
-The Matlab code that was used for this study is available under a MIT License and archived in Zenodo \cite{dehaeze20_activ_dampin_rotat_posit_platf}.
-
-\section*{Acknowledgment}
-\label{sec:orge39bf3f}
-This research benefited from a FRIA grant from the French Community of Belgium.
-
-\bibliography{ref.bib}
-\end{document}
+\end{abstract}

### 2020-10-26 journal/paper.tex
Add Journal folder for extended publication

--- 2020-07-09 paper/paper.tex
@@
-% Created 2020-07-09 jeu. 09:06
+% Created 2020-10-26 lun. 18:45
 % Intended LaTeX compiler: pdflatex
-\documentclass{ISMA_USD2020}
+\documentclass[Afour,sagev,times]{sagej}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{algorithmic, graphicx, textcomp}
-\usepackage{xcolor, import, hyperref}
+\usepackage{xcolor, import}
 \usepackage{subcaption}
 \usepackage[USenglish, english]{babel}
-\setcounter{footnote}{1}
-\input{config.tex}
-\author[1,3] {T. Dehaeze}
-\author[1,2] {C. Collette}
-\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
-\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
-\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
-\bibliographystyle{IEEEtran}
 \usepackage{tikz}
 \usetikzlibrary{shapes.misc,arrows,arrows.meta}
-\date{}
-\title{Active Damping of Rotating Platforms using Integral Force Feedback}
-\hypersetup{
- pdfauthor={},
- pdftitle={Active Damping of Rotating Platforms using Integral Force Feedback},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
- pdflang={English}}
-\begin{document}
-
-\maketitle
-
-\abstract{
+\hypersetup{colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red}
+\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\def\volumeyear{2016}
+\author{Dehaeze Thomas\affilnum{1} and Collette Christophe\affilnum{2}}
+\affiliation{\affilnum{1}Precision Mechatronics Laboratory, University of Liege, Belgium\\
+\affilnum{2}BEAMS Department, Free University of Brussels, Belgium\\
+\affilnum{3}European Synchrotron Radiation Facility, Grenoble, France}
+\email{dehaeze.thomas@gmail.com}
+\bibliographystyle{SageV}
+\begin{abstract}
 This paper investigates the use of Integral Force Feedback (IFF) for the active damping of rotating mechanical systems.
@@
 The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on suspension modes.
-}
+\end{abstract}
+\keywords{active damping, IFF}
+\date{}
+\title{Active Damping of Rotating Platforms using Integral Force Feedback}
+\begin{document}
+
+\maketitle
 
 \section{Introduction}
-\label{sec:orgf2d9f1e}
+\label{sec:orgdef8140}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Platforms}
-\label{sec:orgf97884c}
+\label{sec:org392ac57}
 \label{sec:dynamics}
@@
 \centering
-\includegraphics[scale=1]{figs/system.pdf}
+\includegraphics[width=0.8\linewidth]{figs/system.pdf}
 \caption{\label{fig:system}Schematic of the studied System}
@@
   \begin{aligned}
-    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \quad V = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right),\\
+    T &= \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \\
+    V &= \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right), \\
     D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
@@
   \begin{bmatrix} d_u \\ d_v \end{bmatrix} &= \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gd_mimo_tf} \\
-  \bm{G}_{d} &=
-  \begin{bmatrix}
-    \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
-    \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}
-  \end{bmatrix} \label{eq:Gd_m_k_c}
+  \bm{G}_{d}(1,1) &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
+                  &= \bm{G}_{d}(2,2) \nonumber \\
+  \bm{G}_{d}(1,2) &= \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
+                  &= -\bm{G}_{d}(1,2) \nonumber
 \end{align}
@@
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
+\begin{subfigure}[c]{0.49\linewidth}
 \includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
@@
 \hfill
-\begin{subfigure}[c]{0.45\linewidth}
+\begin{subfigure}[c]{0.49\linewidth}
 \includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
@@
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
+\begin{subfigure}[c]{0.49\linewidth}
 \includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
@@
 \hfill
-\begin{subfigure}[c]{0.45\linewidth}
+\begin{subfigure}[c]{0.49\linewidth}
 \includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgf541d3f}
+\label{sec:orgcaa78cf}
 \label{sec:iff}
@@
 
-\begin{minipage}[t]{0.50\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/system_iff.pdf}
-\captionof{figure}{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.45\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/control_diagram_iff.pdf}
-\captionof{figure}{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
-\end{center}
-\end{minipage}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.8\linewidth]{figs/system_iff.pdf}
+\caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
+\caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
+\end{figure}
 
@@
 \centering
-\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
+\includegraphics[width=\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
 \caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
+\includegraphics[width=\linewidth]{figs/root_locus_pure_iff.pdf}
 \caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgf53673d}
+\label{sec:org704f416}
 \label{sec:iff_hpf}
@@
 
-\begin{minipage}[b]{0.45\linewidth}
-\begin{center}
+\begin{figure}[htbp]
+\centering
 \includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
-\captionof{figure}{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.5\linewidth}
-\begin{center}
+\caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
 \includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
-\captionof{figure}{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
+\caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
+\end{figure}
 
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
+\includegraphics[width=\linewidth]{figs/root_locus_wi_modified_iff.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
+\includegraphics[width=\linewidth]{figs/mod_iff_damping_wi.pdf}
 \caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org4c124af}
+\label{sec:org1c4a11f}
 \label{sec:iff_kp}
@@
 
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
-\captionof{figure}{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{figs/cedrat_xy25xs.png}
-\captionof{figure}{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
-\end{center}
-\end{minipage}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.8\linewidth]{figs/system_parallel_springs.pdf}
+\caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.8\linewidth]{figs/cedrat_xy25xs.png}
+\caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
+\end{figure}
 
@@
 
-\begin{minipage}[b]{0.43\linewidth}
-\begin{center}
+\begin{figure}[htbp]
+\centering
 \includegraphics[scale=1]{figs/plant_iff_kp.pdf}
-\captionof{figure}{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.53\linewidth}
-\begin{center}
-\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
-\captionof{figure}{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
-\end{center}
-\end{minipage}
+\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
+\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\end{figure}
 
@@
 
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
+\begin{figure}[htbp]
+\centering
 \includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
-\captionof{figure}{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
-\end{center}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.48\linewidth}
-\begin{center}
+\caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
 \includegraphics[width=\linewidth]{figs/mod_iff_damping_kp.pdf}
-\captionof{figure}{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
-\end{center}
-\end{minipage}
+\caption{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
+\end{figure}
 
 \section{Comparison and Discussion}
-\label{sec:org537f1b3}
+\label{sec:orgcd508a8}
 \label{sec:comparison}
@@
 \centering
-\includegraphics[scale=1]{figs/comp_root_locus.pdf}
+\includegraphics[width=\linewidth]{figs/comp_root_locus.pdf}
 \caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
@@
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
-\caption{\label{fig:comp_transmissibility} Transmissibility}
-\end{subfigure}
-\hfill
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
-\caption{\label{fig:comp_compliance} Compliance}
-\end{subfigure}
-\hfill
-\caption{\label{fig:comp_active_damping}Comparison of the two proposed Active Damping Techniques, \(\Omega = 0.1 \omega_0\)}
 \centering
+\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
+\caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_compliance.pdf}
+\caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
 \end{figure}
@@
 \section{Conclusion}
-\label{sec:orga805aaa}
+\label{sec:org6cd163b}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:orge39bf3f}
+\label{sec:org7856ac4}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2020-11-02 journal/paper.tex
Convert figures for a 2 column journal

@@
-% Created 2020-10-26 lun. 18:45
+% Created 2020-10-29 jeu. 12:36
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{grffile}
-\usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
 \usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{textcomp}
-\usepackage{amssymb}
 \usepackage{capt-of}
 \usepackage{hyperref}
-\usepackage[most]{tcolorbox}
 \usepackage{bm}
-\usepackage{booktabs}
-\usepackage{tabularx}
-\usepackage{array}
-\usepackage{siunitx}
 \usepackage{amsmath,amssymb,amsfonts, cases}
@@
 \usepackage[USenglish, english]{babel}
-\usepackage{tikz}
-\usetikzlibrary{shapes.misc,arrows,arrows.meta}
+
+\usepackage{natbib}
+\bibliographystyle{SageV}
+
+\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \hypersetup{colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red}
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\def\volumeyear{2016}
-\author{Dehaeze Thomas\affilnum{1} and Collette Christophe\affilnum{2}}
+\author{Dehaeze Thomas\affilnum{1,3} and Collette Christophe\affilnum{1,2}}
 \affiliation{\affilnum{1}Precision Mechatronics Laboratory, University of Liege, Belgium\\
@@
 \email{dehaeze.thomas@gmail.com}
-\bibliographystyle{SageV}
 \begin{abstract}
@@
 \end{abstract}
-\keywords{active damping, IFF}
+\keywords{Active damping, IFF, Rotating platform}
 \date{}
@@
 \section{Introduction}
-\label{sec:orgdef8140}
+\label{sec:org6f081c2}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Platforms}
-\label{sec:org392ac57}
+\label{sec:org42fff77}
 \label{sec:dynamics}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{figs/system.pdf}
+\includegraphics[width=0.8\linewidth]{system.pdf}
 \caption{\label{fig:system}Schematic of the studied System}
@@
 
-The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
+The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in rad/s.
 
-The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
-A payload with a mass \(m\) in \(\si{\kilo\gram}\), representing the sensitive equipment, is mounted on the (rotating) suspended platform.
+The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in N/m, a dashpot with a damping coefficient \(c\) in N/(m/s) and an ideal force source \(F_u, F_v\).
+A payload with a mass \(m\) in kg, representing the sensitive equipment, is mounted on the (rotating) suspended platform.
 
@@
 
+One can verify that without rotation (\(\Omega = 0\)) the system becomes equivalent to two uncoupled one degree of freedom mass-spring-damper systems:
+\begin{subequations}
+\label{eq:oem_no_rotation}
+  \begin{align}
+    m \ddot{d}_u + c \dot{d}_u + k d_u &= F_u \\
+    m \ddot{d}_v + c \dot{d}_v + k d_v &= F_v
+  \end{align}
+\end{subequations}
+
 \par
 To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
+\begin{equation}
+\label{eq:Gd_mimo_tf}
+  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{subequations}
   \begin{align}
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix} &= \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gd_mimo_tf} \\
     \bm{G}_{d}(1,1) &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
@@
   \end{align}
+\end{subequations}
 
@@
 \begin{equation}
-  \omega_0 = \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second}, \quad \xi = \frac{c}{2 \sqrt{k m}}
+  \omega_0 = \sqrt{\frac{k}{m}} \text{ in rad/s}, \quad \xi = \frac{c}{2 \sqrt{k m}}
 \end{equation}
 
-The transfer function matrix \(\bm{G}_d\) becomes equal to
-\begin{equation}
+The elements of the transfer function matrix \(\bm{G}_d\) become equal to
+\begin{subequations}
 \label{eq:Gd_w0_xi_k}
-\bm{G}_{d} =
-  \frac{1}{k}
-  \begin{bmatrix}
-    \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-    \frac{- 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2}}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-  \end{bmatrix}
-\end{equation}
+  \begin{align}
+    \bm{G}_{d}(1,1) &= {\scriptstyle \frac{\frac{1}{k} \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
+    \bm{G}_{d}(1,2) &= {\scriptstyle \frac{\frac{1}{k} \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+  \end{align}
+\end{subequations}
 
-For all further numerical analysis in this study, we consider \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
+For all further numerical analysis in this study, we consider \(\omega_0 = 1\,\text{rad}/s\), \(k = 1\,N/m\) and \(\xi = 0.025 = 2.5\,\%\).
 Even though no system with such parameters will be encountered in practice, conclusions can be drawn relative to these parameters such that they can be generalized to any other set of parameters.
@@
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{campbell_diagram_real.pdf}
 \caption{\label{fig:campbell_diagram_real} Real Part}
@@
 \hfill
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
+\begin{subfigure}[c]{0.45\linewidth}
+\includegraphics[width=\linewidth]{campbell_diagram_imag.pdf}
 \caption{\label{fig:campbell_diagram_imag} Imaginary Part}
@@
 \begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
+\includegraphics[width=\linewidth]{plant_compare_rotating_speed_direct.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\) and \(d_v/F_v\)}
 \end{subfigure}
@@
 \begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
+\includegraphics[width=\linewidth]{plant_compare_rotating_speed_coupling.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\) and -\(d_u/F_v\)}
 \end{subfigure}
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgcaa78cf}
+\label{sec:org955ee19}
 \label{sec:iff}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{figs/system_iff.pdf}
+\includegraphics[width=0.8\linewidth]{system_iff.pdf}
 \caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
@@
 \centering
-\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
+\includegraphics[scale=1]{control_diagram_iff.pdf}
 \caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
@@
 Inserting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
+\begin{equation}
+\label{eq:Gf_mimo_tf}
+  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{subequations}
+\label{eq:Gf}
   \begin{align}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} &= \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gf_mimo_tf} \\
-  \bm{G}_{f} &= \begin{bmatrix}
-  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix} \label{eq:Gf}
+    \bm{G}_{f}(1,1) &= {\scriptstyle \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
+    \bm{G}_{f}(1,2) &= {\scriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
   \end{align}
+\end{subequations}
 
@@
 For non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms inducing a non-minimum phase behavior.
-This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(\SI{180}{\degree}\).
+This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(180\,\text{deg}\).
 
@@
 \centering
-\includegraphics[width=\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
+\includegraphics[scale=1]{plant_iff_compare_rotating_speed.pdf}
 \caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
@@
 In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers \(K_F\) simultaneously.
-As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
-The direction of increasing gain is indicated by arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
+As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by crosses) for \(g = 0\) and coincide with the transmission zeros (shown by circles) as \(g \to \infty\).
+The direction of increasing gain is indicated by arrows.
 
@@
 \centering
-\includegraphics[width=\linewidth]{figs/root_locus_pure_iff.pdf}
+\includegraphics[scale=1]{root_locus_pure_iff.pdf}
 \caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:org704f416}
+\label{sec:orgeb779c5}
 \label{sec:iff_hpf}
@@
 \centering
-\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
+\includegraphics[scale=1]{loop_gain_modified_iff.pdf}
 \caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
+\includegraphics[scale=1]{root_locus_modified_iff.pdf}
 \caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/root_locus_wi_modified_iff.pdf}
+\includegraphics[scale=1]{root_locus_wi_modified_iff.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/mod_iff_damping_wi.pdf}
+\includegraphics[scale=1]{mod_iff_damping_wi.pdf}
 \caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org1c4a11f}
+\label{sec:org41af864}
 \label{sec:iff_kp}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{figs/system_parallel_springs.pdf}
+\includegraphics[width=0.8\linewidth]{system_parallel_springs.pdf}
 \caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{figs/cedrat_xy25xs.png}
+\includegraphics[width=0.8\linewidth]{cedrat_xy25xs.pdf}
 \caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
@@
 The equations of motion are derived and transformed in the Laplace domain
+\begin{equation}
+\label{eq:Gk_mimo_tf}
+  \begin{bmatrix} f_u \\ f_v \end{bmatrix} =
+  \bm{G}_k
+  \begin{bmatrix} F_u \\ F_v \end{bmatrix}
+\end{equation}
+
+\begin{subequations}
+\label{eq:Gk}
 \begin{align}
-\begin{bmatrix} f_u \\ f_v \end{bmatrix} &=
-\bm{G}_k
-\begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gk_mimo_tf} \\
-\bm{G}_k &=
-\begin{bmatrix}
-  \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} \\
-  \frac{\left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} & \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
-\end{bmatrix} \label{eq:Gk}
+\bm{G}_{k}(1,1) &= {\scriptstyle \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
+\bm{G}_{k}(1,2) &= {\scriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
 \end{align}
+\end{subequations}
 
@@
 \centering
-\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
+\includegraphics[scale=1]{plant_iff_kp.pdf}
 \caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
+\includegraphics[scale=1]{root_locus_iff_kp.pdf}
 \caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
@@
 
-This is confirmed in Figure \ref{fig:mod_iff_damping_kp} where the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) and the associated control gain \(g_\text{opt}\) are computed as a function of \(\alpha\).
+This is confirmed in Figure \ref{fig:opt_damp_alpha} where the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) and the associated control gain \(g_\text{opt}\) are computed as a function of \(\alpha\).
 
@@
 \centering
-\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
+\includegraphics[scale=1]{root_locus_iff_kps.pdf}
 \caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/mod_iff_damping_kp.pdf}
-\caption{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
+\includegraphics[scale=1]{opt_damp_alpha.pdf}
+\caption{\label{fig:opt_damp_alpha}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
 \end{figure}
@@
 \section{Comparison and Discussion}
-\label{sec:orgcd508a8}
+\label{sec:org2279161}
 \label{sec:comparison}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/comp_root_locus.pdf}
+\includegraphics[scale=1]{comp_root_locus.pdf}
 \caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
+\includegraphics[scale=1]{comp_transmissibility.pdf}
 \caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
@@
 \centering
-\includegraphics[scale=1]{figs/comp_compliance.pdf}
+\includegraphics[scale=1]{comp_compliance.pdf}
 \caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
@@
 \section{Conclusion}
-\label{sec:org6cd163b}
+\label{sec:org40ed087}
 \label{sec:conclusion}
@@
 \section*{Acknowledgment}
-\label{sec:org7856ac4}
-This research benefited from a FRIA grant from the French Community of Belgium.
+\label{sec:org7ba6f08}
+This research benefited from a FRIA grant (grant number: FC 31597) from the French Community of Belgium.
 

### 2020-11-02 matlab/matlab/s1_system_description.m

@@ -17,7 +17,7 @@ w0 = sqrt(k/m); % [rad/s]
 % Campbell Diagram
 % The Campbell Diagram displays the evolution of the real and imaginary parts of the system as a function of the rotating speed.
 
-% It is shown in Figure [[fig:campbell_diagram]], and one can see that the system becomes unstable for $\Omega > \omega_0$ (the real part of one of the poles becomes positive).
+% It is shown in Figures [[fig:campbell_diagram_real]] and [[fig:campbell_diagram_imag]], and one can see that the system becomes unstable for $\Omega > \omega_0$ (the real part of one of the poles becomes positive).
 
 
 Ws = linspace(0, 2, 51); % Vector of considered rotation speed [rad/s]
@@ -33,25 +33,6 @@ for W_i = 1:length(Ws)
 end
 
 clear pole_G;
-
-figure;
-
-ax1 = subplot(1,2,1);
-hold on;
-for p_i = 1:size(p_ws, 1)
-    plot(Ws, real(p_ws(p_i, :)), 'k-')
-end
-plot(Ws, zeros(size(Ws)), 'k--')
-hold off;
-xlabel('Rotational Speed [rad/s]'); ylabel('Real Part');
-
-ax2 = subplot(1,2,2);
-hold on;
-for p_i = 1:size(p_ws, 1)
-    plot(Ws, imag(p_ws(p_i, :)), 'k-')
-end
-hold off;
-xlabel('Rotational Speed [rad/s]'); ylabel('Imaginary Part');
 
 % Simscape Model
 % In order to validate all the equations of motion, a Simscape model of the same system has been developed.
@@ -103,7 +84,10 @@ Gth = (1/k)/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2)
 freqs = logspace(-1, 1, 1000);
 
 figure;
-ax1 = subplot(2, 2, 1);
+tiledlayout(3, 2, 'TileSpacing', 'None', 'Padding', 'None');
+
+% Magnitude
+ax1 = nexttile([2, 1]);
 hold on;
 plot(freqs, abs(squeeze(freqresp(G(1,1), freqs))), '-')
[…]

### 2020-11-02 matlab/matlab/s2_iff_pure_int.m

@@ -59,7 +59,10 @@ Giff_th = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2)
 freqs = logspace(-1, 1, 1000);
 
 figure;
-ax1 = subplot(2, 2, 1);
+tiledlayout(3, 2, 'TileSpacing', 'None', 'Padding', 'None');
+
+% Magnitude
+ax1 = nexttile([2, 1]);
 hold on;
 plot(freqs, abs(squeeze(freqresp(Giff(1,1), freqs))), '-')
 plot(freqs, abs(squeeze(freqresp(Giff_th(1,1), freqs))), '--')
@@ -68,7 +71,16 @@ set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
 set(gca, 'XTickLabel',[]); ylabel('Magnitude [N/N]');
 title('$f_u/F_u$, $f_v/F_v$');
 
-ax3 = subplot(2, 2, 3);
+ax2 = nexttile([2, 1]);
+hold on;
+plot(freqs, abs(squeeze(freqresp(Giff(1,2), freqs))), '-')
+plot(freqs, abs(squeeze(freqresp(Giff_th(1,2), freqs))), '--')
+hold off;
+set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
+set(gca, 'XTickLabel',[]); ylabel('Magnitude [N/N]');
+title('$f_u/F_v$, $f_v/F_u$');
+
+ax3 = nexttile;
 hold on;
 plot(freqs, 180/pi*angle(squeeze(freqresp(Giff(1,1), freqs))), '-')
 plot(freqs, 180/pi*angle(squeeze(freqresp(Giff_th(1,1), freqs))), '--')
@@ -78,16 +90,7 @@ yticks(-180:90:180);
 ylim([-180 180]);
 hold off;
 
-ax2 = subplot(2, 2, 2);
-hold on;
-plot(freqs, abs(squeeze(freqresp(Giff(1,2), freqs))), '-')
-plot(freqs, abs(squeeze(freqresp(Giff_th(1,2), freqs))), '--')
-hold off;
-set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
-set(gca, 'XTickLabel',[]); ylabel('Magnitude [N/N]');
[…]

### 2020-11-02 matlab/matlab/s3_iff_hpf.m

@@ -51,8 +51,10 @@ Giff = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * 
 freqs = logspace(-2, 1, 1000);
 
 figure;
+tiledlayout(3, 1, 'TileSpacing', 'None', 'Padding', 'None');
 
-ax1 = subplot(2, 1, 1);
+% Magnitude
+ax1 = nexttile([2, 1]);
 hold on;
 plot(freqs, abs(squeeze(freqresp(Giff(1,1)*(g/s), freqs))))
 plot(freqs, abs(squeeze(freqresp(Giff(1,1)*Kiff(1,1), freqs))))
@@ -60,7 +62,8 @@ hold off;
 set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
 set(gca, 'XTickLabel',[]); ylabel('Loop Gain');
 
-ax2 = subplot(2, 1, 2);
+% Phase
+ax2 = nexttile;
 hold on;
 plot(freqs, 180/pi*angle(squeeze(freqresp(Giff(1,1)*(g/s), freqs))), ...
      'DisplayName', 'IFF')
@@ -70,7 +73,9 @@ set(gca, 'XScale', 'log'); set(gca, 'YScale', 'lin');
 xlabel('Frequency [rad/s]'); ylabel('Phase [deg]');
 yticks(-180:90:180);
 ylim([-180 180]);
-legend('location', 'southwest');
+leg = legend('location', 'southwest', 'FontSize', 8);
+leg.ItemTokenSize(1) = 6;
+
 hold off;
 
 linkaxes([ax1,ax2],'x');
@@ -84,7 +89,6 @@ figure;
 
 gains = logspace(-2, 4, 100);
 
-ax1 = subplot(1, 2, 1);
 hold on;
 % Pure Integrator
 set(gca,'ColorOrderIndex',1);
@@ -109,35 +113,20 @@ end
 hold off;
 axis square;
 xlim([-2, 0.5]); ylim([-1.25, 1.25]);
-legend('location', 'northwest');
+leg = legend('location', 'northwest', 'FontSize', 8);
+leg.ItemTokenSize(1) = 8;
 xlabel('Real Part'); ylabel('Imaginary Part');
 
-ax2 = subplot(1, 2, 2);
-hold on;
-% Pure Integrator
[…]

### 2020-11-02 matlab/matlab/s4_iff_kp.m

@@ -55,7 +55,9 @@ Giff_th.OutputName = {'fu', 'fv'};
 freqs = logspace(-1, 1, 1000);
 
 figure;
-ax1 = subplot(2, 2, 1);
+tiledlayout(3, 2, 'TileSpacing', 'None', 'Padding', 'None');
+
+ax1 = nexttile([2, 1]);
 hold on;
 plot(freqs, abs(squeeze(freqresp(Giff(1,1), freqs))), '-')
 plot(freqs, abs(squeeze(freqresp(Giff_th(1,1), freqs))), '--')
@@ -64,17 +66,7 @@ set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
 set(gca, 'XTickLabel',[]); ylabel('Magnitude [N/N]');
 title('$f_u/F_u$, $f_v/F_v$');
 
-ax3 = subplot(2, 2, 3);
-hold on;
-plot(freqs, 180/pi*angle(squeeze(freqresp(Giff(1,1), freqs))), '-')
-plot(freqs, 180/pi*angle(squeeze(freqresp(Giff_th(1,1), freqs))), '--')
-set(gca, 'XScale', 'log'); set(gca, 'YScale', 'lin');
-xlabel('Frequency [rad/s]'); ylabel('Phase [deg]');
-yticks(-180:90:180);
-ylim([-180 180]);
-hold off;
-
-ax2 = subplot(2, 2, 2);
+ax2 = nexttile([2, 1]);
 hold on;
 plot(freqs, abs(squeeze(freqresp(Giff(1,2), freqs))), '-')
 plot(freqs, abs(squeeze(freqresp(Giff_th(1,2), freqs))), '--')
@@ -83,18 +75,28 @@ set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
 set(gca, 'XTickLabel',[]); ylabel('Magnitude [N/N]');
 title('$f_u/F_v$, $f_v/F_u$');
 
-ax4 = subplot(2, 2, 4);
+ax3 = nexttile;
 hold on;
-plot(freqs, 180/pi*angle(squeeze(freqresp(Giff(1,2), freqs))), '-', ...
+plot(freqs, 180/pi*angle(squeeze(freqresp(Giff(1,1), freqs))), '-', ...
      'DisplayName', 'Simscape')
-plot(freqs, 180/pi*angle(squeeze(freqresp(Giff_th(1,2), freqs))), '--', ...
[…]

### 2020-11-02 matlab/matlab/s5_act_damp_comparison.m

@@ -85,7 +85,8 @@ axis square;
 xlim([-1.2, 0.05]); ylim([0, 1.25]);
 
 xlabel('Real Part'); ylabel('Imaginary Part');
-legend('location', 'northwest');
+leg = legend('location', 'northwest', 'FontSize', 8);
+leg.ItemTokenSize(1) = 8;
 
 % Controllers - Optimal Gains
 % In order to compare to three considered Active Damping techniques, gains that yield maximum damping of all the modes are computed for each case.
@@ -204,7 +205,7 @@ hold off;
 set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
 ylim([1e-2, 3e1]);
 xlabel('Frequency [rad/s]'); ylabel('Transmissibility [m/m]');
-legend('location', 'southwest');
+legend('location', 'southwest', 'FontSize', 8);
 
 % Compliance                                                      :ignore:
 
@@ -224,4 +225,4 @@ hold off;
 set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
 ylim([1e-2, 3e1]);
 xlabel('Frequency [rad/s]'); ylabel('Compliance [m/N]');
-legend('location', 'southwest');
+legend('location', 'southwest', 'FontSize', 8);

### 2020-11-02 journal/paper.tex
Change LaTeX journal files => IOP

@@
-% Created 2020-10-29 jeu. 12:36
+% Created 2020-11-02 lun. 14:38
 % Intended LaTeX compiler: pdflatex
-\documentclass[Afour,sagev,times]{sagej}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{grffile}
-\usepackage[normalem]{ulem}
-\usepackage{capt-of}
+\documentclass[10pt]{iopart}
+
+\expandafter\let\csname equation*\endcsname\relax
+\expandafter\let\csname endequation*\endcsname\relax
+\usepackage{capt-of, subcaption}
 \usepackage{hyperref}
-\usepackage{bm}
-\usepackage{amsmath,amssymb,amsfonts, cases}
+\usepackage{amsmath, amssymb, amsfonts, cases, bm}
 \usepackage{algorithmic, graphicx, textcomp}
 \usepackage{xcolor, import}
-\usepackage{subcaption}
 \usepackage[USenglish, english]{babel}
+\usepackage{siunitx}
+\usepackage{tikz}
+\usetikzlibrary{shapes.misc,arrows,arrows.meta}
+\date{}
+\hypersetup{
+ pdfauthor={Thomas Dehaeze},
+ pdftitle={},
+ pdfkeywords={},
+ pdfsubject={},
+ pdfcreator={Emacs 27.1.50 (Org mode 9.4)}, 
+ pdflang={English}}
+\begin{document}
 
-\usepackage{natbib}
-\bibliographystyle{SageV}
+\title{Active Damping of Rotating Platforms using Integral Force Feedback}
+\author{Thomas Dehaeze$^{1,3}$ and Christophe Collette$^{1,2}$}
+\address{$^1$ Precision Mechatronics Laboratory, University of Liege, Belgium}
+\address{$^2$ BEAMS Department, Free University of Brussels, Belgium}
+\address{$^3$ European Synchrotron Radiation Facility, Grenoble, France}
+\ead{dehaeze.thomas@gmail.com}
 
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\vspace{10pt}
+\begin{indented}
+\item[]November 2020
+\end{indented}
 
-\hypersetup{colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red}
-\author{Dehaeze Thomas\affilnum{1,3} and Collette Christophe\affilnum{1,2}}
-\affiliation{\affilnum{1}Precision Mechatronics Laboratory, University of Liege, Belgium\\
-\affilnum{2}BEAMS Department, Free University of Brussels, Belgium\\
-\affilnum{3}European Synchrotron Radiation Facility, Grenoble, France}
-\email{dehaeze.thomas@gmail.com}
 \begin{abstract}
@@
 \end{abstract}
-\keywords{Active damping, IFF, Rotating platform}
-\date{}
-\title{Active Damping of Rotating Platforms using Integral Force Feedback}
-\begin{document}
 
-\maketitle
+\vspace{2pc}
+\noindent{\it Keywords}: Active Damping, IFF
+
+\ioptwocol
 
 \section{Introduction}
-\label{sec:org6f081c2}
+\label{sec:orgcbd1527}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Platforms}
-\label{sec:org42fff77}
+\label{sec:org90939ec}
 \label{sec:dynamics}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{system.pdf}
+\includegraphics[width=\linewidth]{figs/system.pdf}
 \caption{\label{fig:system}Schematic of the studied System}
@@
 
-The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in rad/s.
+The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
 
-The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in N/m, a dashpot with a damping coefficient \(c\) in N/(m/s) and an ideal force source \(F_u, F_v\).
-A payload with a mass \(m\) in kg, representing the sensitive equipment, is mounted on the (rotating) suspended platform.
+The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
+A payload with a mass \(m\) in \(\si{\kilo\gram}\), representing the sensitive equipment, is mounted on the (rotating) suspended platform.
 
@@
   \begin{aligned}
-    T &= \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \\
-    V &= \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right), \\
-    D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
+    T &= \frac{1}{2} m \left( ( \dot{d}_u - \Omega d_v )^2 + ( \dot{d}_v + \Omega d_u )^2 \right), \\
+    V &= \frac{1}{2} k \big( {d_u}^2 + {d_v}^2 \big), \ Q_1 = F_u, \\
+    D &= \frac{1}{2} c \big( \dot{d}_u{}^2 + \dot{d}_v{}^2 \big), \ Q_2 = F_v
   \end{aligned}
@@
 \par
-To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
+To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained.
+
 \begin{equation}
@@
 \begin{align}
-    \bm{G}_{d}(1,1) &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
+  \bm{G}_{d}(1,1) &= {\frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
                   &= \bm{G}_{d}(2,2) \nonumber \\
-    \bm{G}_{d}(1,2) &= \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
+  \bm{G}_{d}(1,2) &= {\frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
                   &= -\bm{G}_{d}(1,2) \nonumber
@@
 \begin{equation}
-  \omega_0 = \sqrt{\frac{k}{m}} \text{ in rad/s}, \quad \xi = \frac{c}{2 \sqrt{k m}}
+  \omega_0 = \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second}, \quad \xi = \frac{c}{2 \sqrt{k m}}
 \end{equation}
 
-The elements of the transfer function matrix \(\bm{G}_d\) become equal to
+The transfer function matrix \(\bm{G}_d\) becomes equal to
 \begin{subequations}
@@
 
-For all further numerical analysis in this study, we consider \(\omega_0 = 1\,\text{rad}/s\), \(k = 1\,N/m\) and \(\xi = 0.025 = 2.5\,\%\).
+For all further numerical analysis in this study, we consider \(\omega_0 = \SI{1}{\radian\per\second}\), \(k = \SI{1}{\newton\per\meter}\) and \(\xi = 0.025 = \SI{2.5}{\percent}\).
 Even though no system with such parameters will be encountered in practice, conclusions can be drawn relative to these parameters such that they can be generalized to any other set of parameters.
@@
 \par
-The poles of \(\bm{G}_d\) are the complex solutions \(p\) of
+The poles of \(\bm{G}_d\) are the complex solutions \(p\) of \eqref{eq:poles}.
+
 \begin{equation}
+\label{eq:poles}
   \left( \frac{p^2}{{\omega_0}^2} + 2 \xi \frac{p}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{p}{\omega_0} \right)^2 = 0
@@
 
-Supposing small damping (\(\xi \ll 1\)), two pairs of complex conjugate poles are obtained:
+Supposing small damping (\(\xi \ll 1\)), two pairs of complex conjugate poles are obtained \eqref{eq:pole_values}.
+
 \begin{subequations}
@@
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{campbell_diagram_real.pdf}
+\begin{subfigure}[c]{0.48\linewidth}
+\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
 \caption{\label{fig:campbell_diagram_real} Real Part}
@@
 \hfill
-\begin{subfigure}[c]{0.45\linewidth}
-\includegraphics[width=\linewidth]{campbell_diagram_imag.pdf}
+\begin{subfigure}[c]{0.48\linewidth}
+\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
 \caption{\label{fig:campbell_diagram_imag} Imaginary Part}
@@
 \begin{figure}[htbp]
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{plant_compare_rotating_speed_direct.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\) and \(d_v/F_v\)}
+\begin{subfigure}[c]{0.48\linewidth}
+\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms}
 \end{subfigure}
 \hfill
-\begin{subfigure}[c]{0.49\linewidth}
-\includegraphics[width=\linewidth]{plant_compare_rotating_speed_coupling.pdf}
-\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\) and -\(d_u/F_v\)}
+\begin{subfigure}[c]{0.48\linewidth}
+\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
+\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms}
 \end{subfigure}
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org955ee19}
+\label{sec:orgabd3121}
 \label{sec:iff}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{system_iff.pdf}
+\includegraphics[width=\linewidth]{figs/system_iff.pdf}
 \caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
@@
 \centering
-\includegraphics[scale=1]{control_diagram_iff.pdf}
+\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
 \caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
@@
 For non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms inducing a non-minimum phase behavior.
-This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(180\,\text{deg}\).
+This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(\SI{180}{\degree}\).
 
@@
 \centering
-\includegraphics[scale=1]{plant_iff_compare_rotating_speed.pdf}
+\includegraphics[width=\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
 \caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
@@
 \label{eq:Kf_pure_int}
-  \bm{K}_F(s) = \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix}, \quad K_F(s) = g \cdot \frac{1}{s}
+\begin{aligned}
+  \bm{K}_F(s) &= \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix} \\
+  K_F(s) &= g \cdot \frac{1}{s}
+\end{aligned}
 \end{equation}
@@
 In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers \(K_F\) simultaneously.
-As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by crosses) for \(g = 0\) and coincide with the transmission zeros (shown by circles) as \(g \to \infty\).
-The direction of increasing gain is indicated by arrows.
+As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
+The direction of increasing gain is indicated by arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
 
@@
 \centering
-\includegraphics[scale=1]{root_locus_pure_iff.pdf}
+\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
 \caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgeb779c5}
+\label{sec:orgb936693}
 \label{sec:iff_hpf}
@@
 \centering
-\includegraphics[scale=1]{loop_gain_modified_iff.pdf}
+\includegraphics[width=\linewidth]{figs/loop_gain_modified_iff.pdf}
 \caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{root_locus_modified_iff.pdf}
+\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
 \caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{root_locus_wi_modified_iff.pdf}
+\includegraphics[width=\linewidth]{figs/root_locus_wi_modified_iff.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{mod_iff_damping_wi.pdf}
+\includegraphics[width=\linewidth]{figs/mod_iff_damping_wi.pdf}
 \caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org41af864}
+\label{sec:org9c04fb0}
 \label{sec:iff_kp}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{system_parallel_springs.pdf}
+\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
 \caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{cedrat_xy25xs.pdf}
+\includegraphics[width=0.8\linewidth]{figs/cedrat_xy25xs.png}
 \caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
@@
 \begin{align}
-\bm{G}_{k}(1,1) &= {\scriptstyle \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
-\bm{G}_{k}(1,2) &= {\scriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+& \bm{G}_{k}(1,1) = \dots \nonumber \\
+& {\scriptstyle \frac{\big( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \big) \big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big) + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2}{\big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big)^2 + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2} } \\
+& \bm{G}_{k}(1,2) = {\scriptscriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
 \end{align}
@@
 \centering
-\includegraphics[scale=1]{plant_iff_kp.pdf}
-\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\includegraphics[width=\linewidth]{figs/plant_iff_kp.pdf}
+\caption{\label{fig:plant_iff_kp}Bode plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \centering
-\includegraphics[scale=1]{root_locus_iff_kp.pdf}
+\includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
 \caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{root_locus_iff_kps.pdf}
+\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
 \caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
@@
 \centering
-\includegraphics[scale=1]{opt_damp_alpha.pdf}
+\includegraphics[width=\linewidth]{figs/opt_damp_alpha.pdf}
 \caption{\label{fig:opt_damp_alpha}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
@@
 \section{Comparison and Discussion}
-\label{sec:org2279161}
+\label{sec:org6e6cf51}
 \label{sec:comparison}
@@
 \centering
-\includegraphics[scale=1]{comp_root_locus.pdf}
+\includegraphics[scale=1]{figs/comp_root_locus.pdf}
 \caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{comp_transmissibility.pdf}
+\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
 \caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
@@
 \centering
-\includegraphics[scale=1]{comp_compliance.pdf}
+\includegraphics[scale=1]{figs/comp_compliance.pdf}
 \caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
@@
 \section{Conclusion}
-\label{sec:org40ed087}
+\label{sec:org0fc9335}
 \label{sec:conclusion}
@@
 
-\section*{Acknowledgment}
-\label{sec:org7ba6f08}
-This research benefited from a FRIA grant (grant number: FC 31597) from the French Community of Belgium.
+\section*{Acknowledgments}
+\label{sec:org45730f8}
+This research benefited from a FRIA grant from the French Community of Belgium.
 
+\section*{References}
+\label{sec:org676de81}
+\bibliographystyle{iopart-num}
 \bibliography{ref.bib}

### 2020-11-02 journal/paper.tex
Change figure names

@@
-% Created 2020-11-02 lun. 14:38
+% Created 2020-11-02 lun. 14:46
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:orgcbd1527}
+\label{sec:org45302f3}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Platforms}
-\label{sec:org90939ec}
+\label{sec:org2c62ca5}
 \label{sec:dynamics}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/system.pdf}
+\includegraphics[width=\linewidth]{figs/fig01.pdf}
 \caption{\label{fig:system}Schematic of the studied System}
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
+\includegraphics[width=\linewidth]{figs/fig02a.pdf}
 \caption{\label{fig:campbell_diagram_real} Real Part}
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
+\includegraphics[width=\linewidth]{figs/fig02b.pdf}
 \caption{\label{fig:campbell_diagram_imag} Imaginary Part}
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
+\includegraphics[width=\linewidth]{figs/fig03a.pdf}
 \caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms}
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
+\includegraphics[width=\linewidth]{figs/fig03b.pdf}
 \caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms}
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgabd3121}
+\label{sec:orgaa40c6a}
 \label{sec:iff}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/system_iff.pdf}
+\includegraphics[width=\linewidth]{figs/fig04.pdf}
 \caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
@@
 \centering
-\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
+\includegraphics[scale=1]{figs/fig05.pdf}
 \caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
+\includegraphics[width=\linewidth]{figs/fig06.pdf}
 \caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
+\includegraphics[scale=1]{figs/fig07.pdf}
 \caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgb936693}
+\label{sec:orgcc80b31}
 \label{sec:iff_hpf}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/loop_gain_modified_iff.pdf}
+\includegraphics[width=\linewidth]{figs/fig08.pdf}
 \caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
+\includegraphics[scale=1]{figs/fig09.pdf}
 \caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/root_locus_wi_modified_iff.pdf}
+\includegraphics[width=\linewidth]{figs/fig10.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/mod_iff_damping_wi.pdf}
+\includegraphics[width=\linewidth]{figs/fig11.pdf}
 \caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org9c04fb0}
+\label{sec:org7af993d}
 \label{sec:iff_kp}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
+\includegraphics[width=\linewidth]{figs/fig12.pdf}
 \caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{figs/cedrat_xy25xs.png}
+\includegraphics[width=0.8\linewidth]{figs/fig13.pdf}
 \caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/plant_iff_kp.pdf}
+\includegraphics[width=\linewidth]{figs/fig14.pdf}
 \caption{\label{fig:plant_iff_kp}Bode plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
+\includegraphics[width=\linewidth]{figs/fig15.pdf}
 \caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
+\includegraphics[scale=1]{figs/fig16.pdf}
 \caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/opt_damp_alpha.pdf}
+\includegraphics[width=\linewidth]{figs/fig17.pdf}
 \caption{\label{fig:opt_damp_alpha}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
@@
 \section{Comparison and Discussion}
-\label{sec:org6e6cf51}
+\label{sec:orgc3da302}
 \label{sec:comparison}
@@
 \centering
-\includegraphics[scale=1]{figs/comp_root_locus.pdf}
+\includegraphics[scale=1]{figs/fig18.pdf}
 \caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
+\includegraphics[scale=1]{figs/fig19.pdf}
 \caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
@@
 \centering
-\includegraphics[scale=1]{figs/comp_compliance.pdf}
+\includegraphics[scale=1]{figs/fig20.pdf}
 \caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
@@
 \section{Conclusion}
-\label{sec:org0fc9335}
+\label{sec:org3e5d606}
 \label{sec:conclusion}
@@
 \section*{Acknowledgments}
-\label{sec:org45730f8}
+\label{sec:org2fdf2e5}
 This research benefited from a FRIA grant from the French Community of Belgium.
@@
 \section*{References}
-\label{sec:org676de81}
+\label{sec:org684d4d0}
 \bibliographystyle{iopart-num}

### 2020-11-02 journal/paper.tex
Submitted to Smart Materials and Structures

@@
-% Created 2020-11-02 lun. 14:46
+% Created 2020-11-02 lun. 15:33
 % Intended LaTeX compiler: pdflatex
@@
 \usetikzlibrary{shapes.misc,arrows,arrows.meta}
-\date{}
 \hypersetup{
@@
 
-\title{Active Damping of Rotating Platforms using Integral Force Feedback}
+\title{Active damping of rotating platforms using integral force feedback}
 \author{Thomas Dehaeze$^{1,3}$ and Christophe Collette$^{1,2}$}
@@
 \ead{dehaeze.thomas@gmail.com}
-
-\vspace{10pt}
-\begin{indented}
-\item[]November 2020
-\end{indented}
 
@@
 
-\ioptwocol
+\submitto{\SMS}
+\maketitle
+% \ioptwocol
 
 \section{Introduction}
-\label{sec:org45302f3}
+\label{sec:orgdf2365d}
 \label{sec:introduction}
@@
 \section{Dynamics of Rotating Platforms}
-\label{sec:org2c62ca5}
+\label{sec:orgb49fb34}
 \label{sec:dynamics}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig01.pdf}
+\includegraphics[scale=0.9]{figs/fig01.pdf}
 \caption{\label{fig:system}Schematic of the studied System}
@@
 
-Substituting equations \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} for both generalized coordinates gives two coupled differential equations
+Substituting \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} for both generalized coordinates gives two coupled differential equations
 \begin{subequations}
@@
 \par
-To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained.
+To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\mathbf{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained.
 
@@
 \label{eq:Gd_mimo_tf}
-  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
+  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \mathbf{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
 \end{equation}
@@
 \begin{align}
-  \bm{G}_{d}(1,1) &= {\frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
-                  &= \bm{G}_{d}(2,2) \nonumber \\
-  \bm{G}_{d}(1,2) &= {\frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
-                  &= -\bm{G}_{d}(1,2) \nonumber
+  \mathbf{G}_{d}(1,1) &= {\frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
+                  &= \mathbf{G}_{d}(2,2) \nonumber \\
+  \mathbf{G}_{d}(1,2) &= {\frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
+                  &= -\mathbf{G}_{d}(1,2) \nonumber
 \end{align}
@@
 
-The transfer function matrix \(\bm{G}_d\) becomes equal to
+The transfer function matrix \(\mathbf{G}_d\) becomes equal to
 \begin{subequations}
@@
   \begin{align}
-    \bm{G}_{d}(1,1) &= {\scriptstyle \frac{\frac{1}{k} \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
-    \bm{G}_{d}(1,2) &= {\scriptstyle \frac{\frac{1}{k} \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+    \mathbf{G}_{d}(1,1) &= {\scriptstyle \frac{\frac{1}{k} \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
+    \mathbf{G}_{d}(1,2) &= {\scriptstyle \frac{\frac{1}{k} \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
   \end{align}
@@
 \par
-The poles of \(\bm{G}_d\) are the complex solutions \(p\) of \eqref{eq:poles}.
+The poles of \(\mathbf{G}_d\) are the complex solutions \(p\) of \eqref{eq:poles}.
 
@@
 
-Looking at the transfer function matrix \(\bm{G}_d\) in Eq. \eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and the two off-diagonal (coupling) terms are opposite.
+Looking at the transfer function matrix \(\mathbf{G}_d\) in \eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and the two off-diagonal (coupling) terms are opposite.
 The bode plot of these two terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
@@
 \hfill
-\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
+\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\mathbf{G}_d\) for several rotational speed \(\Omega\)}
 \centering
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:orgaa40c6a}
+\label{sec:org7b1adf9}
 \label{sec:iff}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig04.pdf}
+\includegraphics[scale=0.9]{figs/fig04.pdf}
 \caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
@@
 \label{eq:Gf_mimo_tf}
-  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
+  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \mathbf{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
 \end{equation}
@@
   \begin{align}
-    \bm{G}_{f}(1,1) &= {\scriptstyle \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
-    \bm{G}_{f}(1,2) &= {\scriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+    \mathbf{G}_{f}(1,1) &= {\scriptstyle \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
+    \mathbf{G}_{f}(1,2) &= {\scriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
   \end{align}
@@
 
-The zeros of the diagonal terms of \(\bm{G}_f\) are equal to (neglecting the damping for simplicity)
+The zeros of the diagonal terms of \(\mathbf{G}_f\) are equal to (neglecting the damping for simplicity)
 \begin{subequations}
@@
 
-The low frequency gain of \(\bm{G}_f\) increases with the rotational speed \(\Omega\)
+The low frequency gain of \(\mathbf{G}_f\) increases with the rotational speed \(\Omega\)
 \begin{equation}
 \label{eq:low_freq_gain_iff_plan}
-  \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
+  \lim_{\omega \to 0} \left| \mathbf{G}_f (j\omega) \right| = \begin{bmatrix}
   \frac{\Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig06.pdf}
+\includegraphics[scale=0.95]{figs/fig06.pdf}
 \caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
@@
 \begin{aligned}
-  \bm{K}_F(s) &= \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix} \\
+  \mathbf{K}_F(s) &= \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix} \\
   K_F(s) &= g \cdot \frac{1}{s}
@@
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgcc80b31}
+\label{sec:orgb29360e}
 \label{sec:iff_hpf}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig08.pdf}
+\includegraphics[scale=0.95]{figs/fig08.pdf}
 \caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig10.pdf}
+\includegraphics[scale=0.95]{figs/fig10.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig11.pdf}
+\includegraphics[scale=0.95]{figs/fig11.pdf}
 \caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:org7af993d}
+\label{sec:orgaa66b9e}
 \label{sec:iff_kp}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig12.pdf}
+\includegraphics[scale=0.9]{figs/fig12.pdf}
 \caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{figs/fig13.pdf}
+\includegraphics[scale=0.17]{figs/fig13.pdf}
 \caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
@@
   \begin{bmatrix} f_u \\ f_v \end{bmatrix} =
-  \bm{G}_k
+  \mathbf{G}_k
   \begin{bmatrix} F_u \\ F_v \end{bmatrix}
@@
 \begin{align}
-& \bm{G}_{k}(1,1) = \dots \nonumber \\
+& \mathbf{G}_{k}(1,1) = \dots \nonumber \\
 & {\scriptstyle \frac{\big( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \big) \big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big) + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2}{\big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big)^2 + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2} } \\
-& \bm{G}_{k}(1,2) = {\scriptscriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+& \mathbf{G}_{k}(1,2) = {\scriptscriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
 \end{align}
@@
 
-Comparing \(\bm{G}_k\) \eqref{eq:Gk} with \(\bm{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
+Comparing \(\mathbf{G}_k\) \eqref{eq:Gk} with \(\mathbf{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
 The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros if the following condition hold
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig14.pdf}
+\includegraphics[scale=0.95]{figs/fig14.pdf}
 \caption{\label{fig:plant_iff_kp}Bode plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig15.pdf}
+\includegraphics[scale=0.95]{figs/fig15.pdf}
 \caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[width=\linewidth]{figs/fig17.pdf}
+\includegraphics[scale=0.95]{figs/fig17.pdf}
 \caption{\label{fig:opt_damp_alpha}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
@@
 \section{Comparison and Discussion}
-\label{sec:orgc3da302}
+\label{sec:orgd845e3a}
 \label{sec:comparison}
@@
 \section{Conclusion}
-\label{sec:org3e5d606}
+\label{sec:org68f7028}
 \label{sec:conclusion}
@@
 \section*{Acknowledgments}
-\label{sec:org2fdf2e5}
-This research benefited from a FRIA grant from the French Community of Belgium.
+\label{sec:org49166ff}
+This research benefited from a FRIA grant (grant number: FC 31597) from the French Community of Belgium.
 
 \section*{References}
-\label{sec:org684d4d0}
+\label{sec:org8c97a5c}
 \bibliographystyle{iopart-num}

### 2021-02-19 journal/paper.tex
Final submission

@@
-% Created 2020-11-02 lun. 15:33
+% Created 2021-02-19 ven. 11:49
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{capt-of, subcaption}
-\usepackage{hyperref}
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
 \usepackage{amsmath, amssymb, amsfonts, cases, bm}
@@
 \usetikzlibrary{shapes.misc,arrows,arrows.meta}
+\usepackage[square,comma,sort&compress,numbers]{natbib}
+\renewcommand{\bibsection}{\section*{References}}
 \hypersetup{
@@
  pdfsubject={},
- pdfcreator={Emacs 27.1.50 (Org mode 9.4)}, 
+ pdfcreator={Emacs 27.1 (Org mode 9.5)}, 
  pdflang={English}}
@@
 \address{$^3$ European Synchrotron Radiation Facility, Grenoble, France}
-\ead{dehaeze.thomas@gmail.com}
+\ead{tdehaeze@uliege.be}
 
@@
 Conditions for stability and optimal parameters are derived.
-The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on suspension modes.
+The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on the suspension modes.
 \end{abstract}
@@
 
-\submitto{\SMS}
+\submitto{{\it Engineering Research Express\/}}
 \maketitle
-% \ioptwocol
+% Two Columns output
+\ioptwocol
 
 \section{Introduction}
-\label{sec:orgdf2365d}
+\label{sec:org1def047}
 \label{sec:introduction}
-There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
-A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
-In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.
+There is an increasing need to reduce the undesirable vibration of sensitive equipment in many different fields such as in aerospace industry~\cite{hanieh03_activ_stewar,hauge04_sensor_contr_space_based_six,souleille18_concep_activ_mount_space_applic}, semi conductor industry~\cite{yoshioka01_activ_microv_isolat_system_hi}, microscopy~\cite{lan08_activ_vibrat_isolat_long_range,fleming15_low_order_dampin_track_contr}, gravitational wave detectors~\cite{matichard15_seism_isolat_advan_ligo} and particles accelerators~\cite{collette10_activ_quadr_stabil_futur_linear_partic_collid,dehaeze18_sampl_stabil_for_tomog_exper}.
 
-In \cite{preumont92_activ_dampin_by_local_force}, the Integral Force Feedback (IFF) control scheme has been proposed, where a force sensor, a force actuator and an integral controller are used to directly augment the damping of a mechanical system.
-When the force sensor is collocated with the actuator, the open-loop transfer function has alternating poles and zeros which facilitate to guarantee the stability of the closed loop system \cite{preumont02_force_feedb_versus_accel_feedb}.
+A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes~\cite{reilly06_critic,poel10_explor_activ_hard_mount_vibrat}.
+\par
+In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances~\cite{collette11_review_activ_vibrat_isolat_strat}.
 
+Many active damping techniques have been developed over the years such as Positive Position Feedback (PPF)~\cite{lin06_distur_atten_precis_hexap_point,fanson90_posit_posit_feedb_contr_large_space_struc}, Integral Force Feedback (IFF)~\cite{preumont91_activ} and Direct Velocity Feedback (DVF)~\cite{karnopp74_vibrat_contr_using_semi_activ_force_gener,serrand00_multic_feedb_contr_isolat_base_excit_vibrat,preumont02_force_feedb_versus_accel_feedb}.
+\par
+In~\cite{preumont92_activ_dampin_by_local_force}, the IFF control scheme has been proposed, where a force sensor, a force actuator and an integral controller are used to directly augment the damping of a mechanical system.
+When the force sensor is collocated with the actuator, the open-loop transfer function has alternating poles and zeros which facilitate to guarantee the stability of the closed loop system~\cite{preumont02_force_feedb_versus_accel_feedb}.
+It was latter shown that this property holds for multiple collated actuator/sensor pairs~\cite{preumont08_trans_zeros_struc_contr_with}. \par
+The main advantages of IFF over other active damping techniques are the guaranteed stability even in presence of flexible dynamics, good performances and robustness properties~\cite{preumont02_force_feedb_versus_accel_feedb}.
+\par
+Several improvements of the classical IFF have been proposed, such as adding a feed-through term to increase the achievable damping~\cite{teo15_optim_integ_force_feedb_activ_vibrat_contr} or adding an high pass filter to recover the loss of compliance at low frequency~\cite{chesne16_enhan_dampin_flexib_struc_using_force_feedb}.
+Recently, an \(\mathcal{H}_\infty\) optimization criterion has been used to derive optimal gains for the IFF controller~\cite{zhao19_optim_integ_force_feedb_contr}. \par
 However, when the platform is rotating, gyroscopic effects alter the system dynamics and IFF cannot be applied as is.
-The purpose of this paper is to study how the IFF strategy can be adapted to deal with these Gyroscopic effects.
-
+The purpose of this paper is to study how the IFF strategy can be adapted to deal with these gyroscopic effects. \par
 The paper is structured as follows.
-Section \ref{sec:dynamics} presents a simple model of a rotating suspended platform that will be used throughout this study.
-Section \ref{sec:iff} explains how the unconditional stability of IFF is lost due to Gyroscopic effects induced by the rotation.
-Section \ref{sec:iff_hpf} suggests a simple modification of the control law such that damping can be added to the suspension modes in a robust way.
-Section \ref{sec:iff_kp} proposes to add springs in parallel with the force sensors to regain the unconditional stability of IFF.
-Section \ref{sec:comparison} compares both proposed modifications to the classical IFF in terms of damping authority and closed-loop system behavior.
+Section~\ref{sec:dynamics} presents a simple model of a rotating suspended platform that will be used throughout this study.
+Section~\ref{sec:iff} explains how the unconditional stability of IFF is lost due to gyroscopic effects induced by the rotation.
+Section~\ref{sec:iff_hpf} suggests a simple modification of the control law such that damping can be added to the suspension modes in a robust way.
+Section~\ref{sec:iff_kp} proposes to add springs in parallel with the force sensors to regain the unconditional stability of IFF.
+Section~\ref{sec:comparison} compares both proposed modifications to the classical IFF in terms of damping authority and closed-loop system behavior.
 
 \section{Dynamics of Rotating Platforms}
-\label{sec:orgb49fb34}
+\label{sec:org414e8cb}
 \label{sec:dynamics}
-In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
-Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.
+In order to study how the rotation affects the use of IFF, a model of a suspended platform on top of a rotating stage is used.
+Figure~\ref{fig:system} represents a schematic of the model which is the simplest in which gyroscopic forces can be studied.
 
@@
 \centering
-\includegraphics[scale=0.9]{figs/fig01.pdf}
-\caption{\label{fig:system}Schematic of the studied System}
+\includegraphics[scale=1,scale=0.9]{figs/fig01.pdf}
+\caption{\label{fig:system}Schematic of the studied system}
 \end{figure}
 
-The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\second}\).
+The rotating stage is supposed to be ideal, meaning it induces a perfect rotation \(\theta(t) = \Omega t\) where \(\Omega\) is the rotational speed in \(\si{\radian\per\s}\).
 
-The suspended platform consists of two orthogonal actuators represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per\meter\second}\) and an ideal force source \(F_u, F_v\).
+The suspended platform consists of two orthogonal actuators each represented by three elements in parallel: a spring with a stiffness \(k\) in \(\si{\newton\per\meter}\), a dashpot with a damping coefficient \(c\) in \(\si{\newton\per(\meter\per\second)^{-1}}\) and an ideal force source \(F_u, F_v\).
 A payload with a mass \(m\) in \(\si{\kilo\gram}\), representing the sensitive equipment, is mounted on the (rotating) suspended platform.
@@
 \par
-To obtain the equations of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
+To obtain the equations of motion for the system represented in Figure~\ref{fig:system}, the Lagrangian equations are used:
 \begin{equation}
@@
 with \(L = T - V\) the Lagrangian, \(T\) the kinetic coenergy, \(V\) the potential energy, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
-The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is disregarded as the motion is considered to be imposed by the rotation stage.
+The equation of motion corresponding to the constant rotation along \(\vec{i}_w\) is disregarded as this motion is considered to be imposed by the rotation stage.
 \begin{equation}
@@
 
-Substituting \eqref{eq:energy_functions_lagrange} into \eqref{eq:lagrangian_equations} for both generalized coordinates gives two coupled differential equations
+Substituting Eq.~\eqref{eq:energy_functions_lagrange} into Eq.~\eqref{eq:lagrangian_equations} for both generalized coordinates gives two coupled differential equations~\eqref{eq:eom_coupled_1} and~\eqref{eq:eom_coupled_2}.
 \begin{subequations}
@@
   \begin{align}
-    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega^2 ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
-    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega^2}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
+    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega^2 ) d_u &= F_u + 2 m \Omega \dot{d}_v \label{eq:eom_coupled_1} \\
+    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega^2}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}} \label{eq:eom_coupled_2}
   \end{align}
@@
 
-The uniform rotation of the system induces two Gyroscopic effects as shown in \eqref{eq:eom_coupled}:
+The uniform rotation of the system induces two gyroscopic effects as shown in Eq.~\eqref{eq:eom_coupled}:
 \begin{itemize}
-\item Centrifugal forces: that can been seen as added negative stiffness \(- m \Omega^2\) along \(\vec{i}_u\) and \(\vec{i}_v\)
-\item Coriolis Forces: that couples the motion in the two orthogonal directions
+\item Centrifugal forces: that can been seen as an added negative stiffness \(- m \Omega^2\) along \(\vec{i}_u\) and \(\vec{i}_v\)
+\item Coriolis Forces: that adds coupling between the two orthogonal directions.
 \end{itemize}
 
-One can verify that without rotation (\(\Omega = 0\)) the system becomes equivalent to two uncoupled one degree of freedom mass-spring-damper systems:
-\begin{subequations}
-\label{eq:oem_no_rotation}
-  \begin{align}
-    m \ddot{d}_u + c \dot{d}_u + k d_u &= F_u \\
-    m \ddot{d}_v + c \dot{d}_v + k d_v &= F_v
-  \end{align}
-\end{subequations}
+One can verify that without rotation (\(\Omega = 0\)) the system becomes equivalent to two uncoupled one degree of freedom mass-spring-damper systems.
 
 \par
-To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\mathbf{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained.
+To study the dynamics of the system, the differential equations of motions~\eqref{eq:eom_coupled} are converted into the Laplace domain and the \(2 \times 2\) transfer function matrix \(\mathbf{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) in Eq.~\eqref{eq:Gd_mimo_tf} is obtained.
+Its elements are shown in Eq.~\eqref{eq:Gd_indiv_el}.
 
@@
 \begin{subequations}
+\label{eq:Gd_indiv_el}
 \begin{align}
-  \mathbf{G}_{d}(1,1) &= {\frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
-                  &= \mathbf{G}_{d}(2,2) \nonumber \\
-  \mathbf{G}_{d}(1,2) &= {\frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
-                  &= -\mathbf{G}_{d}(1,2) \nonumber
+  & \mathbf{G}_{d}(1,1) = \mathbf{G}_{d}(2,2) = \dots \nonumber \\
+  & \quad {\frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}} \\
+  & \mathbf{G}_{d}(1,2) = -\mathbf{G}_{d}(1,2) = \dots \nonumber \\
+  & \quad {\frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}}
 \end{align}
@@
 
-To simplify the analysis, the undamped natural frequency \(\omega_0\) and the damping ratio \(\xi\) are used
+To simplify the analysis, the undamped natural frequency \(\omega_0\) and the damping ratio \(\xi\) are used as in Eq.~\eqref{eq:xi_and_omega}.
 \begin{equation}
+\label{eq:xi_and_omega}
   \omega_0 = \sqrt{\frac{k}{m}} \text{ in } \si{\radian\per\second}, \quad \xi = \frac{c}{2 \sqrt{k m}}
@@
 
-The transfer function matrix \(\mathbf{G}_d\) becomes equal to
+The elements of transfer function matrix \(\mathbf{G}_d\) are now describe by Eq.~\eqref{eq:Gd_w0_xi_k}.
 \begin{subequations}
@@
   \begin{align}
-    \mathbf{G}_{d}(1,1) &= {\scriptstyle \frac{\frac{1}{k} \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
-    \mathbf{G}_{d}(1,2) &= {\scriptstyle \frac{\frac{1}{k} \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+    \mathbf{G}_{d}(1,1) &= {\scriptstyle \frac{\frac{1}{k} \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}}  \\
+    \mathbf{G}_{d}(1,2) &= {\scriptstyle \frac{\frac{1}{k} \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}}
   \end{align}
@@
 \par
-The poles of \(\mathbf{G}_d\) are the complex solutions \(p\) of \eqref{eq:poles}.
+The poles of \(\mathbf{G}_d\) are the complex solutions \(p\) of Eq.~\eqref{eq:poles}.
 
@@
 
-Supposing small damping (\(\xi \ll 1\)), two pairs of complex conjugate poles are obtained \eqref{eq:pole_values}.
+Supposing small damping (\(\xi \ll 1\)), two pairs of complex conjugate poles are obtained as shown in Eq.~\eqref{eq:pole_values}.
 
@@
 
-The real part and complex part of these two pairs of complex conjugate poles are represented in Figure \ref{fig:campbell_diagram} as a function of the rotational speed \(\Omega\).
-As the rotational speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) to lower frequencies.
+The real and complex parts of these two pairs of complex conjugate poles are represented in Figure~\ref{fig:campbell_diagram} as a function of the rotational speed \(\Omega\).
+As the rotational speed increases, \(p_{+}\) goes to higher frequencies and \(p_{-}\) goes to lower frequencies.
 The system becomes unstable for \(\Omega > \omega_0\) as the real part of \(p_{-}\) is positive.
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/fig02a.pdf}
+\centering
+\includegraphics[scale=1]{figs/fig02a.pdf}
 \caption{\label{fig:campbell_diagram_real} Real Part}
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/fig02b.pdf}
+\centering
+\includegraphics[scale=1]{figs/fig02b.pdf}
 \caption{\label{fig:campbell_diagram_imag} Imaginary Part}
@@
 \hfill
-\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
+\caption{\label{fig:campbell_diagram}Campbell diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
 \centering
@@
 
-Looking at the transfer function matrix \(\mathbf{G}_d\) in \eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and the two off-diagonal (coupling) terms are opposite.
-The bode plot of these two terms are shown in Figure \ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
+Looking at the transfer function matrix \(\mathbf{G}_d\) in Eq.~\eqref{eq:Gd_w0_xi_k}, one can see that the two diagonal (direct) terms are equal and that the two off-diagonal (coupling) terms are opposite.
+The bode plot of these two terms are shown in Figure~\ref{fig:plant_compare_rotating_speed} for several rotational speeds \(\Omega\).
 These plots confirm the expected behavior: the frequency of the two pairs of complex conjugate poles are further separated as \(\Omega\) increases.
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/fig03a.pdf}
+\centering
+\includegraphics[scale=1]{figs/fig03a.pdf}
 \caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms}
@@
 \begin{subfigure}[c]{0.48\linewidth}
-\includegraphics[width=\linewidth]{figs/fig03b.pdf}
+\centering
+\includegraphics[scale=1]{figs/fig03b.pdf}
 \caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms}
@@
 \hfill
-\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\mathbf{G}_d\) for several rotational speed \(\Omega\)}
+\caption{\label{fig:plant_compare_rotating_speed}Bode plots for \(\mathbf{G}_d\) for several rotational speed \(\Omega\)}
 \centering
@@
 \section{Decentralized Integral Force Feedback}
-\label{sec:org7b1adf9}
+\label{sec:orgdc87c6d}
 \label{sec:iff}
-In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
+In order to apply IFF to the rotating system, force sensors are added in series with the two actuators (Figure~\ref{fig:system_iff}).
 As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
-The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.
+The control diagram is schematically shown in Figure~\ref{fig:control_diagram_iff}.
 
@@
 \centering
-\includegraphics[scale=0.9]{figs/fig04.pdf}
-\caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
+\includegraphics[scale=1,scale=0.9]{figs/fig04.pdf}
+\caption{\label{fig:system_iff}System with added force sensor in series with the actuators and with a decentralized IFF architecture}
 \end{figure}
@@
 \centering
-\includegraphics[scale=1]{figs/fig05.pdf}
-\caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
+\includegraphics[scale=1,scale=1]{figs/fig05.pdf}
+\caption{\label{fig:control_diagram_iff}Control diagram for decentralized IFF}
 \end{figure}
@@
 \par
-The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_iff} are equal to
+The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure~\ref{fig:system_iff} are described by Eq.~\eqref{eq:measured_force}.
 \begin{equation}
@@
 
-Inserting \eqref{eq:Gd_w0_xi_k} into \eqref{eq:measured_force} yields
+The transfer function matrix \(\mathbf{G}_{f}\) from actuator forces to measured forces in Eq.~\eqref{eq:Gf_mimo_tf} can be obtained by inserting Eq.~\eqref{eq:Gd_w0_xi_k} into Eq.~\eqref{eq:measured_force}.
+Its elements are shown in Eq.~\eqref{eq:Gf_indiv_el}.
+
 \begin{equation}
@@
 \begin{subequations}
+\label{eq:Gf_indiv_el}
 \label{eq:Gf}
   \begin{align}
-    \mathbf{G}_{f}(1,1) &= {\scriptstyle \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \\
-    \mathbf{G}_{f}(1,2) &= {\scriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+    & \mathbf{G}_{f}(1,1) = \mathbf{G}_{f}(2,2) = \dots \nonumber \\
+    & \quad {\scriptstyle \frac{\left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \label{eq:Gf_diag_tf} \\
+    & \mathbf{G}_{f}(1,2) = -\mathbf{G}_{f}(2,1) = \dots \nonumber \\
+    & \quad {\scriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \label{eq:Gf_off_diag_tf}
   \end{align}
@@
 
-The zeros of the diagonal terms of \(\mathbf{G}_f\) are equal to (neglecting the damping for simplicity)
+The zeros of the diagonal terms of \(\mathbf{G}_f\) in Eq.~\eqref{eq:Gf_diag_tf} are computed, and neglecting the damping for simplicity, two complex conjugated poles \(z_{c}\) are obtained in Eq.~\eqref{eq:iff_zero_cc}, and two real zeros \(z_{r}\) in Eq.~\eqref{eq:iff_zero_real}.
 \begin{subequations}
@@
 
-The frequency of the pair of complex conjugate zeros \(z_c\) \eqref{eq:iff_zero_cc} always lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) \eqref{eq:pole_values}.
+It is interesting to see that the frequency of the pair of complex conjugate zeros \(z_c\) in Eq.~\eqref{eq:iff_zero_cc} always lies between the frequency of the two pairs of complex conjugate poles \(p_{-}\) and \(p_{+}\) in Eq.~\eqref{eq:pole_values}.
 
-For non-null rotational speeds, two real zeros \(z_r\) \eqref{eq:iff_zero_real} appear in the diagonal terms inducing a non-minimum phase behavior.
-This can be seen in the Bode plot of the diagonal terms (Figure \ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(\SI{180}{\degree}\).
+For non-null rotational speeds, the two real zeros \(z_r\) in Eq.~\eqref{eq:iff_zero_real} induce a non-minimum phase behavior.
+This can be seen in the Bode plot of the diagonal terms (Figure~\ref{fig:plant_iff_compare_rotating_speed}) where the low frequency gain is no longer zero while the phase stays at \(\SI{180}{\degree}\).
 
-The low frequency gain of \(\mathbf{G}_f\) increases with the rotational speed \(\Omega\)
+The low frequency gain of \(\mathbf{G}_f\) increases with the rotational speed \(\Omega\) as shown in Eq.~\eqref{eq:low_freq_gain_iff_plan}.
 \begin{equation}
@@
 \centering
-\includegraphics[scale=0.95]{figs/fig06.pdf}
+\includegraphics[scale=1,scale=0.95]{figs/fig06.pdf}
 \caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
@@
 \label{sec:iff_pure_int}
-The two IFF controllers \(K_F\) consist of a pure integrator
+The two IFF controllers \(K_{F}\) consist of a pure integrator as shown in Eq.~\eqref{eq:Kf_pure_int} where \(g\) is a scalar representing the gain of the controller.
 \begin{equation}
@@
 \begin{aligned}
-  \mathbf{K}_F(s) &= \begin{bmatrix} K_F(s) & 0 \\ 0 & K_F(s) \end{bmatrix} \\
-  K_F(s) &= g \cdot \frac{1}{s}
+  \mathbf{K}_{F}(s) &= \begin{bmatrix} K_{F}(s) & 0 \\ 0 & K_{F}(s) \end{bmatrix} \\
+  K_{F}(s) &= g \cdot \frac{1}{s}
 \end{aligned}
 \end{equation}
-where \(g\) is a scalar representing the gain of the controller.
 
-In order to see how the IFF affects the poles of the closed loop system, a Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers \(K_F\) simultaneously.
-As explained in \cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
+In order to see how the IFF controller affects the poles of the closed loop system, a Root Locus plot (Figure~\ref{fig:root_locus_pure_iff}) is constructed as follows: the poles of the closed-loop system are drawn in the complex plane as the controller gain \(g\) varies from \(0\) to \(\infty\) for the two controllers \(K_{F}\) simultaneously.
+As explained in~\cite{preumont08_trans_zeros_struc_contr_with,skogestad07_multiv_feedb_contr}, the closed-loop poles start at the open-loop poles (shown by \(\tikz[baseline=-0.6ex] \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){};\)) for \(g = 0\) and coincide with the transmission zeros (shown by \(\tikz[baseline=-0.6ex] \draw[line width=2pt, inner sep=0pt, outer sep=0pt] (0,0) circle[radius=3pt];\)) as \(g \to \infty\).
 The direction of increasing gain is indicated by arrows \(\tikz[baseline=-0.6ex] \draw[-{Stealth[round]},line width=2pt] (0,0) -- (0.3,0);\).
@@
 \centering
-\includegraphics[scale=1]{figs/fig07.pdf}
-\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
+\includegraphics[scale=1,scale=1]{figs/fig07.pdf}
+\caption{\label{fig:root_locus_pure_iff}Root Locus: Evolution of the closed-loop poles with increasing controller gains \(g\)}
 \end{figure}
 
-Whereas collocated IFF is usually associated with unconditional stability \cite{preumont91_activ}, this property is lost as soon as the rotational speed in non-null due to gyroscopic effects.
-This can be seen in the Root Locus plot (Figure \ref{fig:root_locus_pure_iff}) where the poles corresponding to the controller are bound to the right half plane implying closed-loop system instability.
+Whereas collocated IFF is usually associated with unconditional stability~\cite{preumont91_activ}, this property is lost due to gyroscopic effects as soon as the rotational speed in non-null.
+This can be seen in the Root Locus plot (Figure~\ref{fig:root_locus_pure_iff}) where poles corresponding to the controller are bound to the right half plane implying closed-loop system instability.
 
-Physically, this can be explain like so: at low frequency, the loop gain is very large due to the pure integrators in \(K_F\).
+Physically, this can be explained like so: at low frequency, the loop gain is very large due to the pure integrator in \(K_{F}\) and the finite gain of the plant (Figure~\ref{fig:plant_iff_compare_rotating_speed}).
 The control system is thus canceling the spring forces which makes the suspended platform no able to hold the payload against centrifugal forces, hence the instability.
 
-In order to apply decentralized IFF on rotating platforms, two solutions are proposed to deal with this instability problem.
-The first one consists of slightly modifying the control law (Section \ref{sec:iff_hpf}) while the second one consists of adding springs in parallel with the force sensors (Section \ref{sec:iff_kp}).
+In order to apply decentralized IFF to rotating platforms, two solutions are proposed to deal with this instability problem.
+The first one consists of slightly modifying the control law (Section~\ref{sec:iff_hpf}) while the second one consists of adding springs in parallel with the force sensors (Section~\ref{sec:iff_kp}).
 
 \section{Integral Force Feedback with High Pass Filter}
-\label{sec:orgb29360e}
+\label{sec:orgdb88ec7}
 \label{sec:iff_hpf}
@@
 
-In order to limit this low frequency controller gain, an high pass filter (HPF) can be added to the controller
+In order to limit the low frequency controller gain, an High Pass Filter (HPF) can be added to the controller as shown in Eq.~\eqref{eq:IFF_LHF}.
+
 \begin{equation}
@@
 
-This is equivalent to slightly shifting the controller pole to the left along the real axis.
+This is equivalent as to slightly shifting the controller pole to the left along the real axis.
 
-This modification of the IFF controller is typically done to avoid saturation associated with the pure integrator \cite{preumont91_activ}.
+This modification of the IFF controller is typically done to avoid saturation associated with the pure integrator~\cite{preumont91_activ,marneffe07_activ_passiv_vibrat_isolat_dampin_shunt_trans}.
 This is however not the case in this study as it will become clear in the next section.
@@
 \par
-The loop gains, \(K_F(s)\) times the direct dynamics \(f_u/F_u\), with and without the added HPF are shown in Figure \ref{fig:loop_gain_modified_iff}.
+The loop gains, \(K_F(s)\) times the direct dynamics \(f_u/F_u\), with and without the added HPF are shown in Figure~\ref{fig:loop_gain_modified_iff}.
 The effect of the added HPF limits the low frequency gain as expected.
 
-The Root Loci for the decentralized IFF with and without the HPF are displayed in Figure \ref{fig:root_locus_modified_iff}.
-With the added HPF, the poles of the closed loop system are shown to be stable up to some value of the gain \(g_\text{max}\)
+The Root Locus plots for the decentralized IFF with and without the HPF are displayed in Figure~\ref{fig:root_locus_modified_iff}.
+With the added HPF, the poles of the closed loop system are shown to be stable up to some value of the gain \(g_\text{max}\) in Eq.~\eqref{eq:gmax_iff_hpf}.
+
 \begin{equation}
@@
 \end{equation}
-It is interesting to note that \(g_{\text{max}}\) also corresponds to the gain where the low frequency loop gain (Figure \ref{fig:loop_gain_modified_iff}) reaches one.
+
+It is interesting to note that \(g_{\text{max}}\) also corresponds to the controller gain at which the low frequency loop gain (Figure~\ref{fig:loop_gain_modified_iff}) reaches one.
 
@@
 \centering
-\includegraphics[scale=0.95]{figs/fig08.pdf}
+\includegraphics[scale=1,scale=0.95]{figs/fig08.pdf}
 \caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \centering
-\includegraphics[scale=1]{figs/fig09.pdf}
+\includegraphics[scale=1,scale=1]{figs/fig09.pdf}
 \caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
@@
 \par
-Two parameters can be tuned for the modified controller \eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
+Two parameters can be tuned for the modified controller in Eq.~\eqref{eq:IFF_LHF}: the gain \(g\) and the pole's location \(\omega_i\).
 The optimal values of \(\omega_i\) and \(g\) are here considered as the values for which the damping of all the closed-loop poles are simultaneously maximized.
 
-In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Loci for several \(\omega_i\) are displayed in Figure \ref{fig:root_locus_wi_modified_iff}.
-It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the suspension modes, the control gain \(g\) may be limited to small values due to \eqref{eq:gmax_iff_hpf}.
+In order to visualize how \(\omega_i\) does affect the attainable damping, the Root Locus plots for several \(\omega_i\) are displayed in Figure~\ref{fig:root_locus_wi_modified_iff}.
+It is shown that even though small \(\omega_i\) seem to allow more damping to be added to the suspension modes, the control gain \(g\) may be limited to small values due to Eq.~\eqref{eq:gmax_iff_hpf}.
 
@@
 \centering
-\includegraphics[scale=0.95]{figs/fig10.pdf}
+\includegraphics[scale=1,scale=0.95]{figs/fig10.pdf}
 \caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
@@
 In order to study this trade off, the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) is computed as a function of \(\omega_i/\omega_0\).
-The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also displayed and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure \ref{fig:mod_iff_damping_wi}).
+The gain \(g_{\text{opt}}\) at which this maximum damping is obtained is also displayed and compared with the gain \(g_{\text{max}}\) at which the system becomes unstable (Figure~\ref{fig:mod_iff_damping_wi}).
 
@@
 \centering
-\includegraphics[scale=0.95]{figs/fig11.pdf}
+\includegraphics[scale=1,scale=0.95]{figs/fig11.pdf}
 \caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\).
@@
 \item \(0.02 < \omega_i/\omega_0 < 0.2\): the attainable damping ratio is maximized and is reached for \(g \approx 2\)
-\item \(0.2 < \omega_i/\omega_0\): the added damping decreases as \(\omega_i/\omega_0\) increases
+\item \(0.2 < \omega_i/\omega_0\): the added damping decreases as \(\omega_i/\omega_0\) increases.
 \end{itemize}
@@
 \section{Integral Force Feedback with Parallel Springs}
-\label{sec:orgaa66b9e}
+\label{sec:org19946d1}
 \label{sec:iff_kp}
-In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
-Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
+In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the gyroscopic effects.
+Such springs are schematically shown in Figure~\ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.
 
-Amplified piezoelectric stack actuators can also be used for such purpose where a part of the piezoelectric stack is used as an actuator while the rest is used as a force sensor \cite{souleille18_concep_activ_mount_space_applic}.
-The parallel stiffness \(k_p\) then corresponds to the amplification structure.
-An example of such system is shown in Figure \ref{fig:cedrat_xy25xs}.
+Amplified piezoelectric stack actuators can be used for such purpose where a part of the piezoelectric stack is used as an actuator while the rest is used as a force sensor~\cite{souleille18_concep_activ_mount_space_applic}.
+The parallel stiffness \(k_p\) then corresponds to the mechanical amplification structure.
 
@@
 \centering
-\includegraphics[scale=0.9]{figs/fig12.pdf}
+\includegraphics[scale=1,scale=0.9]{figs/fig12.pdf}
 \caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=0.17]{figs/fig13.pdf}
-\caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
-\end{figure}
+\par
+The forces measured by the two force sensors represented in Figure~\ref{fig:system_parallel_springs} are described by Eq.~\eqref{eq:measured_force_kp}.
 
-\par
-The forces \(\begin{bmatrix}f_u & f_v\end{bmatrix}\) measured by the two force sensors represented in Figure \ref{fig:system_parallel_springs} are equal to
 \begin{equation}
@@
 
-In order to keep the overall stiffness \(k = k_a + k_p\) constant, thus not modifying the open-loop poles as \(k_p\) is changed, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
+In order to keep the overall stiffness \(k = k_a + k_p\) constant, thus not modifying the open-loop poles as \(k_p\) is changed, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor as in Eq.~\eqref{eq:kp_alpha}.
+
 \begin{equation}
+\label{eq:kp_alpha}
   k_p = \alpha k, \quad k_a = (1 - \alpha) k
@@
 
-The equations of motion are derived and transformed in the Laplace domain
+After the equations of motion derived and transformed in the Laplace domain, the transfer function matrix \(\mathbf{G}_k\) in Eq.~\eqref{eq:Gk_mimo_tf} is computed.
+Its elements are shown in Eq.~\eqref{eq:Gk_diag} and~\eqref{eq:Gk_off_diag}.
+
 \begin{equation}
@@
 \begin{align}
-& \mathbf{G}_{k}(1,1) = \dots \nonumber \\
-& {\scriptstyle \frac{\big( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \big) \big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big) + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2}{\big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big)^2 + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2} } \\
-& \mathbf{G}_{k}(1,2) = {\scriptscriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} }
+& \mathbf{G}_{k}(1,1) = \mathbf{G}_{k}(2,2) = \dots \nonumber \\
+& \quad {\scriptstyle \frac{\big( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \big) \big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big) + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2}{\big( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \big)^2 + \big( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \big)^2} } \label{eq:Gk_diag} \\
+& \mathbf{G}_{k}(1,2) = -\mathbf{G}_{k}(2,1) = \dots \nonumber \\
+& \quad {\scriptscriptstyle \frac{- \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2} } \label{eq:Gk_off_diag}
 \end{align}
@@
 
-Comparing \(\mathbf{G}_k\) \eqref{eq:Gk} with \(\mathbf{G}_f\) \eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
-The two real zeros \(z_r\) \eqref{eq:iff_zero_real} that were inducing non-minimum phase behavior are transformed into complex conjugate zeros if the following condition hold
+Comparing \(\mathbf{G}_k\) in Eq.~\eqref{eq:Gk} with \(\mathbf{G}_f\) in Eq.~\eqref{eq:Gf} shows that while the poles of the system are kept the same, the zeros of the diagonal terms have changed.
+The two real zeros \(z_r\) in Eq.~\eqref{eq:iff_zero_real} that were inducing a non-minimum phase behavior are transformed into two complex conjugate zeros if the condition in Eq.~\eqref{eq:kp_cond_cc_zeros} holds.
+
 \begin{equation}
@@
 
-Thus, if the added parallel stiffness \(k_p\) is higher than the negative stiffness induced by centrifugal forces \(m \Omega^2\), the direct dynamics from actuator to force sensor will show minimum phase behavior.
-This is confirmed by the Bode plot of the direct dynamics in Figure \ref{fig:plant_iff_kp}.
+Thus, if the added parallel stiffness \(k_p\) is higher than the negative stiffness induced by centrifugal forces \(m \Omega^2\), the dynamics from actuator to its collocated force sensor will show minimum phase behavior.
+This is confirmed by the Bode plot in Figure~\ref{fig:plant_iff_kp}.
 
-Figure \ref{fig:root_locus_iff_kp} shows Root Loci plots for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\) when \(K_F\) is a pure integrator \eqref{eq:Kf_pure_int}.
-It is shown that if the added stiffness is higher than the maximum negative stiffness, the poles of the closed-loop system stay in the (stable) right half-plane, and hence the unconditional stability of IFF is recovered.
+Figure~\ref{fig:root_locus_iff_kp} shows the Root Locus plots for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\) when \(K_F\) is a pure integrator as in Eq.~\eqref{eq:Kf_pure_int}.
+It is shown that if the added stiffness is higher than the maximum negative stiffness, the poles of the closed-loop system are bounded on the (stable) left half-plane, and hence the unconditional stability of IFF is recovered.
 
@@
 \centering
-\includegraphics[scale=0.95]{figs/fig14.pdf}
-\caption{\label{fig:plant_iff_kp}Bode plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\includegraphics[scale=1,scale=0.95]{figs/fig13.pdf}
+\caption{\label{fig:plant_iff_kp}Bode plot of \(G_{k}(1,1) = f_u/F_u\) without parallel spring, with parallel spring stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.95]{figs/fig15.pdf}
-\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
+\includegraphics[scale=1,scale=0.95]{figs/fig14.pdf}
+\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel spring stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
 \end{figure}
@@
 \par
-Even though the parallel stiffness \(k_p\) has no impact on the open-loop poles (as the overall stiffness \(k\) stays constant), it has a large impact on the transmission zeros.
-Moreover, as the attainable damping is generally proportional to the distance between poles and zeros \cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the parallel stiffness \(k_p\) is foreseen to have a large impact on the attainable damping.
+Even though the parallel stiffness \(k_p\) has no impact on the open-loop poles (as the overall stiffness \(k\) is kept constant), it has a large impact on the transmission zeros.
+Moreover, as the attainable damping is generally proportional to the distance between poles and zeros~\cite{preumont18_vibrat_contr_activ_struc_fourt_edition}, the parallel stiffness \(k_p\) is foreseen to have a large impact on the attainable damping.
 
-To study this effect, Root Locus plots for several parallel stiffnesses \(k_p > m \Omega^2\) are shown in Figure \ref{fig:root_locus_iff_kps}.
-The frequencies of the transmission zeros of the system are increasing with the parallel stiffness \(k_p\) and the associated attainable damping is reduced.
-Therefore, even though the parallel stiffness \(k_p\) should be larger than \(m \Omega^2\) for stability reasons, it should not be taken too high as this would limit the attainable bandwidth.
+To study this effect, Root Locus plots for several parallel stiffnesses \(k_p > m \Omega^2\) are shown in Figure~\ref{fig:root_locus_iff_kps}.
+The frequencies of the transmission zeros of the system are increasing with an increase of the parallel stiffness \(k_p\) and the associated attainable damping is reduced.
+Therefore, even though the parallel stiffness \(k_p\) should be larger than \(m \Omega^2\) for stability reasons, it should not be taken too large as this would limit the attainable damping.
 
-This is confirmed in Figure \ref{fig:opt_damp_alpha} where the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) and the associated control gain \(g_\text{opt}\) are computed as a function of \(\alpha\).
+This is confirmed by the Figure~\ref{fig:opt_damp_alpha} where the attainable closed-loop damping ratio \(\xi_{\text{cl}}\) and the associated optimal control gain \(g_\text{opt}\) are computed as a function of \(\alpha\).
 
@@
 \centering
-\includegraphics[scale=1]{figs/fig16.pdf}
-\caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
+\includegraphics[scale=1,scale=1]{figs/fig15.pdf}
+\caption{\label{fig:root_locus_iff_kps}Comparison of the Root Locus plots for three parallel stiffnessses \(k_p\)}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.95]{figs/fig17.pdf}
-\caption{\label{fig:opt_damp_alpha}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
+\includegraphics[scale=1,scale=0.95]{figs/fig16.pdf}
+\caption{\label{fig:opt_damp_alpha}Optimal damping ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
 \end{figure}
@@
 \section{Comparison and Discussion}
-\label{sec:orgd845e3a}
+\label{sec:org3688d53}
 \label{sec:comparison}
-Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
+In order to overcome the instability issue of the classical IFF strategy when applied to rotating platforms, two modifications of IFF have been proposed in Sections~\ref{sec:iff_hpf} and~\ref{sec:iff_kp}.
 These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.
 
-For the following comparisons, the cut-off frequency for the HPF is set to \(\omega_i = 0.1 \omega_0\) and the stiffness of the parallel springs is set to \(k_p = 5 m \Omega^2\).
+For the following comparisons, the cut-off frequency for the HPF is set to \(\omega_i = 0.1 \omega_0\) and the stiffness of the parallel springs is set to \(k_p = 5 m \Omega^2\) (corresponding to \(\alpha = 0.05\)).
+These values are chosen based on the discussion about optimal parameters.
 
 \par
-Figure \ref{fig:comp_root_locus} shows the Root Loci for the two proposed IFF modifications.
+Figure~\ref{fig:comp_root_locus} shows the Root Locus plots for the two proposed IFF modifications.
 While the two pairs of complex conjugate open-loop poles are identical for both techniques, the transmission zeros are not.
@@
 
-One can observe that the closed loop poles of the system with added springs (in red) are bounded to the left half plane implying unconditional stability.
+One can observe that the closed loop poles corresponding to the system with added springs (in red) are bounded to the left half plane implying unconditional stability.
 This is not the case for the system where the controller is augmented with an HPF (in blue).
@@
 \centering
-\includegraphics[scale=1]{figs/fig18.pdf}
+\includegraphics[scale=1,scale=1]{figs/fig17.pdf}
 \caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
@@
 
-The transmissibility is defined as the transfer function from the displacement of the rotating stage to the displacement of the payload.
+The transmissibility is here defined as the transfer function from a displacement of the rotating stage along \(\vec{i}_x\) to the displacement of the payload along the same direction.
 It is used to characterize how much vibration is transmitted through the suspended platform to the payload.
@@
 This is a useful metric when disturbances are directly applied to the payload.
+It is here defined as the transfer function from external forces applied on the payload along \(\vec{i}_x\) to the displacement of the payload along the same direction.
 
-The two techniques are also compared with passive damping (Figure \ref{fig:system}) where the damping coefficient \(c\) is tuned to critically damp the resonance when the rotating speed is null.
+The two techniques are also compared with passive damping (Figure~\ref{fig:system}) where the damping coefficient \(c\) is tuned to critically damp the resonance when the rotating speed is null as shown in Eq.~\eqref{eq:critical_damp}.
 \begin{equation}
+\label{eq:critical_damp}
   c_\text{crit} = 2 \sqrt{k m}
@@
 
-Very similar results are obtained for the two proposed IFF modifications in terms of transmissibility (Figure \ref{fig:comp_transmissibility}) and compliance (Figure \ref{fig:comp_compliance}).
+Very similar results are obtained for the two proposed IFF modifications in terms of transmissibility (Figure~\ref{fig:comp_transmissibility}) and compliance (Figure~\ref{fig:comp_compliance}).
 It is also confirmed that these two techniques can significantly damp the suspension modes.
@@
 \centering
-\includegraphics[scale=1]{figs/fig19.pdf}
-\caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
+\includegraphics[scale=1,scale=1]{figs/fig18.pdf}
+\caption{\label{fig:comp_transmissibility}Comparison of the two proposed active damping techniques - transmissibility}
 \end{figure}
@@
 \centering
-\includegraphics[scale=1]{figs/fig20.pdf}
-\caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
+\includegraphics[scale=1,scale=1]{figs/fig19.pdf}
+\caption{\label{fig:comp_compliance}Comparison of the two proposed active damping techniques - compliance}
 \end{figure}
 
-On can see in Figure \ref{fig:comp_transmissibility} that the problem of the degradation of the transmissibility at high frequency when using passive damping techniques is overcome by the use of IFF.
+On can see in Figure~\ref{fig:comp_transmissibility} that the problem of the degradation of the transmissibility at high frequency when using passive damping techniques is overcome by the use of IFF.
 
-The addition of the HPF or the use of the parallel stiffness permit to limit the degradation of the compliance as compared with classical IFF (Figure \ref{fig:comp_compliance}).
+The addition of the HPF or the use of the parallel stiffness also permits to limit the degradation of the compliance as compared with classical IFF (Figure~\ref{fig:comp_compliance}).
 
 \section{Conclusion}
-\label{sec:org68f7028}
+\label{sec:org2f060ad}
 \label{sec:conclusion}
@@
 This is equivalent as to moving the controller pole to the left along the real axis.
-This renders the closed loop system stable up to some value of the controller gain \(g_\text{max}\).
+This allows the closed loop system to be stable up to some value of the controller gain.
 
@@
 
-Future work will focus on the experimental validation of the proposed active damping techniques.
+Future work will focus on the experimental validation of the proposed IFF modifications.
 
-The Matlab code that was used for this study is available under a MIT License and archived in Zenodo \cite{dehaeze20_activ_dampin_rotat_posit_platf}.
+\section*{Data Availability}
+\label{sec:org6c5e786}
+Matlab~\cite{matlab20} was used for this study.
+The source code is available under a MIT License and archived in Zenodo~\cite{dehaeze20_activ_dampin_rotat_posit_platf}.
 
 \section*{Acknowledgments}
-\label{sec:org49166ff}
+\label{sec:org2c37487}
 This research benefited from a FRIA grant (grant number: FC 31597) from the French Community of Belgium.
+This paper is based on a paper previously presented at the ISMA conference~\cite{dehaeze20_activ_dampin_rotat_platf_integ_force_feedb}.
 
-\section*{References}
-\label{sec:org8c97a5c}
 \bibliographystyle{iopart-num}
-\bibliography{ref.bib}
+\bibliography{ref}
 \end{document}

### 2021-02-20 matlab/index.tex
Add link to matlab pdf and matlab zip

% Created 2021-02-20 sam. 14:43
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper, 10pt, DIV=12, parskip=full]{scrreprt}

\input{preamble.tex}
\addbibresource{ref.bib}
\author{Thomas Dehaeze}
\date{\today}
\title{Active Damping of Rotating Platforms using Integral Force Feedback - Matlab Computation}
\hypersetup{
 pdfauthor={Thomas Dehaeze},
 pdftitle={Active Damping of Rotating Platforms using Integral Force Feedback - Matlab Computation},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

This document gathers the Matlab code used to for the conference paper \cite{dehaeze20_activ_dampin_rotat_platf_integ_force_feedb} and the journal paper \cite{dehaeze21_activ_dampin_rotat_platf_using}.

It is structured in several sections:
\begin{itemize}
\item Section \ref{sec:system_description}: presents a simple model of a rotating suspended platform that will be used throughout this study.
\item Section \ref{sec:iff_pure_int}: explains how the unconditional stability of IFF is lost due to Gyroscopic effects induced by the rotation.
\item Section \ref{sec:iff_pseudo_int}: suggests a simple modification of the control law such that damping can be added to the suspension modes in a robust way.
\item Section \ref{sec:iff_parallel_stiffness}: proposes to add springs in parallel with the force sensors to regain the unconditional stability of IFF.
\item Section \ref{sec:comparison}: compares both proposed modifications to the classical IFF in terms of damping authority and closed-loop system behavior.
\item Section \ref{sec:notations}: contains the notations used for both the Matlab code and the paper
\end{itemize}

The matlab code is accessible on \href{https://zenodo.org/record/3894343}{Zonodo} and \href{https://github.com/tdehaeze/dehaeze20\_contr\_stewa\_platf}{Github} \cite{dehaeze20_activ_dampin_rotat_posit_platf}. It can also be download as a \texttt{.zip} file \href{matlab.zip}{here}.

To run the Matlab code, go in the \texttt{matlab} directory and run the following Matlab files corresponding to each section.

\begin{table}[htbp]
\caption{Paper's sections and corresponding Matlab files}
\centering
\begin{tabular}{ll}
Sections & Matlab File\\
\hline
Section \ref{sec:system_description} & \texttt{s1\_system\_description.m}\\
Section \ref{sec:iff_pure_int} & \texttt{s2\_iff\_pure\_int.m}\\
Section \ref{sec:iff_pseudo_int} & \texttt{s3\_iff\_hpf.m}\\
Section \ref{sec:iff_parallel_stiffness} & \texttt{s4\_iff\_kp.m}\\
Section \ref{sec:comparison} & \texttt{s5\_act\_damp\_comparison.m}\\
\end{tabular}
\end{table}

\chapter{System Description and Analysis}
\label{sec:org866deeb}
\label{sec:system_description}

\section{System description}
\label{sec:org597d9d5}
The system consists of one 2 degree of freedom translation stage on top of a spindle (figure \ref{fig:system}).

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs-paper/system.png}
\caption{\label{fig:system}Schematic of the studied system}
\end{figure}

The control inputs are the forces applied by the actuators of the translation stage (\(F_u\) and \(F_v\)).
As the translation stage is rotating around the Z axis due to the spindle, the forces are applied along \(\vec{i}_u\) and \(\vec{i}_v\).

\section{Equations}
\label{sec:orge2ee0c6}
Based on the Figure \ref{fig:system}, the equations of motions are:
\begin{important}
\begin{equation}
\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
\bm{G}_d
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
Where \(\bm{G}_d\) is a \(2 \times 2\) transfer function matrix.

\begin{equation}
\bm{G}_d = \frac{1}{k} \frac{1}{G_{dp}}
\begin{bmatrix}
   G_{dz} & G_{dc} \\
  -G_{dc} & G_{dz}
\end{bmatrix}
\end{equation}
With:
\begin{align}
  G_{dp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{dz} &= \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
  G_{dc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
\end{align}
\end{important}

\section{Numerical Values}
\label{sec:orgafc7947}
Let's define initial values for the model.
\begin{minted}[]{matlab}
  k = 1;    % Actuator Stiffness [N/m]
  c = 0.05; % Actuator Damping [N/(m/s)]
  m = 1;    % Payload mass [kg]
\end{minted}

\begin{minted}[]{matlab}
  xi = c/(2*sqrt(k*m));
  w0 = sqrt(k/m); % [rad/s]
\end{minted}

\section{Campbell Diagram}
\label{sec:org008e1a4}
The Campbell Diagram displays the evolution of the real and imaginary parts of the system as a function of the rotating speed.

It is shown in Figures \ref{fig:campbell_diagram_real} and \ref{fig:campbell_diagram_imag}, and one can see that the system becomes unstable for \(\Omega > \omega_0\) (the real part of one of the poles becomes positive).

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/campbell_diagram_real.png}
\caption{\label{fig:campbell_diagram_real}Campbell Diagram - Real Part}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/campbell_diagram_imag.png}
\caption{\label{fig:campbell_diagram_imag}Campbell Diagram - Imaginary Part}
\end{figure}

\section{Simscape Model}
\label{sec:org50f1e50}
In order to validate all the equations of motion, a Simscape model of the same system has been developed.
The dynamics of the system can be identified from the Simscape model and compare with the analytical model.

The rotating speed for the Simscape Model is defined.
\begin{minted}[]{matlab}
  W = 0.1; % Rotation Speed [rad/s]
\end{minted}

\begin{minted}[]{matlab}
  open('rotating_frame.slx');
\end{minted}

The transfer function from \([F_u, F_v]\) to \([d_u, d_v]\) is identified from the Simscape model.

\begin{minted}[]{matlab}
  %% Name of the Simulink File
  mdl = 'rotating_frame';

  %% Input/Output definition
  clear io; io_i = 1;
  io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
  io(io_i) = linio([mdl, '/G'], 2, 'openoutput'); io_i = io_i + 1;
\end{minted}

\begin{minted}[]{matlab}
  G = linearize(mdl, io, 0);

  %% Input/Output definition
  G.InputName  = {'Fu', 'Fv'};
  G.OutputName = {'du', 'dv'};
\end{minted}

The same transfer function from \([F_u, F_v]\) to \([d_u, d_v]\) is written down from the analytical model.
\begin{minted}[]{matlab}
  Gth = (1/k)/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
        [(s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2), 2*W*s/(w0^2) ; ...
         -2*W*s/(w0^2), (s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)];
\end{minted}

Both transfer functions are compared in Figure \ref{fig:plant_simscape_analytical} and are found to perfectly match.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_simscape_analytical.png}
\caption{\label{fig:plant_simscape_analytical}Bode plot of the transfer function from \([F_u, F_v]\) to \([d_u, d_v]\) as identified from the Simscape model and from an analytical model}
\end{figure}

\section{Effect of the rotation speed}
\label{sec:org6d643e3}
The transfer functions from \([F_u, F_v]\) to \([d_u, d_v]\) are identified for the following rotating speeds.
\begin{minted}[]{matlab}
  Ws = [0, 0.2, 0.7, 1.1]*w0; % Rotating Speeds [rad/s]
\end{minted}

\begin{minted}[]{matlab}
  Gs = {zeros(2, 2, length(Ws))};

  for W_i = 1:length(Ws)
      W = Ws(W_i);

      Gs(:, :, W_i) = {(1/k)/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
                       [(s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2), 2*W*s/(w0^2) ; ...
                        -2*W*s/(w0^2), (s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)]};
  end
\end{minted}

They are compared in Figures \ref{fig:plant_compare_rotating_speed_direct} and \ref{fig:plant_compare_rotating_speed_coupling}.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_compare_rotating_speed_direct.png}
\caption{\label{fig:plant_compare_rotating_speed_direct}Comparison of the transfer functions from \([F_u, F_v]\) to \([d_u, d_v]\) for several rotating speed - Direct Terms}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_compare_rotating_speed_coupling.png}
\caption{\label{fig:plant_compare_rotating_speed_coupling}Comparison of the transfer functions from \([F_u, F_v]\) to \([d_u, d_v]\) for several rotating speed - Coupling Terms}
\end{figure}

\chapter{Problem with pure Integral Force Feedback}
\label{sec:org02f3cde}
\label{sec:iff_pure_int}
Force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).

Two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs-paper/system_iff.png}
\caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
\end{figure}

\section{Plant Parameters}
\label{sec:orgd2d5c32}
Let's define initial values for the model.
\begin{minted}[]{matlab}
  k = 1;    % Actuator Stiffness [N/m]
  c = 0.05; % Actuator Damping [N/(m/s)]
  m = 1;    % Payload mass [kg]
\end{minted}

\begin{minted}[]{matlab}
  xi = c/(2*sqrt(k*m));
  w0 = sqrt(k/m); % [rad/s]
\end{minted}

\section{Equations}
\label{sec:orgad8546b}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix}
  1 & 0 \\
  0 & 1
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

Which then gives:
\begin{important}
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\bm{G}_{f}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\frac{1}{G_{fp}}
\begin{bmatrix}
  G_{fz} & -G_{fc} \\
  G_{fc} &  G_{fz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{align}
  G_{fp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)
\end{align}
\end{important}

\section{Comparison of the Analytical Model and the Simscape Model}
\label{sec:org5d37f2f}
The rotation speed is set to \(\Omega = 0.1 \omega_0\).
\begin{minted}[]{matlab}
  W = 0.1*w0; % [rad/s]
\end{minted}

\begin{minted}[]{matlab}
  open('rotating_frame.slx');
\end{minted}

And the transfer function from \([F_u, F_v]\) to \([f_u, f_v]\) is identified using the Simscape model.
\begin{minted}[]{matlab}
  %% Name of the Simulink File
  mdl = 'rotating_frame';

  %% Input/Output definition
  clear io; io_i = 1;
  io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
  io(io_i) = linio([mdl, '/G'], 1, 'openoutput'); io_i = io_i + 1;
\end{minted}

\begin{minted}[]{matlab}
  Giff = linearize(mdl, io, 0);

  %% Input/Output definition
  Giff.InputName  = {'Fu', 'Fv'};
  Giff.OutputName = {'fu', 'fv'};
\end{minted}

The same transfer function from \([F_u, F_v]\) to \([f_u, f_v]\) is written down from the analytical model.
\begin{minted}[]{matlab}
  Giff_th = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
            [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
             (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2];
\end{minted}

The two are compared in Figure \ref{fig:plant_iff_comp_simscape_analytical} and found to perfectly match.
\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_comp_simscape_analytical.png}
\caption{\label{fig:plant_iff_comp_simscape_analytical}Comparison of the transfer functions from \([F_u, F_v]\) to \([f_u, f_v]\) between the Simscape model and the analytical one}
\end{figure}

\section{Effect of the rotation speed}
\label{sec:org17fee48}
The transfer functions from \([F_u, F_v]\) to \([f_u, f_v]\) are identified for the following rotating speeds.
\begin{minted}[]{matlab}
  Ws = [0, 0.2, 0.7]*w0; % Rotating Speeds [rad/s]
\end{minted}

\begin{minted}[]{matlab}
  Gsiff = {zeros(2, 2, length(Ws))};

  for W_i = 1:length(Ws)
      W = Ws(W_i);

      Gsiff(:, :, W_i) = {1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
                        [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
                         (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2]};
  end
\end{minted}

The obtained transfer functions are shown in Figure \ref{fig:plant_iff_compare_rotating_speed}.
\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.png}
\caption{\label{fig:plant_iff_compare_rotating_speed}Comparison of the transfer functions from \([F_u, F_v]\) to \([f_u, f_v]\) for several rotating speed}
\end{figure}

\section{Decentralized Integral Force Feedback}
\label{sec:org2d5427a}
The decentralized IFF controller consists of pure integrators:
\begin{equation}
  \bm{K}_{\text{IFF}}(s) = \frac{g}{s} \begin{bmatrix}
    1 & 0 \\
    0 & 1
  \end{bmatrix}
\end{equation}

The Root Locus (evolution of the poles of the closed loop system in the complex plane as a function of \(g\)) is shown in Figure \ref{fig:root_locus_pure_iff}.
It is shown that for non-null rotating speed, one pole is bound to the right-half plane, and thus the closed loop system is unstable.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_pure_iff.png}
\caption{\label{fig:root_locus_pure_iff}Root Locus for the Decentralized Integral Force Feedback controller. Several rotating speed are shown.}
\end{figure}

\chapter{Integral Force Feedback with an High Pass Filter}
\label{sec:orgf9854e9}
\label{sec:iff_pseudo_int}

\section{Plant Parameters}
\label{sec:org11b9a15}
Let's define initial values for the model.
\begin{minted}[]{matlab}
  k = 1;    % Actuator Stiffness [N/m]
  c = 0.05; % Actuator Damping [N/(m/s)]
  m = 1;    % Payload mass [kg]
\end{minted}

\begin{minted}[]{matlab}
  xi = c/(2*sqrt(k*m));
  w0 = sqrt(k/m); % [rad/s]
\end{minted}

\section{Modified Integral Force Feedback Controller}
\label{sec:orgf920a8a}
Let's modify the initial Integral Force Feedback Controller ; instead of using pure integrators, pseudo integrators (i.e. low pass filters) are used:
\begin{equation}
  K_{\text{IFF}}(s) = g\frac{1}{\omega_i + s} \begin{bmatrix}
  1 & 0 \\
  0 & 1
\end{bmatrix}
\end{equation}
where \(\omega_i\) characterize down to which frequency the signal is integrated.

Let's arbitrary choose the following control parameters:
\begin{minted}[]{matlab}
  g = 2;
  wi = 0.1*w0;
\end{minted}

And the following rotating speed.
\begin{minted}[]{matlab}
  Giff = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
          [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
           (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2];
\end{minted}

The obtained Loop Gain is shown in Figure \ref{fig:loop_gain_modified_iff}.
\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/loop_gain_modified_iff.png}
\caption{\label{fig:loop_gain_modified_iff}Loop Gain for the modified IFF controller}
\end{figure}

\section{Root Locus}
\label{sec:org911f45b}
As shown in the Root Locus plot (Figure \ref{fig:root_locus_modified_iff}), for some value of the gain, the system remains stable.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff.png}
\caption{\label{fig:root_locus_modified_iff}Root Locus for the modified IFF controller}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff_zoom.png}
\caption{\label{fig:root_locus_modified_iff_zoom}Root Locus for the modified IFF controller - Zoom}
\end{figure}

\section{What is the optimal \(\omega_i\) and \(g\)?}
\label{sec:org028e747}
In order to visualize the effect of \(\omega_i\) on the attainable damping, the Root Locus is displayed in Figure \ref{fig:root_locus_wi_modified_iff} for the following \(\omega_i\):
\begin{minted}[]{matlab}
  wis = [0.01, 0.1, 0.5, 1]*w0; % [rad/s]
\end{minted}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.png}
\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for the modified IFF controller (zoomed plot on the left)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff_zoom.png}
\caption{\label{fig:root_locus_wi_modified_iff_zoom}Root Locus for the modified IFF controller (zoomed plot on the left)}
\end{figure}

For the controller
\begin{equation}
  K_{\text{IFF}}(s) = g\frac{1}{\omega_i + s} \begin{bmatrix}
  1 & 0 \\
  0 & 1
\end{bmatrix}
\end{equation}
The gain at which the system becomes unstable is
\begin{equation}
  g_\text{max} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right) \label{eq:iff_gmax}
\end{equation}

While it seems that small \(\omega_i\) do allow more damping to be added to the system (Figure \ref{fig:root_locus_wi_modified_iff}), the control gains may be limited to small values due to \eqref{eq:iff_gmax} thus reducing the attainable damping.

There must be an optimum for \(\omega_i\).
To find the optimum, the gain that maximize the simultaneous damping of the mode is identified for a wide range of \(\omega_i\) (Figure \ref{fig:mod_iff_damping_wi}).

\begin{minted}[]{matlab}
  wis = logspace(-2, 1, 100)*w0; % [rad/s]

  opt_xi = zeros(1, length(wis)); % Optimal simultaneous damping
  opt_gain = zeros(1, length(wis)); % Corresponding optimal gain

  for wi_i = 1:length(wis)
      wi = wis(wi_i);
      Kiff = 1/(s + wi)*eye(2);

      fun = @(g)computeSimultaneousDamping(g, Giff, Kiff);

      [g_opt, xi_opt] = fminsearch(fun, 0.5*wi*((w0/W)^2 - 1));
      opt_xi(wi_i) = 1/xi_opt;
      opt_gain(wi_i) = g_opt;
  end
\end{minted}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/mod_iff_damping_wi.png}
\caption{\label{fig:mod_iff_damping_wi}Simultaneous attainable damping of the closed loop poles as a function of \(\omega_i\)}
\end{figure}

\chapter{IFF with a stiffness in parallel with the force sensor}
\label{sec:orgc5ba04a}
\label{sec:iff_parallel_stiffness}

\section{Schematic}
\label{sec:orgc647af5}
In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs-paper/system_parallel_springs.png}
\caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
\end{figure}

In order to keep the overall stiffness \(k = k_a + k_p\) constant, a scalar parameter \(\alpha\) (\(0 \le \alpha < 1\)) is defined to describe the fraction of the total stiffness in parallel with the actuator and force sensor
\begin{equation}
  k_p = \alpha k, \quad k_a = (1 - \alpha) k
\end{equation}

\section{Equations}
\label{sec:org0de17db}
\begin{important}
\begin{equation}
\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
\bm{G}_k
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
\frac{1}{G_{kp}}
\begin{bmatrix}
   G_{kz} & -G_{kc} \\
   G_{kc} &  G_{kz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
With:
\begin{align}
  G_{kp} &= \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{{\omega_0}^2} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
  G_{kz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{{\omega_0}^2} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
  G_{kc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)
\end{align}
\end{important}

If we compare \(G_{kz}\) and \(G_{fz}\), we see that the spring in parallel adds a term \(\alpha\).
In order to have two complex conjugate zeros (instead of real zeros):
\begin{equation}
  \alpha > \frac{\Omega^2}{{\omega_0}^2} \quad \Leftrightarrow \quad k_p > m \Omega^2
\end{equation}

\section{Plant Parameters}
\label{sec:orga1e1958}
Let's define initial values for the model.
\begin{minted}[]{matlab}
  k = 1;    % Actuator Stiffness [N/m]
  c = 0.05; % Actuator Damping [N/(m/s)]
  m = 1;    % Payload mass [kg]
\end{minted}

\begin{minted}[]{matlab}
  xi = c/(2*sqrt(k*m));
  w0 = sqrt(k/m); % [rad/s]
\end{minted}

\section{Comparison of the Analytical Model and the Simscape Model}
\label{sec:orgbea84d1}
The same transfer function from \([F_u, F_v]\) to \([f_u, f_v]\) is written down from the analytical model.
\begin{minted}[]{matlab}
  W = 0.1*w0; % [rad/s]

  kp = 1.5*m*W^2;
  cp = 0;
\end{minted}

\begin{minted}[]{matlab}
  open('rotating_frame.slx');
\end{minted}

\begin{minted}[]{matlab}
  %% Name of the Simulink File
  mdl = 'rotating_frame';

  %% Input/Output definition
  clear io; io_i = 1;
  io(io_i) = linio([mdl, '/K'], 1, 'openinput');  io_i = io_i + 1;
  io(io_i) = linio([mdl, '/G'], 1, 'openoutput'); io_i = io_i + 1;

  Giff = linearize(mdl, io, 0);

  %% Input/Output definition
  Giff.InputName  = {'Fu', 'Fv'};
  Giff.OutputName = {'fu', 'fv'};
\end{minted}

\begin{minted}[]{matlab}
  w0p = sqrt((k + kp)/m);
  xip = c/(2*sqrt((k+kp)*m));

  Giff_th = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
                     (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
                     (2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p)), (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2 ];
  Giff_th.InputName  = {'Fu', 'Fv'};
  Giff_th.OutputName = {'fu', 'fv'};
\end{minted}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_kp_comp_simscape_analytical.png}
\caption{\label{fig:plant_iff_kp_comp_simscape_analytical}Comparison of the transfer functions from \([F_u, F_v]\) to \([f_u, f_v]\) between the Simscape model and the analytical one}
\end{figure}

\section{Effect of the parallel stiffness on the IFF plant}
\label{sec:orge9068cb}
The rotation speed is set to \(\Omega = 0.1 \omega_0\).
\begin{minted}[]{matlab}
  W = 0.1*w0; % [rad/s]
\end{minted}

And the IFF plant (transfer function from \([F_u, F_v]\) to \([f_u, f_v]\)) is identified in three different cases:
\begin{itemize}
\item without parallel stiffness
\item with a small parallel stiffness \(k_p < m \Omega^2\)
\item with a large parallel stiffness \(k_p > m \Omega^2\)
\end{itemize}

The results are shown in Figure \ref{fig:plant_iff_kp}.

One can see that for \(k_p > m \Omega^2\), the systems shows alternating complex conjugate poles and zeros.

\begin{minted}[]{matlab}
  kp = 0;

  w0p = sqrt((k + kp)/m);
  xip = c/(2*sqrt((k+kp)*m));

  Giff = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
      (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
      (2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p)), (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2];
\end{minted}

\begin{minted}[]{matlab}
  kp = 0.5*m*W^2;
  k = 1 - kp;

  w0p = sqrt((k + kp)/m);
  xip = c/(2*sqrt((k+kp)*m));

  Giff_s = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
      (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
      (2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p)), (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2];
\end{minted}

\begin{minted}[]{matlab}
  kp = 1.5*m*W^2;
  k = 1 - kp;

  w0p = sqrt((k + kp)/m);
  xip = c/(2*sqrt((k+kp)*m));

  Giff_l = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
      (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
      (2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p)), (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2];
\end{minted}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_kp.png}
\caption{\label{fig:plant_iff_kp}Transfer function from \([F_u, F_v]\) to \([f_u, f_v]\) for \(k_p = 0\), \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\)}
\end{figure}

\section{IFF when adding a spring in parallel}
\label{sec:org9f1e3df}
In Figure \ref{fig:root_locus_iff_kp} is displayed the Root Locus in the three considered cases with
\begin{equation}
  K_{\text{IFF}} = \frac{g}{s} \begin{bmatrix}
  1 & 0 \\
  0 & 1
\end{bmatrix}
\end{equation}

One can see that for \(k_p > m \Omega^2\), the root locus stays in the left half of the complex plane and thus the control system is unconditionally stable.

Thus, decentralized IFF controller with pure integrators can be used if:
\begin{equation}
  k_{p} > m \Omega^2
\end{equation}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp.png}
\caption{\label{fig:root_locus_iff_kp}Root Locus}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp_zoom.png}
\caption{\label{fig:root_locus_iff_kp_zoom}Root Locus}
\end{figure}

\section{Effect of \(k_p\) on the attainable damping}
\label{sec:orgcb7905c}
However, having large values of \(k_p\) may decrease the attainable damping.

To study the second point, Root Locus plots for the following values of \(k_p\) are shown in Figure \ref{fig:root_locus_iff_kps}.
\begin{minted}[]{matlab}
  kps = [2, 20, 40]*m*W^2;
\end{minted}

It is shown that large values of \(k_p\) decreases the attainable damping.
\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kps.png}
\caption{\label{fig:root_locus_iff_kps}Root Locus plot}
\end{figure}

\begin{minted}[]{matlab}
  alphas = logspace(-2, 0, 100);

  opt_xi = zeros(1, length(alphas)); % Optimal simultaneous damping
  opt_gain = zeros(1, length(alphas)); % Corresponding optimal gain

  Kiff = 1/s*eye(2);

  for alpha_i = 1:length(alphas)
      kp = alphas(alpha_i);
      k = 1 - alphas(alpha_i);

      w0p = sqrt((k + kp)/m);
      xip = c/(2*sqrt((k+kp)*m));

      Giff = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
          (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
          (2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p)), (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2];

      fun = @(g)computeSimultaneousDamping(g, Giff, Kiff);

      [g_opt, xi_opt] = fminsearch(fun, 2);
      opt_xi(alpha_i) = 1/xi_opt;
      opt_gain(alpha_i) = g_opt;
  end
\end{minted}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/opt_damp_alpha.png}
\caption{\label{fig:opt_damp_alpha}Attainable damping ratio and corresponding controller gain for different parameter \(\alpha\)}
\end{figure}

\chapter{Comparison}
\label{sec:org4714bd6}
\label{sec:comparison}
Two modifications to adapt the IFF control strategy to rotating platforms have been proposed.
These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.

\section{Plant Parameters}
\label{sec:org90a54af}
Let's define initial values for the model.
\begin{minted}[]{matlab}
  k = 1;    % Actuator Stiffness [N/m]
  c = 0.05; % Actuator Damping [N/(m/s)]
  m = 1;    % Payload mass [kg]
\end{minted}

\begin{minted}[]{matlab}
  xi = c/(2*sqrt(k*m));
  w0 = sqrt(k/m); % [rad/s]
\end{minted}

The rotating speed is set to \(\Omega = 0.1 \omega_0\).
\begin{minted}[]{matlab}
  W = 0.1*w0;
\end{minted}

\section{Root Locus}
\label{sec:orgf922463}
IFF with High Pass Filter
\begin{minted}[]{matlab}
  wi = 0.1*w0; % [rad/s]

  Giff = 1/(((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))^2 + (2*W*s/(w0^2))^2) * ...
          [(s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2)) + (2*W*s/(w0^2))^2, - (2*xi*s/w0 + 1)*2*W*s/(w0^2) ; ...
           (2*xi*s/w0 + 1)*2*W*s/(w0^2), (s^2/w0^2 - W^2/w0^2)*((s^2)/(w0^2) + 2*xi*s/w0 + 1 - (W^2)/(w0^2))+ (2*W*s/(w0^2))^2];
\end{minted}

IFF With parallel Stiffness
\begin{minted}[]{matlab}
  kp = 5*m*W^2;
  k = k - kp;

  w0p = sqrt((k + kp)/m);
  xip = c/(2*sqrt((k+kp)*m));

  Giff_kp = 1/( (s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2)^2 + (2*(s/w0p)*(W/w0p))^2 ) * [ ...
                     (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2, -(2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p));
                     (2*xip*s/w0p + k/(k + kp))*(2*(s/w0p)*(W/w0p)), (s^2/w0p^2 + kp/(k + kp) - W^2/w0p^2)*(s^2/w0p^2 + 2*xip*s/w0p + 1 - W^2/w0p^2) + (2*(s/w0p)*(W/w0p))^2 ];

  k = k + kp;
\end{minted}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_root_locus.png}
\caption{\label{fig:comp_root_locus}Root Locus plot - Comparison of IFF with additional high pass filter, IFF with additional parallel stiffness}
\end{figure}

\section{Controllers - Optimal Gains}
\label{sec:org1889cfc}
In order to compare to three considered Active Damping techniques, gains that yield maximum damping of all the modes are computed for each case.

The obtained damping ratio and control are shown below.

\begin{center}
\begin{tabular}{lrr}
 & Obtained \(\xi\) & Control Gain\\
\hline
Modified IFF & 0.83 & 1.99\\
IFF with \(k_p\) & 0.83 & 2.02\\
\end{tabular}
\end{center}

\section{Passive Damping - Critical Damping}
\label{sec:org81b0306}
\begin{equation}
  \xi = \frac{c}{2 \sqrt{km}}
\end{equation}

Critical Damping corresponds to to \(\xi = 1\), and thus:
\begin{equation}
  c_{\text{crit}} = 2 \sqrt{km}
\end{equation}

\begin{minted}[]{matlab}
  c_opt = 2*sqrt(k*m);
\end{minted}

\section{Transmissibility And Compliance}
\label{sec:orge56633c}
\label{sec:comp_transmissibilty}

\begin{minted}[]{matlab}
  open('rotating_frame.slx');
\end{minted}

\begin{minted}[]{matlab}
  %% Name of the Simulink File
  mdl = 'rotating_frame';

  %% Input/Output definition
  clear io; io_i = 1;
  io(io_i) = linio([mdl, '/dw'], 1, 'input');  io_i = io_i + 1;
  io(io_i) = linio([mdl, '/fd'], 1, 'input');  io_i = io_i + 1;
  io(io_i) = linio([mdl, '/Meas'], 1, 'output');  io_i = io_i + 1;
\end{minted}
\begin{minted}[]{matlab}
  G_ol = linearize(mdl, io, 0);

  %% Input/Output definition
  G_ol.InputName  = {'Dwx', 'Dwy', 'Fdx', 'Fdy'};
  G_ol.OutputName = {'Dx', 'Dy'};
\end{minted}

\subsection{Passive Damping}
\label{sec:orgc0de759}
\begin{minted}[]{matlab}
  kp = 0;
  cp = 0;
\end{minted}

\begin{minted}[]{matlab}
  c_old = c;
  c = c_opt;
\end{minted}

\begin{minted}[]{matlab}
  G_pas = linearize(mdl, io, 0);

  %% Input/Output definition
  G_pas.InputName  = {'Dwx', 'Dwy', 'Fdx', 'Fdy'};
  G_pas.OutputName = {'Dx', 'Dy'};
\end{minted}

\begin{minted}[]{matlab}
  c = c_old;
\end{minted}

\begin{minted}[]{matlab}
  Kiff = opt_gain_iff/(wi + s)*tf(eye(2));
\end{minted}

\begin{minted}[]{matlab}
  G_iff = linearize(mdl, io, 0);

  %% Input/Output definition
  G_iff.InputName  = {'Dwx', 'Dwy', 'Fdx', 'Fdy'};
  G_iff.OutputName = {'Dx', 'Dy'};
\end{minted}

\begin{minted}[]{matlab}
  kp = 5*m*W^2;
  cp = 0.01;
\end{minted}

\begin{minted}[]{matlab}
  Kiff = opt_gain_kp/s*tf(eye(2));
\end{minted}

\begin{minted}[]{matlab}
  G_kp = linearize(mdl, io, 0);

  %% Input/Output definition
  G_kp.InputName  = {'Dwx', 'Dwy', 'Fdx', 'Fdy'};
  G_kp.OutputName = {'Dx', 'Dy'};
\end{minted}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_transmissibility.png}
\caption{\label{fig:comp_transmissibility}Comparison of the transmissibility}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_compliance.png}
\caption{\label{fig:comp_compliance}Comparison of the obtained Compliance}
\end{figure}

\chapter{Notations}
\label{sec:org61801fb}
\label{sec:notations}

\begin{center}
\begin{tabular}{llll}
 & Mathematical Notation & Matlab & Unit\\
\hline
Actuator Stiffness & \(k\) & \texttt{k} & N/m\\
Actuator Damping & \(c\) & \texttt{c} & N/(m/s)\\
Payload Mass & \(m\) & \texttt{m} & kg\\
Damping Ratio & \(\xi = \frac{c}{2\sqrt{km}}\) & \texttt{xi} & \\
Actuator Force & \(\bm{F}, F_u, F_v\) & \texttt{F} \texttt{Fu} \texttt{Fv} & N\\
Force Sensor signal & \(\bm{f}, f_u, f_v\) & \texttt{f} \texttt{fu} \texttt{fv} & N\\
Relative Displacement & \(\bm{d}, d_u, d_v\) & \texttt{d} \texttt{du} \texttt{dv} & m\\
Resonance freq. when \(\Omega = 0\) & \(\omega_0\) & \texttt{w0} & rad/s\\
Rotation Speed & \(\Omega = \dot{\theta}\) & \texttt{W} & rad/s\\
Low Pass Filter corner frequency & \(\omega_i\) & \texttt{wi} & rad/s\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{llll}
 & Mathematical Notation & Matlab & Unit\\
\hline
Laplace variable & \(s\) & \texttt{s} & \\
Complex number & \(j\) & \texttt{j} & \\
Frequency & \(\omega\) & \texttt{w} & [rad/s]\\
\end{tabular}
\end{center}

\printbibliography

\bibliography{ref}
\end{document}

### 2021-02-20 matlab/preamble.tex
Add link to matlab pdf and matlab zip

\usepackage{float}

\usepackage{caption,tabularx,booktabs}

\usepackage{biblatex}

\usepackage{fontawesome}

\usepackage{caption}
\usepackage{subcaption}

\captionsetup[figure]{labelfont=bf}
\captionsetup[subfigure]{labelfont=bf}
\captionsetup[listing]{labelfont=bf}
\captionsetup[table]{labelfont=bf}

\usepackage{xcolor}

\definecolor{my-blue}{HTML}{6b7adb}
\definecolor{my-pale-blue}{HTML}{e6e9f9}
\definecolor{my-red}{HTML}{db6b6b}
\definecolor{my-pale-red}{HTML}{f9e6e6}
\definecolor{my-green}{HTML}{6bdbb6}
\definecolor{my-pale-green}{HTML}{e6f9f3}
\definecolor{my-yellow}{HTML}{dbd26b}
\definecolor{my-pale-yellow}{HTML}{f9f7e6}
\definecolor{my-orange}{HTML}{dba76b}
\definecolor{my-pale-orange}{HTML}{f9f0e6}
\definecolor{my-grey}{HTML}{a3a3a3}
\definecolor{my-pale-grey}{HTML}{f0f0f0}
\definecolor{my-turq}{HTML}{6bc7db}
\definecolor{my-pale-turq}{HTML}{e6f6f9}

\usepackage{inconsolata}

\usepackage[newfloat=true, chapter]{minted}
\usemintedstyle{autumn}

\setminted{frame=lines,breaklines=true,tabsize=4,fontsize=\scriptsize,autogobble=true,labelposition=topline,bgcolor=my-pale-grey}
\setminted[matlab]{label=Matlab}
\setminted[latex]{label=LaTeX}
\setminted[bash]{label=Bash}
\setminted[python]{label=Python}
\setminted[text]{label=Results}
\setminted[md]{label=Org Mode}

\setmintedinline{fontsize=\normalsize,bgcolor=my-pale-grey}

\usepackage[most]{tcolorbox}

\tcbuselibrary{minted}

\newtcolorbox{seealso}{   enhanced,breakable,colback=my-pale-grey,colframe=my-grey,fonttitle=\bfseries,title=See Also}
\newtcolorbox{hint}{      enhanced,breakable,colback=my-pale-grey,colframe=my-grey,fonttitle=\bfseries,title=Hint}
\newtcolorbox{definition}{enhanced,breakable,colback=my-pale-red, colframe=my-red, fonttitle=\bfseries,title=Definition}
\newtcolorbox{important}{ enhanced,breakable,colback=my-pale-red, colframe=my-red, fonttitle=\bfseries,title=Important}
\newtcolorbox{exampl}[1][]{    enhanced,breakable,colback=my-pale-green,colframe=my-green,fonttitle=\bfseries,title=Example,#1}
\newtcolorbox{exercice}{  enhanced,breakable,colback=my-pale-yellow,colframe=my-yellow,fonttitle=\bfseries,title=Exercice}
\newtcolorbox{question}{  enhanced,breakable,colback=my-pale-yellow,colframe=my-yellow,fonttitle=\bfseries,title=Question}
\newtcolorbox{answer}{    enhanced,breakable,colback=my-pale-turq,colframe=my-turq,fonttitle=\bfseries,title=Answer}
\newtcolorbox{summary}{   enhanced,breakable,colback=my-pale-blue,colframe=my-blue,fonttitle=\bfseries,title=Summary}
\newtcolorbox{note}{      enhanced,breakable,colback=my-pale-blue,colframe=my-blue,fonttitle=\bfseries,title=Note}
\newtcolorbox{caution}{   enhanced,breakable,colback=my-pale-orange,colframe=my-orange,fonttitle=\bfseries,title=Caution}
\newtcolorbox{warning}{   enhanced,breakable,colback=my-pale-orange,colframe=my-orange,fonttitle=\bfseries,title=Warning}

\newtcolorbox{my-quote}[1]{%
  colback=my-pale-grey,
  grow to right by=-10mm,
  grow to left by=-10mm,
  boxrule=0pt,
  boxsep=0pt,
  breakable,
  enhanced jigsaw,
  borderline west={4pt}{0pt}{my-grey}}

\renewenvironment{quote}{\begin{my-quote}}{\end{my-quote}}

\newtcolorbox{my-verse}[1]{%
  colback=my-pale-grey,
  grow to right by=-10mm,
  grow to left by=-10mm,
  boxrule=0pt,
  boxsep=0pt,
  breakable,
  enhanced jigsaw,
  borderline west={4pt}{0pt}{my-grey}}

\renewenvironment{verse}{\begin{my-verse}}{\end{my-verse}}

\usepackage{environ}% http://ctan.org/pkg/environ
\NewEnviron{aside}{%
  \marginpar{\BODY}
}

\renewenvironment{verbatim}{\VerbatimEnvironment\begin{minted}[]{text}}{\end{minted}}

\usepackage{soul}
\sethlcolor{my-pale-grey}

\let\OldTexttt\texttt
\renewcommand{\texttt}[1]{{\ttfamily\hl{\mbox{\,#1\,}}}}

\makeatletter
\preto\Gin@extensions{png,}
\DeclareGraphicsRule{.png}{pdf}{.pdf}{\noexpand\Gin@base.pdf}
\makeatother

\usepackage{hyperref}
\hypersetup{
  colorlinks = true,
  allcolors = my-blue
}

\usepackage{hypcap}
